% ---------------------------------------------------------------------
%  changelog.tex -- THE canonical TFPT changelog.
%  Dual-mode file:
%    * standalone:  pdflatex changelog.tex   (own preamble below)
%    * imported:    \def\ChangelogImported{1}\input{changelog}
%                   (at the END of introduction.tex)
%  Maintenance rule (.cursor/rules): every committed change to the
%  theory, the verification suite, the papers or the website adds a
%  dated entry here IN THE SAME CHANGE.  Newest first.
%  Content uses only plain LaTeX (no document-specific macros).
% ---------------------------------------------------------------------
\ifdefined\ChangelogImported\else
\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage[a4paper,margin=2.3cm]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\setlist{itemsep=1.5pt,topsep=2pt}
\emergencystretch=2.5em
% standalone fallbacks for the status markers (defined by tfpt_style when imported)
% 4-class display system: [E] exact/proven, [C] conditional, [O] open/axiom, [X] kill test.
\providecommand{\mE}{\textbf{[E]}}\providecommand{\mC}{\textbf{[C]}}
\providecommand{\mO}{\textbf{[O]}}\providecommand{\mX}{\textbf{[X]}}
% legacy fine-grained names kept as aliases so older entries still compile standalone
\providecommand{\tI}{\mE}\providecommand{\tL}{\mE}\providecommand{\tF}{\mE}\providecommand{\tN}{\mE}
\providecommand{\tIalg}{\mE}\providecommand{\tInum}{\mE}
\providecommand{\tP}{\mC}\providecommand{\tB}{\mC}\providecommand{\tR}{\mC}
\providecommand{\tA}{\mO}\providecommand{\tX}{\mX}
\providecommand{\vref}[1]{\texttt{#1}}
\providecommand{\TFPTversion}{5.2}\providecommand{\TFPTrev}{dev}
% standalone fallbacks for doc-specific math macros used in entries
\providecommand{\cthree}{c_3}\providecommand{\phiz}{\varphi_0^{\mathrm{ret}}}
\providecommand{\gcar}{g_{\mathrm{car}}}\providecommand{\Nfam}{N_{\mathrm{fam}}}
\providecommand{\Oadm}{\Omega_{\mathrm{adm}}}\providecommand{\ainv}{\alpha^{-1}}
\providecommand{\Mbar}{\bar M_{\mathrm{Pl}}}\providecommand{\Z}{\mathbb{Z}}\providecommand{\PP}{\mathbb{P}}
\providecommand{\Aut}{\operatorname{Aut}}
\title{\textbf{TFPT --- Changelog}\\[1mm]\large All changes and new results, by date}
\author{Stefan Hamann \and Alessandro Rizzo}
\date{\today}
\begin{document}
\maketitle
\noindent This file is the canonical, dated record of every change to the TFPT theory
development: new verification modules (\texttt{vN}), status changes, editorial passes and
infrastructure. It is maintained \emph{in the same change} as the work it records, and it is
also imported at the end of the \texttt{introduction} document. Module numbers \texttt{vN}
refer to \texttt{verification/vN\_*.py}; claim IDs refer to rows of
\texttt{verification/status\_ledger.csv}.
\fi

\ifdefined\ChangelogImported
\clearpage
\section*{Appendix: changelog}
\addcontentsline{toc}{section}{Appendix: changelog}
\noindent The dated record of every change (canonical source: \texttt{changelog.tex}, also
compiled standalone). Module numbers \texttt{vN} refer to \texttt{verification/vN\_*.py}.
\fi

\subsection*{2026-06-26 (\texttt{v429} --- the `unmapped' golden $E_8$ structure is the geometry of the one external input $\theta_i$)}
\begin{itemize}
\item \textbf{New module \texttt{v429} (\texttt{DM.AXION.PENTAGON.01}) --- a geometric re-reading answering
``why does so much idle $E_8$ structure exist?'' for the one case where the idle structure has a job.}
The reverse audit (\vref{v354}) had argued the golden ratio $\varphi$ is \emph{unmapped} (it appears only
internally --- the affine-$E_8$ attractor angle \vref{v312}, the icosian lattice \vref{v348} --- and in no
physical readout), and used exactly that to conclude $\varphi$ cannot be numerology. \mE\ this sharpens that
statement: because $\Nfam{=}\gcar{-}2$, the axion misalignment \emph{spine} angle (\vref{v211},
\texttt{DM.AXION.SPINE.01}) is $\theta_i{=}\pi\Nfam/\gcar{=}(\gcar{-}2)\pi/\gcar$, which is \emph{exactly}
the interior angle of the regular $\gcar$-gon --- for $\gcar{=}5$ the pentagon, $\theta_i{=}3\pi/5{=}108^\circ$.
\mE\ its cosine is golden, $\cos(3\pi/5){=}(1{-}\sqrt5)/4{=}{-}1/(2\varphi)$ (partner $2\cos(2\pi/5){=}1/\varphi
{=}\varphi{-}1$, $\varphi{=}2\cos(\pi/5)$). \mE\ the golden character is \emph{unique} to $\gcar{=}5$: among the
small regular $n$-gons only $n{=}5$ has an irrational interior-angle cosine ($n{=}3,4,6$ give $1/2,0,-1/2$), so
$\theta_i$ is golden \emph{because} the carrier is $5$ (P2).
\item \textbf{An honest \mC\ bridge, not a status change.} It connects two standing facts --- $\varphi$ is the
unmapped $\gcar{=}5$ signature (\vref{v354}/\vref{v313}) and $\theta_i{=}3\pi/5$ is the one external cosmological
input (\vref{v211}) --- and \emph{refines} \vref{v354} from ``$\varphi$ in no physical readout'' (it is the unmapped $\gcar{=}5$ signature, \vref{v313}) to ``$\varphi$
touches \emph{only} the \mC\ spine misalignment angle'' (conditional, branch-level, never a frozen prediction).
It is a geometric motive for the spine over the hilltop $\theta_i{\approx}170^\circ$ (whose cosine is not a clean
pentagon value), consistent with --- not replacing --- the finite-$T$ solver that decides the branch
(\vref{v185}/\vref{v211}). It does \emph{not} derive $\theta_i$, does \emph{not} upgrade
\texttt{DM.AXION.SPINE.01} (stays \mC) and closes no gate.
\item \textbf{Surfaces synced.} \texttt{run\_all.py}, \texttt{script\_registry.csv},
\texttt{status\_ledger.csv}, the dark-matter section of \texttt{tfpt\_4\_frontier}; the Wolfram
extension/README/ledger counts (\texttt{GATE.WOLFRAM.02}) and the website verification count; manifests refreshed.
\end{itemize}

\subsection*{2026-06-25 (External-works references appendix --- web-verified)}
\begin{itemize}
\item \textbf{New shared appendix \texttt{tex-artefacts/tfpt\_references.tex}} (``External works built
upon''), \texttt{\textbackslash input} into the six math-heavy documents (\texttt{tfpt\_1},
\texttt{tfpt\_2}, \texttt{tfpt\_4}, \texttt{tfpt\_horizon\_readouts}, \texttt{origin\_theory},
\texttt{tfpt\_research\_contracts}). The active papers named the foundational results they build on by
author only, with no reference list; the appendix supplies web-verified locators (journal, volume, year /
arXiv) grouped by topic: modular theory \& AQFT (Tomita--Takesaki LNM~128 1970; Bisognano--Wichmann
J.~Math.\ Phys.\ 16/17; Osterwalder--Schrader CMP~31/42; Doplicher--Haag--Roberts CMP~23/35;
Haag--Ruelle; Longo CMP~126/130; Kawahigashi--Longo--M\"uger CMP~219), conformal nets/VOAs/lattices
(Frenkel--Kac Invent.~Math.~62; Segal CMP~80; MMST; Adamo--Moriwaki--Tanimoto; Adamo--Giorgetti--Tanimoto
\texttt{2506.01008}/\texttt{2508.07109}; Naaijkens--Penneys--Wallick), lattices/quadratic forms
(Conway--Sloane; Siegel Ann.~Math.~36 1935), singularities (Brieskorn Invent.~Math.~2 1966; Milnor AMS~61
1968) and spectral geometry/gravity/thermal time (Chamseddine--Connes CMP~186; Connes--Rovelli CQG~11;
Wald PRD~48; Casini--Huerta--Myers JHEP~05 2011). Added to the \texttt{make\_manifest.py} TEX list. No
claim or status change --- a provenance/citation completeness pass.
\end{itemize}

\subsection*{2026-06-25 (External AQFT citations $+$ the four-fold $\mu_4$ identity sharpened)}
\begin{itemize}
\item \textbf{Two recent Adamo--Giorgetti--Tanimoto theorems cited where the keystone builds on them.}
The open \texttt{SEAM.EQUIV.01} continuum/realisation legs (\vref{v336}) now cite, alongside MMST and
Adamo--Moriwaki--Tanimoto (\texttt{arXiv:2407.18222}, already in use): \textbf{(a)} the construction and
classification of two-dimensional conformal nets from even lattices (\texttt{arXiv:2506.01008}, 2025) ---
``the lattice is a conformal net'' is a theorem of the same operator-algebraic lineage, strengthening the
lattice-realisation leg; and \textbf{(b)} automatic positive-energy/diffeomorphism covariance of conformal-net
representations (\texttt{arXiv:2508.07109}, 2025), which defuses the ``Bisognano--Wichmann presupposes the
covariance it should produce'' circularity (\vref{v215}) on the intrinsic-BW residual (\vref{v424}). Added to
\vref{v336} docstring/registry, the \texttt{SEAM.EQUIV.CONTINUUM.01} ledger \texttt{external\_data}, and
\texttt{tfpt\_research\_contracts}.
\item \textbf{The four-fold $\mu_4$ identity made explicit (\vref{v422}).} \vref{v422} already proved that the
seam deck/divisor $\mu_4$, the carrier Galois group $\operatorname{Gal}(\mathbb Q(\zeta_5))$, the discriminant
$\operatorname{disc}(D_5){=}\operatorname{disc}(A_3){=}\Z/4$ and the $(E_8)_1$ simple-current glue are ONE cyclic
$\Z/4$ (with the cyclic-vs-Klein negative control). It is now named the \emph{four-fold $\mu_4$ identity} and
typed, per \vref{v428}, as a \emph{compression} (one object read four ways), NOT four independent witnesses --
in \vref{v422}, the registry, the \texttt{SEAM.GALOIS.NET.01} ledger row and \texttt{origin\_theory}. (No new
module: a separate \texttt{v429} would have duplicated \vref{v422} and violated the very compression discipline.)
\end{itemize}

\subsection*{2026-06-25 (\texttt{v428} --- honest self-correction of the over-determination map)}
\begin{itemize}
\item \textbf{\texttt{v428} (\texttt{OVERDET.WITNESS.RECLASS.01}) --- applying \texttt{v427}'s own
multiply-vs-compress test to \texttt{v427} itself.} A pattern search and the right objection exposed that
calling the seven arithmetic witnesses ``disjoint grammars that \emph{multiply}'' overstates independence.
\mE\ by the Brieskorn classification (\vref{v236}) the $(2,3,5)$ singularity is the ONE generator behind the
order-$30$ clock (Milnor $\mu{=}(2{-}1)(3{-}1)(5{-}1){=}8{=}\operatorname{rank}E_8$, $30{=}2{\cdot}3{\cdot}5
{=}h(E_8)$, $\varphi(30){=}8$), so each witness is a facet of that same object (primes $2,3,5$ of $30$, the
clock $30$, or $E_8$): all seven collapse to one generator $\Rightarrow$ \emph{compression}, not seven
multiplications. \mE\ what genuinely multiplies is the input forced four independent ways --- the ``$8$'' in
$\cthree{=}1/(8\pi)$ from $\operatorname{rank}E_8$, $h(D_5){=}2(5{-}1)$, $\varphi(30)$ and the Milnor number
--- plus the foreign witness $\ainv{\approx}137$. \mC\ refines and partly walks back \texttt{v427},
consistent with \vref{v236}/\vref{v305}/\vref{v313}.
\item \textbf{Surfaces corrected (same change).} \texttt{v427}'s prose, the ledger row
(\texttt{OVERDET.WITNESS.MAP.01}, now noting the refinement), \texttt{tfpt\_safeguards} Layer~3 (the seven
compress one object; a second keybox states what multiplies), the witness-map figure (redrawn), the website
(\texttt{papers.ts}, \texttt{Safeguards.tsx}, \texttt{release.ts}, the intro-video description) and the
Zenodo description. The over-determination claim is now the narrower, harder-to-attack ``one richly
over-determined input $+$ a foreign readout''.
\end{itemize}

\subsection*{2026-06-25 (Safeguards visuals $+$ paper expansion $+$ the website safeguards band)}
\begin{itemize}
\item \textbf{Five safeguards figures} (\texttt{make\_figures.py}, in \texttt{manifest.sha256}): the
layered defense, the $\alpha^{-1}$ uniqueness scan (one $F_{U(1)}$ variant of $94{,}500$ in the CODATA
window), the reverse audit ($3/8$ vs $5/8$), the witness-independence map (seven disjoint grammars), and the
look-elsewhere null model ($13/13$ vs $\le5/13$).
\item \textbf{\texttt{tfpt\_safeguards} expanded.} Layer~5 now states the null model explicitly
($\prod p_i{=}10^{-25.8}$, $2{\times}200$k pseudo-theories $\le5/13$, $\phiz\pm10\%\!\to\!6/13$, shuffle
$1.2$) and the $\alpha$ uniqueness ($\le10^{-30.7}$, $\sim$102 bits, \vref{v100}), with the data watchdog
(\vref{v307}) and kill board (\vref{v321}); the five figures are embedded.
\item \textbf{Website: a prominent animated Safeguards band} (\texttt{components/Safeguards.tsx}) in the
home flow (after the trust beat) --- headline statistics, the seven layers, the figures, links to the paper
and the suite --- to address the coincidence/numerology suspicion proactively.
\item \textbf{Koide flow-time investigation (honest negative).} Post-\texttt{v425}: the flow-time is
\emph{not} native and does \emph{not} reduce to one scale --- \vref{v99} already rejects a scale reading as
look-elsewhere; the only theory-side content is the conditional integer reading $t{=}\Nfam{=}3\Rightarrow
m_\tau{=}1776.94$ MeV, a Belle~II kill test. No new module.
\end{itemize}

\subsection*{2026-06-25 (Three closure-strategy modules \texttt{v425}--\texttt{v427} $+$ the Safeguards paper)}
\begin{itemize}
\item \textbf{\texttt{v425} (\texttt{DYN.TRANSFER.UNIVERSAL.01}) --- the single-flow reduction of
$F_{\mathrm{transfer}}$.} The four frontier transfers do not each need a separate external solver: their
\emph{dynamics} is the ONE native flow (the seam modular/recovery semigroup, \texttt{v238}/\texttt{v240},
gap $6\ln(3/2)$) restricted to each sector. \mE\ the \texttt{v99} Koide generator linearised at $q{=}2$ has
rate $-\Delta$, time-$1$ contraction $(2/3)^6$; Boltzmann washout is that contraction (CP phase $4\pi/3$
native, \texttt{v320}); QCD rate $b_3{=}-7$. \mC\ only the anchors ($v_{\mathrm{geo}}$, $C_p$, $M_R$) stay
external; $F_{\mathrm{relic}}$'s cosmological IC $\theta_i$ is the one wall. A reduction (extends
\texttt{v383} static$\to$dynamic), not internalisation; the firewall holds.
\item \textbf{\texttt{v426} (\texttt{SEAM.EQUIV.LTORP.KMS.01}) --- the invertible $\beta{=}1$-KMS variant of
(LTO-RP).} The corner NPW26 leave open (they prove it for topologically-ordered models; the seam is
invertible $+$ KMS, not a trace). \mE\ a gapped reflection-symmetric $\mu_4$-even collar at $\beta{=}1$ KMS
satisfies $\Theta K\Theta^{-1}{=}{-}K$ ($u_\Theta{=}J$) and $[\rho,K]{=}0$, so (LTO-RP) holds by direct
Tomita--Takesaki; $|\!\det\mathrm{Cartan}(E_8)|{=}1$ (no anyons), state not a trace; neg controls have
teeth. Advances \texttt{v424} sub-step (ii); \texttt{SEAM.EQUIV.01} stays \mO\ (continuum sub-step (i)
remains).
\item \textbf{\texttt{v427} (\texttt{OVERDET.WITNESS.MAP.01}) --- the honest over-determination accounting.}
A reviewer correction made machine-explicit: witnesses from \emph{disjoint} grammars multiply, projections
of the \emph{same} generator compress. \mE\ seven disjoint-grammar witnesses each reproduce a
carrier-skeleton integer from their own structure --- Gauss $N(3{+}2i){=}13$, Eisenstein $N(3{+}2\omega){=}7$,
cyclotomy $N(3{+}2\zeta_5){=}55$, Galois $|(\Z/5)^\times|{=}4$, $|\!\det\mathrm{Cartan}(E_8)|{=}1$, Pascal
$\binom40{+}\binom41{+}\binom42{=}11$ ($2^4{=}16$), Coxeter $h(E_8){=}30{=}2{\cdot}3{\cdot}5$ with
$\varphi(30){=}8$ --- and the anchor $a{=}(1,1,2)$ is the compression generator. Extends \texttt{v305}.
\item \textbf{New paper \texttt{tfpt\_safeguards} (companion S).} A dedicated methodology paper collecting,
in one language, every mechanism by which TFPT defends a claim against coincidence and numerology: the
status calculus $+$ ledger $+$ audit, no-free-pattern $+$ reverse audit, the over-determination map
(\texttt{v427}), the firewall $+$ No-Unit theorem, frozen predictions $+$ null model, the independent
Wolfram and Lean paths, and the red team --- with a final kill-test summary. Registered in
\texttt{build.sh}, \texttt{make\_docs\_map.py}, \texttt{make\_manifest.py} and the document-set box; the
document set is now \textbf{eleven} deliverables (five numbered papers $+$ four companions $+$ introduction
$+$ changelog).
\item \textbf{Surfaces synced.} \texttt{run\_all.py} (421 modules), the registry, the ledger,
\texttt{tfpt\_research\_contracts} (the $F_{\mathrm{transfer}}$ and keystone sections),
\texttt{tfpt\_safeguards}; manifests refreshed.
\end{itemize}

\subsection*{2026-06-25 (The (LTO-RP) reduction of the keystone \texttt{SEAM.EQUIV.01}: \texttt{v424})}
\begin{itemize}
\item \textbf{New module \texttt{v424} (\texttt{SEAM.EQUIV.LTORP.01}).} An honest MMST-style reduction of the one
open keystone --- \texttt{SEAM.EQUIV.01}'s intrinsic Bisognano--Wichmann lemma (the \vref{v308}/\vref{v309}
residual) --- to the recent commuting-projector theorem of Naaijkens--Penneys--Wallick (\texttt{arXiv:2605.10693},
[NPW26]), with the central mapping \emph{corrected}. \mE\ the $\mu_4$ clock is a modular \emph{symmetry}
($[\rho,K]{=}0$, \vref{v309}/\vref{v199}), not the flow --- $\sigma^\psi{=}\rho$ is type-wrong (a one-parameter
group versus a finite order-$4$ element). \mE\ NPW26's axiom (LTO-RP) means $u_\Theta{=}J$ (reflection $=$ modular
conjugation) $=$ the intrinsic BW condition $\theta K\theta{=}-K$, \emph{distinct} from $\omega{\circ}\rho{=}\omega$:
a positive character-block-diagonal $K$ has $[\rho,K]{=}0$ yet never $\theta K\theta{=}-K$, so clock-invariance does
\emph{not} imply (LTO-RP) (refuting that identification). \mO\ make-or-break: NPW26 prove (LTO-RP) for
\emph{topologically ordered} models (Toric Code $|\det K|{=}4$ via a trace; Levin--Wen anyonic), while the seam is
invertible ($|\det\mathrm{Cartan}(E_8)|{=}1$, no anyons) and a $\beta{=}1$ KMS state (not a trace) --- in neither
proved bucket. \mC\ verdict: the BW residual reduces to NPW26 Theorem~A modulo two open sub-steps (realise the seam
as a $\Z_2$-reflection commuting-projector LTO; extend (LTO-RP) to the invertible KMS case) --- a reduction, \emph{not}
a closure; \texttt{SEAM.EQUIV.01} stays \mO. Cited in \texttt{tfpt\_research\_contracts}; Python-only (numpy; the det
discriminators mirrored via \vref{v89}/\vref{v281}).
\item \textbf{Validation provenance.} The three pivotal references of the closure-strategy note were independently
verified real and correctly described: NPW26 (\texttt{arXiv:2605.10693}), the RP--Yang--Mills complete-monotonicity
reconstruction (Int.\ J.\ Geom.\ Meth.\ Mod.\ Phys.\ 2026), and Marolf (\texttt{arXiv:2203.07421}).
\item \textbf{Surfaces synced.} \texttt{run\_all.py}, the script registry, the status ledger and the
\texttt{tfpt\_research\_contracts} keystone section; manifests refreshed.
\end{itemize}

\subsection*{2026-06-25 (No-Ambient-Dependency: no frozen readout is computed from \texttt{QG.AMB.01}: \texttt{v423})}
\begin{itemize}
\item \textbf{New module \texttt{v423} (\texttt{QGAMB.NODEP.01}).} Sharpens the \vref{v369}/\vref{v384}
prose redundancy (``\texttt{QG.AMB.01} is a \mC\ redundancy, not dynamics'') into a machine-checked
DAG${+}$script fact, told honestly. \mE\ gap-decoupling margin
$\Delta_{\mathrm{eff}}=6\ln\tfrac32-31/(4\pi^2)\approx1.648>0$ ($31=2^{\gcar}-1$), susceptibility
$\chi=729/665$ finite (negative control $\mathrm{gap}\!\to\!0\Rightarrow\chi\!\to\!\infty$); \mE\
\texttt{QG.AMB.01} is a certification \emph{sink} (every claim that lists it is a gravity-gate/QG row, never a
frozen prediction) and \emph{not a value source} (no producing script, while $\alpha^{-1}$, the mixing angles
and cosmology are each \emph{computed} by a compiler script, \vref{v3}/\vref{v9}/\vref{v268}/\vref{v7}); \mE\
the one transitive link is architectural --- of the frozen readouts only $\theta_{13}$ references it, via the
4d-QFT contract spine ($\texttt{PS.DIRAC}{\to}\texttt{CONTRACT.QFT4D}{\to}\texttt{QG.G2}{\to}\texttt{GATE.METRIC}$),
a coherence edge, not a numerical input. \mC\ verdict: \texttt{QG.AMB.01} is gap-decoupled certification ---
\vref{v369} as a DAG/script fact; honest scope --- this does \emph{not} discharge \texttt{SEAM.EQUIV.01}, on
which the readouts still depend. Cited in \texttt{tfpt\_4}; Python-only (gap algebra mirrored via \vref{v337}).
\item \textbf{Paper sharpening (seam selector, up front).} The \texttt{tfpt\_4} quantum-gravity keybox now
states explicitly that the open \texttt{SEAM.EQUIV.01} premise is the \emph{holomorphic} $|\det K|{=}1$ point
that selects $(E_8)_1$ --- the central charge $c{=}8$ alone does \emph{not}, being shared by the
non-holomorphic $SO(16)_1$ counterexample (\vref{v277}/\vref{v281}).
\item \textbf{Surfaces synced.} \texttt{run\_all.py}, \texttt{script\_registry.csv},
\texttt{status\_ledger.csv}, \texttt{tfpt\_4}; manifests refreshed.
\end{itemize}

\subsection*{2026-06-25 (The Galois$\leftrightarrow$Net bridge: \texttt{v422})}
\begin{itemize}
\item \textbf{New module \texttt{v422} (\texttt{SEAM.GALOIS.NET.01}).} The seam
$\mu_4=\operatorname{Gal}(\mathbb Q(\zeta_5))$ is the SAME cyclic $\Z/4$ as the $(E_8)_1$ simple-current glue
--- not a mere order-$4$ coincidence --- bridging the Galois gearbox of \vref{v419} to $G_{\mathrm{net}}$/%
\texttt{SEAM.EQUIV.01}. \mE\ $\operatorname{disc}(A_3)=\operatorname{disc}(D_5)=\Z/4$ (one Smith invariant
factor $4$ $=$ cyclic, $\det4$); $D_n$ disc is $\Z/4$ for $n$ odd, $\Z_2{\times}\Z_2$ for $n$ even, so the
carrier $D_5$ (rank $5=\gcar$, odd) is cyclic while $D_8$ (rank $8$, even) is Klein; \mE\
$(\Z/5)^\times=\langle2\rangle$ is cyclic order $4$ (only the carrier prime $5$ gives order $4$); \mE\ in
$\Z_4{\times}\Z_4$ ($16=\dim S^+$) the glue $(1,1)$ is order $4$ with Lagrangian quotient
$16/4^2=1=(E_8)_1$ (\vref{v89}/\vref{v154}); \mE\ negative control: the Klein / order-$2$
$\langle(2,2)\rangle$ gives $16/2^2=4=|\!\operatorname{disc}(D_8)|=SO(16)$ ($\det4$), NOT $E_8$ ($\det1$) ---
cyclic $\Z/4\to E_8$, Klein$\to D_8$. \mC\ the bridge: one cyclic $\Z/4$ threads the seam deck $\mu_4$
(\vref{v419}), $\operatorname{Gal}(\mathbb Q(\zeta_5))$ and the $(E_8)_1$ glue --- the Galois gearbox
$(\Z/30)^\times$ IS the holomorphic net's glue, cyclicity forced by $5$, Klein excluded. Cited in
\texttt{origin\_theory}; Wolfram-mirrored ($324\to327$).
\item \textbf{Surfaces synced.} \texttt{run\_all.py}, \texttt{script\_registry.csv},
\texttt{status\_ledger.csv}, \texttt{origin\_theory}; the Wolfram extension/README/ledger counts
($327/327$) and the website verification count; manifests refreshed.
\end{itemize}

\subsection*{2026-06-25 (F\_pole external: the Koide source$\to$pole transfer is one-loop EM: \texttt{v420})}
\begin{itemize}
\item \textbf{New module \texttt{v420} (\texttt{FR.POLE.QED.01}).} The honest external-physics follow-up to
\vref{v93} and the clock No-Go: the Koide source$\to$pole transfer is a one-loop \emph{electromagnetic}
effect, not an algebraic step. \mE\ Koide $Q$ is rescaling-invariant ($Q(c\,m)=Q(m)$), so flavor-universal
running leaves it fixed and the source$\to$pole shift is purely flavor-split; \mC\ the tree deficit
$\tfrac23-Q_{\mathrm{src}}=0.00220$ is one-loop-EM-sized ($=\varphi_0/24$ to $0.6\%$, $=\alpha/\pi$ to
${\sim}5\%$), the PDG pole sits at $2/3$ (the IR attractor); \mC\ a 1-loop QED
$\mathrm{pole}\!\leftrightarrow\!\overline{\mathrm{MS}}$ per-lepton-log estimate shifts $Q$ by EM-loop order
toward $2/3$ (the \vref{v82} direction); \mO\ the exact flow time $t\approx2.84$ (\vref{v93}) is
scheme/scale-dependent external QED, only sized. \mC\ verdict: $F_{\mathrm{pole}}$ is a one-loop EM effect
--- the lens forces the rate $(2/3)^6$ (\vref{v327}), external EM supplies the flow; \texttt{F\_pole} stays
\mC, firewalled (\vref{v187}), so $F_{\mathrm{transfer}}$ is confirmed genuinely external --- the open theme
sharpened (QED), not closed. Cited in \texttt{tfpt\_4}; numerical (mpmath), Python-only (no Wolfram check,
by the suite convention like \vref{v93}/\vref{v371}).
\item \textbf{Surfaces synced.} \texttt{run\_all.py}, \texttt{script\_registry.csv},
\texttt{status\_ledger.csv}, the Koide section of \texttt{tfpt\_4}; manifests refreshed.
\end{itemize}

\subsection*{2026-06-25 (The seam $\mu_4$ is the carrier's Galois group: \texttt{v419} $+$ figure)}
\begin{itemize}
\item \textbf{New module \texttt{v419} (\texttt{SEAM.GALOIS.01}).} A positive resolution of the
cyclic/Galois asymmetry (\vref{v409}, \texttt{RES.COXETER.SYMMETRY.01}): why the seam $\mu_4$ sits on the
Galois side, not on the cyclic $\zeta_{30}$ dial. \mE\ $h(E_8)=30$ is squarefree, so $\Z/30$ has element
orders $\{1,2,3,5,6,10,15,30\}$ --- \emph{no} order $4$, so the seam $\mu_4$ cannot be a rotation hand and
is forced onto the Galois side; \mE\ by CRT $(\Z/30)^\times=(\Z/2)^\times\times(\Z/3)^\times\times(\Z/5)^\times
=\mu_4\times\Z_2$ (order $\varphi(30)=8=\operatorname{rank}E_8$), and the $\mu_4$ ($\Z/4$) factor IS
$(\Z/5)^\times$ (the
carrier prime $5$), the $\Z_2$ IS $(\Z/3)^\times$ (family $3$ $=$ CP conjugation, \vref{v316}); \mE\ so the
seam $\mu_4=\operatorname{Gal}(\mathbb Q(\zeta_5))$, realised on the carrier clock $C_5$ (\vref{v418}) by the
Frobenius $\zeta_5\mapsto\zeta_5^2$ --- the explicit order-$4$ operator $G$ with $GC_5G^{-1}=C_5^2$, $G^4=I$,
$G^2C_5G^{-2}=C_5^{-1}$. \mC\ this is the positive content of \vref{v409}: the $2^2{=}4$ is the order of
$(\Z/5)^\times$, and ``no contraction rate'' is because the seam is an \emph{automorphism}, not a hand; so
$\mathbb Q(\zeta_{30})$ carries both $E_8$ invariants (cyclic $h{=}30$, Galois $\operatorname{rank}{=}8$).
Cited in \texttt{origin\_theory}; Wolfram-mirrored ($321\to324$).
\item \textbf{New figure \texttt{coxeter\_galois.pdf}.} The order-$30$ cyclic dial with the four flavor
hands (sheet/family/carrier/CP) beside the Galois gears ($\mu_4=\operatorname{Aut}(\zeta_5)$ the seam,
$\Z_2=\operatorname{Aut}(\zeta_3)$ the CP conjugation); added to \texttt{make\_figures.py}, the manifest
figure list and \texttt{origin\_theory}.
\item \textbf{Surfaces synced.} \texttt{run\_all.py}, \texttt{script\_registry.csv},
\texttt{status\_ledger.csv}, the Wolfram extension/README/ledger counts ($324/324$) and the website
verification count; manifests refreshed.
\end{itemize}

\subsection*{2026-06-25 (The cyclotomic norm triple $+$ the carrier-5 clock: \texttt{v418})}
\begin{itemize}
\item \textbf{New module \texttt{v418} (\texttt{ARITH.NORMTRIPLE.01}).} The carrier split $(3,2)$ read in
the three atom-rings gives $(7,13,55)=$(scalaron, $\Delta_Q$, quark numerator), and the carrier-$5$ clock
missing from \vref{v417} is found as the $4{\times}4$ $\Phi_5$-companion $C_5$. \mE\ $C_5^5{=}I$,
$\operatorname{tr}C_5{=}{-}1$, $\det C_5{=}1$ (the four primitive $5$th roots), with the golden ratio as its
real-part data ($2\cos72^\circ{=}1/\varphi$, $2\cos144^\circ{=}{-}\varphi$; output-side, \vref{v313}/\vref{v349};
dim $4$, not $3$ --- this refines \vref{v417}'s gap from ``no operator'' to ``no $3{\times}3$ operator''); \mE\
$N_{\Z[\zeta_5]}(3{+}2\zeta_5){=}\det(3I{+}2C_5){=}55{=}5{\cdot}11{=}\gcar\|\operatorname{Pl}(K)\|_1$, the
$c_u/c_d$ numerator (\vref{v410}/\vref{v411}); \mE\ the triple $\det(3I{+}2\,\mathrm{Comp}(\Phi_n))=(7,13,55)$
for $n{=}3,4,5$ over $\Z[\omega],\Z[i],\Z[\zeta_5]$ (atoms $3,2,5$, \vref{v416}); \mE\ NEG control: the anchor
$(5,4)\to(21,41,461)$ reaches named values only in the $\omega$- and $i$-rings ($21{=}N_\omega(5,4)$,
$41{=}10b_1$, \vref{v222}) but $461$ (prime) in the carrier ring, so the carrier ring separates
$(3,2)\to55$ from $(5,4)\to461$. \mC\ honest: $(3,2)$ is the \emph{forced} carrier split (\vref{v14}), not the
unique clean one --- a scan finds $\{(2,1)\to(3,5,11),(3,2)\to(7,13,55)\}$, a small ladder. The sharper discriminator is
\emph{cross-sector}: only $(3,2)$ spans three physics sectors (gravity $7$, flavor $13$, masses $55$),
the unique cross-sector seed, while $(2,1)$ is all compiler-core. Cited in
\texttt{origin\_theory}; Wolfram-mirrored ($318\to321$).
\item \textbf{Surfaces synced.} \texttt{run\_all.py}, \texttt{script\_registry.csv},
\texttt{status\_ledger.csv}, a triple paragraph in \texttt{origin\_theory}, the Wolfram
extension/README/ledger counts ($321/321$) and the website verification count; manifests refreshed.
\end{itemize}

\subsection*{2026-06-25 (The Eisenstein/CP operator $+$ the order-30 clock: \texttt{v417})}
\begin{itemize}
\item \textbf{New module \texttt{v417} (\texttt{DIAMOND.EISEN.01}).} The hexagonal dual of \vref{v415}:
the $\tau{=}\omega$ flavor side put on operators and unified with the seam into one order-$30$ Coxeter
clock. \mE\ the family rotation $P=(1\,2\,3)$ is the order-$3$ Eisenstein deck ($P^2{+}P{+}I=\mathrm{ONES}$,
so $\omega^2{+}\omega{+}1{=}0$ on the plane $\perp(1,1,1)$), the order-$3$ dual of $J^2{=}{-}I$; \mE\ it
realises the hex CM norm as $(3I{+}2P)(3I{+}2P^2)=7I{+}6\,\mathrm{ONES}$, $\operatorname{Spec}\{7,7,25\}$
($7{=}N_{\Z[\omega]}(3{+}2\omega){=}$ scalaron, $25{=}\gcar^2$) --- the dual of \vref{v415}'s
$\{13,13,9\}$; \mE\ the CP clock $W{=}{-}P^2$ ($\rho$ of \vref{v233}) has $W^2{=}P$, $W^3{=}{-}I$,
$\operatorname{Spec}\{-1,\zeta_6,\zeta_6^{-1}\}$, giving $\delta_{\mathrm{CKM,lead}}{=}\arg\zeta_6{=}\pi/3$
and $\delta_{\mathrm{PMNS}}{=}\arg\zeta_6^4{=}4\pi/3$ (\vref{v316}/\vref{v320}); \mE\ all flavor clocks are
powers of $\zeta_{30}$ ($\zeta_{30}^{15}{=}{-}1$, $\zeta_{30}^{10}{=}\omega$, $\zeta_{30}^{6}{=}\zeta_5$,
$\zeta_{30}^{5}{=}\zeta_6$) while the seam $\mu_4{=}i$ is the Galois side $(\Z/30)^\times$ of order
$\varphi(30){=}8{=}\operatorname{rank}E_8$ --- so $\mathbb Q(\zeta_{30})$ carries both $E_8$ invariants
($h{=}30$ and $\operatorname{rank}{=}8$). \mC\ honest gap: the carrier $\mu_5$ has no $3{\times}3$
operator (the golden $\varphi$ is an output-side trace, \vref{v313}/\vref{v349}); negatives: no
$U,V$-diamond operator carries $\zeta_6$, $[D,P]\neq0$ (no $\mu_{12}$), $N(3{+}2\zeta_6){=}19{\neq}7$.
Cited in \texttt{tfpt\_2}; Wolfram-mirrored ($315\to318$).
\item \textbf{Surfaces synced.} \texttt{run\_all.py}, \texttt{script\_registry.csv},
\texttt{status\_ledger.csv}, the Sheet-Diamond keybox of \texttt{tfpt\_2}, the Wolfram
extension/README/ledger counts ($318/318$) and the website verification count; manifests refreshed.
\end{itemize}

\subsection*{2026-06-25 (The Gaussian operator $+$ the atom trichotomy: \texttt{v415}, \texttt{v416})}
\begin{itemize}
\item \textbf{New module \texttt{v415} (\texttt{DIAMOND.GAUSS.01}).} The square CM-norm dictionary of
\vref{v222}/\vref{v230} is \emph{operator-realised}, and the $\mu_4$ deck becomes an intrinsic diamond
object. \mE\ the integer commutator $J:=\tfrac13[U,V]=\big(\begin{smallmatrix}-1&1&0\\-2&1&0\\-3&1&0\end{smallmatrix}\big)$
has $\operatorname{Spec}(J)=\{i,-i,0\}$, $J^2=-I$ on the rank-$2$ image and $J^3+J=0$ --- a $\mu_4$
quarter-turn born from the binary $V$ and ternary $U$ compilers (\vref{v410}/\vref{v95}); \mE\ $3I+2J$ and
$5I+4J$ have spectra $\{3{+}2i,3{-}2i,3\}$, $\{5{+}4i,5{-}4i,5\}$, so the Gaussian integers $3{+}2i$ (norm
$13{=}\Delta_Q$) and $5{+}4i$ (norm $41{=}10b_1$) are \emph{literal eigenvalues}; \mE\ $(aI{+}bJ)(aI{-}bJ)$
reads $(a^2{+}b^2)$ on the $\mu_4$-plane and the real part$^2$ on the kernel ($\{13,13,9\}$, $\{41,41,25\}$);
\mE\ the intrinsic order-$4$ deck $D=-I+J-J^2$ ($D^4=I$, $\chi_D=(x{+}1)(x^2{+}1)$) has $\chi_2$-line
$\ker[U,V]=a-\mathbf 1$. \mC\ the geometric-deck identification sharpens (does not close) the \vref{v140}
$\Z_3$ residue. Cited in \texttt{tfpt\_2}; Wolfram-mirrored.
\item \textbf{New module \texttt{v416} (\texttt{ARITH.TRICHOTOMY.01}).} The atoms $\{2,3,5\}$ are
ramified/inert/split in the two exceptional CM rings. \mE\ in $\Z[i]$ (square/seam) $2{=}|\Z_2|$ ramifies,
$3{=}\Nfam$ is inert, $5{=}\gcar$ \emph{splits} as $(2{+}i)(2{-}i)$; \mE\ in $\Z[\omega]$ (hex/flavor)
$3{=}\Nfam$ ramifies, $2,5$ are inert; \mE\ the ramified prime of each ring is its own atom; \mE\ the three
quadratic facets $\mathbb Q(i),\mathbb Q(\sqrt{-3}),\mathbb Q(\sqrt5)$ of $K=\mathbb Q(i,\sqrt{-3},\sqrt5)$
(\vref{v403}) ramify over exactly one atom each, product $2\cdot3\cdot5=30=h(E_8)$, two imaginary
(CM/dynamic) $+$ one real (RM/static). \mC\ the seam/flavor/golden reading. Cited in
\texttt{origin\_theory}; Wolfram-mirrored.
\item \textbf{Wolfram extension $308\to315$ $+$ a pre-existing fix.} Added the seven exact checks for
\texttt{v415}/\texttt{v416} and corrected a one-character sign bug in the \texttt{v412}
\texttt{CharacteristicPolynomial} check (Wolfram returns $-\chi$ for odd rank), so
\texttt{tfpt\_readouts\_extension.wl} now runs genuinely clean at $315/315$ (\texttt{GATE.WOLFRAM.02});
README and ledger counts updated.
\item \textbf{Surfaces synced.} \texttt{run\_all.py}, \texttt{script\_registry.csv} and
\texttt{status\_ledger.csv} updated; a new keybox paragraph in the Sheet-Diamond section of \texttt{tfpt\_2}
and a trichotomy sentence in \texttt{origin\_theory}; manifests refreshed.
\end{itemize}

\subsection*{2026-06-24 (The sheet generator $V$ as a binary internal compiler: \texttt{v410}--\texttt{v414})}
\begin{itemize}
\item \textbf{New module \texttt{v410} (\texttt{SHEET.GEN.BINARY.01}).} The rank-$2$ sheet axis
$V=Q\operatorname{diag}(0,1,1)$ of the centered cross (\vref{v95}/\vref{v218}) is a binary internal compiler:
its powers print the carrier spine. \mE\ the closed form $V^n=\big(\begin{smallmatrix}0&2^{n-1}&0\\0&2^n&0\\0&2^{n+1}-2&1\end{smallmatrix}\big)$
(proved by the inductive step $F(n)V{=}F(n{+}1)$), so $V^n\mathbf 1=(2^{n-1},2^n,2^{n+1}-1)=(1,2,3),(2,4,7),(4,8,15),(8,16,31)$;
\mE\ the four bilinear families $\mathbf 1^TV^n\mathbf 1=7\cdot2^{n-1}{-}1$, $\mathbf 1^TV^na=7\cdot2^{n-1}$,
$a^TV^na=11\cdot2^{n-1}$, $a^TV^n\mathbf 1=11\cdot2^{n-1}{-}2$ give $(6,7,9,11)$ at $n{=}1$ and
$\mathbf 1^TV^2\mathbf 1{=}13{=}\Delta_Q$, $\mathbf 1^TV^3\mathbf 1{=}27{=}\mathbf 1^TRa$,
$\mathbf 1^TV^4\mathbf 1{=}55$, $\mathbf 1^TV^4a{=}56{=}\dim\mathbf{56}_{E_7}$; \mC\ the binary spine is FORCED by
$\operatorname{Spec}(V){=}\{0,1,2\}$, so the carrier/Lie matches ($\mathrm{rank}\,E_8{=}8$, $\dim S^+{=}16$,
$248/8{=}31$) and the theta cross-link ($\sigma_3(2){=}9{=}a^TV\mathbf 1$, $\sigma_3(3){=}28{=}\mathbf 1^TV^3a{=}\det(I{+}R)$,
$\sigma_3(5){=}126$) are audit-typed (the \vref{v95} $G_2$-center typing).
\item \textbf{New module \texttt{v411} (\texttt{FLAV.UD.VPOWER.01}).} The quark ratio is a pure $V$-power readout,
$c_u/c_d=(\mathbf 1^TV^4\mathbf 1)/((a^TV\mathbf 1)(\mathbf 1^TV^2\mathbf 1))=55/(9\cdot13)=55/117$, identical to the
established $\gcar\|\mathrm{Pl}(K)\|_1/(\Nfam^2\Delta_Q)=5\cdot11/(9\cdot13)$ (\vref{v94}). \mE\ the identity; \mC\ an
exact \emph{re-encoding} (no new physical input) --- the value and the $u/d$ identification stay conditional, coupled
to the $(U_{\mathrm{wall}})$ readout rigidity.
\item \textbf{New module \texttt{v412} (\texttt{DIAMOND.SHEET.SOURCE.J.01}).} Names the operator on the $\Z_2$ wall
($t{=}{-}2$, $\det{=}2$, \vref{v135}), $J{=}M(1,{-}2){=}C{-}2V$, completing the sheet axis $J,K,C,F{=}M(1,{-}2..1)$.
\mE\ $\chi_J=\lambda^3-6\lambda^2+3\lambda-2\Rightarrow(\mathrm{tr},e_2,\det){=}(6,3,2)$; $a^TJa{=}30{=}h(E_8)$,
$\det(I{+}J){=}12{=}\dim\mathfrak g_{\mathrm{SM}}$ and $\det(2I{+}J){=}40{=}|R(D_5)|$; \mC\ the Lie readings
audit-typed like the $G_2/F_4$ shadows.
\item \textbf{New module \texttt{v413} (\texttt{DIAMOND.SHEET.CALCULUS.01}).} On $M_t{=}C{+}tV$ the
elementary-symmetric coefficients encode the atoms as difference orders: $e_1{=}3t{+}12$, $e_2{=}2t^2{+}15t{+}25$,
$e_3{=}4t^2{+}14t{+}14$ give $\Delta e_1{=}3{=}\Nfam$, $\Delta^2 e_2{=}4{=}|\mu_4|$, $\Delta^2 e_3{=}8{=}\mathrm{rank}\,E_8$
(the $e_3$ curvature is the \vref{v218}/\vref{v224} sheet quadratic; the full triple is new); \mE\ the anchor energy
$a^TM_ta{=}52{+}11t$ ($30{\to}41{\to}52{\to}63$, step $11{=}a^TVa$); \mC\ atom/Lie readings audit-typed.
\item \textbf{New module \texttt{v414} (\texttt{DIAMOND.CENTER.RESOLVENT.01}).} The center $C{=}M(1,0)$ is a resolvent
portal: \mE\ $\det C{=}14{=}\dim G_2$, $\det(I{+}C){=}52{=}\dim F_4$, $\det(2I{+}C){=}120{=}|R^+(E_8)|$, the exceptional
shell ladder $G_2{\to}F_4{\to}E_8^+$ as $\det(C{+}kI)$, $k{=}0,1,2$ (with $\mathrm{tr}\,C{=}12{=}\chi_{E_8}(i)$,
$\sum C{=}31{=}2^{\gcar}{-}1$, \vref{v95}); \mC\ the portal reading.
\item \textbf{Surfaces synced.} Integrated into the Sheet-Diamond section of \texttt{tfpt\_2} (new keybox, five
\texttt{\textbackslash veri} citations) and the $E_8$ theta-raster of \texttt{tfpt\_3}; \texttt{run\_all.py},
\texttt{script\_registry.csv} and the ledger updated; Wolfram extension mirror $303\to308$.
\end{itemize}

\subsection*{2026-06-24 (Two new tracked targets + axion-branch consistency: \texttt{v408}, \texttt{v409})}
\begin{itemize}
\item \textbf{New module \texttt{v408} (\texttt{HYP.PHI0.PUNCTURE.01}).} Names the $\varphi_0$ puncture term
$48c_3^4$ as the order-$|\mu_4|{=}4$ local boundary heat-kernel (Seeley--DeWitt) contact term of the $\mu_4$
puncture divisor, summed over $\Omega_{\mathrm{adm}}{=}\Nfam\dim S^+{=}48$ admissible states --- the analytic
complement of the icosahedral tree term (\vref{v396}). \mE\ the exact split $\varphi_0{=}1/(6\pi){+}48c_3^4$,
the puncture count, the closed form $3/(256\pi^4)$ and the hypergraph negative (reused from
\vref{v396}/\texttt{ARCH.QUAD.01}); \mO\ the from-first-principles heat-kernel proof; \mC\ a FACE of the seam
boundary analysis (the $c_3$ Gauss--Bonnet datum), not a new gate. Cited in \texttt{origin\_theory}; no new number.
\item \textbf{New module \texttt{v409} (\texttt{RES.COXETER.SYMMETRY.01} closed as a structural lemma).} prime-$2$
(the seam sheet involution) is \emph{necessary} but \emph{not autonomous}: $\sigma{=}\operatorname{diag}(1,-1,-1)$
has spectrum $\{\pm1\}$ and projector $(I{+}\sigma)/2$ spectrum $\{0,1\}$, none in $(0,1)$, so prime-$2$ carries
no contraction rate, whereas the genuine rates $2/3$ and $(1/3)^6$ lie in $(0,1)$ and carry prime-$2$ only as a
factor. \mE\ no prime-$2$-only attractor exists; \mC\ dynamics begins only after coupling to family-$3$ or
carrier-$5$ ($|\mu_4|{=}2^2$ the Galois bridge). Resolves the \vref{v394} open question's falsifiable corollary;
cited in \texttt{tfpt\_research\_contracts}; the ledger row \texttt{RES.COXETER.SYMMETRY.01} retyped \mO\ $\to$ \mE/\mC.
\item \textbf{Axion branch consistency (\texttt{tfpt\_4\_frontier}, website \texttt{predictions.ts}, \vref{v185}).}
The dark-matter section's opening $+$ keybox are realigned with the finite-$T$ result already stated later in the
same section: the robust dominant-DM branch is the \emph{spine} angle $\theta_i{=}\pi\Nfam/\gcar{=}3\pi/5{=}108^\circ$
(untuned, in band), while the seam hilltop $\theta_i{\approx}170^\circ$ over-produces ($\sim5.4\times$) and is
disfavoured; the misalignment angle is retyped from a closed \mE\ input to a \mC\ branch decision. The website
prediction card now leads with the spine angle.
\item \textbf{Lean closure of the prime-2 corollary (\texttt{FORM.COXETER.PRIME2.01}).} The v409 result is now
also machine-proved in Lean~4 / Mathlib (new module \texttt{TfptCarrier/CoxeterPrime2.lean}): an involution
eigenvalue ($r^2{=}1$) is $\pm1$, a projector eigenvalue ($r^2{=}r$) is $0$ or $1$, neither lies in the open
interval $(0,1)$, while $2/3$ does --- so \emph{no prime-2-only attractor exists}. Built clean
(\texttt{lake build}); the new theorems are axiom-pure ($\#$\texttt{print axioms} $=$ \texttt{propext},
\texttt{Classical.choice}, \texttt{Quot.sound} only) and pass the \texttt{AuditCheck}/\texttt{AuditContract}
signature locks. This lifts \texttt{RES.COXETER.SYMMETRY.01} to the machine-proof tier.
\item \textbf{Verified, no change (Pl\"ucker $11$).} The quark constant $11{=}\|Pl(K)\|_1{=}\det(\mathbf1|a|\sigma)$
is already typed honestly as an \mE\ identity with ``why $11$'' the lone \mO\ residue (\vref{v407}, \texttt{tfpt\_1});
the repo carried no overstatement, so no edit was required.
\end{itemize}

\subsection*{2026-06-24 (Cross-surface consistency sweep: papers, website, gates, figures realigned)}
\begin{itemize}
\item \textbf{Ledger hygiene.} Resolved a duplicate active \texttt{claim\_id}: \texttt{GATE.UWALL.06--09} was carried by two distinct chains. It is an ID collision (not a supersede): the monodromy/residue chain \texttt{v114}--\texttt{v117} keeps \texttt{.06--.09} (as asserted by \texttt{v123\_inventory\_update.py} and \texttt{run\_all.py}); the older exterior-leg chain \texttt{v42}--\texttt{v45} is renumbered to \texttt{GATE.UWALL.15--.18} (internal \texttt{depends\_on} carried along). No claim content changed.
\item \textbf{Website.} \texttt{papers.ts} document count $8\to9$ (the Red-Team paper was missing from the tally); Red-Team subtitle/highlight \emph{Targets A--E}$\to$\emph{A--F} with a new Target~F section $+$ contribution bullet (the abstract already carried F); \texttt{StatusMatrix.tsx} \emph{Doc~7}$\to$\emph{Doc~8} for the research contracts and the residual interfaces re-typed $v_{\mathrm{geo}}$ \mO, $G_{\mathrm{net}}$ \mC, $F_{\mathrm{transfer}}$ \mC; \texttt{objections} \emph{Paper~1}$\to$\emph{Doc~1}.
\item \textbf{Papers (marker/wording alignment, no canonical status change).} \texttt{tfpt\_1} Strong CP \mE$\to$\mE/\mC\ (given RP) and $\theta_{12}$ ``genuinely open''$\to$``conditionally derived''; \texttt{tfpt\_2} Starobinsky $A_s$ \mE$\to$\mE/\mC\ ($M$ exact, $A_s$ a band over $N_\star\in[50,60]$) and the Part-II abstract ``opens the one remaining gap''$\to$``closes the last structural gap''; \texttt{tfpt\_research\_contracts} the QFT4D ``nonperturbative measure stays open'' line and the ``only $U_{\mathrm{point}}$ stays open'' headline reconciled with the \mC\ redundancy / $v_{\mathrm{geo}}$ reduction stated alongside; \texttt{origin\_theory} class~C re-typed to the ambient-measure \mC\ redundancy; \texttt{introduction} $(U_{\mathrm{wall}})\to v_{\mathrm{geo}}$. Forbidden old-paper attributions (``Papers~1--7'', ``Papers~2/6'', ``Paper-7'', ``Paper-1'') replaced by current document / neutral wording (the \texttt{tfpt\_3} cascade bridge stays exempt).
\item \textbf{Suite README.} The residual-gates table (Alessandro-5.0 vintage) brought to the current model ($v_{\mathrm{geo}}$ \mO; $G_{\mathrm{net}}$/\texttt{SEAM.EQUIV.01}, $F_{\mathrm{transfer}}$, $N_\star$, \texttt{QG.AMB.01} \mC; Wolfram $116/116+303/303$).
\item \textbf{Figures.} Regenerated \texttt{status\_heatmap} (ledger-driven) and extended the narrative figures \texttt{script\_timeline}/\texttt{residual\_chain}/\texttt{qft\_skeleton} through the \texttt{v303}--\texttt{v407} arc (typed solvers, parameter-free local Einstein equation \texttt{v359}, \texttt{QG.AMB.01} \mC\ redundancy, seam closed modulo cited theorems); the \texttt{qft\_skeleton} ``Stelle ghost'' open box is retyped (resolved truncation artefact). Added \texttt{qft\_skeleton}/\texttt{qft\_unification} to the manifest figure list.
\end{itemize}

\subsection*{2026-06-24 (The $\tau{=}\omega$ dual keystone + the flavor residuals it homes: \texttt{v405}--\texttt{v407})}
\begin{itemize}
\item \mE/\mC/\mO\ \textbf{\texttt{v405\_seam\_equiv\_omega.py}} (\texttt{SEAM.EQUIV.02}): the \emph{dual keystone} at $\tau{=}\omega$ -- the family/flavor sector as the order-$3$ Eisenstein$/A_2$ face of $E_8$, dual to the seam $=(E_8)_1$ at $\tau{=}i$ (\vref{v404}). A named contract (genre of \vref{v286}/\vref{v398}), NOT a closure. \mE\ $\chi_{E_8}(\omega)=0$ (the family CM point degenerates $E_8$) vs $\chi_{E_8}(i)=12$; \mE\ $A_2$ is the $\tau{=}\omega$ Eisenstein lattice (Cartan $\det=3=\Nfam$, $h=3=\Nfam$); \mE\ $R$ lives in $E_6{\times}A_2$ ($248=78+8+2{\cdot}27{\cdot}3$, $\det R=8=\dim A_2=\operatorname{rank}E_8$); \mE\ $\delta_{\mathrm{PMNS}}=4\pi/3$ is the $\tau{=}\omega$ CM phase; \mE\ the cusp weights $\{0,1/3,2/3\}$ are the order-$3$ deck $=\Nfam=\det Q$. \mC\ the family sector is the order-$3$ Eisenstein$/A_2$ deck; the two keystones sit at the only two elliptic points of $\mathrm{PSL}(2,\mathbb Z)$. \mO\ residual $=$ the canonical $\mathbb Z_3$ deck map (\vref{v140}) $+$ the $v_{\mathrm{geo}}$-class scale. Cited in \texttt{origin\_theory}; Python-only.
\item \mE/\mC/\mO\ \textbf{\texttt{v406\_pmns\_phase\_origin.py}} (\texttt{FLAV.PMNS.CLOSE.01}): the PMNS dynamics closed \emph{modulo} the $\tau{=}\omega$ keystone -- the CP-phase ORIGIN is the family CM point and the absolute scale is one $v_{\mathrm{geo}}$-class unit, so PMNS has \emph{zero free flavor dials beyond $v_{\mathrm{geo}}$}. \mE\ the three angles (\vref{v9}/\vref{v268}) $\to$ unitary $U_{\mathrm{PMNS}}$ (\vref{v270}); \mC\ $\delta_{\mathrm{PMNS}}=4\pi/3$ is the $\tau{=}\omega$ hexagonal CM phase (\vref{v405}), upgrading \vref{v270}'s \mO\ ``assembled input'' to a keystone consequence; \mC\ $J_{\mathrm{PMNS}}=-0.0297$ derived; \mE\ the absolute scale $=$ one seesaw ratio $=v_{\mathrm{geo}}$-class (\vref{v272}/\vref{v153}). \mO\ residual $=$ the seesaw operator realisation ($M_R$, \vref{v184}) $+$ the $\Sigma m_\nu$ floor kill test. Cited in \texttt{tfpt\_2\_standard\_model}; Python-only.
\item \mE/\mC/\mO\ \textbf{\texttt{v407\_dn\_pairings\_omega.py}} (\texttt{FLAV.SELECTOR.CLOSE.01}): the R4$'$ selector residue folds into the $\tau{=}\omega$ keystone -- the three $(d,n)$ pairings ARE the $\tau{=}\omega$ family-slice atoms. \mE\ the frame $(\mathbf 1,a,\sigma)$ has $\det=11=\|Pl(K)\|_1$ and $n=(5,-9,6)$ is the unique covector with $n{\cdot}\mathbf1=2$, $n{\cdot}a=8$, $n{\cdot}\sigma=121=11^2$ ($\Rightarrow(d,n)\Rightarrow R$, \vref{v136}/\vref{v139}); \mE\ $n{\cdot}a=8=\operatorname{rank}E_8=\dim A_2=\det R$ (the $A_2$ block reading $R$ in $E_6{\times}A_2$, \vref{v405}); \mE\ the pairings $\{2,8,121\}=\{|Z_2|,\dim A_2{=}\det R,\|Pl(K)\|_1^2\}$. \mC\ deriving $(d,n)$ folds into \texttt{SEAM.EQUIV.02} ($d$ anchor-derived, \vref{v139}); \mO\ the lone residue ``why $11{=}\|Pl(K)\|_1$''. Cited in \texttt{tfpt\_1\_architecture\_e8}; Python-only.
\end{itemize}

\subsection*{2026-06-24 (The arithmetic hull + the $E_8$-character CM duality: \texttt{v403}, \texttt{v404})}
\begin{itemize}
\item \mE/\mC\ \textbf{\texttt{v403\_facet\_compositum.py}} (\texttt{ARITH.HULL.01}): the three single-prime number-field facets of the order-$30$ clock (\vref{v390}/\vref{v394}, used so far only one at a time) \emph{compose} to one field $K=\mathbb Q(i,\sqrt{-3},\sqrt5)$. \mE\ the squarefree parts $-1,-3,5$ are independent in $\mathbb Q^\times/(\mathbb Q^\times)^2$, so $[K:\mathbb Q]=2^3=8=\operatorname{rank}E_8=\gcar{+}\Nfam$ with Galois group $(\mathbb Z/2)^3$ (order $8$); \mE\ exactly $7$ quadratic subfields $\{-1,-3,5,3,-5,-15,15\}$, splitting $4$ imaginary $=|\mu_4|$ (CM/dynamic) $+$ $3$ real $=\Nfam$ (RM/static); \mE\ ramified \emph{only} over $\{2,3,5\}=$ the atoms $=$ the primes of $h(E_8)=30$; \mE\ $2^{\omega(h)}=\operatorname{rank}$ is $E_8$-special (the $E_7$ control $h=18$ gives $2^2=4\neq7$). \mC\ $K$ is the abelian $(\mathbb Z/2)^3$ \emph{arithmetic} hull dual to the $E_8$ \emph{lattice} hull; the $7$ quadratic subfields are a candidate for the $7$ $E_8$ audit slices. A synthesis composing the established facets, no new number; cited in \texttt{origin\_theory}; Python-only by the synthesis-module convention (cf.\ \vref{v390}/\vref{v394}).
\item \mE/\mC\ \textbf{\texttt{v404\_e8\_char\_cm\_duality.py}} (\texttt{E8.CMDUAL.01}): the $(E_8)_1$ vacuum character $\chi_{E_8}=E_4/\eta^8=j^{1/3}$ read at \emph{both} CM points, extending \vref{v282} ($\chi_{E_8}(i)=12$) to the second elliptic point. \mE\ $\chi_{E_8}^3=j$ (q-series); \mE\ SEAM $\tau{=}i$ ($\mathbb Q(i)$, order $4$): cross-ratio $2\Rightarrow j=1728\Rightarrow\chi_{E_8}(i)=1728^{1/3}=12$ ($E_8$ present, \vref{v214}/\vref{v282}); \mE\ FAMILY $\tau{=}\omega$ ($\mathbb Q(\sqrt{-3})$, order $6$): the equianharmonic $\lambda$ ($\lambda^2{-}\lambda{+}1=0$) $\Rightarrow j=0\Rightarrow\chi_{E_8}(\omega)=0$ ($E_4$ vanishes, \vref{v220}/\vref{v267}); \mE\ $\tau{=}i,\tau{=}\omega$ are the \emph{only} elliptic points of $\mathrm{PSL}(2,\mathbb Z)$, so the values are forced. \mC\ the seam/flavor rigidity duality: the seam is rigid where $E_8$ is present ($\chi=12$, the keystone \texttt{SEAM.EQUIV.01} closes) while the flavor/CP sector is the soft residual where $E_8$ degenerates ($\chi=0$: $U_{\mathrm{wall}}$, $v_{\mathrm{geo}}$, the CP texture), a candidate dual keystone at $\tau{=}\omega$. Cited in \texttt{origin\_theory}; core values $j=1728/j=0$ already mirrored (\vref{v214}/\vref{v220}/\vref{v267}/\vref{v282}), Python-only.
\end{itemize}

\subsection*{2026-06-24 (The five TOE/QFT closure contracts \texttt{v398}--\texttt{v402} + a ledger rescope)}
\begin{itemize}
\item \mE/\mO\ \textbf{\texttt{v398\_seam\_state\_rigidity.py}} (\texttt{SEAM.RIGIDITY.01}, Paper A): the \emph{Seam State Rigidity Theorem} as ONE named target, consolidating the scattered state-invariance reductions (\vref{v177}/\vref{v199}/\vref{v308}/\vref{v309}/\vref{v335}) and \emph{hardening} the finite-block evidence to a multi-mode sweep. \mE\ RP-definability hinge (OS canonical transfer $T{=}e^{-H}$ from RP $+$ reflection alone, \vref{v54}, quasi-free \vref{v155}, no $\mu_4$ normal form); \mE\ band-limited character-block-diagonal core $[\rho,|k|]{=}0$ swept $N{=}4..64$ (beyond the $3$-dim $H^1$); \mE\ holomorphy $\Rightarrow(E_8)_1$ ($c{=}8$, $|\!\det\mathrm{Cartan}|{=}1$ vs $4$, index $4{=}|\mu_4|$). \mO\ the one residual: $[\rho,\Lambda_\Sigma]{=}0$ on the full $L^2$ (intrinsic Bisognano--Wichmann). NOT a closure of \texttt{SEAM.EQUIV.01} (continuum $=$ cited MMST \vref{v336}).
\item \mE/\mC/\mO\ \textbf{\texttt{v399\_gravity\_complete.py}} (\texttt{GRAVITY.COMPLETE.01}, Paper B): the explicit verdict \emph{Gravity-complete $=$ Boundary-complete $+$ Ambient-redundancy}, combining the parameter-free local equation (\vref{v358}/\vref{v359}) with the ambient redundancy (\vref{v369}). \mE\ the five gravitational readout classes (Newton $8\pi$, $\Lambda$, scalaron $\cthree^7$, horizon $1/|\mu_4|$, recovery $(2/3)^6$) are all boundary/seam/gap, so $\mathcal O_{\mathrm{phys}}\subset\mathcal A_\Sigma$; \mO\ residual $=$ \texttt{SEAM.EQUIV.01} $+$ intrinsic BW (no new gate).
\item \mE/\mO\ \textbf{\texttt{v400\_grav\_nonlocal\_action.py}} (\texttt{GRAV.NONLOCAL.01}, Paper C): the nonlocal spectral-gravity action with the local $R{+}R^2$ as its IR projection (consolidating \vref{v304}/\vref{v370}/\vref{v380}/\vref{v386}, adding the IR-matching check). \mE\ entire $a{=}e^u\Rightarrow$ one pole (ghost-free), every truncation carries a Stelle zero (monotone, \vref{v380}), and the IR order reproduces $R{+}R^2$ with the atom-fixed scale $M_{\mathrm{scal}}^2/\Mbar^2{=}\cthree^7$ (\vref{v36}/\vref{v253}). \mO\ the entire-$a$ assumption $+$ perturbative-only.
\item \mE/\mO\ \textbf{\texttt{v401\_metrology\_closure.py}} (\texttt{METROLOGY.CLOSURE.01}, Paper D): the final input set $\{a,\pi,v_{\mathrm{geo}}\}$ certified --- $0$ dimensionless dials $+$ $1$ unit (consolidating \vref{v153}/\vref{v274}/\vref{v364}/\vref{v384}). \mE\ dimensional bookkeeping mass$/1G/\Lambda/U_{\mathrm{point}}/(m/\mu){=}$ number $\times v_{\mathrm{geo}}^{1,2,4,1,0}$; \mE\ the $G$-vs-$\Lambda$ over-determination $0.11\%$ (\vref{v274}); \mO\ $v_{\mathrm{geo}}$ theorem-forbidden ($\mathrm{TOE}_{\mathrm{strict}}{=}\mathrm{TOE}_{\mathrm{dimensionless}}{+}[v_{\mathrm{geo}}]$).
\item \mE/\mC\ \textbf{\texttt{v402\_ftransfer\_suite.py}} (\texttt{FTRANSFER.SUITE.01}, Paper E): the four frontier sectors as ONE functor $F_{\mathrm{transfer}}$, the composition $F_{\mathrm{obs}}\circ F_{\mathrm{thr}}\circ F_{\mathrm{RG}}$ (consolidating the \texttt{FR.*.SOLVE} solvers), each with an exact atom source, a committed kill test, and the firewall (physical prediction stays \mC/\mO, only the algebraic source \mE; never re-pressed into the compiler, \vref{v187}).
\item \textbf{Ledger rescope (repo hygiene):} \texttt{GATE.METRIC.01} no longer reads ``full covariant metric-sector field equation open'' --- the \emph{local} covariant equation is closed parameter-free (\texttt{GRAV.NONLINEAR.01}/\vref{v359}); the gate is rescoped so the open item is \emph{only} the global nonperturbative ambient measure (\texttt{QG.AMB.01}, a \mC\ redundancy \vref{v369}), removing the stale contradiction with the status card.
\end{itemize}

\subsection*{2026-06-24 ($\varphi_0$ leading term from icosahedral combinatorics: \texttt{v396})}
\begin{itemize}
  \item \mE/\mC\ \textbf{\texttt{v396\_phi0\_icosahedral.py}} (\texttt{HYP.PHI0.01}): the tree-level seed $\varphi_0^{\mathrm{tree}}=1/(6\pi)$ is exactly $F/(4h\pi)=F/(|\Aut|\pi)=(F/(\gcar\Nfam))c_3$ on the icosahedral hypergraph ($F=20$ triangular hyperedges, $h=30$, $|\Aut|=120$); $F/h=|Z_2|/\Nfam=2/3$ (the same survival ratio as \texttt{v327}). \mE\ Gauss--Bonnet consistent with $c_3=1/(|Z_2|4\pi)$ (\texttt{v216}/\texttt{v342}). \mE\ honest negative: the puncture $48c_3^4$ is still analytic, not a hypergraph fraction. \mC\ $\varphi_0^{\mathrm{tree}}$ is a combinatorial reinterpretation, not a new independent injection; the puncture stays \mO.
\end{itemize}

\subsection*{2026-06-24 (Coupled hypergraph rewrite: \texttt{v395} unifies carrier $\times$ family in one local rule)}
\begin{itemize}
  \item \mE\ \textbf{\texttt{v395\_hypergraph\_coupled.py}} (\texttt{HYP.COUPLED.01}): one coupled local rewrite on a $9\times3$ labelled grid (affine-$E_8$ nodes $\times$ family channels) unifies \texttt{v299} (carrier growth), \texttt{v327} (branching rule $M$) and \texttt{v324} (fiber product). Micro-step $=$ network lazy diffusion on each cusp column $+$ $M$ on each node's family vector ($T_{\mathrm{micro}}=T_{\mathrm{net}}\otimes M$); joint attractor marks$\otimes e_0$; one clock hand ($6$ family steps) gives recovery $(2/3)^6$; \texttt{v324}'s $T_{\mathrm{net}}\otimes T_{\mathrm{cusp}}$ emerges as the cusp-readout basis. \mO\ the $3$-arm seed ($P_2$) and analytic $\varphi_0$ remain irreducible (\texttt{v312}).
\end{itemize}

\subsection*{2026-06-24 (A falsifiable clock probe of the frontier: \texttt{v397} how external is the ``external physics''?)}
\begin{itemize}
\item \textbf{\texttt{v397} (\texttt{FR.CLOCK.PROBE.01}) --- do the ``external'' frontier scheme-numbers land on the
$\{2,3,5\}$ clock?} A falsifiable, anti-numerology probe (strict No-Free-Pattern, \vref{v100}: ``on the clock'' means
an \emph{exact} match, not a wide-band fit). \mE\ the $\eta_B$ decuple $A_\Lambda=10=|Z_2|\gcar$ is ON the clock
(\vref{v212}); \mE\ the Koide rate $(2/3)^6=(|Z_2|/\Nfam)^6$ is ON the clock (\vref{v303}); \mE\ the axion spine angle
$\theta_i=\pi\Nfam/\gcar=3\pi/5$ is ON the clock (\vref{v211}/\vref{v373}); \mE\ the proton $C_p\sim2.83\pm0.15$ is
\emph{not} a discriminating clock value --- within its $\pm5.3\%$ band several simple values fit
($2^{3/2},17/6,14/5$), so by No-Free-Pattern it is declared EXTERNAL (the firewall \vref{v187}/\vref{v374} is correct
there). \mC\ verdict: $3$ of the $4$ frontier scheme-numbers land \emph{exactly} on the clock, so the irreducible
``external physics'' residue shrinks to essentially the proton's non-perturbative QCD number $C_p$. Cited in
\texttt{tfpt\_4\_frontier}; a falsifiable probe whose answer could have been ``none on the clock''; Python-only.
\end{itemize}

\subsection*{2026-06-24 (Clockwork coherence + an open question: \texttt{v394} primes $=$ atoms $=$ facets, and \texttt{RES.COXETER.SYMMETRY.01})}
\begin{itemize}
\item \textbf{\texttt{v394} (\texttt{COXETER.ATOMS.01}) --- the three Coxeter primes ARE the three anchor atoms ARE
the three number-field facets.} A bird's-eye \mE\ re-reading tying \vref{v390} (the prime facets) to the anchor
$a=(1,1,2)$ and \vref{v319} (the $5\times6$ clock). \mE\ $a=(1,1,2)$ has $e_3{=}2{=}|Z_2|$, $p_0{=}3{=}\Nfam$,
$e_2{=}5{=}\gcar$, product $2{\cdot}3{\cdot}5=30=h(E_8)$ --- the clock's primes \emph{are} the anchor's atoms.
\mE\ atoms $=$ facet fields (\vref{v390}): $2{\to}\mathbb Q(i)$, $3{\to}\mathbb Q(\sqrt{-3})$, $5{\to}\mathbb Q(\sqrt5)$,
each ramified at its prime. \mE\ the QG susceptibility is pure $\{2,3\}$: $\chi=1/(1{-}(2/3)^6)=729/665=3^6/(3^6{-}2^6)$,
$(2/3)^6=2^6/3^6$, exponent $6=2\Nfam$. \mE\ both dynamic rates carry prime-2: $2/3=|Z_2|/\Nfam$ and
$(\varphi{+}2)/4=(\varphi{+}2)/|\mu_4|$ with $|\mu_4|{=}4{=}2^2$. \mE\ $30=5{\times}6=\gcar(2\Nfam)$ (\vref{v319}).
\mC\ the prime-2 seam is the universal dynamical engine; prime-3 (family) and prime-5 (carrier golden) the two
attractors.
\item \textbf{\texttt{RES.COXETER.SYMMETRY.01} --- a new registered open research question.} Is the
prime-2-as-common-factor reading \emph{forced} (the seam involution provably in every sector's gap, no independent
prime-2 attractor), or is there a residual asymmetry? Resolving it would either tighten \vref{v383}'s ``every sector
is the same gapped operator'' to ``the same \emph{seam-driven} operator'' (with the falsifiable corollary that no
prime-2-only attractor exists), or reveal a missing dynamical slot. Tracked in \texttt{tfpt\_research\_contracts};
a question, not a claim. Cited in \texttt{origin\_theory}; Python-only.
\end{itemize}

\subsection*{2026-06-24 (Correction error-bars: \texttt{v393} the typed budget as actual first-correction magnitudes)}
\begin{itemize}
\item \textbf{\texttt{v393} (\texttt{CORRECTIONS.NUMERIC.01}) --- the typed correction budget (\vref{v388}) as actual
numbers.} The short-term, testable harvest of \vref{v388}: instead of merely typing each prediction's correction, this
gives the magnitude, so a parameter-free central value can be quoted as ``value $\pm$ computed first correction''.
\mE\ FIXED-POINT band (the $\varphi_0$-derived $\theta_{12},\theta_{13},\lambda_C,\beta_{\mathrm{rad}}$) $=$ the explicit
$\varphi_0$ puncture term $36c_3^4/c_3 = 9/(128\pi^3)\approx0.227\%$ (exact; $=\theta_{12}$'s $\varepsilon$
first-correction, $\varepsilon=(3/4)\varphi_0=c_3+36c_3^4$); \mE\ SEAM-GAPPED band (Koide $F_{\mathrm{pole}}$, recovery)
$=(2/3)^6\approx8.78\%$, the QG-decoupling bound capped by $\chi-1=64/665\approx9.62\%$ (\vref{v337}); \mE\
EXACT-IDENTITY band $=0$ structurally ($\det R=8$, $N_\Phi=1$, $\theta_{\mathrm{eff}}=0$); \mE\ EXTERNAL-RATE band $=$
external physics, quoted ($m_p/m_e\,{\pm}7.5\%$ \vref{v374}; $n_s/r$ the $N_\star{\in}[50,60]$ band; $\eta_B\,1.07\times$
\vref{v212}), fenced by \vref{v187}. \mC\ the assembled budget gives each prediction a computed theoretical-uncertainty
band. Cited in \texttt{origin\_theory}, mirrored on the website prediction surface; a harvest of \vref{v388}, no new
number; Python-only.
\end{itemize}

\subsection*{2026-06-24 (Attacking the last open lemma: \texttt{v392} the scaling-limit central charge \emph{converges})}
\begin{itemize}
\item \textbf{\texttt{v392} (\texttt{SEAM.S3.SCALINGLIMIT.01}) --- an honest attack on \texttt{SEAM.EQUIV.01}'s one
open lemma (continuum existence, \vref{v336}).} It does \emph{not} close \vref{v336} (the abstract existence is the
cited MMST theorem); it strengthens the case with the existence-relevant observable \vref{v376} did not test: that
the finite-size data \emph{converge}. \mE\ the Calabrese--Cardy entanglement slope $c_1(L)$ at $L=66,130,258,386,514$
is a monotone Cauchy-like sequence approaching $1$ ($|c_1(L)-1|$ strictly decreasing, $4.6\times10^{-4}\to7\times10^{-6}$);
\mE\ a $1/L$ Richardson fit extrapolates to $c_1(\infty)\approx1.000$, so the $16$-Majorana collar $c=8c_1\approx8.00
=\gcar{+}\Nfam$ is reached \emph{in} the limit; \mE\ the successive differences are themselves strictly decreasing
(a numerical Cauchy sequence). \mO\ convergent data are evidence, not a proof of existence (the cited MMST theorem,
\vref{v336}), and do not pin $(E_8)_1$ over the same-$c$ $SO(16)_1$ (the holomorphy discriminator, \vref{v377}/\vref{v378}).
Strengthens the residual, does \emph{not} close it. Cited in \texttt{tfpt\_research\_contracts}; Python-only.
\end{itemize}

\subsection*{2026-06-24 (Lean 4: \texttt{FORM.SPECTRALGAP.01} extended to the finite-dimensional Perron--Frobenius case)}
\begin{itemize}
\item \textbf{\texttt{FORM.SPECTRALGAP.01} --- the multi-dimensional case, reduced to the scalar core.} The Lean
module \texttt{TfptCarrier/SpectralGapAttractor.lean} now also proves the \emph{finite-dimensional} gapped-operator
statement (\texttt{lake build} OK, no \texttt{sorry}): \mE\ \texttt{component\_tendsto} (a non-dominant eigencomponent
$|r|<1$ decays, $r^n c\to0$); \mE\ \texttt{deviation\_tendsto} (with the dominant eigenvalue normalised to $1$, the
deviation vector --- all non-dominant components --- tends to $0$, so the iterate converges to the dominant
eigendirection, the unique attractor, for any start); \mE\ \texttt{deviation\_unique} (two starts give deviation
vectors both $\to0$, so the selected eigendirection is independent of the start --- parameter-freeness in finite
dimensions); \mE\ \texttt{flavor\_deviation\_tendsto} (a concrete instance on the cusp-transfer spectrum
$\{1,(2/3)^6,(1/3)^6\}$, \vref{v56}/\vref{v82}/\vref{v383}). Honest scope: this is the finite-dimensional
\emph{diagonalisable} case (the genuine multi-dimensional content, reduced to the scalar core); the general
non-diagonalisable / infinite-dimensional Perron--Frobenius theorem stays the cited statement. Referenced in
\texttt{origin\_theory}.
\end{itemize}

\subsection*{2026-06-24 (Website: an animated ``Universal Gap Lab'' visualising \texttt{v383}--\texttt{v391})}
\begin{itemize}
\item \textbf{Website --- the \texttt{UniversalGapLab} animation on \texttt{/verification}.} A new client
component (Framer Motion, no new dependency) with three linked, module-grounded views: (A) every sector as the
gap contraction $\mathrm{iter}_n=x_\star+r^n(x_0-x_\star)$ racing to its attractor at $r=(2/3)^6$ (seam-gapped,
\vref{v303}/\vref{v387}/\vref{v388}) or the golden $(\varphi+2)/4$ (\vref{v312}), with a gapless $r=1$ track that
never forgets its start (the Lean theorem \texttt{FORM.SPECTRALGAP.01}) --- the rate \emph{is} the first-correction
size (\vref{v388}); (B) the entire-form-factor graviton ratio $e^{-u}$ falling faster than any power, ghost-free and
UV-soft (\vref{v386}/\vref{v389}); (C) the residual matrix as certification, not construction --- every open item
external, zero open internal mechanisms (\vref{v384}). Mirror-only: every number is grounded in a module; no theory
change.
\end{itemize}

\subsection*{2026-06-24 (Honest attempt at an external target: \texttt{v391} reduces it, not a closure)}
\begin{itemize}
\item \textbf{\texttt{v391} (\texttt{ALPHA.QUILLEN.PROGRESS.01}) --- an honest attempt at the external target
\texttt{ALPHA.QUILLEN.EXACT.01} (\vref{v382}, door~5).} It REDUCES the open step to a sharper named sub-target via a
solvable model but does \emph{not} close it: \texttt{ALPHA.QUILLEN.EXACT.01} stays \mO\ (external math, type~A,
\vref{v384}). \mE\ a solvable model $\det_\zeta(-\partial_\tau^2+m^2)$ on a circle of circumference $\beta$ equals
$(2\sinh(\beta m/2))^2$, whose $m$-variation $\beta\coth(\beta m/2)=2/m+(\beta^2/6)m-(\beta^4/360)m^3+\dots$ is a closed
heat-kernel/Laurent series (the $m^3$ coefficient $-1/360$ verified). \mE\ so a $\zeta$-determinant's coupling-variation
is structured heat-kernel data, and \vref{v382}'s counterterm $8b_1\cthree^6$ (a Gauss--Bonnet heat-kernel power) is the
right \emph{kind} of object; the \vref{v382} split is re-verified at $\ainv=137.0359992$. \mE\ the reduction: the open
step now reduces to the named sub-target ``the seam $U(1)$ operator's Seeley--DeWitt coefficient $=8b_1\cthree^6$''.
\mO\ \emph{not closed}: the actual seam-operator $\zeta$-determinant proof stays open, and \texttt{SEAM.EQUIV.01}
continuum existence (MMST, \vref{v336}) stays the other external \mO; the value $\ainv$ stays \mE. An attempt that
reduces, does not close. Cited in \texttt{tfpt\_1\_architecture\_e8}; Python-only.
\end{itemize}

\subsection*{2026-06-24 (Lean 4: \texttt{FORM.SPECTRALGAP.01} formalises the scalar core of the universal spectral-gap principle)}
\begin{itemize}
\item \textbf{\texttt{FORM.SPECTRALGAP.01} --- a Lean 4 proof of the gap $\Rightarrow$ unique-attractor $\Rightarrow$
parameter-free core (door~4).} New module \texttt{TfptCarrier/SpectralGapAttractor.lean} (\texttt{lake build} OK,
no \texttt{sorry}, only the three standard kernel axioms), formalising the meta-theorem of \vref{v303}/\vref{v383}/\vref{v387}
at the one-dimensional reduction --- the affine gap contraction $x\mapsto x_\star+r(x-x_\star)$ with multiplier
$r=\lambda_2/\lambda_1$. \mE\ \texttt{iter\_sub}: the closed form $\mathrm{iter}_n-x_\star=r^n(x_0-x_\star)$ (general $n$);
\mE\ \texttt{iter\_tendsto}: $0\le r<1$ (the gap) $\Rightarrow\mathrm{iter}_n\to x_\star$ (the unique attractor);
\mE\ \texttt{starts\_agree}: two starts differ by $r^n(a-b)\to0$, so the attractor is independent of the initial state
(parameter-freeness); \mE\ \texttt{no\_gap\_no\_forget}: $r=1$ (no gap) leaves $\mathrm{iter}_n-x_\star=x_0-x_\star$ constant
--- the initial condition is then a free parameter, so the gap is exactly what removes it; \mE\ the seam rate $(2/3)^6$ and
the golden $(\varphi+2)/4=(5+\sqrt5)/8$ both lie in $[0,1)$. Honest scope: the scalar reduction (the contraction core
\vref{v303}/\vref{v383} iterate numerically); the full multi-dimensional Perron--Frobenius statement stays the cited theorem.
Referenced in \texttt{origin\_theory}; ledger row \texttt{FORM.SPECTRALGAP.01}.
\end{itemize}

\subsection*{2026-06-24 (Completing the Coxeter clock: \texttt{v390} the prime-2 (Gaussian / $\mathbb Z/4$-seam) facet of $30=2{\cdot}3{\cdot}5$)}
\begin{itemize}
\item \textbf{\texttt{v390} (\texttt{COXETER.PRIME2.01}) --- the prime-2 facet of the order-30 Coxeter clock.}
\vref{v383}/\vref{v387} named two number-field facets of the clock $30=2{\cdot}3{\cdot}5=h(E_8)$ --- the golden
$\varphi\in\mathbb Q(\sqrt5)$ (prime-5, carrier) and $(2/3)^6\in\mathbb Q$ (prime-3, family). This names the
\emph{prime-2} facet and identifies it with structure already in the theory: the Gaussian field $\mathbb Q(i)$, i.e.\
the CM point $\tau=i$ and the order-4 $\mu_4=\mathbb Z/4$ \emph{square} seam deck (\vref{v282}/\vref{v288}/\vref{v333}).
\mE\ $h(E_8)=30$ factors into exactly three primes; one quadratic facet field per prime, each ramified at its prime:
$\operatorname{disc}\mathbb Q(i)=-4$ (2 ramifies), $\operatorname{disc}\mathbb Q(\sqrt{-3})=-3$ (3 ramifies),
$\operatorname{disc}\mathbb Q(\sqrt5)=5$ (5 ramifies); the ramified primes are $\{2,3,5\}$ with product $30=h(E_8)$.
\mE\ the prime-2 (Gaussian) facet is the $\mathbb Z/4$ seam deck: min.\ poly $x^2+1$, $j(i)=1728=12^3$, $\tau=i$ fixed by
the modular $S$ of order $4=2^2$, $|\mu_4|=4=2^2$ --- the static, even, seam-orientation facet. \mC\ so the three primes
of the clock now each carry a facet (square/hexagon/pentagon $=$ seam/CP/carrier); the prime set $\{2,3,5\}$ is forced by
$h(E_8)=30$, not chosen. Cited in \texttt{origin\_theory}; a synthesis, no new number; Python-only.
\end{itemize}

\subsection*{2026-06-24 (Graviton loop finiteness: \texttt{v389} the entire form factor is UV-finite at the loop level by power counting)}
\begin{itemize}
\item \textbf{\texttt{v389} (\texttt{GRAV.LOOP.FINITE.01}) --- the entire-form-factor graviton is UV-finite at the \emph{loop} level.}
The honest next step past \vref{v386} (which established the tree amplitude), extending \vref{v304}/\vref{v370}/\vref{v380}/\vref{v386}
from the propagator to the superficial degree of divergence of loop graphs. This is the standard infinite-derivative /
nonlocal-gravity finiteness statement (Tomboulis; Biswas--Mazumdar--Siegel; Modesto), \emph{not} a full proof of
perturbative quantum gravity. \mE\ super-polynomial falloff: $p^k e^{-p^2/M^2}\to0$ for every degree $k$. \mE\ one dressed
line turns a quadratic divergence into the finite $(M^2/2)e^{-p_0^2/M^2}$, while the GR $\int p^3/p^2\,dp$ diverges
quadratically. \mE\ the superficial degree $\to-\infty$ at every loop order $L$ (the form factor multiplies the integrand by
$e^{-(\#\mathrm{internal})p^2/M^2}$; dressed cutoff-ratio $\to1$ vs GR $\to4$). \mE\ the regulator is the seam scale
$M=M_{\mathrm{scal}}=\cthree^{7/2}\Mbar$ (\vref{v253}/\vref{v259}), not a dial. \mC\mO\ loop \emph{unitarity} of the nonlocal
form factor (Lorentzian continuation / macro-causality, Pius--Sen / Briscese--Modesto) stays the honest open point --- tree
unitarity is \vref{v386}; not claimed solved. Cited in \texttt{tfpt\_4\_frontier}; Python-only.
\end{itemize}

\subsection*{2026-06-24 (Typed correction budget: \texttt{v388} the gap correction is keyed to the mechanism class, not a uniform band)}
\begin{itemize}
\item \textbf{\texttt{v388} (\texttt{CORRECTIONS.BUDGET.01}) --- the gap-driven correction (\vref{v387}) is a \emph{typed} budget.}
A machine-checked answer to ``does the $(\lambda_2/\lambda_1)^n$ correction apply to \emph{all} predictions?'' --- the
answer is \emph{no}, and for one whole class a band would be \emph{wrong}. Because the size is the distance from a
gapped operator's leading eigenvector, it is defined only where a subleading $\lambda_2$ exists, so the prediction
surface splits into four classes. \mE\ \emph{seam-gapped} (Koide $F_{\mathrm{pole}}$ \vref{v303}, recovery \vref{v221},
the QG bound capped by $\chi=729/665$ \vref{v337}): rate $(2/3)^6$; the discrete compiler: golden $(\varphi+2)/4$
(\vref{v312}). \mE\ \emph{exact identity} ($\det R=8$, $N_\Phi=1$, $\theta_{\mathrm{eff}}=0$, $\sin^2\theta_{13}=\varphi_0
e^{-5/6}$): no $\lambda_2$, so the correction is $0$ structurally and a band would contradict the \mE\ status. \mE\
\emph{external-rate} ($\eta_B$ washout, axion freeze, $m_p/m_e$ RG): the gapped \emph{shape} with an external rate ---
only $F_{\mathrm{pole}}$ has the seam rate (\vref{v303}), firewalled (\vref{v187}). \mE\ \emph{fixed-point}: the texture
is already explicit (e.g.\ $\sin^2\theta_{12}$, $\varepsilon=(3/4)\varphi_0=c_3+36c_3^4$). \mE\ the Koide first correction
(door~2): $F_{\mathrm{pole}}$ is the one seam-gapped prediction, rate $(2/3)^6\approx0.0878$ (\vref{v371}), the source
quotient $0.33\%$ below $2/3$ --- the rate is the suppression \emph{scale}, not the residual. \mC\ so a uniform band on
all predictions is wrong; the size is keyed to the mechanism class. A typing of \vref{v387} (as \vref{v384} is of
\vref{v383}); cited in \texttt{origin\_theory}; Python-only.
\end{itemize}

\subsection*{2026-06-24 (Harvesting the QFT/gravity machinery: \texttt{v385} the UV-branch kill-test surface, \texttt{v386} the graviton-exchange amplitude, \texttt{v387} the gap-driven correction calculus)}
\begin{itemize}
\item \textbf{\texttt{v385} (\texttt{UVBRANCH.KILLTEST.01}) --- the carrier-Pati--Salam UV branch on the all-order footing.}
A consolidation that ties the all-order EG/BRST closure (\vref{v381}) to the optional UV branch and computes the
one genuinely new thing: the \emph{proton-decay safety hierarchy}. \mE\ the carrier content is the SM with no new
states, so the SM-non-unification (\vref{v246}) is now all-order-robust; \mX\ the plain-SM 4D-GUT stays killed
($\sin^2\theta_W=3/8$ vs $0.231$); \mC\ the optional carrier-PS branch sits at $M_{PS}=\kappa M_{\mathrm{scal}}\approx
3\times10^{13}$ GeV ($\kappa\in[1.0,1.2]$, \vref{v253}); \mE\ minimal PS gauge bosons are $SU(4)$ leptoquarks that
mediate rare LFV ($K_L\to\mu e$), \emph{not} $p\to e^+\pi^0$, so the branch clears the binding bound by
$M_{PS}/M_{\mathrm{bound}}\sim10^7$ -- proton-safe, with \emph{no} fake $\tau_p$ window (\vref{v265}). Cited in
\texttt{tfpt\_5\_redteam}; Python-only.
\item \textbf{\texttt{v386} (\texttt{GRAV.AMPLITUDE.01}) --- the graviton-exchange amplitude is finite and UV-soft.}
Extends \vref{v304}/\vref{v370}/\vref{v380} from the propagator to the actual tree amplitude. \mE\ the dressed spin-2
propagator $e^{-p^2/M^2}/p^2$ has its only pole at $p^2=0$ (residue $1>0$, ghost-free), is exponentially softened in
the UV (the ratio $e^{-u}$ falls faster than any power) and reduces to GR $+$ a calculable $-p^2/M^2$ correction at
low energy ($M=M_{\mathrm{scal}}$, \vref{v253}); \mC\ a single positive-residue pole gives tree unitarity, so
perturbative graviton scattering $A\sim(T{\cdot}P_2{\cdot}T')e^{-p^2/M^2}/p^2$ is an explicit finite computation
(perturbative-only; \texttt{QG.AMB.01} stays a \mC\ redundancy, \vref{v369}). Cited in \texttt{tfpt\_4\_frontier};
Python-only.
\item \textbf{\texttt{v387} (\texttt{CORRECTIONS.GAP.01}) --- the gap-driven correction calculus.}
The practical harvest of \vref{v383}: the same spectral gap that makes a sector parameter-free also sets the
\emph{size} of its first correction ($\mathrm{correction}_n\sim(\lambda_2/\lambda_1)^n$). \mE\ flavor, horizon
recovery and the QG bound all share the $(2/3)^6$ rate (the family-$3$ facet; QG susceptibility
$\chi=729/665$), while the discrete compiler transient decays at the golden $(\varphi+2)/4$ (the carrier-$5$ facet)
--- the two number-field facets of \vref{v314}/\vref{v383}. \mC\ the gap does double duty (why no free parameter
\emph{and} how big the first correction), so sub-leading magnitudes are organised, not free. Cited in
\texttt{origin\_theory}; Python-only.
\end{itemize}

\subsection*{2026-06-23 (Bird's-eye synthesis: two new structural patterns --- \texttt{v383} the universal spectral-gap principle and \texttt{v384} the residual is certification, not construction)}
\begin{itemize}
\item \textbf{\texttt{v383} (\texttt{DYNAMICS.UNIVERSAL.01}) --- the universal spectral-gap / Perron--Frobenius principle.}
A fresh bird's-eye pass found that \emph{every} TFPT sector is the \emph{same} structural object: a gapped operator with
a \emph{unique} leading attractor (the physics) and a spectral gap (the reason there is no free parameter).
\vref{v303} named this only for $F_{\mathrm{transfer}}$; this module extends it to the sectors made parameter-free
\emph{after} it. \mE\ three gaps are computed --- the flavor transfer $\{1,(2/3)^6,(1/3)^6\}$ with gap $6\ln(3/2)$
(\vref{v56}/\vref{v82}); the affine-$E_8$ adjacency with Perron eigenvalue $2$ (Kac marks) and subleading
$2\cos(\pi/5)=\varphi$, gap $2-\varphi=1/\varphi^2$ (\vref{v312}/\vref{v313}); the decoupling margin
$\Delta_{\mathrm{eff}}\approx1.648$ (\vref{v76}/\vref{v337}). \mE\ the two number-field facets (\vref{v314}): golden
$\varphi\in\mathbb Q(\sqrt5)$ (carrier-5, static) and $(2/3)^6\in\mathbb Q$ (family-3, dynamic) are the prime-5 and
prime-3 facets of the order-30 Coxeter clock $30=2{\cdot}3{\cdot}5=h(E_8)$. \mC\ the other sectors are the same
structure --- gravity ($\delta S{=}0$ equilibrium, \vref{v358}/\vref{v359}), the QG measure (Gaussian saddle,
\vref{v365}), the boundary QFT (holomorphic $c{=}8$ RG fixed point, \vref{v157}/\vref{v158}), the all-order S-matrix
(adiabatic limit, \vref{v381}), recovery (Petz fixed point, \vref{v221}), $\tau{=}i$ (\vref{v333}). \mC\ the
meta-theorem: gapped $\Rightarrow$ unique attractor $\Rightarrow$ parameter-free, theory-wide. Cited in
\texttt{origin\_theory}; a synthesis (no new number), Python-only.
\item \textbf{\texttt{v384} (\texttt{RESIDUAL.CERTIFICATION.01}) --- the residual is certification, not construction.}
After \vref{v369}/\vref{v381}/\vref{v382} the \emph{kind} of every open item has shifted: there is \emph{no} open TFPT
physics mechanism left. A ledger-CI audit classifies every residual into exactly three external kinds: \mE\ (A)~external
math proof (\texttt{SEAM.EQUIV.01} continuum existence $=$ the cited MMST/Adamo theorem \vref{v336};
\texttt{ALPHA.QUILLEN.EXACT.01} \vref{v382}; \texttt{QG.AMB.01} the constructive measure, a \mC\ redundancy \vref{v369}),
\mE\ (B)~theorem-forbidden ($v_{\mathrm{geo}}$, the No-Unit theorem \vref{v153}/\vref{v364}), \mE\ (C)~external physics
($F_{\mathrm{transfer}}$, \vref{v371}--\vref{v374}, firewalled \vref{v187}). The two load-bearing facts are verified
(No-Unit dimensionlessness; the gap-decoupling margin $1.648>0$), and the count of open \emph{internal} TFPT mechanisms
is \textbf{zero}. \mC\ convergence: the only hard things left are theorems and external physics, not missing dynamics.
Cited in \texttt{tfpt\_research\_contracts}; an audit (no new number), Python-only.
\end{itemize}

\subsection*{2026-06-23 (External-review closure: the two genuine residual targets named --- \texttt{v381} the all-order Epstein--Glaser/BRST contract for $S_{\mathrm{pert}}$, and \texttt{v382} the Quillen determinant-line variation as a tracked target)}
\begin{itemize}
\item \textbf{\texttt{v381} (\texttt{QFT4D.EG.ALLORDER.01}) --- the all-order 4D perturbative-QFT closing statement.}
A mathematical-physics review of the QFT/TOE layers identified exactly one genuinely new, buildable item: the
\emph{all-order} Epstein--Glaser/BRST contract for the perturbative 4D S-matrix $S_{\mathrm{pert}}$ (the previous
documents had the $S_{\mathrm{pert}}$ skeleton and one-loop, \vref{v269}/\vref{v271}/\vref{v273}/\vref{v278}, but no
named all-order claim). This module types the standard causal-perturbation-theory closure for the TFPT finite
interaction class --- it does \emph{not} build a path integral. \mE\ power-counting: every gauge$+$matter vertex
(Yang--Mills $+$ Dirac--Yukawa $+$ Higgs $+$ ghost) is a mass-dimension-4 marginal operator, so the EG singular
order $\omega\le4$ and the counterterm space is finite at every order; \mE\ BRST nilpotency $s^2{=}0$ verified
exactly via the Jacobi identity for $su(2)$ and $su(3)$ (the carrier weak$+$colour content); \mE\ the seam gap
$\Delta=6\log\tfrac32>0$ (\vref{v302}) gives the IR-safe adiabatic limit. \mC\ the two heavy legs are imported
rigorous theorems --- all-order $T_n$ existence by causal factorisation (Epstein--Glaser 1973) and all-order BRST
invariance (Piguet--Sorella / Kugo--Ojima) --- applied to the TFPT class. Matter$+$gauge \emph{only}: the
$R^2$/Weyl$^2$ gravity sub-sector is the entire-form-factor resummation (\vref{v304}/\vref{v370}/\vref{v380}), and
$S_{\mathrm{pert}}$ is not the ambient measure \texttt{QG.AMB.01} (a \mC\ redundancy, \vref{v369}). NET \mC,
prerequisites \mE; not \mE\ and not a path integral. Cited in \texttt{tfpt\_5\_redteam} and \texttt{tfpt\_2}; Python-only.
\item \textbf{\texttt{v382} (\texttt{ALPHA.QUILLEN.EXACT.01}) --- the Quillen determinant-line variation, named as a target.}
Per the same review, the ``why \emph{this} $F_{U(1)}$ functional'' obligation (previously tracked only as
\texttt{EM.WARD.01}'s residual, \vref{v341}/\vref{v342}) is elevated to its own citable target:
$\delta_\tau(\log\det_\zeta\Delta_{U(1)}+8b_1\cthree^6\log\varphi_{\mathrm{seam}})=0$ on the determinant line over the
$\mu_4$ seam moduli. \mE\ the Quillen split holds at the $\ainv{=}137.0359992$ root with every coefficient a named
atom (index $8b_1$, heat-kernel $\cthree^{3,6}$, discriminant $q(D_5){+}q(A_3){=}2$); \mE\ the value stays closed
(\vref{v3}); \mO\ the from-first-principles exactness proof is the target. \mC\ it is a \emph{face} of
\texttt{SEAM.EQUIV.01} (\vref{v336}) --- the seam $U(1)$ determinant line lives on the same holomorphic net --- so it
adds \emph{no} second independent gate; it makes the existing residual trackable. No new number (reuses the
Wolfram-mirrored \vref{v341} identities). Cited in \texttt{tfpt\_1\_architecture\_e8}; Python-only.
\end{itemize}

\subsection*{2026-06-23 (Track 2 of the forward plan v2 --- the AMBIENT REDUNDANCY statement (\texttt{v369}): the holographic route to Gravity-complete that sidesteps building the general Euclidean QG measure)}
\begin{itemize}
\item \textbf{\texttt{v369} (\texttt{QGAMB.REDUNDANCY.01}) --- Track 2 (forward plan v2).} Instead of
constructing the non-perturbative ambient measure (the conformal-factor swamp, \vref{v332}/\vref{v334}), assemble
the established discriminators that prove the ambient sector carries \emph{no} physical degrees of freedom relative
to the holomorphic boundary algebra, so the QG measure (gate C7/\texttt{QG.AMB.01}) is a non-fundamental
\emph{certification} object (like a coordinate choice in GR), not missing dynamics. \mE\ holomorphy
$\Rightarrow$ $\mathrm{DHR}((E_8)_1)=\mathrm{Vec}$: $\#$primaries $=|\det\mathrm{Cartan}|=1$ for $E_8$ vs $4$ for
$SO(16)$ $\Rightarrow$ no nontrivial superselection charge a bulk could carry invisibly; \mE\ no torus
ground-state degeneracy ($|\det K|=1$); \mE\ finite Petz recovery rate $(2/3)^6$ (\vref{v221}); \mE\ the
gap-decoupling margin $\Delta_{\mathrm{eff}}=6\log\tfrac32-\tfrac{31}{4\pi^2}\approx1.648>0$ (\vref{v76}/\vref{v337}).
\mC\ with the Bisognano--Wichmann reconstruction map (\vref{v258}/\vref{v309}/\vref{v323}) the redundancy statement
$\mathcal O_{\mathrm{phys}}^{\mathrm{bulk}}/\mathrm{Diff}\cong\mathcal A_\Sigma^{\mu_4}$ is well-posed. \mO\ residual:
the two consumed premises --- \texttt{SEAM.EQUIV.01} (the S3 lattice input, \vref{v366}) and the BW intrinsicality
of the raw collar (\vref{v329}); it does \emph{not} construct \texttt{QG.AMB.01} but provides the
\emph{alternative} (holographic redundancy) route: Gravity-complete $=$ Boundary-complete $+$ Ambient-redundancy.
Cited in \texttt{tfpt\_research\_contracts}; Python-only.
\end{itemize}

\subsection*{2026-06-23 (Status propagation: the \texttt{v365}--\texttt{v380} $+$ \texttt{FORM.SEAM.MMST.01} status carried into the remaining papers, the \texttt{README} and the Zenodo description)}
\begin{itemize}
\item \textbf{Deep-sync of the post-S3 status.} The canonical surfaces (\texttt{tfpt\_status}, \texttt{introduction})
were already current; this pass propagated the same honest wording into \texttt{origin\_theory},
\texttt{tfpt\_1}--\texttt{tfpt\_5}, \texttt{tfpt\_research\_contracts}, the root \texttt{README.md}, the Zenodo
description and \texttt{website/lib/papers.ts}: \texttt{SEAM.EQUIV.01} is \emph{closed modulo a cited theorem}
(lattice \vref{v367}/\vref{v368} $+$ the $S_3$ stack \vref{v376}--\vref{v379} $+$ Lean \texttt{FORM.SEAM.MMST.01};
residual \mO\ $=$ the cited MMST/OS existence only); \texttt{QG.AMB.01} is a \mC\ \emph{redundancy} (\vref{v369}/\vref{v379}),
a certification object not missing dynamics; perturbative graviton unitarity is established (the Stelle ghost is a
Seeley--DeWitt truncation artefact, \vref{v304}/\vref{v370}/\vref{v380}); and the frontier transfers are typed runnable
solvers with kill tests (\vref{v371}--\vref{v374}) $+$ the observatory CI (\vref{v375}). No new claim --- a wording
propagation so every surface matches the ledger; \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-23 (\texttt{v380} --- the KMS Entire Hessian: the Stelle ghost is EXACTLY the Seeley--DeWitt truncation, and resummation pushes it to infinity)}
\begin{itemize}
\item \textbf{\texttt{v380} (\texttt{GRAV.KMS.HESSIAN.01}).} Upgrades \vref{v304}/\vref{v370} from the
\emph{assumption} ``the resummed graviton form factor is entire'' to a derived statement. \mE\ the seam KMS
cutoff $f(u){=}e^{-u}$ (\vref{v259}) gives the dressed spin-2 propagator $e^{-p^2/M^2}/p^2 = 1/(p^2 a)$ with
$a(u){=}e^u$ entire and nowhere zero (only the $p^2{=}0$ pole). \mE\ each finite Seeley--DeWitt truncation is a
Taylor partial sum of $a$ and carries a Stelle-ghost zero ($T_1{=}1{+}u\to u{=}-1$; $T_2\to-1{\pm}i$); the
entire $a$ has none. \mE\ the modulus of the nearest truncation-zero grows monotonically with the order
($1,1.41,\dots,3.07$ for $n{=}1..8$) $\to\infty$ --- the ghost decouples, ``entire'' $=$ ``do not truncate''.
\mC\ $\Rightarrow$ perturbative graviton unitarity; \mO\ the exact off-shell curved-space Hessian
identification is the cited heat-kernel resummation, perturbative-only. Cited in \texttt{tfpt\_5\_redteam}
(Target F); Python.
\end{itemize}

\subsection*{2026-06-23 (Lean: the S3 continuum leg formalised as ``closed modulo a cited theorem'' --- \texttt{FORM.SEAM.MMST.01})}
\begin{itemize}
\item \textbf{\texttt{FORM.SEAM.MMST.01} --- Lean 4 formalisation.} The S3 continuum leg is now
machine-formalised in a new module (\texttt{SeamScalingLimit.lean}), lake build OK and \texttt{\#print axioms}
clean, in the audit-contract style of \texttt{SeamEquivChain.lean}. The MMST applicability hypotheses for the seam collar
are \emph{provable} by kernel \texttt{decide} (no axioms): $D = 16$, $\operatorname{rank} = c = 8$, the range
$8 \le 8 \le 16$, $c_- = 8 \neq 0$, and $\det K = 1$ vs $SO(16)$'s $4$. The MMST scaling-limit theorem (CMP 2022) and
the Adamo--Moriwaki--Tanimoto OS reconstruction (2024) are \emph{named cited axioms}; the conclusion
$(E_8)_1$ follows by a well-typed composition whose residual (\texttt{\#print axioms}) is exactly those two
published theorems plus the carrier gap --- no hidden assumption, no \texttt{sorry}. Mirrors the S3 closure
stack \texttt{v376}--\texttt{v379}; so \texttt{SEAM.EQUIV.01} is now ``closed modulo a cited theorem'', the
honest formalisation ceiling. Cited in \texttt{tfpt\_research\_contracts}; \texttt{lean\_manifest} refreshed.
\end{itemize}

\subsection*{2026-06-23 (S3 closure stack --- the target of the seam scaling limit pinned at EVERY computable level: central charge $c{=}8$ from the lattice (\texttt{v376}), the $(E_8)_1$ character (\texttt{v377}), the genus-1 torus count $=1$ (\texttt{v378}), and reflection positivity (\texttt{v379}); only the abstract continuum existence (cited MMST) stays external)}
\begin{itemize}
\item \textbf{\texttt{v376} (\texttt{SEAM.S3.CENTRALCHARGE.01}).} The Calabrese--Cardy finite-size
entanglement-entropy scaling of the critical free-fermion content gives $c=1.0000$ per complex mode
(Peschel correlation-matrix EE; the $L{=}4m{+}2$ sizes avoid the half-filling zero-mode), so the
16-Majorana ($=8$ complex) collar has $c=8=\gcar{+}\Nfam$, chiral ($c_-{=}8$, \vref{v367}/\vref{v368}).
Numerical $c{=}8$ from the lattice. Python (numpy).
\item \textbf{\texttt{v377} (\texttt{SEAM.S3.E8CHARACTER.01}).} The exact affine character
$\chi = E_4/\eta^8 = q^{-1/3}(1 + 248q + 4124q^2 + \dots)$ gives $c = 8$ and 248 level-1 currents (one
primary); the $\mu_4$/GSO promotion $248 = 240 + 8 = 120 + 128$ ($240 = 16{\cdot}5{\cdot}3$) pins $(E_8)_1$
over the same-$c$ rival $SO(16)_1$ (120 currents, 4 primaries). Python (sympy q-series).
\item \textbf{\texttt{v378} (\texttt{SEAM.S3.MODULAR.01}).} The genus-1 discriminator: KLM condensation
$\mu(\text{carrier}){=}16\to\mu(E_8){=}16/4^2{=}1$, $|\det\mathrm{Cartan}(E_8)|{=}1$ vs $D_8{=}4$, and the
single character's modular $T$-eigenvalue $e^{-2\pi i/3}$ give torus ground-state degeneracy 1 (holomorphic
$=(E_8)_1$) --- the ``hard part'' \vref{v344} isolated. Python (sympy).
\item \textbf{\texttt{v379} (\texttt{SEAM.S3.RP.01}).} Reflection positivity (the OS axiom) of the explicit
gapped collar: the positive spectral measure makes the Hankel/reflection Gram matrix PSD (a ghost mode
breaks it). With $c{=}8$ $+$ $(E_8)_1$ in hand, the OS inputs are complete and C7/\texttt{QG.AMB.01} is then
discharged by the redundancy theorem \vref{v369}. Python (numpy).
\item \textbf{Net:} S3 is the master key --- on the explicit lattice model the target net $(E_8)_1$ is pinned
exactly (central charge, character, genus-1 count, RP); the only remaining residual is the abstract
\emph{continuum existence} of the scaling limit (the cited MMST theorem \vref{v336}), which lives outside the
computational suite. Cited in \texttt{tfpt\_research\_contracts}.
\end{itemize}

\subsection*{2026-06-23 (Track 4 --- the prediction OBSERVATORY: a status-typed CI over the frozen prediction registry that makes the falsifiability surface machine-checkable, with a live data scorecard (\texttt{v375}))}
\begin{itemize}
\item \textbf{\texttt{v375} (\texttt{OBSERVATORY.REGISTRY.01}).} A CI over \texttt{freeze\_file.csv}: \mE\ every
prediction carries a kill criterion (falsifiability complete, no orphan claims); \mE\ the headline values
re-derive from $\{\phiz\}$ ($\sin^2\theta_{12}{=}1/3{-}\phiz/2$, $\sin^2\theta_{13}{=}\phiz e^{-5/6}$,
$\beta_{\mathrm{rad}}{=}\phiz/(4\pi)$); \mC\ a live scorecard records $\theta_{12}$ vs the JUNO first run
($0.28\sigma$, compatible), $\theta_{13}$ vs NuFIT~6.0 NO ($2.0\sigma$, the flagged most-tensioned core
prediction), $\beta_{\mathrm{rad}}$ vs ACT~DR6 ($0.37\sigma$, a hint), $r<0.036$ (compatible). Tooling that
makes the closed pieces usable and the open ones honestly fenced; no new physics. Cited in
\texttt{tfpt\_5\_redteam}; Python (stdlib).
\end{itemize}

\subsection*{2026-06-23 (Track 3 --- the $F_{\mathrm{transfer}}$ functor promoted from contracts to TYPED runnable solvers with kill tests: Koide source$\to$pole (\texttt{v371}), $\eta_B$ Boltzmann (\texttt{v372}), axion finite-$T$ relic (\texttt{v373}), $m_p/m_e$ uncertainty budget (\texttt{v374}))}
\begin{itemize}
\item \textbf{\texttt{v371} (\texttt{FR.POLE.SOLVE.01}).} A clean \emph{negative}: standard QED/EW running cannot
be the Koide source$\to$pole transfer (it pushes $Q$ above $2/3$; the required $\epsilon$ is negative while
QED's is positive), so the transfer is the non-QED $53/54$ operator / $(2/3)^6$ Moebius generator
(\vref{v183}/\vref{v82}). \mC, plain running excluded as the kill. Python (numpy$+$scipy).
\item \textbf{\texttt{v372} (\texttt{FR.BOLTZMANN.SOLVE.01}).} The integrated Buchmueller--Di Bari--Pluemacher
Boltzmann ODE at the TFPT-frozen $M_1{=}M_{\mathrm{scal}}(\phiz)^2/A_\Lambda$ (\vref{v212}) gives $\eta_B$ within a
factor ${\sim}1.1$ of $6.1{\times}10^{-10}$ with no $M_R$ dial; replaces the \vref{v326} toy washout. \mC/\mX.
\item \textbf{\texttt{v373} (\texttt{FR.RELIC.SOLVE.01}).} The finite-$T$ axion misalignment ODE decides the
branch: the frozen spine angle $3\pi/5$ gives $\Omega_a h^2{\sim}0.12$ (in $[0.08,0.16]$, lands on
$\Omega_{\mathrm{DM}}$ untuned) while the hilltop $170^\circ$ over-produces (${\sim}5.4\times$); replaces the
\vref{v326} toy. \mC/\mX (lattice $\chi(T)$ input).
\item \textbf{\texttt{v374} (\texttt{FR.QCD.BUDGET.01}).} The $m_p/m_e$ uncertainty budget: with $b_3{=}-7$
\mE\ and the two declared externals ($\alpha_s(M_Z)$, $C_p$, ${\sim}5.3\%$ each), the central ${\sim}1824$
(\vref{v262}) carries a propagated ${\pm}7.5\%$ band $[\sim1690,\sim1960]$ CONTAINING $1836.15$; lattice
tightening is the kill. The falsifiability companion to \vref{v262}; \mC.
\end{itemize}

\subsection*{2026-06-23 (Track 1 --- the S3 input made CONCRETE: an explicit gapped chiral-Majorana ($p{+}ip$) lattice model with numerical Chern $|C|{=}1$ realises the $c_-{=}8$ edge (\texttt{v367}), and a strip shows the chiral edge exists by anomaly inflow (\texttt{v368}))}
\begin{itemize}
\item \textbf{\texttt{v367} (\texttt{SEAM.S3.LATTICE.01}) --- Track 1.} The abstract S3 residual of
\vref{v356}/\vref{v366} (``the collar realised as a genuine lattice chiral free-fermion invertible phase'')
is turned into a RUNNABLE model. \mE\ the $p{+}ip$ Bloch model is gapped at $M{=}1$ with a numerically
computed Fukui--Hatsugai--Suzuki Chern number $|C|{=}1$ ($C{=}0$ trivially at $M{=}3$); \mE\
$N_{\mathrm{Maj}}{=}\dim S^+{=}16$ copies give $c_-{=}16/2{=}8{=}\gcar{+}\Nfam$, with the edge K-matrix
$SO(16)_1$ ($\det 4$) $\to(E_8)_1$ ($\det 1$) by the order-4 $\mu_4$ clock (\vref{v351}/\vref{v369}). \mC\ the
$\mu_4$ condensation (\vref{v154}/\vref{v351}); \mO\ the continuum scaling-limit existence (MMST, \vref{v336})
stays open. Cited in \texttt{tfpt\_research\_contracts}; Python (numpy + sympy).
\item \textbf{\texttt{v368} (\texttt{SEAM.S3.INFLOW.01}) --- Track 1.} The bulk-edge / anomaly-inflow leg (S4)
made concrete on the \vref{v367} model: \mE\ a finite strip has an edge-localised in-gap chiral branch
($\min_{k_x}|E|\sim0$) in the topological phase and a clean gap in the trivial phase (neg control); \mE\
bulk-edge correspondence gives one chiral Majorana per edge ($c_-{=}8$). \mC\ so by anomaly inflow the chiral
edge EXISTS as a consequence of the invertible bulk, discharging the \vref{v336}/\vref{v351} ``does the edge
exist?'' residual on the lattice. \mO\ the continuum scaling limit stays open. Cited in
\texttt{tfpt\_research\_contracts}; Python (numpy).
\end{itemize}

\subsection*{2026-06-23 (Track 2 --- perturbative graviton unitarity sector-by-sector: the Barnes--Rivers spin decomposition localises the Stelle ghost in the spin-2 sector, cured by the entire KMS form factor; the spin-0 mode by the GHP contour (\texttt{v370}))}
\begin{itemize}
\item \textbf{\texttt{v370} (\texttt{GRAV.SPIN2.UNITARITY.01}) --- Track 2.} Extends \vref{v304} (the scalar
$1/(p^2(p^2{+}M^2))$ pole algebra) to the actual tensor spin structure. \mE\ the Barnes--Rivers projectors are
complete ($\operatorname{tr}P_2{=}(d{-}2)(d{+}1)/2$, $\operatorname{tr}P_1{=}d{-}1$,
$\operatorname{tr}P_{0s}{=}\operatorname{tr}P_{0w}{=}1$ sum to $d(d{+}1)/2$; $d{=}4$ split $5{+}3{+}1{+}1{=}10$),
the EH propagator is $P_2/p^2-\tfrac1{d-2}P_{0s}/p^2$, and the Stelle ghost is a \emph{spin-2} state. \mE\ the
entire KMS form factor $e^{p^2/M^2}$ (\vref{v304}/\vref{v259}) makes the spin-2 sector ghost-free; \mC\ the
wrong-sign spin-0 conformal mode (\vref{v332}) is cured separately by the GHP contour (\vref{v334}). \mC\ so the
full \emph{perturbative} graviton is ghost-free sector-by-sector (conditional on \vref{v304}'s entire-analyticity
assumption). \mO\ residual: perturbative-only $+$ the open analyticity assumption; not the non-perturbative
measure. \mO\ DECLINE: $\operatorname{tr}P_2{=}5$ is dimension counting, not $\gcar$ (\vref{v354}/\vref{v355}).
Cited in \texttt{tfpt\_5\_redteam} (Target F); Python-only.
\end{itemize}

\subsection*{2026-06-23 (Directions 3 \& 7 --- the two hard functional-analysis residuals ADVANCED: the QG measure as one-loop fluctuations around the parameter-free saddle (\texttt{v365}), and the seam collar verified IN MMST's free-fermion class so the scaling limit is $(E_8)_1$ (\texttt{v366}))}
\begin{itemize}
\item \textbf{\texttt{v365} (\texttt{QGAMB.SADDLE.01}) --- Direction 3.} With the parameter-free saddle
(\vref{v358}/\vref{v359}) the QG \emph{measure} (gate C7/\texttt{QG.AMB.01}) organises as a one-loop Gaussian
fluctuation determinant. \mE\ the fluctuation stiffness is $1/\cthree=8\pi$ (no free dial, so the one-loop
problem is now well-posed); \mE\ the fluctuation operator is gapped
$M\ge\Delta_{\mathrm{eff}}=6\log\tfrac32-\tfrac{31}{4\pi^2}\approx1.648>0$ (\vref{v76}/\vref{v337}) $\Rightarrow$
mode-by-mode convergence, finite model log-det $\operatorname{Tr}'\log M=6\log\tfrac92$; \mC\ the conformal mode
converges on the GHP contour (\vref{v334}); \mE\ the admissible projective limit exists ($\chi=729/665$,
\vref{v330}) with $0$ new dials (\vref{v364}). \mO\ residual: the full non-perturbative projective limit on the
ambient sector. Sharpens C7 from ``diffuse full QG'' to a one-loop Gaussian problem around the parameter-free
saddle; does not close it. Cited in \texttt{tfpt\_research\_contracts}; Python-only.
\item \textbf{\texttt{v366} (\texttt{SEAM.MMST.INCLASS.01}) --- Direction 7.} The seam collar is verified IN
MMST's free-lattice-fermion scaling-limit class hypothesis-by-hypothesis: \mE\ $D{=}\dim S^+{=}16$ Majoranas,
$c{=}\gcar{+}\Nfam{=}8$, $\operatorname{rank}E_8{=}8$ so $\operatorname{rank}\le c\le D$ is $8\le8\le16$ (in
range); \mE\ gapped ($\Delta{=}6\log\tfrac32{>}0$, derived \vref{v302}); \mC\ quasi-free CAR class
(\vref{v155}/\vref{v160}); \mE\ chiral ($c_-{=}D/2{=}8\neq0$). \mC\ the MMST scaling-limit theorem then applies,
and \mE\ the order-$4$ $\mu_4$ clock pins the target to $(E_8)_1$ ($\det K{=}1$ vs $SO(16)$ $\det K{=}4$,
\vref{v351}). \mO\ residual: the single S3 input (the collar as a genuine lattice chiral invertible phase, the
seam one-sidedness, \vref{v297}/\vref{v356}). Reduces the continuum side of \texttt{SEAM.EQUIV.01} to one named
input; ADVANCES, does not close. Cited in \texttt{tfpt\_research\_contracts}; Python-only.
\end{itemize}

\subsection*{2026-06-23 (Consistency pass: the parameter-free \emph{full covariant} Einstein equation (\texttt{v358}/\texttt{v359}) propagated across ALL stale paper and website surfaces; new \texttt{v359} keybox; homepage gravity animation)}
\begin{itemize}
\item \textbf{Deep-sync of the parameter-free gravity status.} A cross-surface audit found several
documents and website components still framing gravity as ``exact only in the $R+R^2$ regime'' or the
metric-sector field equation as ``open''. These were reconciled with the canonical post-\vref{v358}/\vref{v359}
status: the \emph{local} covariant field equation $G_{ab}+\Lambda g_{ab}=\cthree^{-1}T_{ab}$ is
PARAMETER-FREE (both coefficients fixed); what remains open is the Jacobson equation-of-state status, the
global ambient measure (\texttt{QG.AMB.01}/C7), and the single unit $v_{\mathrm{geo}}$. Touched:
\texttt{introduction}, \texttt{tfpt\_2\_standard\_model}, \texttt{tfpt\_3\_e8\_audit\_bootstrap},
\texttt{tfpt\_4\_frontier} (summary table), \texttt{tfpt\_research\_contracts}, \texttt{origin\_theory}.
\item \textbf{New \texttt{v359} keybox} added to \texttt{tfpt\_research\_contracts} (full covariant equation:
fixed-volume $\Rightarrow$ Einstein tensor, Lovelock $\Rightarrow$ conservation an output); the \vref{v358}
residual corrected from ``linear$\to$nonlinear'' (stale --- \vref{v359} closed it) to the
equation-of-state\,$+$\,C7\,$+\,v_{\mathrm{geo}}$ residual, including the generated script index
(\texttt{script\_registry.csv}).
\item \textbf{Website.} The \texttt{GravityEmergence} animation (three origins of $\cthree$ converging to
$1/(8\pi)$; the parameter-free Einstein equation) was updated to the full covariant result and surfaced as a
dedicated homepage section (\texttt{/\#gravity}); gravity-status wording aligned across
\texttt{ReconstructionChain}, \texttt{VerificationDag}, \texttt{StatusMatrix}, \texttt{WhatTfptClaims},
\texttt{ThreeDecoderMap}, \texttt{StatusPyramid}, \texttt{papers.ts}, \texttt{glossary.ts} and the review page.
\end{itemize}

\subsection*{2026-06-23 (Direction 6, $v_{\mathrm{geo}}$ sharpened: after the parameter-free gravity, the \emph{gravity} sector adds NO new dimensionful input either, so $v_{\mathrm{geo}}$ is the SINGLE dimensionful input of the complete theory --- final tally $\{v_{\mathrm{geo}},\pi\}$, ZERO dimensionless dials: \texttt{v364})}
\begin{itemize}
\item \textbf{\texttt{v364} (\texttt{VGEO.SHARPEN.01}) --- Direction 6.} The No-Unit Theorem (\vref{v153}) already made
$v_{\mathrm{geo}}$ a forced metrology primitive. \mE\ The SHARPENING after the parameter-free gravity
(\vref{v358}/\vref{v359}/\vref{v361}): the Einstein coefficient $1/\cthree=8\pi$ and the $\Lambda$ prefactor
$(8\pi)^2{\cdot}48\cthree^4=3/(4\pi^2)$ are dimensionless, so $1/G\sim v_{\mathrm{geo}}^2$ and
$\Lambda\sim(\text{dimensionless})\,v_{\mathrm{geo}}^4$ reduce to $v_{\mathrm{geo}}$ times atoms --- the gravity sector
adds no new scale. \mE\ FINAL TALLY: every dimensionful quantity $=$ (a dimensionless ratio)$\times$(a power of
$v_{\mathrm{geo}}$); TFPT's free content is $\{v_{\mathrm{geo}},\pi\}$ with ZERO dimensionless dials, a ${\sim}26\to1$
reduction vs the SM. \mO\ $v_{\mathrm{geo}}$ stays irreducibly primitive (No-Unit; $1/G$ UV-sensitive, Sakharov
\vref{v68}). Direction 6 is clarity --- the last dimensionful anchor named and shown to be the only one. Cited in
\texttt{tfpt\_research\_contracts}; Python-only.
\end{itemize}

\subsection*{2026-06-23 (Direction 5, the matter--gravity backreaction: the carrier's gravitational anomaly is forced $c_-{=}8$, and the matter vacuum-energy backreaction is finite ($\to$ the forced $\Lambda$ from $\alpha$, not $M_{\mathrm{Pl}}^4$) --- the loop closes; no new SM-quantum-number read-out (declined): \texttt{v361})}
\begin{itemize}
\item \textbf{\texttt{v361} (\texttt{GRAV.BACKREACT.01}) --- Direction 5.} With the parameter-free equation (\vref{v359})
and the explicit J3 flux (\vref{v358}), the backreaction of TFPT's carrier matter is computed. \mE\ the carrier's
gravitational anomaly is forced: $c_-=16/2=8=\gcar{+}\Nfam$ (the chiral central charge of the $16$-Majorana content).
\mE\ the backreaction is FINITE $\to\Lambda$ from $\alpha$: the matter vacuum energy through $G_{ab}=\cthree^{-1}T_{ab}$
is gap-suppressed (Decoupling Thm \vref{v337}) to $\rho_\Lambda/\Mbar^4=(3/(4\pi^2))e^{-2\alpha^{-1}}$ (\vref{v60}),
the $123$ orders $=119.03+3.92$ --- \emph{not} the $M_{\mathrm{Pl}}^4$ catastrophe; the loop (\vref{v359}$+$\vref{v60}
$+$ the carrier vacuum) closes. \mE\ J3 explicit: $\delta\langle K_B\rangle=(8\pi^2R^4/15)\delta\langle T_{00}\rangle$,
carrier $T_{ab}=$ the SM's (\vref{v159}). \mC\ the SM trace anomaly is reproduced (content $=$ SM). \mO\ DECLINE: no
new atom-forced read-out of individual SM quantum numbers beyond $c_-{=}8$ and $\Lambda$ --- per \vref{v354}/\vref{v355}
declined. The backreaction is finite and consistent, adding no new dial. Cited in \texttt{tfpt\_4}; Python-only.
\end{itemize}

\subsection*{2026-06-23 (Direction 2, the disciplined result: the gap-induced GR correction is the known $R^2$ scalaron --- already falsifiable via $n_s/r$; a \emph{new} forced near-term deviation does NOT survive the discriminator and is declined: \texttt{v360})}
\begin{itemize}
\item \textbf{\texttt{v360} (\texttt{GRAV.GAPCORR.01}) --- Direction 2, run honestly.} Does the seam transfer gap
$\{1,(2/3)^6,(1/3)^6\}$ yield a NEW, calculable, FORCED deviation from GR (a near-term kill test) beyond the known
$R^2$ scalaron? With the \vref{v354}/\vref{v355} discriminator the answer is \emph{no}, and this is recorded rather
than manufacturing a coefficient. \mE\ the leading higher-curvature term IS the $R^2$ scalaron (spectral-action
$a_4{=}R^2/72$, \vref{v36}; $M_{\mathrm{scal}}^2/\Mbar^2=\cthree^7$, exponent $7{=}\gcar{+}\Nfam{-}1$) --- the
calculable beyond-Einstein correction, already in TFPT. \mC\ it is the entanglement-equilibrium NEXT order (the Wald
first law $\to f(R){=}R{+}R^2$, \vref{v28}/\vref{v359}). \mE\ it is ALREADY falsifiable via $n_s{=}1{-}2/N_\star$,
$r{=}12/N_\star^2$ (live CMB-S4 kill test). \mE\ the gap $\Delta{=}6\ln\tfrac32$ is a dimensionless rate, so a
distinct gap-induced curvature$^2$ term sits at $\xi\,v_{\mathrm{geo}}\sim$ the seam/Planck scale (not near-term
observable). \mO\ DECLINE: a new dimensionless coefficient is not atom-forced (the scalaron exponent $7{=}g{+}N{-}1$
and the gap exponent $6{=}2\Nfam$ are different; $\cthree^7$ and $(2/3)^6$ unrelated) --- per \vref{v354}/\vref{v355}
declined. Direction 2 yields no new near-term forced prediction; the answer is the existing scalaron. Cited in
\texttt{tfpt\_4}; Python-only.
\end{itemize}

\subsection*{2026-06-23 (the FULL covariant Einstein equation, parameter-free: the fixed-volume entanglement equilibrium gives $G_{ab}+\Lambda g_{ab}=\cthree^{-1}T_{ab}$ with BOTH coefficients TFPT-fixed ($8\pi=1/\cthree$ from \texttt{v358}, $\Lambda$ from $\alpha$ via \texttt{v60}); B6 closed at the local level: \texttt{v359})}
\begin{itemize}
\item \textbf{\texttt{v359} (\texttt{GRAV.NONLINEAR.01}) --- Direction 1, the full covariant equation.} Extends \vref{v358}
from the linearised (fixed-radius, Ricci-level) result to the FULL covariant equation. \mC\mE\ Jacobson 2015: demanding
stationarity of the small-ball entanglement entropy at fixed \emph{volume} brings in the EINSTEIN TENSOR $G_{ab}$
(not just $R_{ab}$) --- trace $g^{ab}G_{ab}=(1-d/2)R=-R$ in $d{=}4$, the structure that carries $\Lambda$. \mE\
Lovelock: $G_{ab}$ is the unique symmetric divergence-free second-order metric tensor, so $\nabla^a(G_{ab}+\Lambda
g_{ab})=0$ forces $\nabla^a T_{ab}=0$ --- conservation is an output. \mE\ coefficient 1: $8\pi G\to 8\pi=1/\cthree$
fixed (\vref{v358}). \mE\ coefficient 2: Jacobson leaves $\Lambda$ free, TFPT fixes it ---
$\rho_\Lambda/\Mbar^4=(3/(4\pi^2))e^{-2\alpha^{-1}}$, prefactor $(8\pi)^2{\cdot}48\cthree^4=3/(4\pi^2)$ (\vref{v60}); so
BOTH coefficients are TFPT-fixed, not free integration constants. \mC\ all timelike directions $\to$ the covariant
tensor equation; the matter side is the assembled CHM ball modular flux (\vref{v358}/\vref{v323}). NET: the original B6
``full covariant Einstein-side field equation'' is now PARAMETER-FREE at the local level. \mO\ residual: the Jacobson
equation-of-state status (not a from-action quantisation) $+$ the global ambient measure (C7/\texttt{QG.AMB.01},
separate, gap-decoupled); $v_{\mathrm{geo}}$ the one unit. Cited in \texttt{tfpt\_research\_contracts}; mirrored in
Wolfram (\texttt{303/303}). (\texttt{next-plan.md} Direction 4 folded in: the $\Lambda$ here matches the $\alpha$-readout.)
\end{itemize}

\subsection*{2026-06-23 (the classical gravity field equation, parameter-free: the entanglement first law $\delta S=\delta\langle K\rangle$ with TFPT's atoms gives the LINEARISED Einstein equation with $G$ from $\cthree$; the thermodynamic and geometric origins of $\cthree$ coincide via $|\mu_4|=|\Z_2|\chi=4$; the two formerly-open pieces (matter flux J3, entropy-density coefficient) closed/atom-fixed: \texttt{v358})}
\begin{itemize}
\item \textbf{\texttt{v358} (\texttt{GRAV.ENTROPY.EQUILIBRIUM.01}) --- the bridge to the dynamic world, instantiated on the
gravity side.} Carrying out the Jacobson-2015 / Faulkner-et-al.\ ``first law of entanglement $\Rightarrow$ Einstein
equation'' with TFPT's atoms. \mE\ PARAMETER-FREE COEFFICIENT: $\delta S=\delta\langle K\rangle$ gives
$G_{ab}=\cthree^{-1}T_{ab}$ with $\cthree^{-1}=8\pi$ fixed; all four $\cthree$-roles consistent (Unruh
$1/(2\pi){=}4\cthree$, EH $1/(16\pi){=}\cthree/2$, Einstein $8\pi{=}1/\cthree$, Bekenstein $1/4{=}1/|\mu_4|$) ---
no free dimensionless Newton dial. \mE\ THERMO $=$ GEO COINCIDENCE (new): the first law's coefficient $2\pi/\eta$
equals the geometric $|\Z_2|2\pi\chi$ iff $|\mu_4|=|\Z_2|\chi=4$ (\vref{v216}) --- the thermodynamic and geometric
origins of $\cthree$ are ONE. \mC\ J3 SOLVED: the CHM ball modular Hamiltonian (boost via BW, \vref{v323}) gives the
matter flux $\delta\langle K_B\rangle=\tfrac{8\pi^2R^4}{15}\delta\langle T_{00}\rangle$. \mE\ ENTROPY DENSITY
ATOM-FIXED: $1/4{=}1/|\mu_4|$ (\vref{v57}) $+$ central charge $c=\gcar{+}\Nfam=8$ (form \vref{v59}). \mO\ residual:
linear$\to$full non-linear (the original B6) $+$ the $v_{\mathrm{geo}}$ unit. Closes the LINEARISED Einstein
equation parameter-free; cited in \texttt{tfpt\_research\_contracts}; mirrored in Wolfram (\texttt{302/302}).
\end{itemize}

\subsection*{2026-06-23 (the two frontier walls attacked directly: Direction A assembles the continuum chain of \texttt{SEAM.EQUIV.01} theorem-by-theorem and ties its residual to the seam one-sidedness; Direction B was found ALREADY closed by \texttt{v40} (harmonic metric $=$ finite linear algebra, not a PDE): \texttt{v356})}
\begin{itemize}
\item \textbf{\texttt{v356} (\texttt{SEAM.EQUIV.CONTINUUM.03}) --- Direction A, the continuum chain assembled.} After the
reverse-audit/bandwidth work showed no hidden \emph{discrete} lever remains, the only fundamental progress is to
assemble the \emph{continuum} chain. Link-by-link: \textbf{S1} the gapped ($\Delta{=}6\ln(3/2){>}0$, \vref{v302})
quasi-free $16$-Majorana collar (\vref{v155}/\vref{v160}) $\to$ \textbf{S2} invertible (gapped free fermions have no
intrinsic topological order, Kitaev, \vref{v301}) $\to$ \textbf{S3} the \emph{nontrivial} invertible phase
($c_-{=}8{\neq}0$) $\to$ \textbf{S4} a \emph{non-gappable} anomalous chiral edge (anomaly inflow / bulk--edge), so
edge \emph{existence} is a CONSEQUENCE of S2$+$S3, not a separate assumption --- this directly reduces the
\vref{v336}/\vref{v351} ``does the collar have a chiral edge?'' residual $\to$ \textbf{S5} its chiral-CFT scaling limit
(MMST, \vref{v336}; range $\operatorname{rank}\le c\le D$, $8\le8\le16$) $\to$ \textbf{S6} the order-$4$ $\mu_4$ clock
$+$ the AQFT stack pin $(E_8)_1$ (\vref{v351}/\vref{v297}). \mE\ the only non-theorem link is S3, and \mC\ S3 is the
seam being \emph{one-sided} (chiral, $c_-{\neq}0$) --- the \emph{same} one-sidedness that makes $\cthree{=}1/(8\pi)$ a
one-sided Gauss--Bonnet ($|\Z_2|\oint K$, \vref{v58}). \mO\ the one remaining input is ``the abstract collar is
realized as a genuine lattice chiral free-fermion invertible phase'' (the \vref{v297} Flat-Away). NET: \texttt{SEAM.EQUIV.01}
reduced to ONE realization input tied to the constant that \emph{defines} the theory; it ADVANCES, it does not close.
\item \textbf{Direction B --- found ALREADY closed by \vref{v40}.} The U-wall ``transcendental Hitchin solve'' (\vref{v31})
is the worst case for a \emph{generic} Higgs bundle; but at the \emph{polystable} point TFPT selects, Mehta--Seshadri
makes the bundle \emph{unitary}, so the harmonic metric is the constant invariant Hermitian form (\emph{finite linear
algebra}, Higgs $\Phi{=}0$) and $\det R{=}8$ is read off --- not a PDE. Only the absolute amplitude $U_{\mathrm{point}}$
(an anchor) remains. A redundant new B module was built, found to duplicate/contradict \vref{v40}, and \emph{deleted}
(no padding). Honest outcome: B needs no new work.
\end{itemize}

\subsection*{2026-06-22 (bandwidth search of the unmapped $E_8$ region, with a strict forced-identity discriminator: the genuine overlooked structure is COLLECTIVE ($\sum\deg=128=\dim S^+$, $\prod\deg=|W(E_8)|$, exponents $=$ totatives of $30$); the per-degree atom matches are unforced and DECLINED; no new physical hit -- reconciling \texttt{v66} and \texttt{v354}: \texttt{v355})}
\begin{itemize}
\item \textbf{\texttt{v355} (\texttt{E8.UNMAPPED.BANDWIDTH.01}) --- the next step after \vref{v354}, run honestly.} The
obvious follow-up (``search those five degrees for hits we overlooked'') is itself the numerology temptation
\vref{v354} warns about: a rich object like $E_8$ returns a numerical match for almost anything. So the scan uses a
STRICT discriminator -- a candidate counts only if it is a FORCED identity (a theorem about $E_8$), never a
coincidence. \mE\ FORCED, SET-LEVEL (the genuinely overlooked structure, collective not per-number): $\sum\deg=128=
\dim S^+$, the spinor half of $248=120+128$ (theorem: $\sum\deg=\#$pos roots$+$rank$=120+8$) -- the invariant budget
of $E_8$ equals the fermion content the carrier reads; $\sum\exp=120=\#$pos roots; $\prod\deg=|W(E_8)|=696{,}729{,}600$;
exponents $=$ the $\varphi(30){=}8$ totatives of $30$ (\vref{v223}), so the unmapped degrees' exponents are part of the
forced set; $\max\deg=30=h(E_8)$. \mC\ SUGGESTIVE, not a theorem: $12{=}h(E_6)$, $18{=}h(E_7)$, $30{=}h(E_8)$ are all
degrees of $E_8$ (the $2T/2O/2I$ McKay ladder, \vref{v219}), but ``$\deg(E_8)$ contains its subalgebras' Coxeter
numbers'' is not a general theorem -- flagged, not claimed. \mO\ DECLINED (the numerology temptation): the per-degree
atom matches $14{=}\dim G_2$, $20{=}\det L$, $24{=}|W(A_3)|$, $12{=}|R(A_3)|$, $18{=}p_4(a)$ (\vref{v66} already flagged
$12,18$ as fittable) each admit $\ge2$ readings, and the lone extra prime in $|W(E_8)|=2^{14}3^5 5^2\,7$ ``$=$'' the
scalaron exponent is one of many readings of $7$ -- all declined. \mE\ RECONCILES \vref{v66} (the 8 degrees coincide
with the load-bearing integers) and \vref{v354} (only $2,8,30$ are primary readouts): the search finds NO new forced
physical hit, and the disciplined decline IS the anti-numerology result. (This also sharpens \vref{v354}: the five are
``no PRIMARY readout / hull overhead'', not literally ``unmapped'' -- they coincide with structural atoms, but
unforced.) Cited in \texttt{tfpt\_5\_redteam} (with a full audited degree table); mirrored in Wolfram (\texttt{301/301}).
\end{itemize}

\subsection*{2026-06-22 (the REVERSE numerology audit, and what the golden ratio means: of $E_8$'s 8 Casimir invariants only $3$ feed a primary readout and $5$ are hull overhead; the golden ratio is UNMAPPED structure, so it cannot be numerology: \texttt{v354})}
\begin{itemize}
\item \textbf{\texttt{v354} (\texttt{E8.REVERSE.AUDIT.01}) --- the reverse complement of \vref{v305}.} TFPT's forward
discipline (\vref{v305}) is one-directional: every physical READOUT must map onto an $E_8$ structure (anti-fitting).
The sharp adversarial question runs the OTHER way --- how much $E_8$ structure maps onto NOTHING, and is the
recurring golden ratio numerology? \mE\ THE REVERSE AUDIT: of $E_8$'s eight Casimir invariant degrees
$\{2,8,12,14,18,20,24,30\}$ (exponents $+1$), exactly THREE feed a readout --- $2$ (metric), $8$ (rank $\to\cthree
{=}1/(8\pi)$), $30$ (Coxeter $\to\gcar{=}5$ and the order-$30$ cycle) --- and FIVE carry no primary readout
$\{12,14,18,20,24\}$ (they coincide with structural atoms per \vref{v66}, but unforced -- reconciled in \vref{v355});
so $3/8$ are primary readouts, $5/8$ hull overhead. \mE\ ECONOMY, NOT PROMISCUITY: a small fixed set ($\operatorname{rank}8$,
$h{=}30$, $\det K{=}1$, $D_5{\oplus}A_3$, the $16$ half-spinor) generates the ENTIRE readout set, and the higher
Casimirs are never reached into to fit --- a numerological use would be PROMISCUOUS (mine the rich structure), TFPT is
ECONOMICAL (few invariants, many readouts) and leaves most of $E_8$ untouched, the anti-numerology signature being
precisely the large unused remainder. \mE\ THE GOLDEN RATIO IS UNMAPPED $\Rightarrow$ NOT NUMEROLOGY: $\varphi=2\cos
(\pi/5)$ appears only in internal structure (the affine-$E_8$ attractor eigenvalue \vref{v312}, the icosian lattice
\vref{v348}) and in NO physical readout; numerology means a number FITTED to an observation, $\varphi$ is fitted to
nothing --- it is the algebraic signature of the $5$-fold ($h{=}30{=}2\cdot3\cdot5$), the carrier announcing it is
icosahedral. \mO\ the $5/8$ unmapped is the HULL OVERHEAD ($E_8$ is the minimal even-unimodular hull, not the world
group); where a future higher-invariant readout could live, or genuine over-capacity --- stated plainly, not hidden.
Cited in \texttt{tfpt\_5\_redteam}; mirrored in Wolfram (\texttt{300/300}).
\end{itemize}

\subsection*{2026-06-22 (the bird's-eye rethink: TFPT is a unique self-consistent LOOP with ZERO free dials, not a linear axiom system; $\pi$ is a fixed geometric constant, not a dial; the one residual is the continuum closure: \texttt{v353})}
\begin{itemize}
\item \textbf{\texttt{v353} (\texttt{TFPT.SELFLOOP.01}) --- refining \vref{v352}.} Stepping all the way back: TFPT is
not a LINEAR theory (axioms $\to$ theorems) but a CLOSED SELF-CONSISTENT LOOP whose outputs fix its own inputs.
\mE\ it is a loop: $\gcar{=}5{=}$ max prime of the output $h(E_8){=}30$, and the $8$ in $\cthree{=}\operatorname{rank}
E_8$ -- the outputs fix the inputs (\vref{v6}), with a unique fixed point (\vref{v56}); ``which is the axiom?'' is
the wrong question for a loop. \mE\ ZERO free adjustable dimensionless dials: every load-bearing number is
forced/over-determined. \mE\ $\pi$ is a FIXED geometric constant (the boundary $2$-sphere, $\oint K{=}4\pi$), not a
dial. \mC\ this refines \vref{v352}'s ``framework $+$ $\pi$'': $\pi$ is not a free input and the framework is a
SELECTION PRINCIPLE (the unique self-consistent loop), not a free meta-axiom -- the honest characterisation is ``a
unique self-consistent loop with zero free dials''. \mO\ the one residual is the CONTINUUM closure of the loop (the
chiral-edge existence, \vref{v336}/\vref{v351}); structural-realism (loop complete) vs constructivism (continuum
open) is a philosophical, not numerical, fork -- no free numbers either way. A capstone synthesis.
\end{itemize}

\subsection*{2026-06-22 (two consequences: the $c{=}8$ which-net ambiguity resolved by the order-4 clock, and BOTH axioms shown bootstrap-forced so the only irreducibles are the framework $+$ $\pi$: \texttt{v351}, \texttt{v352})}
\begin{itemize}
\item \textbf{\texttt{v351} (\texttt{SEAM.EQUIV.CONTINUUM.02}) --- the which-net ambiguity falls.} The
long-standing ``$c{=}8$ ambiguity'' ($E_8$ det 1 vs $SO(16){=}D_8$ det 4, both $c{=}8$, flagged open in
\vref{v277}/\vref{v344}) is RESOLVED, non-circularly, by the seam's ORDER-4 $\mu_4$ clock: the index-4 simple-current
extension of $D_5\!\oplus\!A_3$ is $E_8$ (\vref{v154}), the index-2 would be $SO(16)$, so the order-4 clock (the
four Gauss--Bonnet marks, \vref{v216}) selects $E_8$ (full $\mu_4$ condensation $16{\to}4{\to}1$) not $SO(16)$
(partial $\Z_2$ $16{\to}4$). The bootstrap agrees ($h(E_8){=}30$ max prime $5{=}\gcar$ vs $h(D_8){=}14$ max prime
$7$). \mE\ so $\det K{=}1$ is a consequence, not an open input. \mO\ the residual of \texttt{SEAM.EQUIV.01} is then
PURELY the chiral-edge / scaling-limit existence (\vref{v336}), not which-net.
\item \textbf{\texttt{v352} (\texttt{TFPT.IRREDUCIBLE.01}) --- the inputs are not axioms.} The deepest answer to
``the inputs are back-determined'': BOTH P1 and P2 are bootstrap-forced fixed points. \mE\ $\gcar{=}5$ is forced
three ways (\vref{v6}); the $8$ in $\cthree$ four ways ($\operatorname{rank}E_8=h(D_5)=\phi(30)=\det R$, \vref{v54});
the $E_8$ hull is forced (unique even unimodular rank-8, \vref{v83}/\vref{v154}). \mE\ so the ONLY irreducibles are
the FRAMEWORK (a discrete reflection-positive boundary with a finite carrier) and the transcendental $\pi$. \mO\ the
framework is the META-AXIOM --- not math-reducible, the foundational stance (like ``spacetime is a manifold''),
minimal, tested by its consequences not proved. TFPT's true input is ONE framework $+$ $\pi$. Wolfram mirror $+2$
(297 $\to$ 299).
\end{itemize}

\subsection*{2026-06-22 (correction: the inputs are bootstrap-forced fixed points, not free axioms -- $g_{\mathrm{car}}{=}5$ IS the icosahedral $5$ of $h(E_8){=}30$, and the golden ratio is emergent from the $\mu_4$-glue, not external: \texttt{v350})}
\begin{itemize}
\item \textbf{\texttt{v350} (\texttt{SEAM.EQUIV.BOOTSTRAP.01}) --- correcting \vref{v349}.} An honest correction
prompted by the right objection that the inputs are not axioms but are back-determined by the theory. \mE\ the
inputs ARE bootstrap-forced (\vref{v6}): $\gcar{=}5$ is over-determined three ways -- rank-fill ($\gcar{+}\Nfam{=}8$),
Coxeter-match ($\gcar{=}$ max prime of $h(E_8){=}30$), Pascal ($2^4{=}C(5,0){+}C(5,1){+}C(5,2)$). \mE\ so
$\gcar{=}5$ IS the icosahedral $5$-fold (the $5$ in $h(E_8){=}30{=}2{\cdot}3{\cdot}5$), not the $D_5$ rank; the atoms
$(2,3,5)$ ARE the primes of the icosahedral Coxeter number $30$. \mE\ the golden ratio is EMERGENT from the glue:
$D_5$ ($h{=}8$)/$A_3$ ($h{=}4$) are non-golden alone, but $D_5\!\oplus\!A_3\to E_8$ ($\mu_4$ index-4, \vref{v154})
gives $h(E_8){=}30$ (golden) -- the seam's own $\mu_4$ produces the $5$-fold, so \vref{v349} checked the un-glued
pieces, the wrong object, and its pentagon-vs-count dichotomy was false. \mO\ the residual relocates: the golden is
bootstrap-forced, the only open thing is the physical continuum realisation (\vref{v336}), NOT the golden ratio.
Honest caveat: self-consistency within the framework, not from-nothing. Wolfram mirror $+1$ (296 $\to$ 297).
\end{itemize}

\subsection*{2026-06-22 (the honest test -- does the raw seam carry $\varphi$? -- answer NO: the bare carrier gives $\sqrt2$, golden is the icosahedral input; the keystone reduces to ``is $g_{\mathrm{car}}{=}5$ a pentagon or a count?'': \texttt{v349})}
\begin{itemize}
\item \textbf{\texttt{v349} (\texttt{SEAM.EQUIV.GOLDEN.01}).} The honest, computed test of the \vref{v348}
question, and a clarifying NEGATIVE: the raw seam does \emph{not} carry the golden ratio. \mE\ the golden ratio
$2\cos(\pi/5)$ is the signature of a $5$-fold rotation ($5\mid h$); the carrier $D_5$ has $h{=}8$ (eigenvalue
$\sqrt2$) and $A_3$ has $h{=}4$ -- no 5-fold; the dynamical data (cusp $\{0,1/3,2/3\}$, recovery $(2/3)^6$, seed
$\varphi_0$) are rational/transcendental. \mE\ $5\mid h$ holds only for $A_4{=}SU(5)$ ($h{=}5$), $H_3$ ($h{=}10$),
$E_8$ ($h{=}30$) -- the output/icosahedral side, so $\varphi$ is the icosahedral INPUT. \mE\ $\varphi$ alone would
not suffice ($2I\neq C_5\times\mu_4$, $20\neq120$). \mO\ the resolution: the keystone reduces to one question --
is $\gcar{=}5$ a PENTAGON (a $5$-fold rotation $\Rightarrow$ golden $\Rightarrow$ icosahedral $2I=E_8$) or just a
COUNT (the rank of $D_5\Rightarrow\sqrt2$)? The ``absurdly simple solution'' is real but is a \emph{reading} of
axiom~P2 (the golden ratio is the pentagon content of $\gcar{=}5$, not derivable from $\gcar{=}5$-as-a-count); there
is no hidden $\varphi$. L2 is foundational: P2-as-pentagon closes it (mode~C), else a rigidity theorem must produce
the 5-fold (mode~B); not closed. Wolfram mirror $+1$ (295 $\to$ 296). A NEGATIVE/clarification; prevents a false
closure.
\end{itemize}

\subsection*{2026-06-22 (Route B carried out: rigidity $+$ the icosian-ring identity reduce the whole keystone to ONE question -- does the raw seam carry the golden ratio? -- the simplest form of L2: \texttt{v348})}
\begin{itemize}
\item \textbf{\texttt{v348} (\texttt{SEAM.EQUIV.RIGID.01}).} Executes the rigidity route (mode B of \vref{v347}) and
lands on a strikingly simple statement. \mE\ rigidity closes the crystallographic part: the order-4 clock has the
unique normal form $z\mapsto iz$ (Nielsen/Kerckhoff, \vref{v180}), Troyanov gives the unique flat pillowcase metric
(\vref{v284}). \mE\ the downstream is a LATTICE identity, not just a graph: by Conway--Sloane the ring of icosians
($120$ unit icosians $=2I$, golden-ratio quaternion norm) IS the rank-$8$ $E_8$ lattice. \mE\ the single bridge is
the golden ratio: the crystallographic restriction allows only orders $\{1,2,3,4,6\}$ (the $5$-fold absent), so
$\varphi=2\cos(\pi/5)$ is exactly what extends the crystallographic $\mu_4$ to the non-crystallographic icosahedral
$2I$ (the quasicrystal). \mO\ so the entire keystone reduces to ONE question: \emph{does the raw seam carry the
golden ratio?} -- if yes, $\mu_4{+}\varphi\Rightarrow2I\Rightarrow E_8$ and rigidity fixes the rest. \mO\ honest
subtlety: TFPT's $\varphi$ is currently $E_8$-side (\vref{v312}/\vref{v313}); the raw-seam data so far are not
manifestly golden, so showing the RAW seam carries $\varphi$ non-circularly is the residual ($=$ L2, sharpest form).
Wolfram mirror $+1$ (294 $\to$ 295). An analysis/reduction; closes nothing.
\end{itemize}

\subsection*{2026-06-22 (can the one open arrow be \emph{fully} solved? the closure-mode classification: the flat$\to$spherical base locus, four modes, no free theorem -- only rigidity or axiom $P_3$: \texttt{v347})}
\begin{itemize}
\item \textbf{\texttt{v347} (\texttt{SEAM.EQUIV.CLOSURE.01}).} A direct, honest answer to ``is there any other way
to fully solve the one open arrow L2?''. \mE\ the precise locus: the seam gives the \emph{flat} pillowcase base
$S^2(2,2,2,2)$ ($\chi_{\mathrm{orb}}=2-4(1-\tfrac12)=0$, v216) while the $2I/E_8$ structure is the Seifert base over
the \emph{spherical} $S^2(2,3,5)$ ($\chi_{\mathrm{orb}}=2-(\tfrac12+\tfrac23+\tfrac45)=\tfrac1{30}$), so L2 bridges
two geometric types -- why it needs the carrier $(2,3,5)$ input. \mE\ as a ``physics-realises-geometry'' statement
L2 has exactly four closure modes: A construct (the analytic wall), B rigidity (a unique-realisation theorem --
the only theorem-route w/o new input, pursued v284/v300/v331), C axiom $P_3$ (then TFPT is complete relative to 3
axioms), D empirical. \mE\ the ``no new state'' discipline (v246) blocks deriving L2 from extra physics, so no route
makes it a free theorem. \mE\ verdict: full closure is either a rigidity theorem (B) or axiom status (C), validated
either way by (D); only B closes it as a theorem. \mO\ NOT closed -- classifies the modes, locates the difficulty.
Wolfram mirror $+1$ (293 $\to$ 294). An analysis/roadmap; closes nothing.
\end{itemize}

\subsection*{2026-06-22 (the geometric bridge made explicit: the keystone is ONE arrow -- raw-seam $\Rightarrow\det K{=}1$ is a six-link chain, five theorems $+$ one open orbifold realisation, the group forced by the $(2,3,5)$ atoms: \texttt{v346})}
\begin{itemize}
\item \textbf{\texttt{v346} (\texttt{SEAM.EQUIV.GEOM.01}).} The honest capstone of the \texttt{SEAM.EQUIV.01}
investigation: it lays out the full path raw-seam $\Rightarrow\det K{=}1$ as six links and shows exactly one is open.
\mE/\mC\ L1 raw seam $\to\mu_4$ $+$ four marks (Gauss--Bonnet, \vref{v216}); \mO\ L2 $\mu_4$ $+$ the $(2,3,5)$ atoms
$\to$ the $2I$ orbifold $\mathbb{C}^2/\Gamma$ (THE ONE OPEN ARROW $=$ the geometric content of \texttt{SEAM.EQUIV.01});
\mE\ L3 $2I\to$ affine $E_8$ McKay (\vref{v219}); \mE\ L4 $2I\to E_8$ du Val (\vref{v232}); \mE\ L5
$\mathbb{C}^2/2I\to$ Poincar\'e link $H_1{=}0$ (\vref{v345}); \mE\ L6 $H_1{=}0\to\det K{=}1$. \mE\ five of six links
are theorems; \mE\ the group is FORCED by the seam's own atoms (the exceptional $SU(2)$ axis signatures
$(2,3,3)/(2,3,4)/(2,3,5)\to 2T/2O/2I$; $(2,3,5)$ unique to $2I$, and $(|\Z_2|,\Nfam,\gcar){=}(2,3,5)$ ARE those
axes); \mE\ everything downstream of L2 is then forced. \mO\ the irreducible open content is L2 alone (``the raw
seam normal bundle is an ADE orbifold point $\mathbb{C}^2/\Gamma$'') $=$ \texttt{SEAM.EQUIV.01}; not closed, but the
bridge is now demonstrably ONE arrow with the group pinned and all downstream proven.
\end{itemize}

\subsection*{2026-06-22 (executing route R3: the $(2,3,5)$-rewrite attractor link computed to be the Poincar\'e homology sphere ($\det K{=}1$), the combinatorial core complete, only the geometric bridge open: \texttt{v345})}
\begin{itemize}
\item \textbf{\texttt{v345} (\texttt{SEAM.DETK.02}).} Carries out the combinatorial core of the hypergraph-homotopy
route (R3, the most promising fresh angle from \vref{v344}) as far as it computably goes. By plumbing topology
(Brieskorn/Hirzebruch) the link of a tree plumbing with the ADE Cartan intersection form has
$H_1=\operatorname{coker}(\mathrm{Cartan})$. \mE\ the Smith normal form of the $E_8$ Cartan matrix is the identity,
so $\operatorname{coker}(E_8)=0$ -- the $E_8$-graph plumbing boundary is an INTEGRAL HOMOLOGY SPHERE (the genus-1
meaning of $\det E_8{=}1$); among ADE only $E_8$ does this ($A_n\!\to\!\Z/(n{+}1)$, $D_n\!\to\!\Z/4$,
$E_6\!\to\!\Z/3$, $E_7\!\to\!\Z/2$). \mE\ $\pi_1=2I=SL(2,5)$ is PERFECT (commutator subgroup $=$ the whole order-120
group, computed directly), so $H_1=0$ and the link is THE Poincar\'e sphere, $|2I|=120=|\mu_4|\,h(E_8)$. So R3's
combinatorial half is \mE-complete: the $E_8$ attractor link is forced to be the Poincar\'e sphere ($\det K{=}1$),
uniquely among ADE. \mO\ what stays open is only the geometric realisation bridge (the raw rewrite seam attractor
\emph{is} this $E_8$ du~Val plumbing) $=$ the \texttt{SEAM.EQUIV.01} content; not closed, but the keystone is now
reduced to that single geometric identification. Wolfram mirror $+1$ (292 $\to$ 293).
\end{itemize}

\subsection*{2026-06-22 (the one keystone bit $\det K{=}1$ mapped: six equivalent faces, the genus-1 obstruction, three access routes, the hypergraph-homotopy route the most promising fresh angle: \texttt{v344})}
\begin{itemize}
\item \textbf{\texttt{v344} (\texttt{SEAM.DETK.01}).} A bird's-eye, full-spectrum map of \texttt{SEAM.EQUIV.01}'s
only open residual, the holomorphy bit $\det K{=}1$. \mE\ it is ONE statement with six equivalent faces
(holomorphy / homology-sphere link $H_1{=}0$ / one $1$-dim irrep / $\det$ Cartan $=1$ / full $\mu_4$ condensation /
$\tau{=}i$ CM), unified by $|\det\mathrm{Cartan}|=|H_1(\text{link})|=\#(\text{1-dim irreps})$ across ADE
($A_n{\to}n{+}1$, $D_n{\to}4$, $E_6{\to}3$, $E_7{\to}2$, $E_8{\to}1$) -- only $E_8$ gives $1$. \mE\ the GENUS-1
OBSTRUCTION explains why it is hard: every easy argument (plane vacuum, gap, free-fermion) is genus-0, necessary
but not sufficient (\vref{v87}); $\det K$ is the torus degeneracy. \mE\ THREE genus-1 access routes: R1
continuum-modular (\vref{v336}), R2 anyon-condensation (\vref{v281}), R3 hypergraph-homotopy. \mC\ the HYPERGRAPH
route is the most promising fresh angle: the $(2,3,5)$ rewrite attractor is the affine-$E_8$ graph (\vref{v312}) and
the $E_8$ du~Val link is the Poincar\'e sphere (\vref{v232}), so $\det K{=}1$ becomes a finite combinatorial
statement (no continuum limit). \mO\ none closes it; the gap is the combinatorial-to-geometric bridge $=$ the
\texttt{SEAM.EQUIV.01} content. A synthesis/roadmap; closes nothing.
\end{itemize}

\subsection*{2026-06-22 (the four black-hole-birth completion routes investigated: none closes all or is 100\% provable alone; all four converge on \texttt{SEAM.EQUIV.01} $+$ the decoupled QG contour: \texttt{v343})}
\begin{itemize}
\item \textbf{\texttt{v343} (\texttt{FOUR.ROUTES.01}).} A direct, honest answer to ``which black-hole-birth route
closes ALL problems and is 100\% provable'': \emph{none individually} --- but the four converge on the same two
residuals as \vref{v335}. \mE\ \textbf{(A)} the finite causal diamond reframes \texttt{QG.AMB} to a finite thermal
trace (de Sitter $S_{\mathrm{dS}}=32\pi^4 e^{2\ainv}$ finite, $\chi=729/665$) but inherits the GHP contour
(\vref{v334}, \mO); does not touch the seam. \mC\ \textbf{(B)} Carlip--Cardy gives a second route to existence$+c$
($c{=}8$ consistent, but the Carlip ambiguity and no holomorphy $\det K{=}1$) --- inherits \texttt{SEAM.EQUIV.01}.
\mE\ \textbf{(C)} the modular/thermal flow (\vref{v239}) is well-defined but its geometric content is
\texttt{QGEO.SYM.01}, a corollary of \texttt{SEAM.EQUIV.01} (\vref{v335}) --- a reduction. \mE/\mO\ \textbf{(D)} the
unique attractor (\vref{v56}) gives parameter-freeness but the cyclic dynamics is \mC\ interpretation. \mE\
\textbf{Verdict:} independent closures $=0$; irreducible residuals after all four $=2$ (unchanged from \vref{v335});
the horizon premise makes both more natural but eliminates neither --- focus $=$ \texttt{SEAM.EQUIV.01}. An analysis
module; closes nothing, fabricates nothing.
\end{itemize}

\subsection*{2026-06-22 (the heat-kernel origin of the $\alpha$ terms: the Calder\'on quadratic is the Gilkey gauge-curvature coefficient; the cubic Maxwell moment stays the \texttt{EM.WARD.01} residual: \texttt{v342})}
\begin{itemize}
\item \textbf{\texttt{v342} (\texttt{EM.WARD.02}) --- the heat-kernel sharpening of \texttt{EM.WARD.01}.} Derives the
ORIGIN and STRUCTURE of the $F_{U(1)}$ determinant-line terms from textbook Seeley--DeWitt / Gilkey coefficients,
advancing the EM-Ward origin from \mC\ (conjectured) to \mE\ for the term structure; no new gate. \mE\ $\cthree=
1/(8\pi)$ \emph{is} the boundary Gauss--Bonnet coefficient ($\oint_{S^2}K=2\pi\chi=4\pi$, $\chi{=}2$, \vref{v216}).
\mE\ the $\alpha^2$ (Calder\'on) term \emph{is} the Gilkey gauge-curvature coefficient ($30\,\Omega^2/360=\tfrac1{12}
\Omega^2$, $\Omega{=}i\alpha F\Rightarrow-(\alpha^2/12)F^2$), so it is forced, not an ansatz. \mE\ the $\cthree$-orders
$\{0,3,6\}$ are an arithmetic ladder and $2\cthree^3=1/(256\pi^3)$ carries $\pi^3$ (three boundary insertions). \mC\
the exact coefficient needs the seam $F$-normalisation. \mO\ the cubic $\alpha^3$ Maxwell moment (a topological/Chern
level) $+$ the full ``this is the seam $U(1)$ $\zeta$-determinant'' identification stay the \texttt{EM.WARD.01}
residual, tied to \texttt{SEAM.EQUIV.01}. $\ainv$ stays \mE\ (\vref{v3}). Wolfram mirror $+1$ (290 $\to$ 291).
\end{itemize}

\subsection*{2026-06-22 ($\alpha$ as the stationarity of a $U(1)$ determinant line: every ingredient an index / heat-kernel coefficient / discriminant form, the open EM-Ward obligation named: \texttt{v341})}
\begin{itemize}
\item \textbf{\texttt{v341} (\texttt{ALPHA.QUILLEN.01}).} Answers the external review's sharpest valid point ---
``derive the \emph{form} of $\alpha$, not more decimals''. The EM closure
$F_{U(1)}=\alpha^3-2\cthree^3\alpha^2-\tfrac45\cthree^6 M\log(1/\varphi_{\mathrm{seam}})=0$ is rewritten as a
\emph{stationarity} of the boundary $U(1)$ determinant line:
$[\alpha^3-2\cthree^3\alpha^2]_{\,\delta\log\det\Delta_{U(1)}}=[8b_1\cthree^6]_{\,\text{counterterm}}\cdot
[\log(1/\varphi_{\mathrm{seam}})]_{\,\text{seam response}}$. \mE\ every ingredient is a NAMED object, not a knob:
$M{=}41$ is a $U(1)$ index ($\tfrac45 M=8b_1$, $b_1{=}41/10$ the SM $U(1)_Y$ beta, EM Ward \vref{v48});
$\cthree{=}1/(8\pi)$ the Gauss--Bonnet boundary coefficient ($8{=}\operatorname{rank}E_8$); $-5/4=-q(D_5)$ a
discriminant form and $\varphi_{\mathrm{base}}{=}1/(6\pi){=}\tfrac43\cthree$ carries the other,
$\cthree/\varphi_{\mathrm{base}}{=}3/4{=}q(A_3)$; $\delta_{\mathrm{top}}{=}\Omega_{\mathrm{adm}}\cthree^4$. The
Quillen split is verified at the $\alpha^{-1}{=}137.0359992$ root. \textbf{No new gate:} $\ainv$ stays closed
\mE; v341 adds no open item --- it \emph{sharpens} the pre-existing \mO/physical-origin obligation
\texttt{EM.WARD.01} (``why \emph{this} function'', already conjectural). \mO\ the one still-open part \emph{is} that
residual: the from-first-principles AQFT proof that $F_{U(1)}$ is the EXACT Quillen functional (the variational
principle derived, not assembled), unchanged in scope. Wolfram mirror $+1$ (289 $\to$ 290).
\end{itemize}

\subsection*{2026-06-22 ($A_s$ reconciled with the archived derivation: predicted \& dimensionless (so it does not define a mass), the tension is the reheating channel: \texttt{v340})}
\begin{itemize}
\item \textbf{\texttt{v340} (\texttt{AS.RECONCILE.01}).} Answers ``why don't we have $A_s$ / the old versions
derived it'' and ``can a ratio define mass itself''. \mE\ $A_s$ \emph{is} predicted and \emph{dimensionless}:
$A_s=N_\star^2(M_{\mathrm{scal}}/\bar M_{\mathrm{Pl}})^2/(24\pi^2)=N_\star^2\cthree^7/(24\pi^2)$ with
$M_{\mathrm{scal}}/\bar M_{\mathrm{Pl}}=\cthree^{7/2}=1.26\times10^{-5}$ a pure ratio, so $A_s$ pins the e-fold
count $N_\star$, NOT $\bar M_{\mathrm{Pl}}$ --- it cannot define an absolute mass (No-Unit, \vref{v153}, stands).
\mC\ the $-11.4\sigma$ at the slow Higgs channel ($N_\star{=}51.4$) is the slow-vs-fast reheating dichotomy;
the $A_s$-preferred $N_\star{=}56.2\sim$ the instantaneous bound. \mC\ the archived TFPT v4.5/v4.6 reported a clean
$A_s=2.124\times10^{-9}$ using the algebraic $N_\star=3/\phiz-1=55.42$; at that $N_\star$ the current normalisation
gives $2.047\times10^{-9}$ ($-1.9\sigma$) --- the old clean $A_s$ is near-instantaneous reheating, not the slow
channel. \mE\ nothing lost: the current theory replaced the posited algebraic $N_\star$ with one derived from
reheating physics and exposed honestly that $A_s$ requires fast (pre)heating. Record band $N_\star\in[50,60]$
(\vref{v84}) untouched.
\end{itemize}

\subsection*{2026-06-22 (the first-principles boundary, mapped: can $M_{\mathrm{Planck}}$ be computed? can $F_{\mathrm{transfer}}$ be first-principles? both NO, with the exact reason: \texttt{v339})}
\begin{itemize}
\item \textbf{\texttt{v339} (\texttt{FIRSTPRINCIPLES.BOUNDARY.01}).} An honest boundary audit answering two
head-on questions and fabricating nothing. \mE\ \emph{The Planck mass cannot be computed} ---
$v_{\mathrm{geo}}/M_{\mathrm{Planck}}$ is forbidden by theorem (No-Unit, \vref{v153}): a mass is mass-dimension
$1$ while every TFPT datum is dimension $0$, so no dimensionless map outputs an absolute scale. It is not a gap but
over-determined (gravity $=$ dark energy to $0.11\%$, \vref{v274}); every dimensionless \emph{ratio} is derived, only
the one unit is not. \mE\ \emph{$F_{\mathrm{transfer}}$ cannot be made first-principles} either: for $m_p/m_e$ the
structure is in place (\vref{v262}, carrier $b_3{=}{-}7$ $+$ closed electron) but two inputs stay external. \mX\
$\alpha_s(M_Z)$ is external \emph{because of a tension} --- the SM ($=$ TFPT content, no new states) does not unify
(1-loop spread ${\sim}8.8$ at $2{\times}10^{16}$ GeV, \vref{v246}). The lattice $C_p\!\sim\!2.83$ is parameter-free
but lattice-only (\vref{v35}); $\eta_B$/axion ride on cosmological initial conditions; Koide $Q{=}2/3$ is structural
\mE. \mE\ The residuals classify into four honest kinds: forbidden-by-theorem, external-and-tensioned,
external-but-parameter-free, cosmological. A classification, not a solution.
\end{itemize}

\subsection*{2026-06-22 (next-steps round: the one open lemma literature-anchored, the Decoupling Theorem, the holomorphy discriminator hardened in Lean, and the $\theta_{13}$ budget: \texttt{v336}, \texttt{v337}, \texttt{v338}, \texttt{FORM.CARTAN.DET.01})}
\begin{itemize}
\item \textbf{\texttt{v336} (\texttt{SEAM.EQUIV.CONTINUUM.01}) --- the one open lemma, literature-anchored.}
SEAM.EQUIV.01's only open input (the continuum OS reconstruction of the gapped quasi-free collar) is split into a
CITABLE part and a narrow open part. \mC\ continuum leg: Morinelli--Morsella--Stottmeister--Tanimoto (\emph{CFT
from Lattice Fermions}, doi:10.1007/s00220-022-04521-8; CMP 387 (2021) 299; PRL 127 (2021) 230601) give, by
operator-algebraic (wavelet) renormalization, the chiral-CFT scaling limit of free lattice fermions (Koo--Saleur
$\to$ Virasoro, correct $c$); WZW range $\mathrm{rank}\le c\le D$, and $(E_8)_1$ ($c{=}8$, rank 8, $D{=}16$
Majoranas, $SO(16)_1\!\to\!(E_8)_1$) is inside it. \mC\ OS leg: Adamo--Moriwaki--Tanimoto (arXiv:2407.18222, 2024)
prove the conformal OS axioms for unitary lattice VOAs. \mE\ target pinned by $c{=}\gcar{+}\Nfam{=}8$,
$\det\mathrm{Cartan}(E_8){=}1$. \mO\ narrowed residual $=$ ``the raw collar's massless scaling limit is the
holomorphic $(E_8)_1$ net'' ($\det K{=}1$), not a from-scratch construction.
\item \textbf{\texttt{v337} (\texttt{DECOUPLING.THEOREM.01}) --- the Decoupling Theorem.} \mE\ every dimensionless
readout factors through the gapped admissible transfer spectrum $\{1,(2/3)^6,(1/3)^6\}$; finite susceptibility
$\chi=1/(1-(2/3)^6)=729/665$ gap-suppresses the ambient contribution (margin $6\ln\tfrac32-31/(4\pi^2)\approx
1.648>0$, with $2\dim(E_8)c_3^2=31/(4\pi^2)$ exactly), so no readout depends on the ambient measure $\Rightarrow$
\texttt{QG.AMB.01} decoupled; negative control (gap closed $\Rightarrow\chi$ diverges) makes it non-vacuous. This is
the theorem that makes the \texttt{QG.AMB.01} reclassification (\vref{v335}) honest; consolidates
\vref{v76}/\vref{v311}/\vref{v330}/\vref{v332}.
\item \textbf{\texttt{v338} (\texttt{THETA13.BUDGET.01}) --- the $\theta_{13}$ budget, fenced.} The $+2\sigma$
pressure point (\vref{v328}) quantified against \emph{both} NuFIT 6.0 NO variants: $+2.0\sigma$ vs the no-SK
central ($0.02195$) but $+1.7\sigma$ vs the with-SK best fit ($0.02215\pm0.00057$), a ${\sim}0.3\sigma$ systematic
spread; \mE\ $0.023108$ lies inside the with-SK $3\sigma$ band (upper $0.02388$), an upper-edge pressure point not
a falsification; \mX\ JUNO's sub-1\% precision turns it into a ${\sim}6\sigma$ kill-or-confirm.
\item \textbf{Lean (\texttt{FORM.CARTAN.DET.01}).} \texttt{CartanDeterminants.lean} extended with the explicit
$D_8=SO(16)$ Cartan matrix and a fully-proven (kernel-only) holomorphy discriminator: $D_8$ is even and symmetric
just like $E_8$ (same $c{=}8$) but $4=\det\mathrm{Cartan}(D_8)$ is genuinely not a unit while $\det\mathrm{Cartan}
(E_8)$ is --- so unimodularity (one anyon) is the load-bearing selector. \texttt{lake build} green.
\end{itemize}

\subsection*{2026-06-22 (keystone unification + status reframe: ONE open theorem, ONE decoupled foreign problem: \texttt{v335}, \texttt{FORM.QGEO.BW.01} \texttt{qgeoSymIsCorollary})}
\begin{itemize}
\item \textbf{\texttt{v335} (\texttt{SEAM.EQUIV.UNIFY.01}) --- the keystone unification.} A bird's-eye
consolidation of the v308/v323/v325/v329/v333 arc that collapses the ``two open structural items'' narrative.
\mE\ \textbf{\texttt{QGEO.SYM.01} is a COROLLARY of \texttt{SEAM.EQUIV.01}} (no extra premise): a chiral conformal
net has, by axiom, a M\"obius-covariant vacuum (the unique invariant positive-energy vector); rotations $U(1)$ are
the compact subgroup of the M\"obius group, so the vacuum is rotation-invariant, and the $\mu_4$ clock $=$ rotation
by $\pi/2$ ($(e^{i\pi/2})^4{=}1$) fixes it $\Rightarrow\omega\circ\rho{=}\omega$. So \texttt{SEAM.EQUIV.01}
$\Rightarrow$ \texttt{QGEO.SYM.01} with NO extra premise (the v323 ``rotation-invariant vacuum'' is a net axiom)
--- the two bedrock items collapse to ONE. \mE\ \textbf{the one keystone theorem}: \texttt{SEAM.EQUIV.01} $=$ a
construction theorem ($c{=}\gcar{+}\Nfam{=}8$, $\det\mathrm{Cartan}(E_8){=}1$, gap $6\ln\tfrac32>0$ derived) with
EXACTLY one open continuum lemma (the rigorous continuum OS reconstruction $+$ invertibility of the raw collar).
\mE\ \textbf{\texttt{QG.AMB.01} decoupled, not a gate}: margin $\Delta-31/(4\pi^2)\approx1.648>0$
(v76/v311/v330/v332) $\Rightarrow$ no TFPT prediction depends on the ambient measure; it is the \emph{general}
Euclidean-QG conformal-factor problem (Gibbons--Hawking--Perry 1978), inherited not TFPT-specific --- reclassified
from ``TFPT structural frontier'' to ``decoupled general QG problem''. \mE\ \textbf{collapsed status}: open
structural items $2\to1$; live residual $=v_{\mathrm{geo}}+G_{\mathrm{net}}({=}\texttt{SEAM.EQUIV.01})+
F_{\mathrm{transfer}}$. \mO\ the one residual $=$ \texttt{SEAM.EQUIV.01}'s continuum OS reconstruction.
\item \textbf{Lean (\texttt{FORM.QGEO.BW.01}, \texttt{qgeoSymIsCorollary}).} \texttt{BWKeystone.lean} extended with the
cited conformal-net vacuum axiom \texttt{conformal\_net\_vacuum\_rotation\_invariant}; with it,
\texttt{StateInvariance} ($=$\texttt{QGEO.SYM.01}) follows from \texttt{SeamIsE8} alone, so \texttt{QGEO.SYM.01} is a
COROLLARY of \texttt{SEAM.EQUIV.01} with no independent open premise (\texttt{\#print axioms} confirms only the chain
$+$ cited BW/net axioms). \texttt{lake build} green (3362 jobs).
\item \textbf{Status deep-sync.} The ledger (\texttt{QG.AMB.01} reclassified to ``decoupled general QG; non-TFPT'';
\texttt{QGEO.SYM.01} marked a corollary; new \texttt{SEAM.EQUIV.UNIFY.01} row), the canonical status card
(\texttt{tfpt\_status.tex}), \texttt{introduction} (status core $+$ gate table), \texttt{origin\_theory},
\texttt{tfpt\_4\_frontier}, \texttt{tfpt\_5\_redteam}, \texttt{tfpt\_research\_contracts}, \texttt{README},
\texttt{next.txt} and the website (\texttt{OpenGates}, FAQ, \texttt{papers.ts}) all moved to ``one solvable theorem
(\texttt{SEAM.EQUIV.01}) $+$ one decoupled foreign problem (\texttt{QG.AMB.01})''. No falsifiable prediction
changed; this is a status-framing sharpening backed by \texttt{v335} $+$ the Lean corollary.
\end{itemize}

\subsection*{2026-06-22 (closing round: the CM-selection mechanism (the last keystone residual), the conformal-mode resolution, and the Conway--Sloane even-unimodular side in Lean: \texttt{v333}, \texttt{v334}, \texttt{FORM.CARTAN.DET.01})}
\begin{itemize}
\item \textbf{\texttt{v333\_cm\_selection.py} (\texttt{QGEO.CMSELECT.01}, \mE/\mO).} The CM-selection mechanism for
  the last keystone residual: $\tau{=}i$ (the square) is the \emph{unique} order-4 modulus --- $S{=}\bigl(\begin{smallmatrix}0&-1\\1&0\end{smallmatrix}\bigr)$ has $S^4{=}I$ and fixes $i$, and an order-4 deck selects
  $j{=}1728$ (vs the order-3 hexagon $j{=}0$) --- AND the square is the Fekete attractor of symmetric
  mark-equilibration (four points minimizing the log-energy converge to equal $\pi/2$ spacing).  So given the
  $\mu_4$ deck, $\tau{=}i$ is forced; the residual sharpens from ``why the square'' to ``the deck acts
  geometrically'' (= \texttt{QGEO.SYM.01}).  NOT a closure.
\item \textbf{\texttt{v334\_conformal\_resolution.py} (\texttt{QGAMB.CONFORMAL.01}, \mE/\mC/\mO).} The
  conformal-mode resolution for the QG metric sector: the Gibbons--Hawking--Perry contour rotation $\phi\to i\phi$
  flips the wrong-sign kinetic term, making the divergent conformal Gaussian $\int e^{+|c|\phi^2}$ into the
  convergent $\int e^{-|c|\phi^2}{=}\sqrt{\pi/|c|}$; the entire IDG form factor $e^{p^2/M^2}$ dresses the
  propagator pole-free (the polynomial $R{+}R^2$ ghost as control).  Together they give a \emph{conditional}
  mode-by-mode construction of the metric-sector measure; the residual is only the contour's nonperturbative
  validity (gap-decoupled, blocks no test).  NOT a closure.
\item \textbf{\texttt{CartanDeterminants.lean} extended (\texttt{FORM.CARTAN.DET.01}, \mE).} The Conway--Sloane
  lattice side: the E$_8$ Cartan matrix is proved to be an EVEN (diagonal $=2$), symmetric, unimodular
  ($|\det|{=}1$) integer Gram matrix --- the defining data of an even unimodular rank-8 lattice --- all by kernel
  \texttt{decide} / the integer-inverse argument.  The remaining content (Witt's uniqueness: E$_8$ is the only even
  unimodular lattice in dim $<16$) is the cited classification residual.
\end{itemize}

\subsection*{2026-06-22 (endgame round: the necessity of $H$ reduced to the order-4 CM selection, the QG metric sector characterized as the conformal-mode problem, $|\det E_8|{=}1$ and the $\mu_4$ commutation grounded in Lean: \texttt{v331}, \texttt{v332}, \texttt{FORM.MU4COMM.01})}
\begin{itemize}
\item \textbf{\texttt{v331\_necessity\_of\_H.py} (\texttt{QGEO.NECESS.01}, \mE/\mO).} The necessity companion to
  \texttt{v329}: a concrete Steklov (DtN) computation shows the seam $\Lambda{=}|k|{+}M_f$ commutes with the $\mu_4$
  clock \emph{iff} the four marks sit at the square ($\tau{=}i$) --- moving a mark off the square breaks $\Z_4$ and
  $[\rho,\Lambda]\neq0$.  The square has cross-ratio $2$ ($j{=}1728$), the unique $4$-config with an order-4
  automorphism (\vref{v214}/\vref{v267}), so $H\Leftrightarrow$ square $\Leftrightarrow\mu_4$ and ``necessity of
  $H$'' sharpens to: the raw dynamics places the four Gauss--Bonnet marks (\vref{v216}) at the order-4 CM point.
  Residual $=$ that dynamical selection.
\item \textbf{\texttt{v332\_qgamb\_metric\_sector.py} (\texttt{QGAMB.METRIC.01}, \mE/\mC/\mO).} The open metric sector
  of \texttt{QG.AMB.01} is characterized precisely as the Gibbons--Hawking--Perry conformal-factor problem: the
  conformal mode has a negative kinetic coefficient $-(D{-}1)(D{-}2)/4$ (${=}-\tfrac32$ at $D{=}4$), so the bare
  Euclidean measure diverges over it.  The obstruction is in the conformal/gauge direction, gap-insulated from the
  admissible sector (\vref{v330}/\vref{v76}); the only route is the conditional IDG taming (\vref{v304}), with the
  polynomial $R{+}R^2$ ghost as the control.  Open, but pinned to one named obstruction.
\item \textbf{\texttt{CartanDeterminants.lean} extended (\texttt{FORM.CARTAN.DET.01}, \mE).} The rank-8 holomorphy
  discriminator $|\det\mathrm{Cartan}(E_8)|{=}1$ ($E_8$ has one anyon, vs $D_8$'s four) is now proved principally and
  kernel-only: \texttt{cartanE8 * cartanE8inv = 1} by \texttt{decide} on the 8$\times$8 PRODUCT gives
  \texttt{IsUnit (det E8)} via $\det E_8\cdot\det E_8^{-1}{=}\det 1{=}1$ --- no 8! determinant, no
  \texttt{native\_decide} (Mathlib itself leaves \texttt{E\textsubscript{8}\_det = 1} a \texttt{proof\_wanted}).
\item \textbf{\texttt{Mu4Commutation.lean} (\texttt{FORM.MU4COMM.01}, Lean 4, \mE).} The v201/v323 mark-locality
  criterion as exact linear algebra over the Gaussian integers $\Z[i]$: $i^4{=}1$, $i^2{=}-1$, and (on concrete
  $6\times6$ matrices) an offset-4 coupling commutes with the $\mu_4$ clock while an offset-2 coupling does not ---
  all by kernel \texttt{decide}.  Built \texttt{lake build} on Lean v4.29.1 $+$ Mathlib.
\end{itemize}

\subsection*{2026-06-22 (frontier round: the OS step discharged at the many-body level, the ambient measure built on the gap-decoupled sector, and the carrier Cartan determinants grounded in Lean: \texttt{v329}, \texttt{v330}, \texttt{FORM.CARTAN.DET.01})}
\begin{itemize}
\item \textbf{\texttt{v329\_os\_gap\_reduction.py} (\texttt{QGEO.OSGAP.01}, \mE/\mO).} The one analytic input the v308
  keystone chain still cited --- ``the OS-reconstructed bulk gap $=$ the transfer gap'' --- is discharged at the
  many-body level: the OS/Euclidean Hamiltonian is the second quantization $d\Gamma(-\log T)$, whose spectrum is the
  set of sums of single-mode energies, so the bulk gap $=$ the smallest positive single-mode energy $=6\ln\tfrac32$,
  \emph{independent of system size}.  Together with $H\Rightarrow\omega\circ\rho{=}\omega$ and $H\Rightarrow$ SRE
  $\Rightarrow(E_8)_1$, this exhibits the rotation-invariant flat-pillowcase premise $H$ as the \emph{single
  sufficient premise} of both bedrock IDs; residual $=$ the necessity of $H$ on the raw collar.
\item \textbf{\texttt{v330\_qgamb\_admissible\_measure.py} (\texttt{QGAMB.MEASURE.01}, \mE/\mO).} The constructive
  step \texttt{v275}'s roadmap calls for: on the gap-decoupled \emph{admissible} sector the ambient measure is built
  as a bona fide OS object --- reflection-positive (symmetric PSD transfer), exponentially clustering
  ($C(n)/C(n{-}1)\to(2/3)^6$), with finite susceptibility $\chi=729/665$ so $\mathrm{Var}(S_\Lambda)/\Lambda\to\chi$
  converges $\Rightarrow$ uniform tightness (Prokhorov) $\Rightarrow$ the projective limit exists; OS reconstruction
  gives $H_{\mathrm{OS}}\ge0$ with gap $6\ln\tfrac32$.  The full $\mathrm{QG}_{\mathrm{amb}}$ (the metric sector)
  stays open, gap-decoupled --- a genuine \emph{partial} construction, not a closure.
\item \textbf{\texttt{CartanDeterminants.lean} (\texttt{FORM.CARTAN.DET.01}, Lean 4, \mE).} The carrier piece of the
  holomorphy/anyon discriminator is grounded in real \texttt{Matrix.det} computations (kernel \texttt{decide}, no
  extra axiom): $|\det\mathrm{Cartan}(A_3)|{=}4{=}|\mu_4|$ (3$\times$3, \texttt{det\_fin\_three}) and
  $|\det\mathrm{Cartan}(D_5)|{=}4$ (5$\times$5, \texttt{decide}), giving the carrier $|\det\mathrm{Gram}|{=}4\cdot4{=}16$
  (the \texttt{v281} anyon count).  The rank-8 $E_8/D_8$ case stays the Nat discriminator --- Mathlib's own
  \texttt{Data.Matrix.Cartan} leaves \texttt{E\textsubscript{8}\_det = 1} as a \texttt{proof\_wanted}.  Built
  \texttt{lake build} on Lean v4.29.1 $+$ Mathlib.
\end{itemize}

\subsection*{2026-06-22 (next-steps round: the keystone collapsed to one shared premise (Lean $+$ one citable theorem), the $F_{\mathrm{transfer}}$ solver suite, the cusp weight derived from a minimal rewrite, and the $\theta_{13}$ pressure point: \texttt{FORM.QGEO.BW.01}, \texttt{v325}, \texttt{v326}, \texttt{v327}, \texttt{v328})}
\begin{itemize}
\item \textbf{\texttt{BWKeystone.lean} (\texttt{FORM.QGEO.BW.01}, Lean 4, \mE/\mO).} The \texttt{v323} Bisognano--Wichmann
  linkage formalised: the nodes $\textsf{RotationInvariantVacuum}\to\textsf{GeometricModularFlow}\to
  \textsf{Mu4ModularSymmetry}\to\textsf{StateInvariance}$ (=\texttt{QGEO.SYM.01}) composed over the \texttt{v308} chain.
  The theorem \texttt{bedrockReducesToRotationInvariance} shows the WHOLE bedrock \texttt{QGEO.SYM.01} reduces to
  the SINGLE shared open premise \texttt{RotationInvariantVacuum} --- the two open bedrock items collapse to one ---
  with \texttt{\#print axioms} confirming the residual $=$ the cited chain steps $+$ recovery gap $+$ the named BW
  steps $+$ that one premise.  Plus a \texttt{decide}-proven discriminator $(1\mid4)\wedge\neg(4\mid1)$ (BW geometric
  flow strictly stronger than \texttt{v309} clock invariance).  Built \texttt{lake build} on Lean v4.29.1 $+$ Mathlib.
\item \textbf{\texttt{v325\_pillowcase\_keystone.py} (\texttt{QGEO.KEYSTONE.01}, \mE/\mO).} The keystone as ONE
  citable theorem: IF the raw seam state is the flat $\tau{=}i$ pillowcase (rotation-invariant) state THEN the whole
  bedrock closes (4 square marks, $\mu_4$ deck, $\omega\circ\rho{=}\omega$, holomorphic $c{=}8\Rightarrow(E_8)_1$,
  with the recovery gap as input); all pieces machine-checked (incl.\ the pillowcase $\chi_{\mathrm{orb}}{=}0$), the
  single open lemma shared by both bedrock IDs and Lean-pinned.  An assembly certificate, not a closure.
\item \textbf{\texttt{v326\_ftransfer\_suite.py} (\texttt{FR.SUITE.01}, \mE/\mC).} The four $F_{\mathrm{transfer}}$
  readouts productised into one runnable harness, each a gapped relaxation to a unique attractor: $F_{\mathrm{pole}}$
  (Koide, seam rate $(2/3)^6$), $F_{\mathrm{Boltzmann}}$ ($\eta_B$, H-theorem), $F_{\mathrm{relic}}$ (axion adiabatic
  invariant), $F_{\mathrm{QCD}}$ ($m_p/m_e$, RG to the UV fixed point), plus the $F_{\mathrm{RareKaon}}$ bridge.
  Only $F_{\mathrm{pole}}$ carries the seam rate; the four external rates are honestly fenced (\texttt{v187}/\texttt{v303}).
\item \textbf{\texttt{v327\_hypergraph\_rewrite.py} (\texttt{HYP.REWRITE.01}, \mE/\mO).} The cusp weight $2/3$ is
  DERIVED from a minimal rewrite: a 3-channel/1-absorbing family rule has spectrum $\{1,2/3,0\}$, so
  $2/3{=}(\Nfam{-}1)/\Nfam{=}|\Z_2|/\Nfam$ emerges from the rule arity and $(2/3)^6{=}64/729$ is the recovery gap;
  with a PROOF that $2/3$ is not a root of the affine-$E_8$ charpoly ($p(2/3){=}-3520/19683\ne0$, sharpening \texttt{v312}).
  \texttt{v324}'s injected datum is reduced to the anchor arity $\{2,3\}$.
\item \textbf{\texttt{v328\_theta13\_pressure.py} (\texttt{FLAV.TH13.PRESSURE.01}, \mC/\mX) $+$ \texttt{v307}
  hardening.} The honest weak spot named and quantified: $\sin^2\theta_{13}{=}\phiz e^{-5/6}{=}0.023108$ is
  $+2.0\sigma$ above NuFIT 6.0 NO, a SEPARATE carrier-trace channel (\texttt{v268}), not relieved by any
  freeze-respecting correction (RG $<1\%$, exponent $5/6$ exact), pre-registered as the kill.  The \texttt{v307}
  watchdog gains a data provenance/date check and the rare-kaon $F_{\mathrm{transfer}}$ bridge row.
\item \textbf{Wolfram mirror $285\to288$.} \texttt{v325} ($\chi_{\mathrm{orb}}{=}0$) and \texttt{v327} (rewrite
  spectrum $\{0,2/3,1\}$, $(2/3)^6{=}64/729$, and the non-graph-spectral proof) added to
  \texttt{tfpt\_readouts\_extension.wl}; \texttt{GATE.WOLFRAM.02} and the Wolfram README updated to $288/288$.
\end{itemize}

\subsection*{2026-06-22 (consistency + de-accretion editorial pass: current-state alignment across papers, website and ledger; no new modules)}
\begin{itemize}
\item \textbf{Keystone naming reconciled to \texttt{SEAM.EQUIV.01}.} Following \texttt{v323}/\texttt{QGEO.BW.01}
  (the deck premise is downstream of the seam being a chiral net), the single named open keystone is now
  \texttt{SEAM.EQUIV.01} \emph{everywhere}, with \texttt{QGEO.SYM.01} stated as its \emph{downstream}
  conformal-deck face. The ledger row \texttt{QGEO.SYM.01} was updated (it no longer calls itself ``the single
  structural residual of the whole theory''; it now depends on \texttt{SEAM.EQUIV.01}/\texttt{QGEO.BW.01}), and
  the superseded ``\texttt{GATE.QGEO} open gate'' / ``two research gates $(U_{\mathrm{wall}})$ and
  $G_{\mathrm{metric}}$'' framing was replaced by the current $\text{Rest}=v_{\mathrm{geo}}\oplus G_{\mathrm{net}}
  \oplus F_{\mathrm{transfer}}$ with the two structural items \texttt{SEAM.EQUIV.01} $+$ \texttt{QG.AMB.01}
  (intro status card, \texttt{tfpt\_4\_frontier}, \texttt{origin\_theory}, \texttt{tfpt\_5\_redteam},
  \texttt{tfpt\_research\_contracts}, and the website).
\item \textbf{De-accretion: the sprint-by-sprint reduction history was moved to this changelog, where it belongs.}
  Several reader-facing sections had grown by accretion (each round appended a clause). They were rewritten to
  state the \emph{current} result once, with the round-by-round narrative left here: the introduction closure
  ledger (``honest bottom line'') and hard-reduction subsection; the \texttt{origin\_theory} ``residual
  inventory'' (the five ``Update/\ldots/Terminal'' passes collapsed to one current inventory); the
  \texttt{tfpt\_5\_redteam} Target-A Outcome; and on the website the FAQ ``What is still open?'', the
  \texttt{OpenGates} closing-condition block, the \texttt{papers.ts} research-contracts/red-team entries, the
  verification-DAG \texttt{qft} node, the glossary \texttt{G\_net} entry, the Rosetta lexicon, and the
  verification/review pages. No scientific content or \texttt{\textbackslash veri} citation was dropped; only the
  embedded version-stamp logs were removed.
\item \textbf{Stale facts corrected.} Version label \texttt{5.0}$\to$\texttt{v5.2} (intro, single-sourced via
  \texttt{\textbackslash TFPTversion}); Lean build \texttt{1886}$\to$\texttt{3357} jobs (\texttt{FORM.SEAMEQUIV.01});
  README Python suite \texttt{v213}/\,212$\to$\texttt{v324}/\,322 modules; Wolfram extension
  \texttt{269/269}\,/\,\texttt{249/249}$\to$\texttt{285/285} (README, website replication page,
  \texttt{zenodo\_description.html}); residual ``Paper-3'' old-paper attributions in \texttt{tfpt\_2} neutralised.
\end{itemize}
\noindent\emph{(Original 2026-06-22 entry follows.)}

\subsection*{2026-06-22 (external-review pass: a registry bug fix, the NA62 2026 rare-kaon update, CP-phase prose hygiene, and three firewall/visualisation enhancements: \texttt{v202}, \texttt{v203}, \texttt{v305}, \texttt{v307}, \texttt{v321})}
\begin{itemize}
\item \textbf{Bug fix --- $\delta_{\mathrm{CKM}}$ display value.} The predictions table (\texttt{tex-artefacts/predictions.tex})
  showed $\delta=\tfrac\pi3+3\lambda^2=66.96^\circ$, but that formula evaluates to $68.65^\circ$ (the canonical
  frozen \texttt{DELTA\_CKM\_RAD}$=1.198232$ rad, used by \texttt{v88}/\texttt{v202}/\texttt{FLAV.CP.01}
  everywhere else). Corrected to $68.65^\circ$. An external review correctly flagged the inconsistency; it was an
  isolated display typo (the website was already clean).
\item \textbf{\texttt{v202\_rare\_kaon.py} --- NA62 2016--2024 update (\mE/\mC).} The charged-mode comparison is
  moved from the historical NA62 $2016$--$2022$ observation $(13.0^{+3.3}_{-3.0})\times10^{-11}$ ($\sim1.2\sigma$
  above) to the full $2016$--$2024$ combination $\mathrm{BR}(K^+)=(9.6^{+1.9}_{-1.8})\times10^{-11}$
  (La~Thuile~2026), on which the prediction $9.45\times10^{-11}$ lands at $+0.08\sigma$. Framed honestly: a strong
  \emph{consistency} hit for the closed CKM point, but an $F_{\mathrm{transfer}}$ bridge --- \emph{not} a unique
  TFPT-vs-SM discriminator (the SM $(8.6\pm0.4)\times10^{-11}$ is also inside the NA62 error). Propagated to the
  ledger (\texttt{FR.RAREKAON.01}), \texttt{freeze\_file} (new \texttt{rare\_kaon} kill row), the watchdog
  (\texttt{v307}, a new $F_{\mathrm{transfer}}$ bridge row), the forward board (\texttt{v321}, rank 9), and
  \texttt{tfpt\_2\_standard\_model} $+$ the website.
\item \textbf{CP-phase prose hygiene.} The Galois CP lock is tightened from ``a relation to the \emph{measured}
  quark phase'' to ``a relation to the \emph{leading} ($\pi/3$) component of the quark phase'': the lock is to the
  structural $\pi/3$, not the full measured $\gamma=\delta_{\mathrm{CKM}}^{\mathrm{lead}}+3\lambda_C^2\approx68.7^\circ$,
  so $\delta_{\mathrm{PMNS}}=240^\circ$ (not $248.7^\circ$). Fixed in \texttt{tfpt\_2\_standard\_model},
  \texttt{origin\_theory}, \texttt{papers.ts} and \texttt{predictions.ts}.
\item \textbf{\texttt{v305\_witness\_independence.py} --- the No-Golden-Dynamics rule (\mE).} The number-field
  split is made an explicit anti-numerology firewall rule: $\phi=2\cos(\pi/5)\in\mathbb Q(\sqrt5)$ is the
  \emph{static} carrier ($\Z/5$) field, every \emph{dynamic} rate is rational ($\mathbb Q$, the $\Z/6$ hand), so a
  dynamic rate explained by $\phi$ is a cross-field false friend (\texttt{v314}/\texttt{v315}).
\item \textbf{\texttt{v203\_eht\_achromatic.py} --- the $\mu_4$ Fourier fourth null (\mX).} The EHT residual
  pre-registration gains a fourth null: the azimuthal residual must carry power \emph{only} at $m\equiv0\bmod4$
  (the $\mu_4$ fingerprint of the four marks, \texttt{v201}); a $\mu_4$-orbit profile has $\sim0$ off-mode power
  while a $\Z_2$ control leaks at $m=2$.
\item \textbf{Seed-hyperplane figure (Fig.~\ref{fig:seed-hyperplane}).} A new figure visualises \texttt{v306}:
  every scorecard observable inverts \emph{independently} to the one latent seed $\varphi_0$, the error-weighted
  mean matching the axiom to $0.04\%$, with $\sin^2\theta_{13}$ the $\sim2\sigma$ pressure point. Added to
  \texttt{make\_figures.py}, \texttt{tfpt\_5\_redteam} and the manifest.
\end{itemize}

\subsection*{2026-06-22 (Wolfram mirror of the arithmetic arc $+$ three sharpening steps: the CP-lock made quantitative, the Bisognano--Wichmann keystone, the minimal hypergraph fibre: \texttt{v322}, \texttt{v323}, \texttt{v324})}
\begin{itemize}
\item \textbf{Wolfram mirror of the cyclotomic/Galois arithmetic arc (the independent second path).} The exact
  algebraic results of the arc are now mirrored in \texttt{verification/wolfram/tfpt\_readouts\_extension.wl} (ten new
  \texttt{checkExact} blocks, $275\to285$, \emph{all passing}): \texttt{v313} (the affine-$E_8$ characteristic
  polynomial with the golden factor $x^2{-}x{-}1$; the $(2,3,5)$ atoms as
  $2\cos(\pi/k)$; the $31/30$ selection), \texttt{v314} (the rational kernel vs $\mathbb Q(\sqrt5)$
  dynamic-rate split), \texttt{v315} ($30{=}5{\cdot}6$, $\varphi(30){=}8$, the Galois group $\mu_4\times\Z_2$, the
  $\sqrt5$ Gauss sum), \texttt{v316} ($\rho{=}\zeta_6{=}\zeta_{30}^5$, $\rho^4{=}-\rho$, $\mathrm{Gal}{=}\Z_2{=}$ CP
  conjugation), \texttt{v317} ($\Nfam{=}3$ as the $\mu_3$ orbit, the $1{+}2$ Galois split), \texttt{v318}
  ($\phiz{=}(4/3)\cthree{+}48\cthree^4$ a pure function of $\pi$) and \texttt{v320} (the CP lock
  $\delta_{\mathrm{PMNS}}{=}240^\circ$). Ledger \texttt{GATE.WOLFRAM.02} and the Wolfram README updated to $285/285$.
\item \textbf{\texttt{v322\_cp\_lock\_sharpened.py} (\texttt{GALOIS.CP.SHARPEN.01}, \mE/\mC/\mX).} The \texttt{v320}
  CP-lock sharpened into a quantitative, pre-registered kill test. \mE\ the leading phase sits on the six hexagonal
  nodes $\arg\rho^k{=}k\cdot60^\circ$, and \emph{which} one is selected is the deck order:
  $\delta_{\mathrm{PMNS}}^{\mathrm{lead}}{=}|\mu_4|\,\delta_{\mathrm{CKM}}^{\mathrm{lead}}{=}4(\pi/3)$ (node $4$);
  \mC\ the sub-leading correction is bounded by the quark analogue $3\lambda^2\approx8.7^\circ$, so the prediction is
  the band $240^\circ\pm\sim9^\circ$; \mC\ against NuFIT~6.0 (NO, $\delta_{CP}{=}212^{+26}_{-41}{}^\circ$) the leading
  value is $+1.08\sigma$, the band edge $+0.74\sigma$ -- compatible today; \mX\ the nearest wrong node is $60^\circ$
  away, far beyond the budget, so DUNE/Hyper-K ($\sim5$--$15^\circ$) discriminate cleanly. Cited in
  \texttt{origin\_theory}; ledger \texttt{GALOIS.CP.SHARPEN.01}.
\item \textbf{\texttt{v323\_bw\_geometric\_modular.py} (\texttt{QGEO.BW.01}, \mE/\mC/\mO).} The keystone pushed one
  honest step via Bisognano--Wichmann. \mE\ the $\mu_4$ clock is a geometric rotation
  $\rho{=}\mathrm{diag}(i^n){=}\exp(i\tfrac\pi2 L)$, $\mu_4\subset U(1)_{\mathrm{rot}}$; \mE\ for a rotation-covariant
  covariance $C{=}f(L)$ the modular Hamiltonian $K{=}\log((1{-}C)/C){=}g(L)$, so $[K,L]{=}0$ (the modular flow is
  geometric) and the clock is a modular symmetry \emph{for free} (the discriminator: a period-$4$ curvature preserves
  the clock but its flow is not geometric, $[K,L]\ne0$); \mC\ given the seam is the $(E_8)_1$ chiral net
  (\texttt{v308}), BW/Hislop--Longo make the vacuum modular flow geometric, so \texttt{QGEO.SYM.01}
  ($\omega\circ\rho{=}\omega$) is \emph{downstream} of \texttt{SEAM.EQUIV.01} $+$ a rotation-invariant vacuum, not an
  independent axiom; \mO\ residual: the raw collar vacuum is rotation-invariant (cleaner than \texttt{v309}, shared
  with \texttt{v308}). Cited in \texttt{origin\_theory}; ledger \texttt{QGEO.BW.01}.
\item \textbf{\texttt{v324\_hypergraph\_fiber.py} (\texttt{HYP.FIBER.01}, \mE/\mC).} The constructive \texttt{v312}
  follow-up: the \emph{minimal} substrate that carries both the $E_8$ skeleton and the recovery gap is a
  \emph{product}. \mE\ the carrier network $T_{\mathrm{net}}{=}(A{+}2I)/4$ (attractor $=$ Kac marks $=$ skeleton)
  fibred by the $3$-node family cusp $T_{\mathrm{cusp}}{=}\mathrm{diag}((1{-}w)^{2\Nfam})$, $w\in\{0,\tfrac13,\tfrac23\}$
  (spectrum $\{1,(2/3)^6,(1/3)^6\}$); the fibred $T_{\mathrm{net}}\otimes T_{\mathrm{cusp}}$ has top eigenvalue $1$
  (eigenvector $\mathrm{marks}\otimes(w{=}0)$) and $(2/3)^6$ as a genuine eigenvalue ($\mathrm{marks}\otimes(w{=}\tfrac13)$)
  -- the $\Nfam{=}3$ cusp is the minimal fibre and the substrate $=$ carrier $\times$ family $=$ the
  $30{=}\gcar(2\Nfam){=}5{\times}6$ of \texttt{v315}; \mC\ honestly (\texttt{v312}) the cusp weight is still
  \emph{injected}, not derived from the graph -- a consistent realisation, not a derivation of $2/3$ from a pure
  rewrite. Cited in \texttt{origin\_theory}; ledger \texttt{HYP.FIBER.01}.
\end{itemize}

\subsection*{2026-06-22 (the forward kill-test board: the decisive upcoming measurements ranked, each locked to a freeze row --- incl. the new Galois-CP relation: \texttt{v321})}
\begin{itemize}
\item \textbf{\texttt{v321\_killtest\_board.py} (\texttt{KILL.BOARD.01}, \mE).} The forward companion to \texttt{v307}
  (the current-data board): the decisive \emph{upcoming} measurements, ranked and each locked to a
  \texttt{freeze\_file.csv} kill row -- \#1 JUNO $\sin^2\theta_{12}{=}0.306747$ (fastest), \#2 CMB-S4/LiteBIRD $r$
  (kill $r{>}0.01$), \#3 DESI/Euclid $w$ (kill $w{\ne}{-}1$), \#4 DUNE/Hyper-K $\delta_{\mathrm{PMNS}}{=}240^\circ$
  (the new \texttt{v320} Galois-CP relation), \#5 DUNE/LEGEND/nEXO ordering$+m_{\beta\beta}$, \#6 PSI n2EDM, \#7 JUNO
  $\sin^2\theta_{13}$ ($\sim2\sigma$ now), \#8 LiteBIRD $\beta$. A forward decision ledger (publicly-stated
  experimental reach), complementing \texttt{v307}; no new physics. Cited in \texttt{origin\_theory}; ledger row
  \texttt{KILL.BOARD.01}.
\end{itemize}

\subsection*{2026-06-22 (Lean: the \texttt{SEAM.EQUIV.01} composition chain formalised --- the keystone residual machine-pinned to the named cited steps: \texttt{FORM.SEAMEQUIV.01})}
\begin{itemize}
\item \textbf{\texttt{SeamEquivChain.lean} (\texttt{FORM.SEAMEQUIV.01}, Lean 4, \mE/\mO).} A Lean~4 mirror of the
  \texttt{v308} closing chain: the four nodes $\textsf{GapPositive}\to\textsf{InvertibleSRE}\to\textsf{HolomorphicC8}
  \to\textsf{SeamIsE8}$ assembled as a well-typed composition theorem \texttt{seamEquivChain}, with the three cited
  literature steps (Kitaev free-fermion invertibility; M\"uger / Kawahigashi--Longo--M\"uger holomorphy;
  Conway--Sloane $E_8$ uniqueness) as named \texttt{axiom}s and the carrier recovery gap (the OS step) as the single
  open input. \mE\ \texttt{\#print axioms seamEquivChain} confirms the residual is exactly those named steps $+$
  \texttt{recovery\_gap} (no hidden assumption); \mE\ a \texttt{decide}-proven discriminator
  $\textsf{primariesE8}=1\ne\textsf{primariesD8}=4$ (the $|\det\mathrm{Cartan}|$ that separates the holomorphic
  $E_8$ from the same-$c$ rival $D_8{=}SO(16)$). Built end-to-end (\texttt{lake build}, 3357 jobs) on Lean
  v4.29.1 $+$ Mathlib. \mO\ The value is the machine-checked composition $+$ axiom audit (pinning the keystone
  residual), \emph{not} a from-scratch proof --- it does NOT close \texttt{SEAM.EQUIV.01}. Ledger row
  \texttt{FORM.SEAMEQUIV.01}; mirrors \texttt{v308}.
\end{itemize}

\subsection*{2026-06-22 (a NEW falsifiable prediction from the Galois structure: the two CP phases are locked, $\delta_{\mathrm{PMNS}}=\delta_{\mathrm{CKM}}^{\mathrm{lead}}+\pi$: \texttt{v320})}
\begin{itemize}
\item \textbf{\texttt{v320\_galois\_cp\_relation.py} (\texttt{GALOIS.CP.PREDICT.01}, \mE/\mC/\mX).} The \texttt{v316}
  follow-up turned into a testable cross-prediction. \mE\ both leading CP phases are powers of the \emph{one}
  hexagonal unit $\rho=\zeta_6$ of the family Galois factor: $\delta_{\mathrm{CKM}}^{\mathrm{lead}}=\arg\rho=\pi/3$
  ($60^\circ$), $\delta_{\mathrm{PMNS}}=\arg\rho^4=4\pi/3$ ($240^\circ$), and $\rho^4=-\rho$ locks them as
  $\delta_{\mathrm{PMNS}}=\delta_{\mathrm{CKM}}^{\mathrm{lead}}+\pi$ (the $\Z_2$ sheet flip); \mC\ this upgrades the
  previously assigned $\delta_{\mathrm{PMNS}}=240^\circ$ to a Galois-forced relation to the measured quark phase
  (the quark and lepton leading CP phases are not independent); \mX\ kill test: a $\delta_{\mathrm{PMNS}}$ robustly
  incompatible with $240^\circ$ ($>3\sigma$ at DUNE/Hyper-K/JUNO) falsifies the Galois-CP organisation; $240^\circ$
  is currently within the broad NuFIT 6.0 range. A genuine new falsifiable consequence of the \texttt{v313}--%
  \texttt{v319} arithmetic arc (also a \texttt{freeze\_file.csv} \texttt{cp\_phase\_relation} kill row). Cited in
  \texttt{origin\_theory}; ledger row \texttt{GALOIS.CP.PREDICT.01}.
\end{itemize}

\subsection*{2026-06-22 (the translation clock: the discrete$\leftrightarrow$dynamic bridge \emph{is} the order-$30$ Coxeter element, a clock with two coprime hands $5\times6$, read law-inclusive ($0..5$) or live-only ($1..5$): \texttt{v319})}
\begin{itemize}
\item \textbf{\texttt{v319\_translation\_clock.py} (\texttt{TRANSLATE.CLOCK.01}, \mE/\mC).} A synthesis of the
  \texttt{v313}--\texttt{v318} arc with \texttt{v124}/\texttt{v55}, answering the question ``is the
  static$\leftrightarrow$dynamic translation a clock running $0,1,2,3,4,5$ or $1,2,3,4,5$?''. \mE\ the only object
  holding both the static carrier ($\mathbb Q(\sqrt5)$) and the dynamic family (rational) data is the order-$30$
  Coxeter element (\texttt{v314}); $30=h(E_8)=\gcar(2\Nfam)=5\cdot6$ and $\gcd(5,6)=1\Rightarrow\Z/30=\Z/5\times\Z/6$
  (two coprime hands, \texttt{v315}). \mE\ the \emph{dynamic} hand is $\Z/6=2\Nfam$ (ticks $0,\dots,5$): the recovery
  exponent is exactly $6=2\Nfam$, rate $(2/3)^6=(|\Z_2|/\Nfam)^{2\Nfam}$, order-$6$ generator $c^5$
  ($\zeta_6=\zeta_{30}^5$, \texttt{v316}). \mE\ position $0$ is the \emph{conserved law} --- the resummed clock
  $\mathrm{rate}(n)=-p_2\ln(1-n/\Nfam)$ (\texttt{v124}) has $\mathrm{rate}(0)=0$ (the attractor, eigenvalue $1$,
  \texttt{v56}), the live decaying modes from $n{=}1$, and the $E_8$ live phases (totatives of $30$) start at $1$
  ($\{1,7,\dots,29\}$), the $0$ phase not a totative --- so ``$0,1,2,3,4,5$'' is law-inclusive, ``$1,2,3,4,5$''
  live-only. \mE\ the \emph{static} hand is $\Z/5=\gcar$ (ticks $1,\dots,5$): the golden field $\mathbb Q(\sqrt5)$
  ($\varphi=2\cos(\pi/5)$), field-obstructed (no rational dynamic image, \texttt{v314}) --- static-only;
  $\zeta_5=\zeta_{30}^6$ carries no phase. \mE\ one full turn $=\operatorname{lcm}(5,6)=30=h(E_8)$, rank
  $E_8=8=\varphi(30)$ live phases pairing into $|\mu_4|=4$ invariant planes (\texttt{v55}). \mC\ verdict: the
  discrete$\to$dynamic translation \emph{is} the order-$30$ clock $=$ (static $5$-ring) $\times$ (dynamic $6$-ring),
  the dynamic hand carrying the rate (exponent $6=2\Nfam$), the static hand the golden carrier (no rate), and
  ``$0$ vs $1$'' $=$ law-inclusive vs live-only; the arithmetic is \mE, the ``it is one clock'' reading \mC.
  Python-only (\texttt{sympy}), like the rest of the arc. New figure \texttt{figures/translation\_clock.pdf}
  (concentric $5$- and $6$-hands). Cited in \texttt{origin\_theory}; ledger row \texttt{TRANSLATE.CLOCK.01}.
\end{itemize}

\subsection*{2026-06-21 (capstone: the SM structural sector is $\mathbb Q(\zeta_{30})+$ Galois $\mu_4\times\Z_2$, and the complete input is $\{a,\pi,v_{\mathrm{geo}}\}$ --- zero dimensionless free parameters: \texttt{v318})}
\begin{itemize}
\item \textbf{\texttt{v318\_arithmetic\_capstone.py} (\texttt{ARITH.CAPSTONE.01}, \mE/\mO).} The synthesis of the
  \texttt{v313}--\texttt{v317} arc. \mE\ the SM \emph{structural} sector (the $3$ generations, the $2$ CP phases,
  their orbit/hierarchy) is the cyclotomic field $\mathbb Q(\zeta_{30})$ with Galois group $\mu_4\times\Z_2$ (degree
  $\varphi(30)=8=$ rank $E_8$, $30=|\Z_2|\Nfam\gcar=h(E_8)$), forced by the anchor atoms $\{2,3,5\}=e(a)$; \mE\ the
  magnitude seed $\varphi_0=(|\mu_4|/\Nfam)c_3+\Omega_{\mathrm{adm}}c_3^4=\tfrac43 c_3+48 c_3^4$ ($c_3=1/(8\pi)$) is a
  pure function of $\pi$ (no free parameters, anchor-derived coefficients), so the magnitudes
  ($\sin^2\theta_{12}=\tfrac13-\varphi_0/2$) are $\{a,\pi\}$-determined, not free; \mE\ free inventory: \emph{zero}
  dimensionless free parameters, $\pi$ the unique transcendental primitive (\texttt{ARCH.CORE.01}), $v_{\mathrm{geo}}$
  the unique dimensionful input (No-Unit Theorem) --- complete input $\{a,\pi,v_{\mathrm{geo}}\}$. \mO\ honest
  residual: this rigidity holds \emph{given} the axioms and does not realise the structure on the raw seam
  (\texttt{QGEO.SYM.01}/\texttt{SEAM.EQUIV.01} stay \mO). Cited in \texttt{origin\_theory}; ledger row
  \texttt{ARITH.CAPSTONE.01}.
\end{itemize}

\subsection*{2026-06-21 (are the 3 generations a $\mu_3$/Galois orbit? Yes ($\mu_3$), Galois-refined $1{+}2$ with the fixed generation $=$ the recovery attractor: \texttt{v317})}
\begin{itemize}
\item \textbf{\texttt{v317\_galois\_family.py} (\texttt{GALOIS.FAMILY.01}, \mE/\mC).} The \texttt{v316} follow-up to the
  generation structure. \mE\ the three cusp weights $\{0,\tfrac13,\tfrac23\}$ (with $\mathrm{Spec}(Q_+)=\{1,2,3\}$,
  the $A_3$ exponents) are the cube roots of unity $\{1,\zeta_3,\zeta_3^2\}$ under $w\mapsto e^{2\pi i w}$, and the
  cyclic family symmetry $w\mapsto w{+}\tfrac13$ is a \emph{transitive} $\mu_3$ orbit (the family IS the cube-root
  orbit); \mE\ the transfer eigenvalues $(1{-}w)^6=\{1,(2/3)^6,(1/3)^6\}$ attach to the weights (attractor $=$
  eigenvalue $1$ at $w{=}0$); \mE\ the family Galois $\Z_2$ ($\zeta_3\mapsto\zeta_3^2=\bar\zeta_3$, $=$ the
  \texttt{v316} CP conjugation) refines the orbit to $1{+}2$ --- fixing $w{=}0$ (rational) and swapping
  $w{=}\tfrac13\leftrightarrow\tfrac23$; \mE\ so the Galois-FIXED generation is the recovery ATTRACTOR (the law) and
  the Galois-conjugate pair the decaying hierarchy. \mC\ verdict: the family STRUCTURE is the same arithmetic as the
  CP phase (a $\mu_3$ orbit, Galois-refined $1{+}2$), the mass MAGNITUDES remaining the analytic seed. Cited in
  \texttt{origin\_theory}; ledger row \texttt{GALOIS.FAMILY.01}.
\end{itemize}

\subsection*{2026-06-21 (does the Galois $\mu_4\times\Z_2$ organize the readouts? Yes --- the CP phases are the family-factor cyclotomic data, Galois $\Z_2=$ CP conjugation: \texttt{v316})}
\begin{itemize}
\item \textbf{\texttt{v316\_galois\_readout.py} (\texttt{GALOIS.READOUT.01}, \mE/\mC).} The \texttt{v315} follow-up to
  phenomenology: does the Galois coupling $\mu_4\times\Z_2$ reach the physics? \mE\ it does, through the \emph{family}
  factor --- the hexagonal CP unit $\rho=\zeta_6=\zeta_{30}^5$ is exactly the order-$6=2\Nfam$ factor $c^5$ of
  \texttt{v315} (the carrier being $\zeta_5=\zeta_{30}^6$); \mC\ the leading CP phases are its cyclotomic arguments
  $\delta_{\mathrm{CKM}}^{\mathrm{lead}}=\pi/3=\arg\zeta_6$ and $\delta_{\mathrm{PMNS}}=4\pi/3=\arg\zeta_6^4$ (power
  $4=|\mu_4|$), with $\zeta_6^4=-\zeta_6$ the $\Z_2$ sheet flip and $\mu_6=\mu_3\times\mu_2$ (inherits
  \texttt{v231}/\texttt{v233}); \mE\ the family Galois $\mathrm{Gal}(\mathbb Q(\zeta_6)/\mathbb Q)=\Z_2$
  ($\zeta_6\mapsto\zeta_6^5=\bar\zeta_6$) \emph{is} CP conjugation $\delta\mapsto-\delta$; \mE\ the carrier factor
  $\zeta_5$ (golden $\sqrt5$) carries no phase ($\mu_4$ static), and the magnitudes
  ($\sin^2\theta_{12}=\tfrac13-\varphi_0/2$, transcendental $\varphi_0$) are not cyclotomic. \mC\ verdict: the Galois
  bridge reaches phenomenology in the phase sector predicted by the \texttt{v314} field split. Cited in
  \texttt{origin\_theory}; ledger row \texttt{GALOIS.READOUT.01}.
\end{itemize}

\subsection*{2026-06-21 (couple or factorize? the order-30 Coxeter element couples the carrier and family sectors as a cyclotomic compositum, Galois $=\mu_4\times\Z_2$: \texttt{v315})}
\begin{itemize}
\item \textbf{\texttt{v315\_coxeter\_coupling.py} (\texttt{COX.COUPLE.01}, \mE/\mC).} Answers the \texttt{v314}
  question --- does $30=\gcar(2\Nfam)=5\cdot6$ couple the carrier ($5$-fold, golden, $\mathbb Q(\sqrt5)$) and family
  ($6=2\cdot3$, rational) sectors, or just factorize? \mE\ the cyclic group \emph{factorizes}: $\gcd(5,6)=1\Rightarrow
  \Z/30=\Z/5\times\Z/6$ (direct product, group-decoupled, in line with the \texttt{v314} field obstruction); \mE\ the
  $E_8$ exponents $=$ totatives$(30)$ split as totatives$(5)\times$ totatives$(6)$, $\varphi(30)=4\cdot2=8=$ rank
  $E_8$; \mE\ but the \emph{field} couples: $\mathbb Q(\zeta_{30})$ is the compositum of the carrier
  $\mathbb Q(\zeta_5)\ni\sqrt5$ and the family $\mathbb Q(\zeta_3)$, degree $8=$ rank $E_8$; \mE\ the Galois group is
  exactly $(\Z/5)^\times\times(\Z/3)^\times=\Z/4\times\Z/2=\mu_4\times\Z_2$ (order $8$, max element order $4$), so the
  $\mu_4$ seam clock \emph{is} the Galois group of the carrier's golden field and $\Z_2$ that of the family field
  (refining \texttt{v223}); \mE\ $\sqrt5=\phi+1/\phi$ is the quadratic Gauss sum in $\mathbb Q(\zeta_5)$. \mC\ verdict:
  $30=5\cdot6$ does not dynamically entangle the sectors --- it couples them as the cyclotomic compositum, the
  static$\leftrightarrow$dynamic bridge being \emph{Galois}, not a dynamical map. Cited in \texttt{origin\_theory};
  ledger row \texttt{COX.COUPLE.01}.
\end{itemize}

\subsection*{2026-06-21 (do the discrete-kernel and dynamic rates translate? An exact number-field split $\mathbb Q$ vs $\mathbb Q(\sqrt5)$: \texttt{v314})}
\begin{itemize}
\item \textbf{\texttt{v314\_rate\_translation.py} (\texttt{RATE.TRANSLATE.01}, \mE/\mC).} Answers, exactly, whether
  the discrete kernel (the affine-$E_8$ network, carrying the golden ratio) and the dynamic part (the seam transfer,
  carrying the recovery rate $(2/3)^6$) translate. \mE\ FIELD SPLIT: the adjacency spectrum is the rational part
  $\{0,\pm1,\pm2\}\subset\mathbb Q$ plus the golden part $\{\pm\phi,\pm1/\phi\}\subset\mathbb Q(\sqrt5)$, while the
  transfer spectrum $\{1,(2/3)^6,(1/3)^6\}$ is \emph{entirely} rational; \mE\ the family/sheet rates DO translate
  (the rational angles $2\cos(\pi/2){=}0=|\mathbb Z_2|$ and $2\cos(\pi/3){=}1=\Nfam$ build
  $(2/3)^6=(|\mathbb Z_2|/\Nfam)^{2\Nfam}\in\mathbb Q$, same field, same atoms), but \mE\ the carrier $5$-fold
  (golden, $\mathbb Q(\sqrt5)$) has NO rational dynamic image -- a field obstruction ($2/3$ is neither an adjacency
  nor a lazy-update eigenvalue; heat-kernel $t=\Delta/(2-\phi)\approx6.37$ not clean), so the carrier is
  \emph{static-only}; \mE\ the only object holding both is the order-$30$ Coxeter element
  $30=\gcar(2\Nfam)=5\cdot6$, and the $\phi$-quasicrystal $E_8=H_4{+}\phi H_4$ ($240=2\cdot120$) carries the carrier
  but not the (rational, $3$-fold) cusp-weight family dynamics. Cited in \texttt{origin\_theory}; ledger row
  \texttt{RATE.TRANSLATE.01}.
\end{itemize}

\subsection*{2026-06-21 (the golden ratio made precise: the $(2,3,5)$ atoms are the affine-$E_8$ network spectral angles, $\phi=2\cos(\pi/5)$ the $\gcar{=}5$ signature: \texttt{v313})}
\begin{itemize}
\item \textbf{\texttt{v313\_golden\_atoms\_spectral.py} (\texttt{GOLD.ATOMS.01}, \mE/\mC).} A follow-up to \texttt{v312}'s
  observation, made exact. \mE\ the affine-$E_8$ adjacency characteristic polynomial factors as
  $x(x^2{-}4)(x^2{-}1)(x^2{-}x{-}1)(x^2{+}x{-}1)$, so the golden minimal polynomial $x^2{-}x{-}1$ divides it and
  $\phi=2\cos(\pi/5)=(1{+}\sqrt5)/2$ is an \emph{exact} eigenvalue; \mE\ the non-trivial eigenvalues are
  $2\cos(\pi/k)$ for exactly $k\in\{2,3,5\}=\{|\mathbb Z_2|,\Nfam,\gcar\}$ ($2\cos(\pi/2){=}0$, $2\cos(\pi/3){=}1$,
  $2\cos(\pi/5){=}\phi$, $2\cos(2\pi/5){=}1/\phi$), so the golden ratio is \emph{specifically} the $\gcar{=}5$
  ($5$-fold) signature and $\gcar{=}5$ gains a new spectral witness distinct from Pascal/Riemann--Roch (raising the
  \texttt{v305} multiplicity); \mE\ the $(2,3,5)$ spherical excess $1/2{+}1/3{+}1/5=31/30>1$ (the condition selecting
  the finite $2I\Rightarrow E_8$) ties the \texttt{v63}/\texttt{v76} gap-margin numerator $31=2^{\gcar}{-}1=248/8=1{+}h(E_8)$
  to the Coxeter $30=h(E_8)$ --- a unification of already-anchored quantities, NOT new evidence (honest
  anti-numerology, \texttt{v305}); \mE\ honest null: $\phi$ is a structural lattice/network quantity, not a
  phenomenological readout. \mC\ direction: $\phi$ is the $E_8$-quasicrystal (Elser--Sloane cut-and-project) ratio,
  a candidate aperiodic substrate for the \texttt{v312} question. Cited in \texttt{origin\_theory}; ledger row
  \texttt{GOLD.ATOMS.01}.
\end{itemize}

\subsection*{2026-06-21 (TOE-roadmap solver round: the \texttt{SEAM.EQUIV.01} keystone certificate, the modular bedrock, the carrier$\to$SM closure, the gap-decoupled measure, and the sharpened hypergraph substrate: \texttt{v308}--\texttt{v312})}
\begin{itemize}
\item \textbf{\texttt{v308\_seam\_equiv\_chain.py} (\texttt{SEAM.EQUIV.CHAIN.01}, \mE/\mO).} TOE attack point~1:
  the keystone ``the raw seam-Calder\'on net is the holomorphic $c{=}8$ $(E_8)_1$ net'' assembled into ONE
  well-typed logical chain $\text{gap}{>}0\to\text{invertible/SRE (Kitaev)}\to\text{holomorphic }c{=}8\
  (\text{M\"uger/KLM})\to(E_8)_1\ (\text{Conway--Sloane})$, with the exact discriminators
  $|\det\mathrm{Cartan}(E_8)|{=}1$ vs $|\det\mathrm{Cartan}(D_8{=}SO(16))|{=}4$, the carrier tower
  $4{\cdot}4{=}16\to4\to1$ and $c{=}\gcar{+}\Nfam{=}8$ all machine-checked; the input gap is the derived recovery gap
  $6\ln(3/2){>}0$. The only undischarged premise is the cited OS step --- an assembly/reduction certificate (a Lean
  target), not an end-to-end closure. Cited in \texttt{tfpt\_research\_contracts}; ledger row \texttt{SEAM.EQUIV.CHAIN.01}.
\item \textbf{\texttt{v309\_modular\_bedrock.py} (\texttt{QGEO.MODHAM.01}, \mE/\mO).} TOE attack point~2: the bedrock
  $\omega{\circ}\rho{=}\omega$ via an explicit modular Hamiltonian, non-circular --- the four marks come from
  Gauss--Bonnet (\texttt{v216}) and the order-$4$ clock from cross-ratio $2$ (\texttt{v214}), so $\mu_4$ is derived;
  the quasi-free modular Hamiltonian $K=\log((1{-}C)/C)$ round-trips to the seam operator and $[\rho,K]{=}0
  \Leftrightarrow\omega{\circ}\rho{=}\omega$ (a $\mathbb Z_2$ profile breaks it). Reduces the bedrock to the
  Bisognano--Wichmann intrinsicality of the raw collar; not a closure of \texttt{QGEO.SYM.01}. Cited in
  \texttt{tfpt\_research\_contracts}; ledger row \texttt{QGEO.MODHAM.01}.
\item \textbf{\texttt{v310\_carrier\_sm\_anomaly.py} (\texttt{CAR.SM.ANOM.01}, \mE).} TOE attack point~3: the carrier
  half-spinor $16=\Lambda^{\mathrm{even}}(\mathbb C^5)=1{+}10{+}5$ is exactly one anomaly-free Standard-Model
  generation ($SU(5)\subset SO(10)$: $10{+}\bar5{+}1$), with $\sum Y=\sum Y^3=[SU(2)]^2U(1)=[SU(3)]^2U(1)=0$ (exact)
  and the one-loop $(b_1,b_2,b_3)=(\tfrac{41}{10},-\tfrac{19}{6},-7)$; a fourth family shifts $b_1$, so $\Nfam{=}3$
  pins the RG. Closes the spectrum/anomaly/$\beta$ sub-question; the interacting Epstein--Glaser $S$-matrix and the
  Yukawa sector stay \mC/\mO. Cited in \texttt{tfpt\_research\_contracts}; ledger row \texttt{CAR.SM.ANOM.01}.
\item \textbf{\texttt{v311\_gap\_decoupled\_measure.py} (\texttt{QGAMB.CLUSTER.01}, \mE/\mC/\mO).} TOE attack point~4:
  the physical QG measure as a gap-decoupled, exponentially-clustering object --- the transfer spectrum
  $\{1,(2/3)^6,(1/3)^6\}$ gives geometric clustering at rate $(2/3)^6$ (correlation length $1/(6\ln(3/2))$, finite
  susceptibility $729/665$), and the \texttt{v76} margin $6\ln(3/2)-31/(4\pi^2){\approx}1.648{>}0$ decouples the
  physical sector from the un-built ambient. \texttt{QG.AMB.01} stays \mO\ (gap-decoupled, inert). Cited in
  \texttt{tfpt\_research\_contracts}; ledger row \texttt{QGAMB.CLUSTER.01}.
\item \textbf{\texttt{v312\_hypergraph\_substrate.py} (\texttt{HYP.INJECT.01}, \mE/\mO).} TOE attack point~5: the
  hypergraph substrate sharpened --- the affine-$E_8$ Kac marks are the Perron eigenvector ($A\,m{=}2m$) and the
  subleading eigenvalue is exactly $2\cos(\pi/5)=$ the golden ratio, but the recovery rate $(2/3)^6$ is \emph{not}
  any eigenvalue and $\varphi_0$ is not a rational edge fraction; so a full-structure rewrite must inject exactly two
  non-graph-spectral data --- the cusp weight $2/3{=}|\mathbb Z_2|/\Nfam$ and the analytic seed $\varphi_0$. The open
  question is precisely delimited, not closed. Cited in \texttt{introduction}; ledger row \texttt{HYP.INJECT.01}.
\end{itemize}

\subsection*{2026-06-21 (adversarial-review follow-ups: a structural anti-numerology firewall, an out-of-sample seed cross-validation, an operational data watchdog, and the Target-A holomorphy kill test: \texttt{v305}--\texttt{v307})}
\begin{itemize}
\item \textbf{\texttt{v305\_witness\_independence.py} (\texttt{WITNESS.ECON.01}, \mE).} The \emph{structural} anti-numerology
  firewall complementing the \texttt{v100} phenomenological null test, against the sharpest self-deception worry
  (``the same integer counted many times as if independent''). Every headline integer ($|\mu_4|{=}4$,
  $g_{\mathrm{car}}{=}5$, $|\mathbb Z_2|{=}2$, $N_{\mathrm{fam}}{=}3$, $\dim S^+{=}16$, $\operatorname{rank}E_8{=}8$,
  $240$, $248$, $|2I|{=}120$, $h(E_8){=}30$, $|W(D_5)|{=}1920$, $\Omega_{\mathrm{adm}}{=}48$, the gap exponent $6$)
  is a documented image of the single anchor $a{=}(1,1,2)$ with $\pi$ the only transcendental primitive ($13$ atoms
  from $2$ free primitives, $6.5\times$ compression made explicit), so the recurring $2/3{=}|\mathbb Z_2|/N_{\mathrm{fam}}$
  and $(2/3)^6$ are \emph{one} ratio; the $E_8$ spine is overdetermined ($\ge3$ structurally independent witnesses)
  while the pure-seed readouts are single-witness (scored jointly by \texttt{v100}, never multiplied); the negative
  control shows $\alpha^{-1}$'s ``$137$'' is foreign to the anchor family (an independent witness via the $F_{U(1)}$
  cubic, \texttt{v3}). Cited in the \texttt{tfpt\_5\_redteam} body; ledger row \texttt{WITNESS.ECON.01}. Python-only.
\item \textbf{\texttt{v306\_seed\_crossval.py} (\texttt{SEED.CROSSVAL.01}, \mE).} A leave-one-out cross-validation
  turning the ``many observables, one seed $\varphi_0$'' worry into a falsifiable out-of-sample test: back-solving
  $\varphi_0$ from each of the five seed-grammar observables ($\sin^2\theta_{12}$, $\sin^2\theta_{13}$, $\beta$,
  $\Omega_b$, $\lambda_C$; NuFIT 6.0 / ACT DR6 / Planck / PDG) and error-weighted-averaging reproduces the axiom seed
  $\varphi_0=1/(6\pi)+48c_3^4=0.0531720$ to $0.04\%$; leave-one-out predicts every held-out observable within $3\sigma$
  out of sample (most-tensioned $=\sin^2\theta_{13}$, ${\sim}2\sigma$); a data$\leftrightarrow$formula shuffle explodes
  the $\chi^2$ by $>100\times$. Cited in \texttt{tfpt\_5\_redteam}; ledger row \texttt{SEED.CROSSVAL.01}. Python-only.
\item \textbf{\texttt{v307\_data\_watchdog.py} (\texttt{DATA.WATCHDOG.01}, \mE).} The operational decision pipeline over
  the frozen registry (\texttt{v84}): it classifies all twenty registry entries
  \textsc{pass}/\textsc{watch}/\textsc{tension}/\textsc{kill} by live $n_\sigma$ against the repo-documented current
  bests (CODATA 2022, NuFIT 6.0, ACT DR6, Planck 2018, PDG 2024, BK18). No decidable prediction is in \textsc{kill};
  the watch items are $\alpha^{-1}$ ($1.9\sigma$), $s_{23}$ ($1.8\sigma$) and the most-tensioned core prediction
  $\sin^2\theta_{13}$ ($2.0\sigma$, the honest current pressure point); $\sin^2\theta_{12}=0.306747$ is compatible
  ($0.02\sigma$, the JUNO falsifier), the $r\in[0.0033,0.0048]$ band is below the BK18 limit and the kill, and
  $w{=}{-}1$ is flagged as the DESI dark-energy watchdog. Cited in \texttt{origin\_theory}; ledger row
  \texttt{DATA.WATCHDOG.01}. Python-only.
\item \textbf{Target-A holomorphy kill test (\texttt{freeze\_file.csv}).} A new \texttt{seam\_holomorphy} freeze row
  records the sharpened \emph{physical} kill criterion for Target~A: a raw quasi-free seam bulk showing topological
  ground-state degeneracy on the torus ($|\det K|>1$, the same-$c$ rival $SO(16)_1$) would break holomorphy and kill
  ``seam net $=(E_8)_1$'' --- since holomorphic $c{=}8\Leftrightarrow E_8$ is machine-proven (\texttt{v83}/\texttt{v143})
  and $\det K{=}1\Leftrightarrow$ invertible/SRE (\texttt{v237}/\texttt{v301}/\texttt{v302}).
\end{itemize}

\subsection*{2026-06-19 (an infinite-derivative narrowing of the Stelle-ghost attack, the double-pushout figure, and the ``constancy of $c$'' framing of \texttt{SEAM.EQUIV.01}: \texttt{v304})}
\begin{itemize}
\item \textbf{\texttt{v304\_idg\_nonlocal\_ghost.py} (\texttt{QGAMB.IDG.01}, \mC/\mO).} A conditional,
  parameter-free narrowing of the red-team \texttt{rt\_F}/\vref{v278} Stelle-ghost attack on the perturbative
  gravity sector. \mE\ the local $R{+}R^2/$Weyl$^2$ four-derivative propagator $1/(p^2(p^2{+}M^2))$ carries a
  negative-residue massive spin-2 mode (the Stelle ghost) only as a \emph{truncation artefact}; \mE\ for an
  \emph{entire} graviton form factor $a(p^2)=e^{p^2/M^2}$ (nowhere zero) the dressed propagator $1/(p^2a)$ has no
  extra pole (Tomboulis 1997; Biswas--Mazumdar--Siegel 2006), whereas any \emph{polynomial} truncation has a real
  zero $=$ the ghost; \mC\ the spectral-action cutoff is the seam KMS weight $f(u)=e^{-u}$ (\vref{v259}), so the
  un-truncated trace points to a nonlocal form factor with \emph{no new parameter}. \mO\ It does \emph{not} close
  \texttt{QG.AMB.01}: the trace regulator is not yet shown to resum to an entire $a(\Box)$, and a ghost-free
  \emph{perturbative} graviton is not the nonperturbative ambient measure. Cited in the red-team Target~F body;
  ledger row \texttt{QGAMB.IDG.01}.
\item \textbf{Double-pushout figure (\texttt{tfpt\_1\_architecture\_e8}).} A new shared TikZ macro
  (\texttt{TFPTdoublepushout} in \texttt{tex-artefacts/tfpt\_figures.tex}) draws the commuting square showing that
  the order-$|\mu_4|{=}4$ glue is \emph{one} operation in two categories: the lattice pushout
  $D_5\oplus A_3+\mu_4\Rightarrow E_8$ (\vref{v1}) and the conformal-net / anyon-condensation extension
  $(D_5)_1\otimes(A_3)_1\rtimes\mu_4\cong(E_8)_1$ (\vref{v92}/\vref{v281}/\vref{v234}/\vref{v277}/\vref{v260}).
  Expository only; no new claim.
\item \textbf{Framing (\texttt{introduction}, \texttt{tfpt\_research\_contracts}).} \texttt{SEAM.EQUIV.01} is now
  stated explicitly as the \emph{one} irreducible structural postulate of the theory --- the role the constancy of
  $c$ plays in relativity (cf.\ \vref{v267}). Prose sharpening; no status change.
\end{itemize}

\subsection*{2026-06-19 (the discrete$\to$dynamic lens on \texttt{F\_transfer}: one shape, one seam-rate, \texttt{v303})}
\begin{itemize}
\item \textbf{\texttt{v303\_ftransfer\_dynamics.py}} asks whether the main-branch mechanism --- a gapped,
  positivity-preserving relaxation to a \emph{unique} attractor (the local-averaging update $\to$ the $E_8$ marks,
  gap $6\ln(3/2)$) --- is also the shape of the four \texttt{F\_transfer} instances, or an unrelated bolt-on. It
  is the \emph{same} shape: \mE\ F\_pole (Koide) \emph{is} the seam dynamics (M\"obius multiplier
  $F'{=}(2/3)^6{=}\lambda_2$, the seam-clock eigenvalue $\Rightarrow$ a unique attractor at the seam rate,
  \vref{v82}/\vref{v54}); \mC\ F\_Boltzmann ($\eta_B$) is a gapped positive contraction (washout
  $\kappa_f\in(0,1)$, H-theorem); \mC\ F\_relic (axion) freezes at an adiabatic fixed point; \mE\ F\_QCD
  ($m_p/m_e$) is the 1-loop RG flow with the carrier $b_3{=}-7$ (asymptotic freedom, Gaussian UV attractor). \mO\
  Verdict: one shape underlies all four; F\_pole has the seam rate $(2/3)^6$ \emph{exactly}, the other three share
  only the shape with external rates (thermal/cosmological/RG). So \texttt{F\_transfer} is the readout end of the
  one discrete$\to$dynamic principle, \emph{not} a bolt-on; the theory's simplicity is preserved because the
  external rates are honestly fenced (\vref{v187}), not reduced to the seam. \mE\ suite \texttt{v303} $5/5$,
  \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-19 (the last lever: the seam mass gap \emph{is} the derived Recovery gap $6\ln(3/2)$, \texttt{v302})}
\begin{itemize}
\item \textbf{\texttt{v302\_seam\_gap.py}} closes the chain on the single statement \vref{v301} had left:
  ``the quasi-free seam bulk is gapped''.  That gap is \emph{not} a free input --- it is the established
  \emph{Recovery gap} of the seam transfer operator, derived from the carrier.  \mE\ the frozen transfer
  spectrum is $\mathrm{spec}(T)=\{1,(2/3)^6,(1/3)^6\}$ (\vref{v160}/\vref{v162}), a simple Perron eigenvalue
  $1$ separated from the rest; \mE\ the gap is $\Delta=-\ln((2/3)^6)=6\ln(3/2)=2\Nfam\ln(3/2)\approx2.4328>0$
  (multiplicative gap $1-(2/3)^6=665/729$; $(2/3)^6$ the $\mu_4$-deck transfer eigenvalue forced by the
  carrier); \mE\ with the decoupling margin $\Delta-31/(4\pi^2)\approx1.648>0$ (\vref{v76}) it is robust, and
  Perron--Frobenius primitivity makes the leading mode simple; \mC\ by Osterwalder--Schrader / quasi-free
  clustering a transfer-operator gap $\Delta>0$ \emph{is} a mass gap of the reconstructed Hamiltonian.
  \mO\ \textbf{Bottom line:} with \vref{v300}/\vref{v301}, \texttt{SEAM.EQUIV.01}'s entire residual is now a
  composition of \emph{standard cited theorems} (OS/quasi-free clustering $+$ Kitaev free-fermion invertibility
  $+$ the \vref{v297} AQFT stack) over \emph{established} TFPT facts ($16$ quasi-free Majoranas; transfer gap
  $6\ln(3/2)$) --- \emph{no undischarged TFPT-internal assumption remains}.  It stays \mO\ (not machine-proved
  end-to-end), but the open front is reduced to citable machinery over a spectral gap that is provably positive.
  \mE\ suite \texttt{v302} $5/5$, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-19 (Route A's last hypothesis discharged: the gapped quasi-free bulk is invertible by the free-fermion classification, \texttt{v301})}
\begin{itemize}
\item \textbf{\texttt{v301\_route\_a\_invertible.py}} attacks the single remaining \emph{unconditional} gap of
  \texttt{SEAM.EQUIV.01}.  Since \vref{v300} collapsed Route B into Route A's rationality, that gap is Route A's
  open hypothesis (\vref{v297} LIT-A): ``the raw quasi-free seam bulk is invertible (SRE)''.  A \emph{gapped}
  free-fermion (Gaussian) $2{+}1$D bulk cannot carry intrinsic topological order --- free fermions give the
  integer (IQHE/Chern) phases, all \emph{invertible}; intrinsic topological order needs interactions (Kitaev's
  periodic table, class D).  \mE\ the carrier is $16$ Majoranas, $c=g_{\mathrm{car}}{+}\Nfam=8=16/2$
  (\vref{v148}); \mE\ $SO(16)_1\supset(E_8)_1$ ($\dim\mathfrak{so}(16)=120$ currents $+\,128$ spinor $=248$,
  \vref{v154}); \mC\ so a gapped quasi-free bulk is invertible automatically; \mE\ the invariant
  $|\det K|=\#$anyons is $1$ for $E_8$ (invertible) vs $4$ for the gauged $D_8{=}SO(16)$ (anyons), which free
  fermions cannot produce.  \mO\ LIT-A's `invertible bulk' now \emph{follows} from `gapped 16-Majorana quasi-free
  bulk' (\vref{v148}/\vref{v160}$+$the mass gap), so the residual changes from a topological-order statement to a
  spectral one.  \mO\ \textbf{Bottom line:} with \vref{v300}, the whole open content of \texttt{SEAM.EQUIV.01}
  reduces to the \emph{single spectral statement} ``the quasi-free seam bulk is gapped'' --- the topological-order
  obstruction (hidden anyons) is removed; the gap is not manufactured.  \mE\ suite \texttt{v301} $6/6$,
  \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-19 (the Flat-Away attack: a hard discrete obstruction $+$ the pin derived from $(E_8)_1$, \texttt{v300})}
\begin{itemize}
\item \textbf{\texttt{v300\_flataway\_rigid.py}} attacks the single external fact the three Flat-Away routes
  (\vref{v291}/\vref{v293}/\vref{v295}) left open, on two fronts. \emph{Harden:} the flat seam was only a
  \emph{soft} minimum (``the spectral mismatch grows with $\varepsilon$''); here the obstruction becomes a
  \emph{discrete} on/off invariant. \mE\ the flat fingerprint --- $\mathrm{spec}(|D_\theta|)$ is the integer
  ladder with every level $n\ge1$ of multiplicity exactly $2$; \mE\ the resonant mode $4k$ splits level $2k$ by
  gap $=g_k$ (sympy $2\times2$ $[[2k,g/2],[g/2,2k]]\Rightarrow 2k\pm g/2$, $+$ an $O(g^2)$ common shift),
  validated against the full Toeplitz operator; \mE\ any $g_k\ne0$ lifts the resonant degeneracy
  ($2\to1{+}1$) and changes the spectral \emph{multiset}, so preserving the flat ladder \emph{with} its mult-$2$
  degeneracies forces every $g_k=0\Rightarrow f=0$ --- strictly stronger than the ``deviation grows'' scan; \mE\
  with the \vref{v295} convexity, flat is isolated analytically \emph{and} discretely. \emph{Derive the pin:} \mC\
  the $(E_8)_1$ character $E_4/\eta^8=q^{-1/3}(1+248q+4124q^2+\dots)$ has integer $q$-coefficients ($248$ at
  level $1$; $E_8$ even unimodular $\Rightarrow$ integer weights), so by 2d Steklov conformal rigidity the integer
  ladder $\Leftrightarrow$ flat seam, i.e.\ the external pin \emph{is} the $(E_8)_1$ rationality (Route~A). \mO\
  verdict: Flat-Away carries \emph{zero} new open content beyond Route~A --- the two \texttt{SEAM.EQUIV.01} routes
  converge on one rationality fact. \mE\ suite \texttt{v300} $6/6$, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-19 (the hypergraph/Wolfram bridge hardened: the $(2,3,r)$ seed reaches $E_8$ as the last finite point, \texttt{v299})}
\begin{itemize}
\item \textbf{\texttt{v299\_hypergraph\_0d\_autonomous.py}} hardens the Wolfram/hypergraph reading into a precisely
  typed bridge (builds on \vref{v219}/\vref{v298}): \mE\ the icosahedron is a 3-uniform hypergraph
  ($|\mathrm{Aut(graph)}|=120=|I_h|=|A_5{\times}\mathbb{Z}_2|$; the McKay group is the $SU(2)$ binary lift $2I$, a
  \emph{different} order-120 group whose McKay graph is affine $E_8$; $30$ edges $=h(E_8)$); \mE\ the $1\to4$
  subdivision rewrite is equivariant (all $120$ symmetries at every scale); \mE\ the $2I$ fusion tensor is a
  weighted 3-uniform hypergraph whose 2-dim slice is the affine $E_8$ McKay graph; \mE\ Smith
  ($\rho\le2\Leftrightarrow$ affine ADE) $+$ Collatz--Wielandt ($\rho\le2\Leftrightarrow$ a local witness
  $Am\le2m$); \mE* the autonomous rule (diffusion-generated witness $+$ \emph{local} gate $Am\le2m$, Perron only
  as audit) runs $E_6\to E_7\to E_8\to\hat E_8$; \mE\ the negative controls $\rho(A_n)=2\cos\frac{\pi}{n+1}$ and
  $\rho(D_n)=2\cos\frac{\pi}{2n-2}$ are $<2$ for \emph{all} $n$ (closed form), so neither family ever reaches
  $E_8$. Honest type: \mO\ the $(2,3,\cdot)$ seed is the single irreducible input $=$ P2 --- \emph{the rule
  reaches $E_8$ as the last finite point on this seed; it is not a derivation of P2}. \mE\ build green,
  \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (E8 as a network attractor --- the Wolfram-program reading, \texttt{v298})}
\begin{itemize}
\item \textbf{\texttt{v298\_e8\_network\_attractor.py}} is an honest audit of the ``TFPT as a hypergraph/rewrite
  system'' idea, on the \vref{v219} McKay bedrock. \mE\ the affine-$E_8$ Kac marks $(1,2,3,4,5,6,4,2,3)$ are the
  \emph{unique dynamical attractor} of a minimal local-averaging update $m\!\leftarrow\!(A{+}2I)/4\,m$ on the
  $(2,3,5)$ McKay graph (converges from any positive start; $A\,m=2m$, top eigenvalue $2$); the spherical tower
  terminates at $E_8$ and the cascade is nested-subgraph coarse-graining. \mC\ the Wolfram reading ``$E_8$ is the
  universal attractor of a minimal $(2,3,5)$ network'' holds at the Coxeter-skeleton level. \mO\ a minimal
  hypergraph \emph{rewrite} reproducing the \emph{full} structure stays open; honest negatives: $\phiz$ is the
  analytic seed $\tfrac{4}{3}c_3=1/(6\pi)$, not an edge fraction, and recovery is a 1-D M\"obius fixed point, not
  a rewrite. \mE\ build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (a$_2$ closed form + Route A literature stack, \texttt{v296}--\texttt{v297})}
\begin{itemize}
\item \textbf{\texttt{v296\_flataway\_a2\_closed.py} (\texttt{FLATAWAY.A2.CLOSED.01})} evaluates the exact $a_2$
  coefficient in \emph{closed form}: the operator tails telescope geometrically
  ($C_k+D_k e^{-4kt}=4kt(1-e^{-4kt})$) to $W_k^{\mathrm{tail}}=t(1-e^{-4kt})/(8k(1-e^{-t}))$, leaving a finite
  $(4k{-}1)$-term middle; e.g.\ $W_1(t)=t(2t e^{t}+e^{3t}+3e^{2t}+e^{t}-1)e^{-3t}/8$. Manifestly positive,
  small-$t$ law $W_k=t/2+O(t^3)$ (the $t^2$ term cancels). Reproduces \vref{v295} to machine precision.
\item \textbf{\texttt{v297\_route\_a\_literature\_stack.py} (\texttt{SEAM.EQUIV.A.LIT.01})} writes Route A's one
  import as a citable stack: LIT-A (Kitaev; Freed--Hopkins) $\to$ LIT-B (M\"uger; Kawahigashi--Longo--M\"uger)
  $\to$ LIT-C (Conway--Sloane; Dong--Xu) compose into ``invertible bulk $\Rightarrow(E_8)_1$'', all legs
  established; the single open hypothesis (seam-bulk invertibility) coincides with Route B's Flat-Away, and the
  stack is non-circular with Route B (the \vref{v286} firewall holds). \mE\ build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (Flat-Away heat route made exact + Lean-formalised, \texttt{v295} / \texttt{FORM.FLATAWAY.01})}
\begin{itemize}
\item \textbf{\texttt{v295\_flataway\_a2\_exact.py} (\texttt{FLATAWAY.A2.01})} upgrades the \vref{v292}
  positive-definiteness from a numerical scan to a \emph{proof}: the first variation of
  $\mathrm{Tr}\,e^{-t\Lambda}$ vanishes (zero-mean off-mark curvature, Gauss-Bonnet), and since
  $\Lambda\mapsto\mathrm{Tr}\,e^{-t\Lambda}$ is convex (Klein/Peierls), $\varepsilon{=}0$ is the \emph{global}
  minimum --- so $\Delta\mathrm{Tr}\ge0$ for all deformations, $=0$ iff $f=0$. The exact second-order
  coefficient is the divided-difference kernel of $e^{-tx}$ (Duhamel), validated to rel.\ err $<10^{-6}$.
\item \textbf{Lean \texttt{FORM.FLATAWAY.01}} (\texttt{SeamDeckClosure.lean} Part 5): the formal
  $\Delta{=}0\Leftrightarrow$ flat step --- a positive-weighted sum of squares is positive-definite
  (\texttt{heatDeviation\_eq\_zero\_iff}); built and axiom-checked (only \texttt{propext},
  \texttt{Classical.choice}, \texttt{Quot.sound}). So the heat route's positive-definiteness is now both
  analytically proved and machine-formalised; only the single external fact (the seam fixes $a_2$) remains.
  \mE\ build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (Flat-Away attacked on all three routes, \texttt{v292}--\texttt{v294})}
\begin{itemize}
\item \textbf{\texttt{v292\_flataway\_heat\_reduction.py} (\texttt{FLATAWAY.HEAT.01})}: the heat route, made
  precise. The heat-trace deviation $\Delta\mathrm{Tr}(e^{-t\Lambda})=c(t)\varepsilon^2+O(\varepsilon^4)$ is a
  \emph{positive-definite} quadratic form in the off-mark curvature ($c_k(t)>0$ for every $\mathbb{Z}_4$ mode,
  positive on all combinations), leading invariant $\|f\|_{L^2}$ --- so Flat-Away reduces to the single fact
  ``the seam fixes the $a_2$ heat coefficient''.
\item \textbf{\texttt{v293\_flataway\_spectral\_hessian.py} (\texttt{FLATAWAY.SPEC.01})}: the spectral route,
  upgraded from one direction to the \emph{full} smooth-$\mathbb{Z}_4$ space. Mode $4k$ splits the degenerate
  Steklov level $|2k|$ at first order; the Hessian of the spectral mismatch over modes $\{4,8,12\}$ is
  positive-definite (eigenvalues $\{0.497,0.500,0.503\}$), so the flat seam is a strict isolated minimum --- the
  ``only one direction'' objection is answered.
\item \textbf{\texttt{v294\_flataway\_rp\_energy.py} (\texttt{FLATAWAY.ENERGY.01})}: the variational route. With
  the rigid mark divisor (4 cone angles $\pi$, Gauss-Bonnet $4\pi$), Troyanov uniqueness gives a unique flat
  cone metric, and the curvature energy $\int f^2$ is strictly convex (Hessian $2\pi I$) with a unique
  minimiser --- Flat-Away reduces to ``RP$+$gap realises the energy-minimiser''. The three routes converge on
  one selection principle for the flat metric; closing any one closes Route B. \mE\ build green,
  \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (Route-B red-team: the smooth $\mathbb{Z}_4$ adversary + Flat-Away as a mini-theorem, \texttt{v290}--\texttt{v291})}
\begin{itemize}
\item \textbf{\texttt{v290\_z4\_smooth\_curvature\_adversary.py} (\texttt{SEAM.ADVERSARY.01})} is the honest
  red-team that $\mathbb{Z}_4$ block-diagonality is \emph{not} mark-locality: a smooth $\mathbb{Z}_4$
  off-mark curvature $f=\varepsilon\cos(4\theta)$ \mE\ passes the \vref{v288} commutator
  ($\|[\rho,\Lambda]\|=0$, same as mark-local) yet \mE\ shifts the DtN spectrum ($\max|\Delta\lambda|=0.155$)
  and the heat trace ($\Delta=0.019$). So the commutator is necessary, not sufficient; the modulus is
  excluded by the spectral data, not $[\rho,\Lambda]{=}0$ --- which is exactly why Flat-Away cannot be
  read off the commutator.
\item \textbf{\texttt{v291\_flataway\_contract.py} (\texttt{FLATAWAY.RP.01})} states Flat-Away as its own
  named mini-theorem and types three independent proof routes: \mE\ spectral-rigidity and \mE\ heat-kernel
  (the flat seam is the \emph{unique} spectral/heat match of the smooth $\mathbb{Z}_4$ family --- deviation
  zero only at $\varepsilon{=}0$) and \mC\ RP-energy/Troyanov (constant-curvature minimiser). Closing any one
  closes Route B. \mE\ build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (Route B sharpened: raw mark-locality decomposed + reviewer firewalls, \texttt{v289} / \texttt{v287}--\texttt{v288})}
\begin{itemize}
\item \textbf{\texttt{v289\_marklocal\_raw.py} (\texttt{MARKLOCAL.RAW.01})} decomposes the one remaining
  Route-B residual (`why is the raw seam sub-principal term mark-local?') into a 5-lemma chain and
  isolates the \emph{single} open analytic lemma: \mC\ L1 conic parametrix (b-calculus/Melrose, imported);
  \mO\ L2 \textbf{Flat-Away} --- RP$+$gap$+$4 marks $\Rightarrow$ curvature vanishes away from the marks;
  \mE\ L3 orbit-source (\vref{v195}/\vref{v216}), L4 Fourier-support on $4\Z$ (\vref{v264}/\vref{v288}),
  L5 full-operator $[\rho,\Lambda]{=}0$ (\vref{v288}). 4/5 discharged --- Route B reduces to exactly L2.
\item \textbf{\texttt{v288} reviewer firewall}: a SCOPE FIREWALL check makes the exact-label split explicit
  (Fourier lemma Formal/Exact; numerical test Numerical Exact; transfer to the raw conic DtN Conditional,
  \vref{v264}; mark-locality from the RP seam Open Selection, \vref{v289}) --- so it can never be read as
  `full-$L^2$ QGEO proved'.
\item \textbf{\texttt{v287} literature matrix}: L3 (`invertible bulk $\Rightarrow$ single-sector') is typed as
  a composition of citable results (LIT-A Kitaev/Freed--Hopkins, LIT-B M\"uger/Kawahigashi--Longo--M\"uger,
  LIT-C Kawahigashi--Longo) conditional on one open hypothesis --- seam-bulk invertibility, which coincides
  with Route B. \mE\ build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (closing sprint: the Seam Equivalence Theorem named + both routes attacked, \texttt{v286}--\texttt{v288})}
\begin{itemize}
\item \textbf{\texttt{v286\_seam\_equivalence\_contract.py} (\texttt{SEAM.EQUIV.01})} names the one open theorem
  --- \emph{the raw RP seam state is the holomorphic $(E_8)_1$ net at $\tau{=}i$} --- and concentrates the whole
  open structure on it: four objects, six arrows (2 closed, 1 conditional \vref{v282}, 1 open Gral), an
  \textbf{import firewall} proving the two routes (\vref{v276}/\vref{v280}/\vref{v284} vs
  \vref{v277}/\vref{v281}/\vref{v285}) never import each other (no `$E_8$ into the geometry and back'
  circularity), and an exact-label taxonomy. Writes \texttt{seam\_equivalence.json}.
\item \textbf{\texttt{v287\_free\_rp\_bulk\_to\_holomorphic\_boundary.py} (\texttt{SEAM.EQUIV.A01})}: Route A
  (AQFT) dependency checker --- the 5-lemma chain RP$+$gap$+$chirality$+$Gaussian$+$invertible
  $\Rightarrow\mu{=}1\Rightarrow$ holomorphic $\Rightarrow(E_8)_1$ is logically complete \emph{modulo one}
  standard theorem: \emph{invertible (SRE) Gaussian bulk $\Rightarrow$ single-sector boundary} (the AQFT form
  of $\det K{=}1$). 4/5 discharged.
\item \textbf{\texttt{v288\_full\_l2\_subprincipal\_z4.py} (\texttt{SEAM.EQUIV.B01})}: Route B (DtN) ---
  \emph{proves} the full-$L^2$ lift of the sub-principal $\mathbb{Z}_4$ block-diagonality (a mark-sourced
  curvature has Fourier support only on $m\equiv0$ mod 4, so $\Lambda=|n|+M_f$ commutes with
  $\rho=\mathrm{diag}(i^n)$ on the full operator, $\|[\rho,\Lambda]\|\sim2{\times}10^{-15}$; generic curvature
  $\to 4.44$), lifting \vref{v201}/\vref{v284} to $L^2$. The residual shrinks to one sharper question: why is the
  raw seam sub-principal term mark-local? \mE\ build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (the two proof routes decomposed: Route (i) and Route (ii) into lemma chains, \texttt{v284}/\texttt{v285})}
\begin{itemize}
\item \textbf{\texttt{v284\_route\_i\_rp\_uniqueness.py} (\texttt{QGEO.ROUTEI.01})} turns Route (i) (RP-state
  uniqueness) into a 6-lemma chain: \mE\ 5/6 lemmas are already discharged --- L1 RP$\to$DtN (\vref{v194}),
  L2 marks$\to$pillowcase (\vref{v195}/\vref{v216}/\vref{v214}), L3 flat Steklov $=\sqrt{-\Delta_{\mathrm{flat}}}$
  (verified here), L4 covariance from DtN (\vref{v258}), L5 $\mu_4$-invariance (\vref{v276}/Lean/\vref{v280}); \mC\
  Troyanov ($\chi_{\mathrm{orb}}{=}0\Rightarrow$ unique flat $\tau{=}i$) reduces the residual to one lemma. \mO\
  the one open lemma: \emph{the raw seam is the constant-curvature geometric state}.
\item \textbf{\texttt{v285\_route\_ii\_seam\_condensation.py} (\texttt{QGAMB.ROUTEII.01})} turns Route (ii)
  (seam-net condensation) into a 4-lemma chain: \mE\ 3/4 discharged (no abelian sector $\Leftrightarrow\det K{=}1
  \Leftrightarrow$ holomorphic $\Leftrightarrow E_8$; the tower $16{\to}4{\to}1$), and \textbf{its open lemma
  coincides with Route (i)'s} --- both are ``the raw seam is the $(E_8)_1$-at-$\tau{=}i$ object'' (\vref{v282}),
  so proving \emph{either} route closes \emph{both}. \mO\ the unified open lemma: a canonical equivalence
  between the raw seam KMS/DtN state and the holomorphic $(E_8)_1$ net at $\tau{=}i$. Build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (self-investigation round: pillowcase DtN, modular data, the E8-at-$\tau{=}i$ unification, live scorecard, \texttt{v280}--\texttt{v283})}
\begin{itemize}
\item \textbf{\texttt{v280\_pillowcase\_steklov.py} (\texttt{QGEO.STEKLOV.01})} runs the QGEO chain on the actual
  flat $\tau{=}i$ pillowcase orbifold: the order-4 deck permutes the 4 cone points (2 fixed $+$ 1 swap) and the
  geometric chain $[\rho,\Delta]{=}0\Rightarrow[\rho,H]{=}0\Rightarrow[\rho,C]{=}0\Rightarrow\omega\circ\rho{=}\omega$
  is numerically exact --- route-(i) evidence for \texttt{QGEO.OBLIG.01}; the premise stays \mO.
\item \textbf{\texttt{v281\_holomorphy\_modular\_data.py} (\texttt{QGAMB.MODULAR.01})}: \#anyons $=|\det\mathrm{Gram}|$
  (E8$\to$1, SO(16)$\to$4), the anyon-condensation tower $16\to4\to1$, Gauss--Milgram $\to c{=}8$; holomorphy
  ($\det K{=}1$) is the single Tier-B discriminator.
\item \textbf{\texttt{v282\_e8\_tau\_i\_unification.py} (\texttt{QGAMB.UNIFY.01})}: the candidate
  \emph{simplification} --- $\chi_{E_8}{=}j^{1/3}$ gives $\chi_{E_8}(i){=}1728^{1/3}{=}12$, so $\tau{=}i$ is both
  the order-4 CM point (QGEO) and the $(E_8)_1$ modulus (QG.AMB): the two obligations are two faces of one object
  (the seam is $(E_8)_1$ at $\tau{=}i$), \textbf{obligation count $2\to1$}.
\item \textbf{\texttt{v283\_live\_killtest\_scorecard.py} (\texttt{PRED.LIVE.01})}: the recent round's
  computable predictions vs current data --- all consistent $<2\sigma$, with two sharp near-term kill tests
  ($\Sigma m_\nu$ floor $0.0586$ eV; proton decay $1.55{\times}10^{35}$ yr).
\item Wolfram $275/275$ (v281/v282 exact-mirrored); build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (the Gr\"al: QGEO.SYM.01 as one precise lemma $+$ the all-orders step Lean-formalised, \texttt{v279}/\texttt{FORM.QGEO.03})}
\begin{itemize}
\item \textbf{\texttt{v279\_qgeo\_obligation\_lemma.py} (\texttt{QGEO.OBLIG.01}) writes the bedrock as ONE precise
  constructive-QFT lemma.} Given the premise \emph{the raw seam carries the flat $\tau{=}i$ pillowcase metric}
  (Troyanov-unique, $\Lambda_\Sigma{=}\sqrt{-\Delta_{\mathrm{flat}}}$), then $\omega_\Sigma\circ\rho=\omega_\Sigma
  \to$ mark-locality $\to E_8$. \mE\ the reduction DAG from `free RP seam' has exactly \emph{one} open leaf ---
  `the raw seam state is the flat state'; \mE\ the geometric side is fixed (flat DtN diagonal, $\rho$ commutes to
  all orders), so the obligation is a state-identification, with \mC\ two proof routes (RP-state uniqueness, or
  Troyanov $+$ OS).
\item \textbf{\texttt{FORM.QGEO.03}: the all-orders step is now machine-proved in Lean.}
  \texttt{SeamDeckClosure.lean} gains \texttt{diagonal\_commutesClock} and
  \texttt{flat\_all\_orders\_clock}: any spectral function $g(\Delta_{\mathrm{flat}})$ of the Fourier-diagonal
  flat Laplacian commutes with the carrier clock $\rho{=}\mathrm{diag}(i^n)$ --- so the \vref{v276} all-orders
  closure is a Lean theorem (only \texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}; no
  \texttt{sorry}; full \texttt{lake build} green, $3356$ jobs). The premise (the seam \emph{is} flat) stays the
  \mO\ \texttt{QGEO.SYM.01} input. Build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (4D QFT: the $S_{\mathrm{pert}}\to S_{\mathrm{phys}}$ LSZ bridge $+$ one-loop unitarity, \texttt{v278})}
\begin{itemize}
\item \textbf{\texttt{v278\_lsz\_bridge\_unitarity.py} (\texttt{QFT4D.SPERT.04}) connects the perturbative
  S-matrix to the physical asymptotic one and verifies one-loop unitarity.} \mE\ LSZ bridge: the EG
  $T$-products of $S_{\mathrm{pert}}$ (\vref{v269}) \emph{are} the OS Wick-rotated correlators (\vref{v240}), so
  amputate$+$on-shell-residue gives $S_{\mathrm{pert}}\xrightarrow{\mathrm{LSZ}}S_{\mathrm{phys}}$; \mC\ the gap
  $\Delta{=}6\log(3/2){>}0$ gives Haag--Ruelle asymptotic states. \mE\ \emph{one-loop optical theorem}: the
  bubble discontinuity $\operatorname{Im}B(s)/\pi=x_+{-}x_-=\sqrt{1-4m^2/s}$ \emph{exactly} $=$ the two-body
  phase space, so $2\operatorname{Im}M=\sum\!\int d\Pi|M|^2$ (cutting rule) holds --- the matter$+$gauge sector
  is unitary, with the cut turning on at the physical two-particle threshold. \mO\ the gravity sector's Stelle
  ghost (\vref{v269}/\texttt{rt\_F}) is non-unitary $\to$ \texttt{QG.AMB.01}. Exact core mirrored in Wolfram
  ($273/273$). Build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (QG.AMB.01 Tier-B made concrete: the seam-Calder\'on $\to(E_8)_1$ match, \texttt{v277})}
\begin{itemize}
\item \textbf{\texttt{v277\_seam\_calderon\_e8\_match.py} (\texttt{QGAMB.TIERB.01}) reduces Tier-B to ONE bit.}
  \mE\ the full $(E_8)_1$ matching target is computed and matches: $c{=}8$, $\det\mathrm{Cartan}(E_8){=}1$, the
  holomorphic character $E_4/\eta^8{=}j^{1/3}{=}q^{-1/3}(1{+}248q{+}\dots)$ with a single primary and exactly
  $248{=}\dim E_8$ weight-1 currents ($240$ roots). \mE\ the discriminator is holomorphy --- the $c{=}8$
  counterexample $(D_8){=}SO(16)_1$ has $\det\mathrm{Cartan}{=}4$ (non-holomorphic), so the one condition is
  $|\det K|{=}1$. \mC\ the seam side matches via \vref{v276} (flat $\tau{=}i$) $+$ \vref{v260} (Kummer/K3).
  \mO\ residual $=$ the single holomorphy bit; reduced, not closed. Exact core mirrored in Wolfram
  ($272/272$). Build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (QGEO.SYM.01 narrowed: the flat pillowcase closes the commutator to all orders, \texttt{v276})}
\begin{itemize}
\item \textbf{\texttt{v276\_qgeo\_flat\_closes\_commutator.py} (\texttt{QGEO.SYM.03}) collapses the bedrock
  to ONE geometric postulate.} The state-level residual the whole bedrock rests on is the operator equation
  $[\rho,H]{=}0$. \mE\ if $H=f(\Delta_{\mathrm{flat}})$ and the order-4 deck $\rho$ ($z{\mapsto}iz$) is a
  flat-$\tau{=}i$ isometry, then $[\rho,\Delta]{=}0\Rightarrow[\rho,H]{=}0$ \emph{exactly}, to all orders
  (verified on the discretised square torus: $\rho^4{=}I$, $[\rho,\Delta]{=}0$, $[\rho,\sqrt{-\Delta}]{=}0$;
  generic non-isometry fails) --- upgrading the leading-order \vref{v198}/\vref{v201} to the full $H$. \mC\
  $\tau{=}i$ is forced by order-4 ($j{=}1728$; hexagonal $j{=}0$ is order-6, excluded). \mO\ \texttt{QGEO.SYM.01}
  therefore collapses to the single statement ``the raw seam IS the flat $\tau{=}i$ pillowcase quasi-free
  state'' --- one human constructive-QFT proof, or an honest axiom. Narrows, does not close. Build green,
  \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (Red Team Target F --- adversarial audit of the v269--v275 round, \texttt{rt\_F})}
\begin{itemize}
\item \textbf{\texttt{redteam/rt\_F\_qft4d.py} (\texttt{REDTEAM.F.01}) stress-tests the just-published round}
  (the perturbative $S_{\mathrm{pert}}$ layer, the PMNS Jarlskog, the $\nu$-scale, the over-determination,
  the \texttt{QG.AMB.01} roadmap). \textsc{Survives (narrowed)}: two attacks land and are folded in.
  \textbf{(1)} the gravity $R^2/$Weyl$^2$ sub-sector is power-counting renormalizable but \emph{non-unitary}
  (the Stelle ghost: the four-derivative propagator $1/(p^2(p^2+M^2))$ has a negative-residue massive spin-2
  mode), so $S_{\mathrm{pert}}$ is unitary for the matter$+$gauge sector only --- which is exactly why the
  nonperturbative \texttt{QG.AMB.01} is the real frontier (caveat added to \vref{v269}). \textbf{(2)} the
  $0.11\%$ anchor over-determination is conditional on the $\Lambda$-branch readout (\texttt{LAMBDA.BRANCH.01},
  \mC), the gravity route being unconditional (caveat added to \vref{v274}). Added as Target F in
  \texttt{tfpt\_5\_redteam} + the red-team table; \texttt{run\_redteam.py} green.
\end{itemize}

\subsection*{2026-06-18 (Zenodo release 5.2 (rev 191) --- the perturbative 4D-QFT layer + scale closure, v269--v275)}
\begin{itemize}
\item \textbf{Published to Zenodo.} Version \texttt{5.2 (rev 191)} of the ten-PDF document set was published
  as a new version of the TFPT deposit --- record \texttt{20743347}, DOI \texttt{10.5281/zenodo.20743347}.
  This release carries the perturbative 4D-QFT layer (the Epstein--Glaser $S_{\mathrm{pert}}$ skeleton
  \vref{v269}, the concrete one-loop quartic \vref{v271} and gauge $\beta$-coefficients \vref{v273}), the
  complete complex PMNS matrix and leptonic CP strength \vref{v270}, the honest absolute $\nu$-mass-scale
  typing \vref{v272}, the over-determination of the single mass anchor \vref{v274}, and the \texttt{QG.AMB.01}
  obligation roadmap \vref{v275}. Suite \texttt{273} modules (highest ID \texttt{v275}; v186/v226 skipped),
  Wolfram \texttt{271/271}, \texttt{run\_all.py} green, \texttt{AUDIT OK}, \texttt{npm} build clean. The Zenodo
  description (\texttt{zenodo\_description.html}) and the public website were synced in the same release.
\end{itemize}

\subsection*{2026-06-18 (scale + frontier round: $\nu$-mass scale, EG gauge running, over-determination, QG roadmap, \texttt{v272}--\texttt{v275})}
\begin{itemize}
\item \textbf{\texttt{v272\_nu\_mass\_scale.py} (\texttt{FLAV.NUSCALE.01}) types the absolute neutrino-mass scale
  honestly} (no fabricated $\Sigma m_\nu$ --- would contradict the \vref{v184} firewall). \mE\ the absolute
  scale reduces to \emph{one} seesaw ratio $m_3=(y_\nu v_{\mathrm{EW}})^2/M_R$ (one UV input, like $v_{\mathrm{geo}}$,
  \vref{v153}); \mC\ the observed $m_3{=}0.050$ eV with the TFPT PS$\to$GUT window $M_R\in[4.2{\times}10^{13},
  2.4{\times}10^{15}]$ GeV (\vref{v249}) needs $y_\nu\in[0.26,2.0]$ --- $O(1)$, no tuning; \mO\ $M_R$ is not a clean
  $\Mbar$ power, so the absolute value stays open; \mX\ the NO floor $\Sigma m_\nu{=}0.0586$ eV is the cosmological
  kill test. Closes the PMNS bookkeeping (the last \mO\ is one seesaw ratio).
\item \textbf{\texttt{v273\_eg\_gauge\_running.py} (\texttt{QFT4D.SPERT.03}) derives the SM one-loop $b_i$ via the EG
  gauge self-energy.} \mE\ the gauge 2-point is the same scaling-degree-4 extension as the quartic (\vref{v271}),
  giving $(b_1,b_2,b_3)=(41/10,-19/6,-7)$ from the carrier/SM content (the same $41$ as the carrier algebra,
  \vref{v159}); \mO\ two-loop $+$ all-order stay open. Exact $b_i$ mirrored in Wolfram.
\item \textbf{\texttt{v274\_scale\_overdetermination.py} (\texttt{SCALE.OVERDET.01}) shows the single mass anchor is
  over-determined.} \mE/\mC\ two independent routes to $\Mbar$ agree --- gravity $(8\pi G)^{-1/2}=2.4353{\times}10^{18}$
  GeV and cosmology (the compiler prediction $\rho_\Lambda/\Mbar^4=(3/4\pi^2)e^{-2\alpha^{-1}}$ with
  $\rho_\Lambda^{1/4}=2.24$ meV) $=2.438{\times}10^{18}$ GeV, to $0.11\%$; the seam being a conformal $c{=}8$ CFT
  makes ``no derivable absolute scale'' a theorem, not a gap. Sharpens \vref{v153}/\vref{v78}.
\item \textbf{\texttt{v275\_qgamb\_roadmap.py} (\texttt{QGAMB.ROADMAP.01}) gives the open gate \texttt{QG.AMB.01} a
  module.} \mE\ Tier A gap decoupling ($\Delta_{\mathrm{eff}}=1.648>0$, \vref{v36}/\vref{v76}); \mE/\mC\ Tier B
  reduction to the holomorphic $(E_8)_1$ boundary net (\vref{v77}); \mC\ the perturbative layer in hand
  (\vref{v269}/\vref{v271}/\vref{v273}); \mO\ the nonperturbative ambient measure stays the one structural frontier.
\item Suite \texttt{271/271} Wolfram, \texttt{run\_all} green, \texttt{AUDIT OK}, build green.
\end{itemize}

\subsection*{2026-06-18 (4D QFT: a concrete Epstein--Glaser one-loop quartic renormalization, \texttt{v271})}
\begin{itemize}
\item \textbf{\texttt{v271\_eg\_oneloop\_quartic.py} (\texttt{QFT4D.SPERT.02}) takes the \vref{v269} $S_{\mathrm{pert}}$
  skeleton from ``exists'' to an actual EG number} (no path integral). \mE\ the first renormalization is the
  order-2 product $T_2$; the massless propagator has scaling degree $\mathrm{sd}{=}2$ in $d{=}4$, the one-loop
  bubble has $\mathrm{sd}{=}4{=}d$, so $\omega{=}\mathrm{sd}{-}d{=}0$ $\Rightarrow$ exactly one logarithmic local
  counterterm ($C(\omega{+}d,d){=}1$, finite, no infinite tower); the loop factor $\Omega_3/(2(2\pi)^4)=1/(16\pi^2)$
  exactly --- the \emph{same} factor that normalises the spectral-action $a_4$ geometric quartic. \mC\ the
  $\phi^4$ one-loop $\beta_\lambda=3\lambda^2/(16\pi^2)$ (symmetry $3$ $=$ $s,t,u$ channels), EG initial condition
  $\lambda_\Phi(\mathrm{UV})=1/(16\pi^2)$. \mO\ order-2/one-loop only; the all-order EG construction and the
  nonperturbative measure \texttt{QG.AMB.01} stay open. Exact core mirrored in Wolfram ($270/270$). \mE\ build
  green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (PMNS: the complete complex matrix + the leptonic Jarlskog CP strength, \texttt{v270})}
\begin{itemize}
\item \textbf{\texttt{v270\_pmns\_jarlskog\_assembly.py} (\texttt{FLAV.PMNS.03}) assembles the four TFPT
  channels} ($\sin^2\theta_{12}{=}\tfrac13{-}\tfrac{\phiz}2$, $\sin^2\theta_{23}{=}\tfrac12$,
  $\sin^2\theta_{13}{=}\phiz e^{-5/6}$, $\delta{=}4\pi/3$) \textbf{into one exactly-unitary complex PMNS
  matrix and derives the leptonic CP strength.} \mE\ $U=R_{23}U_{13}(\delta)R_{12}$ is unitary; \mC\ the
  Jarlskog $J_{\mathrm{PMNS}}=\Im(U_{e1}U_{\mu2}U_{e2}^{*}U_{\mu1}^{*})=-0.02965$ ($J_{\max}=0.03424$) is a
  \emph{derived} number, the leptonic analogue of the CKM $J$ (\vref{v88}); \mC\ data: $J_{\max}$ vs NuFIT\,5.2
  $0.0332$ ($\sim3\%$), $J$ vs best fit $-0.026$, the negative CP-violating sign reproduced. \mO\ $\delta$ is
  the $\mu_6$/triality phase (assembled, not from $M_\nu/D_F$) and the absolute $\nu$-mass scale stays open ---
  closes the CP-\emph{strength} readout, not the phase origin nor the scale. \mE\ build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (4D QFT: the perturbative S-matrix as an Epstein--Glaser / pAQFT skeleton, \texttt{v269})}
\begin{itemize}
\item \textbf{\texttt{v269\_spert\_paqft\_skeleton.py} (\texttt{QFT4D.SPERT.01}) builds the honest middle
  layer of the three-layer S-matrix} (the first concrete 4D-QFT step beyond the spectral-action contract),
  \emph{not} a nonperturbative closure. \mE\ three distinct layers: $S_{\mathrm{top}}$ (2d DHR braiding
  $|M|{=}1$, statistics, \vref{v243}), $S_{\mathrm{pert}}$ (4d Epstein--Glaser/BV S-matrix of the spectral
  action), $S_{\mathrm{phys}}$ (LSZ on the OS Wightman functions, \vref{v240}). \mE\ the spectral-action
  $a_4$ interaction is power-counting renormalizable (all operators dim $\le4$; $7$ marginal $+\,3$ relevant,
  a finite counterterm basis), so \mC\ by the Epstein--Glaser theorem the perturbative S-matrix exists order
  by order (causal factorisation $+$ finite local extension; no path integral, no UV divergences). \mC\ the
  gap $\Delta=6\log(3/2)$ gives an IR-safe adiabatic limit ($S_{\mathrm{pert}}\to S_{\mathrm{phys}}$ via LSZ).
  \mO\ perturbative only --- the ambient measure \texttt{QG.AMB.01} stays open, the canonical 4d reading
  remains boundary-only (\vref{v265}). \mE\ build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (PMNS: the reactor-angle exponent closed as the carrier hypercharge trace, \texttt{v268})}
\begin{itemize}
\item \textbf{\texttt{v268\_theta13\_carrier\_trace.py} (\texttt{FLAV.TH13.01}) closes the $\theta_{13}$
  exponent origin.} The value $\sin^2\theta_{13}=\phiz e^{-5/6}=0.0231$ was already checked (\vref{v16}); now
  the exponent is exact: \mE\ $\gamma=5/6=\mathrm{tr}_E Y^2$, the carrier hypercharge-squared trace
  ($Y=\mathrm{diag}(-\tfrac13,-\tfrac13,-\tfrac13,\tfrac12,\tfrac12)$, roots of $6Y^2-Y-1=0$; complement
  $\tfrac16$ the neutrino ratio). \mE\ own channel: the $\mu\tau$-breaking $\varepsilon=\tfrac34\phiz$
  induces only ${\sim}1.6\times10^{-3}\ll0.023$, so $\theta_{13}$ is a separate carrier-trace channel ---
  correcting the tempting (and wrong) ``$\theta_{13}$ from $M_\nu$'' route flagged by the new script atlas.
  \mO\ the CP magnitude and the absolute $\nu$-mass scale remain the open PMNS items. Exact core mirrored in
  Wolfram. \mE\ build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (Infrastructure: a generated causal ``script atlas'' so the suite is navigable at a glance)}
\begin{itemize}
\item \textbf{\texttt{verification/make\_script\_atlas.py} generates \texttt{verification/script\_atlas.md}} ---
  a single grouped, dependency-aware view fusing the existing single sources (\texttt{status\_ledger.csv} for
  claim$\to$status$\to$dependencies$\to$supersedes, \texttt{script\_registry.csv}/\texttt{script\_clusters.csv}
  for the theme grouping, \texttt{docs\_map.csv} for where each script is cited). It lists every registered
  script by cluster with its claim(s), four-class marker, one-liner, resolved dependencies and citing papers,
  plus a \emph{supersede map} (which old claim each new one replaces) and a dependency/most-depended-on
  overview --- the antidote to duplicating work or forgetting superseded results. No new data, a re-projection
  only; wired into \texttt{bash build.sh gen}. \mE\ build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (The bedrock in its minimal-axiom form: a rigidity theorem for \texttt{QGEO.SYM.01}, \texttt{v267})}
\begin{itemize}
\item \textbf{\texttt{v267\_qgeo\_rigidity\_minimal\_axiom.py} (\texttt{QGEO.SYM.02}) sharpens the one bedrock
  postulate to its irreducible kernel} (it does \emph{not} close it). \mE\ the \emph{single} bare statement
  ``the seam admits the carrier order-$4$ clock as a conformal symmetry permuting its four marks''
  ($=\omega\circ\rho=\omega$) forces \emph{everything}: an order-$4$ M\"obius orbit $\{a,ia,-a,-ia\}$ has
  cross-ratio $2$ independent of $a$; cross-ratio $2\Leftrightarrow j{=}1728$ (only $\lambda\in\{-1,\tfrac12,2\}$)
  $\Leftrightarrow$ the order-$4$ CM automorphism on $y^2{=}x^3{-}x$; and the unique flat pillowcase metric,
  mark-locality, $[\rho,\Lambda]{=}0$ and $\omega\circ\rho{=}\omega$ all follow (\vref{v214}/\vref{v201}/\vref{v264}/\vref{v198}).
  \mE\ neg controls: generic config $j\neq1728$ ($\Z_2$ only), hexagonal $j{=}0$ ($\Z_6$, order $6$) --- only
  the square (order-$4$) realises the $\mu_4$ clock. \mC\ second, independent reason: $\{1,i,-1,-i\}$ over
  $\mathbb Q$ with $j{=}1728$ (CM by $\Z[i]$), Belyi/dessins Galois-rigidity. \mO\ the bare order-$4$ symmetry stays
  the one foundational postulate (like $c{=}$const) --- the \emph{reduction} is closed (axiom $\Rightarrow$
  everything), the axiom is not. \mE\ build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (Branch B decided: the explicit PS threshold model $+$ proton-decay window --- minimal content killed, $+(15,1,1)$ survives, Hyper-K decisive, \texttt{v266})}
\begin{itemize}
\item \textbf{\texttt{v266\_ps\_threshold\_proton.py} (\texttt{PS.PROTON.02}/\texttt{PS.THRESHOLD.02}) decides
  branch B of the \vref{v265} fork.} The explicit two-step Pati--Salam thresholds give $d{=}6$
  $\tau_p(p{\to}e^+\pi^0)$ (writes \texttt{ps\_threshold\_proton.json}): \mX\ the minimal $16$-Higgs content
  ($M_{GUT}{\sim}2.4{\times}10^{15}$) gives $\tau_p{\sim}4.4{\times}10^{33}$ yr $<$ Super-K and is
  \emph{killed} even at the high hadronic band; \mC\ the $E_8$-allowed $(15,1,1)$ [the single $45$] raises
  $M_{GUT}{\sim}5.9{\times}10^{15}$ $\Rightarrow\tau_p{\sim}1.6{\times}10^{35}$ yr, proton-safe \emph{now};
  \mX\ but that sits at the Hyper-K reach (${\sim}1.4{\times}10^{35}$ yr) --- a \emph{dated} kill test
  decisive within the decade. So branch B is promoted from ``well-mannered candidate'' to
  \emph{content-selected (must be $+(15,1,1)$), Hyper-K-decisive UV branch}; \mO\ structurally marginal
  (only one $45$ in the hull, \vref{v247}) with an $O(3)$ $\tau_p$ band. Branch A (boundary-only) is
  unchanged and canonical. \mE\ build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (The 4D-QFT fork frozen as a branch policy: boundary-only canonical, Pati--Salam a falsifiable UV branch, SM-only GUT killed, \texttt{v265})}
\begin{itemize}
\item \textbf{\texttt{v265\_qft4d\_fork\_freeze.py} (\texttt{QFT4D.FORK.01}) turns the 4D-QFT fork from an open
  ambiguity into a frozen decision tree} (\texttt{qft4d\_fork\_freeze.json}), no new physics. \textbf{A
  (canonical):} boundary-only is the default 4D reading --- a 4D-GUT is \emph{not claimed by default}
  ($E_8$ is the audit hull). \mX\ SM-only 4D-GUT unification is killed (1-loop: at the
  $\alpha_1{=}\alpha_2$ scale $\alpha_3^{-1}$ off by ${\sim}5.6$, spread ${\sim}8.8$ at $2{\times}10^{16}$
  GeV, re-deriving \vref{v246}) --- the canonical expectation, not a failure. \textbf{B (conditional):}
  carrier-native Pati--Salam is a falsifiable UV branch only with the $E_8$-allowed content
  $\{1,10,16,45\}$ (no $\mathbf{126}$, \vref{v247}), $\sin^2\theta_W{=}3/8$ (\vref{v248}), the $O(1)$
  $\kappa{=}M_{PS}/M_s$ band (\vref{v249}/\vref{v253}), a threshold model and a proton-decay kill test
  (\mX, no fake $\tau_p$ window; carrier gauging stays the contract). \mE\ a prose guard
  (\texttt{QFT4D.NO\_OVERCLAIM.01}) forbids bare 4D over-claims and requires the scoped policy wording. New
  ledger rows \texttt{QFT4D.BOUNDARY.DEFAULT.01}, \texttt{QFT4D.SMONLYGUT.01}, \texttt{PS.UVBRANCH.01},
  \texttt{PS.THRESHOLD.01}, \texttt{PS.PROTON.KILL.01}. A fork-policy box added to
  \texttt{tfpt\_research\_contracts}; \mE\ build green, \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (Three open-residual advances: the $F_{\mathrm{QCD}}$ solver, $M_\nu$ from $D_F$, and the raw-seam$\Rightarrow$mark-locality reduction, \texttt{v262}--\texttt{v264})}
\begin{itemize}
\item \textbf{\texttt{v262\_fqcd\_mp\_me.py} (\texttt{FR.MPME.02}) implements the one contract-only
  $F_{\mathrm{transfer}}$ pipeline.} A real two-loop $\alpha_s$ solver runs $\alpha_s(M_Z){=}0.1179$ with
  $n_f$ thresholds (carrier $b_3{=}-7$, \mE) to $\alpha_s(2\,\text{GeV}){\sim}0.30$ and
  $\Lambda^{(3)}_{\overline{\rm MS}}{\sim}0.33$\,GeV; with the lattice bridge $C_p$ (external $O(1)$) and the
  closed $m_e$ it reproduces $m_p/m_e{\sim}1824$ vs the measured $1836.15$ within the $\sim7\%$ external
  budget. A \mC\ transfer reproduction (firewall: no compiler integer for $1836$), advancing
  \texttt{FR.MPME.01} (\mO) to \texttt{FR.MPME.02} (\mC).
\item \textbf{\texttt{v263\_mnu\_from\_df.py} (\texttt{FLAV.PMNS.02}) makes $M_\nu$ a seesaw operator of
  $D_F$.} \mE\ $M_\nu=-m_D M_R^{-1} m_D^\top$ is symmetric, seesaw-suppressed and (for $\mu\tau$-symmetric
  inputs) $\mu\tau$-symmetric; \mC\ it reproduces $\theta_{23}{=}45^\circ$ and
  $\sin^2\theta_{12}{=}\tfrac13{-}\tfrac{\phiz}{2}$ (\vref{v9}) under the seam misalignment; \mO\
  $\theta_{13}{=}0$ in the leading texture, the CP \emph{magnitude} ($240^\circ$) is the $\mu_6$/triality
  phase (\vref{v231}/\vref{v233}), and $M_R$ is the free seesaw scale. An operator advance, not a closure
  of full PMNS dynamics.
\item \textbf{\texttt{v264\_raw\_seam\_marklocal.py} (\texttt{QGEO.ENERGY.03}) sharpens the bedrock.}
  Composing \vref{v216}$+$\vref{v201}$+$\vref{v198} on the canonical pillowcase: the flat-pillowcase
  curvature lives only at the $4$ marks, so the DtN sub-principal symbol is $\Z_4$-invariant (Fourier on
  $4\Z$, FFT-verified), block-diagonal, and $[\rho,\Lambda]{=}0\Rightarrow\omega\circ\rho{=}\omega$ on this
  metric. So the whole bedrock collapses to the single metric statement ``the raw RP seam carries the
  uniformising flat pillowcase metric'' ($=$\texttt{QGEO.SYM.01}). A reduction/sharpening, \mO\ --- it does
  \emph{not} prove the seam must carry that metric (negative control: curvature off the $\mu_4$ orbit breaks
  the chain). Paper citations added in \texttt{tfpt\_4\_frontier}, \texttt{tfpt\_2\_standard\_model} and
  \texttt{tfpt\_research\_contracts}. \mE\ \texttt{AUDIT OK}, build green.
\end{itemize}

\subsection*{2026-06-18 (Paper consistency pass: the closure ledger and the status/QFT sections updated for the Modular Spectral Closure, with an explicit ``what is \emph{not} closed'' line)}
\begin{itemize}
\item \textbf{Five paper sections that predated the \texttt{v238}--\texttt{v261} round are brought up to date}
  (additive, no status marker moved). The \texttt{introduction} closure-ledger table and the
  ``five questions'' item now carry a \emph{boundary QFT (Modular Spectral Closure)} row --- one relative
  object $\mathsf{TFPT}_{\mathrm{QFT}}=(\mathcal A_\Sigma,\omega_\Sigma,\Delta_\Sigma,\rho,A_F,H_F,D_F,J,
  \gamma,S_{\mathrm{rel}})$ closed modulo \texttt{QGEO.SYM.01} (\vref{v258}--\vref{v261}) --- plus an explicit
  list of what the closure does \emph{not} reach: the full measured pole masses, the absolute QCD scales
  ($m_p/m_e$), the complete PMNS dynamics, and the real $4$D interacting QFT / ambient measure. The
  \texttt{tfpt\_2} ``ambient closure'' section now states that the cutoff of its $S_{\mathrm{rel}}$ \emph{is}
  the seam KMS weight ($f_2/f_0{=}1$, \vref{v259}) and $D_{\mathrm{rel}}$ the covariance induction
  (\vref{v258}); the \texttt{tfpt\_2} ``(4) Constructive QFT closure'' section adds the relative-object
  pointer; \texttt{tfpt\_4\_frontier}'s full-quantum-gravity section records that the cutoff moment $f_0$ is
  pinned by the seam state (\vref{v255}/\vref{v259}); and \texttt{origin\_theory}'s honest-status keybox notes
  that the whole boundary QFT collapses onto the same \texttt{QGEO.SYM.01} postulate (no sixth structural
  class). An editorial consistency pass so every status surface agrees with the ledger. \mE\ build green
  (\texttt{10 ok, 0 failed}), \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-18 (Consistency pass: the Modular Spectral Closure surfaced structurally across the website and the intro status card)}
\begin{itemize}
\item \textbf{The \texttt{v258}--\texttt{v261} closure is now reflected on every ``what is open'' surface, not just the
  research-contracts paper.} The homepage open-gates section and compiler-pipeline diagram, the hostile-referee
  FAQ, the glossary $G_{\mathrm{net}}$ entry, the reviewer page and the verification residual-chain caption now
  state that the \emph{entire} emergent-QFT layer (Dirac, cutoff, gauging, glue, orientability) collapses onto
  the \emph{same} premise \texttt{QGEO.SYM.01} via the Modular Spectral Closure --- the boundary QFT is one
  relative object that adds \emph{no new open item}, ambient QG separate. The introduction status card
  (``the structural residual is one condition'') carries the same sentence. No status marker moved; this is an
  editorial consistency pass so the public surfaces agree with the ledger and the paper. \mE\ build green,
  \texttt{AUDIT OK}.
\end{itemize}

\subsection*{2026-06-17 (The Modular Spectral Closure: Dirac as covariance induction, the modular cutoff, the Kummer/K3 unification, and the assembly certificate, \texttt{v258}--\texttt{v261})}
\begin{itemize}
\item \textbf{\texttt{v258\_dirac\_covariance\_induction.py} (\texttt{PS.DIRAC.03}) closes the
  ``posited Yukawa vs derived operator'' gap of \vref{v250}/\vref{v252}.} The finite Dirac operator $D_F$
  is the modular/covariance \emph{induction} of the boundary seam quasi-free (KMS, $\beta{=}1$) state: a
  Gaussian state is fixed by its covariance $C$ (a positive contraction) with one-particle modular
  Hamiltonian $H=\log((1{-}C)C^{-1})$ (Araki; Casini--Huerta), inverse to the KMS occupation
  $C=(1{+}e^{H})^{-1}$. \mE\ the inversion identity holds exactly; \mE\ $C_F$ is a positive contraction;
  \mE\ the induced operator is chirality-odd; \mE\ it is unitarily equivalent to the \vref{v252} $D_F$ (same
  mass spectrum); \mE\ the Majorana/seesaw $m_D^2/M_R$ is an off-diagonal covariance entry. \mC\
  $C_F=P_F C_\Sigma P_F$, so $D_F$ is the Kasparov shadow $[D_\Sigma]\widehat\otimes_{(E_8)_1}[\mathcal
  K_{\mathrm{car}}]$ of the boundary geometry and the \vref{v18} Yukawas are the readout of $C_\Sigma$.
\item \textbf{\texttt{v259\_modular\_cutoff\_kappa.py} (\texttt{PS.SPECACT.02}) fixes the last open
  spectral-action input.} The cutoff $f$ is the seam's own modular/KMS weight: by
  Tomita--Takesaki/Bisognano--Wichmann the seam is KMS at $\beta{=}1$ (\vref{v239}) and $2\pi{=}1/(4c_3)$
  (\vref{v58}) fixes $\beta$, so the heat-kernel cutoff $f(u)=e^{-u}$ is \emph{derived}. \mE\ its moments
  give $f_2/f_0=f_4/f_2=1$ exactly; \mE\ a generic Gaussian cutoff gives $\sqrt\pi/2\neq1$ (the choice is
  non-vacuous); \mE\ hence $\kappa=\sqrt{(f_2/f_0)\,c_{PS}/c_{\rm grav}}=\sqrt{c_{PS}/c_{\rm grav}}$ loses
  its scheme factor. \mC\ the open \mO\ cutoff freedom of \vref{v253}/\vref{v255} becomes a finite trace
  ratio over the $96$-dim $H_F$ (the RG $\kappa{\approx}1.3$ pins $c_{PS}/c_{\rm grav}{\approx}1.7$).
\item \textbf{\texttt{v260\_k3\_kummer\_unification.py} (\texttt{ARCH.K3.01}) unifies seam, carrier and
  lattice on one surface.} The pillowcase is the elliptic-involution quotient $T^2_{\tau=i}/(z{\mapsto}{-}z)$
  (\vref{v214}); squaring it gives the Kummer/K3 surface, whose three facets are three TFPT objects. \mE\ the
  $E_8$ Cartan is even/$\det1$/positive-definite; \mE\ $H^2(\mathrm{K3},\Z)=U^3\oplus E_8({-}1)^2$ (rank $22$,
  $\det{-}1$, even, signature $(3,19)$); \mE\ the seam is $T^2/(z{\mapsto}{-}z)$ with $4$ marks (orbifold
  Euler char $0$); \mE\ the carrier-$16$ are the $|A[2]|{=}2^4{=}16$ Kummer nodes $=\dim S^+$ (\vref{v197}),
  $16{=}4{\times}4$; \mE\ honest note --- the rank-$16$ Kummer lattice is \emph{not} the $E_8({-}1)^2$
  summand. \mC\ so the \vref{v1} ``glue $D_5{\oplus}A_3{+}\mu_4{\Rightarrow}E_8$'' is the lattice shadow of a
  single object; $E_8$ appears both locally (du Val $\mathbb C^2/2I$, \vref{v232}/\vref{v236}) and globally
  ($H^2$ summand). A unification, not a closure.
\item \textbf{\texttt{v261\_modular\_spectral\_closure.py} (\texttt{QFT.MSC.01}) is the assembly capstone.}
  The whole QFT round (\vref{v238}--\vref{v260}) is certified as \emph{one} relative object
  $\mathsf{TFPT}_{\mathrm{QFT}}=(\mathcal A_\Sigma,\omega_\Sigma,\Delta_\Sigma,\rho,A_F,H_F,D_F,J,\gamma,
  S_{\mathrm{rel}})$ reduced to \emph{one} open premise. \mE\ the cross-consistency invariants agree:
  $4=[B{:}A]=|\mu_4|=2\chi=|(\Z/2)^2|$ (index $=$ marks $=$ fixed points $=$ glue order), one carrier-$16$
  (spinor $=$ lattice $=$ triple), one gap $6\log(3/2)$ (OS $=$ recovery $=$ Lindblad); \mE\ the three
  closures re-derived; \mE\ the ten-component manifest present. \mO\ the QFT layer reduces to
  \texttt{QGEO.SYM.01} (seam realisation), the ambient QG measure \texttt{QG.AMB.01} kept separate. \mC\
  the \emph{Modular Spectral Universality} master statement: the unique RP holomorphic index-$4$ KMS seam
  state induces the $96$-dim KO-$6$ triple whose inner fluctuations give the gauged Pati--Salam spectral
  action --- the honest sense in which the boundary QFT is complete.
\end{itemize}

\subsection*{2026-06-17 (Infrastructure: the changelog is now a public website page, generated from \texttt{changelog.tex} and audit-gated)}
\begin{itemize}
\item \textbf{The canonical changelog now also drives a public \texttt{/changelog} website page.}
  A new generator \texttt{verification/make\_changelog\_web.py} parses this file (dated
  \texttt{\textbackslash subsection*} entries, \texttt{itemize} items, and the inline markup
  \texttt{\textbackslash textbf}/\texttt{\textbackslash emph}/\texttt{\textbackslash texttt}/\texttt{\textbackslash vref},
  the status markers \mE/\mC/\mO/\mX, inline math and accents) into the typed data file
  \texttt{website/\allowbreak lib/\allowbreak changelog.ts}, rendered server-side (math via KaTeX) by
  \texttt{website/\allowbreak app/\allowbreak changelog/\allowbreak page.tsx} $+$ \texttt{website/\allowbreak components/\allowbreak Changelog.tsx}. The
  generator is wired into \texttt{bash build.sh gen}; its freshness is enforced by
  \texttt{audit\_sync.py} (section A.generated), so the page can never drift from this file --
  editing the changelog and re-running \texttt{gen} is the only supported path (the \texttt{.ts}
  mirror is never hand-edited). \texttt{/changelog} is linked from the navbar, footer and sitemap.
  The \texttt{tfpt-workflow}, \texttt{website-sync} and \texttt{sync-maps} cursor rules were updated
  to record the new single-source generation step. \mE\ build (\texttt{npm run build} green,
  \texttt{/changelog} prerendered static) and \texttt{bash build.sh audit} (\texttt{AUDIT OK}).
\end{itemize}

\subsection*{2026-06-17 (Orientability + Poincar\'e duality: the honest, literature-confirmed status --- strict fail, weakened hold, \texttt{v257})}
\begin{itemize}
\item \textbf{\texttt{v257\_quasiorient\_modpd.py} (\texttt{PS.NCG.ORIENT.02}) corrects the slightly
  too-generous \vref{v256} typing.} The published result (Cacic--Stephan arXiv:0902.2068; CCM07;
  SM-vacuum hep-th/0601192) is that the Chamseddine--Connes--Marcolli Standard-Model finite triple
  (KO-dimension $6$, with three right-handed neutrinos --- exactly the TFPT seesaw case) \emph{genuinely
  fails} strict orientability and strict Poincar\'e duality, and instead satisfies the physically correct
  weakened versions. Verified on the explicit \vref{v252} triple: \mE\ strict orientability fails
  ($\gamma\notin\mathrm{span}\{\lambda(a)\rho(b)\}$); \mE\ \emph{quasi-orientability} holds (the left/right
  $A$-irrep boxes are disjoint by chirality: $L=H$ weak-doublet, $R=\mathbb C$ singlet, so
  $L^{\mathrm{LR}}(\mathcal H^{\mathrm{even}},\mathcal H^{\mathrm{odd}})=\{0\}$); \mE\ strict Poincar\'e
  duality fails (KO-$6$ skew intersection form, corank $1$, the equal-$L/R$-neutrino case); \mC\ modified
  Poincar\'e duality holds (CCM), Stephan's alternative triple (St06) restoring strict PD with identical
  physics. A known property of the NCG-SM model class, not a TFPT defect --- no faked closure.
\end{itemize}

\subsection*{2026-06-17 (Remaining NCG obligations discharged or honestly typed: inner fluctuations, spectral action, orientability/Poincar\'e, \texttt{v254}--\texttt{v256})}
\begin{itemize}
\item \textbf{\texttt{v254\_inner\_fluctuations.py} (\texttt{PS.NCG.FLUCT.01}) closes \vref{v250} \#5 + the
  no-junk obligation.} The inner fluctuations $\Omega^1_D(A_F)$ of the finite Dirac operator are computed
  explicitly: \mE\ they are purely chirality-odd (scalars), and for the SM algebra sit \emph{exactly} in the
  one Higgs doublet $(1,2)_{1/2}$ --- no junk, no triplet, no $(10,1,3)/\mathbf{126}$. \mE\ the $\sigma$
  ($\nu_R$ Majorana) direction is absent for the SM algebra but present for Pati--Salam (the CCvS
  beyond-first-order scalar), and \mE\ $\sigma$ is an SM singlet $(1,1,0)$ with $B{-}L=2$. \mC\
  $\sigma={}$scalaron.
\item \textbf{\texttt{v255\_spectral\_action\_expansion.py} (\texttt{PS.SPECACT.01}) closes the
  spectral-action expansion (\vref{v252} \#11).} The Seeley--DeWitt expansion
  $S=2f_4\Lambda^4 a_0+2f_2\Lambda^2 a_2+f_0 a_4$: \mE\ structure ($a_0$ cosmological, $a_2$
  Einstein--Hilbert$+$Higgs-mass, $a_4$ Yang--Mills$+$Weyl$^2+R^2+$Higgs-quartic, $N=96$); \mE\ $b/a^2=1/3$
  (top-dominated); \mE\ $\sin^2\theta_W=3/8$; \mE\ the $R^2$ spin-$0$ mode $=$ the Starobinsky scalaron; \mC\
  Higgs quartic $\to{\sim}125$\,GeV with $\sigma$; \mC\ $\kappa=\sqrt{(f_2/f_0)c_{PS}/c_{\rm grav}}$ explicit;
  \mO\ exact decimal needs the cutoff moments.
\item \textbf{\texttt{v256\_orientability\_poincare.py} (\texttt{PS.NCG.ORIENT.01}) --- honest status, no
  faked proof.} KO-dimension $6$ forces the intersection form $\mathrm{Tr}(\gamma\,\pi(p)J\pi(q)J^{-1})$ to be
  \emph{antisymmetric}: \mE\ skew form (verified), \mE\ rank $2$, corank $1$, null $\sim(1,1,-1)$ on the SM
  K-theory $\mathbb Z^3$; \mE\ the orientability local condition $[\gamma_F,\pi(a)]=0$. \mC\ the canonical
  hypercharge-faithful SM/PS triple satisfies orientability and Poincar\'e duality (van Suijlekom; CCM); \mO\
  a self-contained machine proof needs the complete canonical bimodule.
\end{itemize}

\subsection*{2026-06-17 (Full $96$-dim finite spectral triple built + NCG axioms verified, and $\kappa$ pinned to $O(1)$, \texttt{v252}--\texttt{v253})}
\begin{itemize}
\item \textbf{\texttt{v252\_full\_finite\_triple.py} (\texttt{PS.DIRAC.02}) advances the Dirac contract
  \vref{v250} from a $7$-obligation contract to a concrete object discharging $5$ to \mE.} The full
  $96$-dim finite spectral triple $(A_F,H_F,D_F,J,\gamma)$ --- $H_F$ the particle$\oplus$antiparticle
  doubling of three $SO(10)$ $\mathbf{16}$-plets --- is built explicitly and the NCG axioms are checked by
  direct computation: \mE\ reality ($J^2{=}{+}1$, $JD{=}DJ$), grading ($\gamma^2{=}1$, $[\gamma,a]{=}0$,
  $J\gamma{=}{-}\gamma J$), KO-dimension $6$, order-zero, the first-order condition (HOLDS for the SM algebra
  including the Majorana; VIOLATED for the Pati--Salam algebra exactly by the Majorana, localized to
  $\{\nu_R,e_R\}$ --- the CCvS beyond-first-order mechanism on the full triple), and the spectrum of $D_F$
  reproducing the fermion masses and the type-I seesaw $m_{\rm light}{=}m_D^2/M_R$. \mC\ Poincar\'e duality;
  \mO\ orientability, no-junk, spectral-action expansion.
\item \textbf{\texttt{v253\_kappa\_scalaron\_ps.py} (\texttt{PS.KAPPA.01}) discharges residual 6(b) of
  \vref{v249}.} $\kappa$ in $M_{PS}=\kappa\,M_s$ ($M_s=c_3^{7/2}\bar M\approx3.06{\times}10^{13}$\,GeV, exact)
  is pinned by an RG scan (PDG errors $\times$ the two $E_8$-allowed contents) to a tight $O(1)$ interval
  ($\approx1.3$). \mC\ heat-kernel origin: $\kappa=\sqrt{(f_2/f_0)\,c_{PS}/c_{\rm grav}}$ is a scale-free
  ratio of heat-kernel traces over the $96$-dim $H_F$ ($\Lambda$ cancels). \mX\ the $\mathbf{126}$-content
  drives $\kappa$ out of the $O(1)$ window (content-selective). \mO\ the exact decimal needs $f_2/f_0$ fixed.
\end{itemize}

\subsection*{2026-06-17 (Spectral triple, first step: the first-order condition is violated exactly by the Majorana/$\sigma$ --- the CCvS Pati--Salam mechanism, \texttt{v251})}
\begin{itemize}
\item \textbf{\texttt{v251\_first\_order\_sigma.py} (\texttt{PS.DIRAC.01}) advances the Dirac contract
  \vref{v250} from a contract to an exhibited mechanism.} On a faithful lepton-block model
  ($H=H_F\oplus H_F^c$, $H_F=\mathbb C^3$), the real even structure is checked ($J^2{=}{+}1$,
  $\gamma^2{=}1$, $D\gamma{=}{-}\gamma D$, KO-dim-6 signs), order-zero holds, the first-order condition
  HOLDS for the Yukawa block, and is VIOLATED \emph{exactly} by the Majorana ($\nu_R\nu_R^c=\sigma$) block
  --- the Chamseddine--Connes--van Suijlekom ``beyond first order'' mechanism by which the inner
  fluctuations promote the SM to Pati--Salam and generate $\sigma$. Honest correction to the review:
  $\sigma$ does \emph{not} rescue the first-order condition; its controlled violation \emph{is} the
  mechanism. \mC\ $\sigma={}$scalaron (\vref{v249}); \mO\ the full $96$-dim triple $+$ spectral action.
\end{itemize}

\subsection*{2026-06-17 (Carrier-native Pati--Salam program: $E_8$ forbids the 126, PS algebra, unification kill-test, Dirac contract, \texttt{v247}--\texttt{v250})}
\begin{itemize}
\item \textbf{Four scripts turning the gauge-unification finding into typed claims with negative controls.}
  \texttt{v247\_e8\_branching\_no126.py} (\texttt{PS.E8BRANCH.01}): the $E_8$ hull branches under
  $SO(10){\times}SU(4)$ as $(45,1){+}(1,15){+}(10,6){+}(16,4){+}(\overline{16},\bar4)$, so the $SO(10)$
  content is exactly $\{1,10,16,45\}$ and the $\mathbf{126}$ is \emph{absent} --- the renormalisable
  $126_H$ is algebraically forbidden and $10{+}16{+}45$ is $E_8$-supplied (only one $45\Rightarrow$
  proton-marginal). \texttt{v248\_ps\_algebra.py} (\texttt{PS.ALGEBRA.01}):
  $A_F=\mathbb H_L\oplus\mathbb H_R\oplus M_4(\mathbb C)\to SU(2)_L{\times}SU(2)_R{\times}SU(4)_c$, exact
  hypercharges $Y=T_{3R}+(B{-}L)/2$, matching $\alpha_1^{-1}=\tfrac35\alpha_{2R}^{-1}+\tfrac25\alpha_4^{-1}$,
  $\sin^2\theta_W=3/8$ (colour $SU(4)_c\subset D_5$, distinct from the family $A_3$).
  \texttt{v249\_ps\_unification.py} (\texttt{PS.RGTEST.01}): the two-step PS$\to SO(10)$ unification kill-test
  with negative controls (SM-only fails; $126$ breaks the scalaron match; proton decay selects content),
  $M_{PS}/M_s=1.0$--$1.7$. \texttt{v250\_dirac\_triple\_contract.py} (\texttt{CONTRACT.QFT4D.DIRAC.01}): the
  spectral-triple contract ($H_F=3{\times}16$, the seven NCG axioms, $\sigma=$scalaron) that would turn
  ``carrier is gauged'' from a fork into a theorem. The root-level \texttt{qft.txt} carries the full analysis.
\end{itemize}

\subsection*{2026-06-17 (Honest data cross-check + emergent-QFT figures: the unification tension, \texttt{v246})}
\begin{itemize}
\item \textbf{\texttt{v246\_unification\_data\_crosscheck.py} (\texttt{QFT4D.RGTEST.01}) --- the first hard
  data confrontation of the spectral-action prediction.} TFPT's gauge-charged content \emph{is} the
  Standard Model (\vref{v159}) and the theory adds no new states; the $E_8$ cascade is an arithmetic spine
  (\vref{v5}), not a threshold tower. So the run \emph{is} the SM run: at one loop the couplings spread
  ${\sim}10^{13}$--$10^{17}$\,GeV (residual $\Delta\alpha^{-1}\approx9$ at $2{\times}10^{16}$\,GeV), and at
  two loops (RK4) the minimal spread is $\Delta\alpha^{-1}\approx3.2$ at $1.7{\times}10^{14}$\,GeV --- the
  three never meet. Typed \mX/\mO: with ``no new state'' there is \emph{no} admissible threshold source, so
  the spectral-action 4d-GUT route is in genuine tension (same status as NCG-SM), likely falsified unless
  extended --- never a confirmation, and \emph{not} rescued by a cascade. Two new figures
  (\texttt{figures/qft\_skeleton.pdf},
  \texttt{figures/qft\_unification.pdf}) added via \texttt{make\_figures.py} (PDF $+$ website PNG) and
  embedded in \texttt{tfpt\_research\_contracts.tex}; a root-level \texttt{qft.txt} summarises the
  emergent-QFT skeleton, what each script proves, the data status and the open questions.
\end{itemize}

\subsection*{2026-06-17 (Spectral-action matter content: the $SO(10)$ \textbf{16} $=$ one anomaly-free SM generation, \texttt{v245})}
\begin{itemize}
\item \textbf{\texttt{v245\_spectral\_matter\_content.py} (\texttt{QFT4D.MATTER.01})
  discharges the computable core of the 4d contract \vref{v244}.} The carrier
  half-spinor (the $SO(10)$ \textbf{16}) is verified, in exact rational arithmetic,
  to be one Standard-Model generation: $\mathbf{16}=SU(5)(\mathbf{10}{+}\bar{\mathbf
  5}{+}\mathbf1)$, the SM multiplet dimensions sum to $16=\dim S^+$ ($15$ Weyl
  fermions $+\,\nu_R$), the electric charges $Q=T_3+Y$ are exactly the SM values,
  all four gauge anomalies cancel ($\sum Y=\sum Y^3=[SU(2)]^2U(1)=[SU(3)]^2U(1)=0$),
  the spectral-action normalisation gives $\sin^2\theta_W=3/8$
  ($g_3=g_2=\sqrt{5/3}\,g_1$), and the Higgs is the $(1,2)_{1/2}$ inner fluctuation.
  So the matter-content $+$ tree-relation half of \texttt{CONTRACT.QFT4D.01} is now
  \mE; only the seam$\to$Dirac realisation and the run-down couplings stay \mO.
  Wired into \texttt{run\_all.py}, the ledger, the registry, cited in
  \texttt{tfpt\_research\_contracts.tex}, mirrored to the website.
\end{itemize}

\subsection*{2026-06-17 (The QFT skeleton on the seam: thermal time, GNS/OS reconstruction, DHR sectors, the braiding S-matrix, and the 4d spectral-action contract, \texttt{v239}--\texttt{v244})}
\begin{itemize}
\item \textbf{Six emergent-QFT skeleton scripts (\vref{v238}).}
  \texttt{v239\_\allowbreak kms\_\allowbreak thermal\_\allowbreak time.py} (\texttt{DYN.KMS.01}): the modular flow is KMS
  at $\beta=1$, and $2\pi=1/(4c_3)$ fixes the modular temperature as $T_H=c_3/M$ ---
  thermal time $=$ horizon time. \texttt{v240\_gns\_os\_reconstruction.py}
  (\texttt{DYN.GNS.01}): GNS reconstructs the Hilbert space from $(\mathcal M,\omega)$
  and the OS Hamiltonian $H_{\mathrm{OS}}=-\log T=-L$ is positive with gap $\Delta$
  (the \vref{v64} mass gap). \texttt{v241\_dhr\_sectors.py} (\texttt{DHR.SECTORS.01}):
  particles $=$ DHR sectors $=$ the discriminant anyons of the Lean glue form, with
  the condensation tower $16\to4\to1$ (\vref{v235}/\vref{v237}).
  \texttt{v242\_spin\_statistics\_modular.py} (\texttt{DHR.MODULAR.01}):
  spin-statistics, the modular $(S,T)$ data, Verlinde fusion, and Gauss--Milgram
  $c=8$. \texttt{v243\_haag\_ruelle\_braiding.py} (\texttt{DHR.SMATRIX.01}): the
  $2$-particle S-matrix $=$ the braiding monodromy (factorised, crossing), with the
  \vref{v238} mass gap supplying Haag--Ruelle asymptotic states.
  \texttt{v244\_spectral\_action\_contract.py} (\texttt{CONTRACT.QFT4D.01}): the 4d
  Lagrangian via the Connes spectral action --- the carrier half-spinor $16$ is one
  generation, the SM gauge group sits in the carrier, gravity is \vref{v36}; the
  matter Lagrangian is the open \mO\ contract. Net: the residual to a full 4d QFT is
  \emph{one premise} (\texttt{QGEO.SYM.01}) plus \emph{one contract}
  (\texttt{CONTRACT.QFT4D.01}). All wired into \texttt{run\_all.py}, the ledger and
  registry, cited in \texttt{tfpt\_research\_contracts.tex}, mirrored to the website.
\end{itemize}

\subsection*{2026-06-17 (The static$\to$dynamic flip: modular flow $+$ a recovery Lindblad generator, \texttt{v238})}
\begin{itemize}
\item \textbf{New \texttt{v238\_modular\_lindblad\_dynamics.py} (\texttt{DYN.SEMIGROUP.01}, cluster
  \texttt{registry}).} A companion to the modular round (\vref{v196}/\vref{v198}) and the recovery code
  (\vref{v221}/\vref{v64}) that reads the \emph{same} seam objects \emph{dynamically} rather than
  statically. \mE\ the modular flow $\sigma_t=e^{i t\Lambda_\Sigma}$ is a unitary one-parameter group
  (Tomita--Takesaki) whose conservation of the $\mu_4$ clock,
  $\rho\sigma_t\rho^{-1}=\sigma_t\Leftrightarrow[\rho,\Lambda_\Sigma]=0$, IS the \vref{v198}
  state-invariance --- so the static commutator is the conservation law of modular time. \mE\ the
  recovery channel's generator $L=\log T$ is a doubly-stochastic/CPTP-classical Markov generator
  ($e^{L}=T$, $e^{L\tau}\to$ the democratic projector $=$ the arrow of time). \mE\ keystone: the
  dissipative gap $=-\log((2/3)^6)=6\log(3/2)=$ the OS mass gap $\Delta$ (\vref{v64}) --- the static
  recovery bound (\vref{v221}) and the dynamical mass gap (\vref{v64}) are one number, one
  exponentiated. \mE\ the GKSL split $G=i\Lambda_\Sigma+L$ (imaginary $+$ real$\le0$ spectrum). \mO\
  the residual is the \emph{geometric} modular flow (Connes--Rovelli ``thermal time $=$ physical
  time'') on the full seam algebra $=$ \texttt{QGEO.SYM.01} (\vref{v198}) --- a target, not a closure.
  Wired into \texttt{run\_all.py}, \texttt{status\_ledger.csv}, \texttt{script\_registry.csv} and cited
  in \texttt{tfpt\_research\_contracts.tex}; mirrored to \texttt{website/public/verification}.
\end{itemize}

\subsection*{2026-06-17 (Experiments: black-hole-cosmology signatures, the $\eta_B$ Boltzmann solve, the Petz/baby-universe realisation, and a real-data GW-echo pipeline)}
\begin{itemize}
\item \textbf{Three new standalone black-hole-cosmology experiments (\texttt{experiments/}, all
  \texttt{data\_limited}, not load-bearing).} From the \texttt{problem\_b} black-hole-cosmology survey:
  (i) \texttt{ccbh-dark-energy} --- the de~Sitter seam interior ($w_{\mathrm{in}}{=}{-}1$) forces the
  Croker--Weiner cosmological-coupling index $k={-}3w_{\mathrm{in}}=3$, hence a population $w={-}1$;
  vs.\ Farrah+2023 $k=3.11\pm0.79$ ($-0.14\sigma$), a \emph{contested} downstream bridge and an
  \emph{alternative reading} of the same $w={-}1$ the DESI watchdog tests (\texttt{alternative\_group}
  \texttt{w\_de\_eos}, never double-counted). (ii) \texttt{gravastar-compactness} --- the Nariai
  $Q_{\mathrm{geom}}{=}3/8$ equals the Jampolski--Rezzolla (2026) maximum horizonless compactness
  $\mathcal C{=}3/8$ (shared de~Sitter endpoint $1/2$); since $1/3{<}3/8{<}4/9{<}1/2$ this is a
  light-trapping ECO, yielding an echo template (round-trip delay ${\sim}0.7$ ms at $62\,M_\odot$,
  amplitude $\le(2/3)^6$) --- a \mC\ structural echo, no $\mathcal C\!\leftrightarrow\!Q_{\mathrm{geom}}$
  map proven. (iii) \texttt{cosmic-handedness} --- a parity watchdog (Shamir JADES ${\sim}3.3\sigma$
  spin monopole, most likely a Milky-Way-aberration dipole), explicitly \emph{not} promoted (frontier).
\item \textbf{$\eta_B$ --- full BDP Boltzmann ODE solve confirms the route at the frozen scale
  (\texttt{experiments/ftransfer/leptogenesis\_boltzmann/fboltzmann\_solve.py}; \texttt{tfpt\_4\_frontier},
  \mC).} Integrating the Buchm\"uller--Di~Bari--Pl\"umacher Boltzmann network (integrated efficiency
  $\kappa_f=0.092$, validating the analytic fit) at the \emph{frozen} heavy scale
  $M_1=M_{\mathrm{scal}}(\phiz)^2/A_\Lambda\approx8.65\times10^9$ GeV with $\delta_{\mathrm{CP}}=4\pi/3$ gives
  $\eta_B=6.5\times10^{-10}$ --- a factor $1.07$ from the observed $6.1\times10^{-10}$, with \emph{no} free
  $M_R$ dial. This moves the leptogenesis route from ``solve pending'' to a consistent \mC\ readout (the full
  \emph{flavored} density-matrix solve is the next refinement); \texttt{tfpt\_4\_frontier} Route~C synced.
\item \textbf{The Petz recovery map and the rank-one baby universe, realised numerically
  (\texttt{experiments/recovery-channel}; \texttt{tfpt\_horizon\_readouts}, \mC; companion to \vref{v221}).}
  The gapped transport contracts to a \emph{rank-one} projector at exactly $\|T^n-P_\infty\|=(2/3)^{6n}$ ---
  the one-dimensional baby-universe Hilbert space (Engelhardt 2025) --- and the explicit Petz map is CPTP,
  recovers the reference, and equals the identity only on the protected $\lambda{=}1$ (Knill--Laflamme) mode;
  free-ratio and degenerate-spectrum negative controls hold. So the Petz identification \vref{v221} deferred is
  now verified at the channel level (\texttt{internal\_consistency}, no new datum); the full holographic
  reading stays gated on the Seam--Horizon theorem.
\item \textbf{GW ringdown echo --- Stage-1 matched filter validated, then run on real GWOSC strain
  (\texttt{experiments/gw-ringdown-echo}; \texttt{tfpt\_horizon\_readouts} search-targets).} The Stage-1
  machinery (Kerr-ringdown subtraction $\to$ matched filter on the residual, ratio $(2/3)^6$ frozen, lag free,
  $+$ free-ratio control) classifies $3/3$ synthetic injections; run on \emph{real} GWOSC strain
  (GW150914, GW190521; PSD-whitening $+$ off-source background): \textbf{no kernel-ratio echo coincident in
  $\ge2$ detectors}, consistent with the $(2/3)^6$ \emph{upper} bound (a single loud H1 excess has
  $\hat q\approx2$, far from $(2/3)^6$, so the free-ratio control flags it as residual ringdown, not an echo).
  First pass: dominant-QNM subtraction, incoherent combination --- full multi-mode $+$ coherent stacking is the
  next step; no detection claim.
\item \textbf{Scorecard + website synced.} \texttt{experiments/evidence\_scorecard.json} now $51$ rows
  ($26$ consistent, $7$ null, $13$ data-limited, $4$ tension, $1$ parked); the website
  \texttt{EXPERIMENTS\_AUDIT} mirror and the $\eta_B$ prediction entry are updated to match. These are
  standalone \texttt{experiments/} surfaces (not in the verification suite or ledger); the
  \texttt{tfpt\_4\_frontier}/\texttt{tfpt\_horizon\_readouts} and \texttt{papers.ts}/\texttt{predictions.ts}
  edits are the in-same-change sync.
\end{itemize}

\subsection*{2026-06-17 (Red-team layer re-synced to the paper; shadow export mirrors \texttt{figures/})}
\begin{itemize}
\item \textbf{Red Team Target~A re-synced to \texttt{tfpt\_5\_redteam} (\texttt{rt\_A\_e8net.py},
  \texttt{redteam\_table.txt}, \texttt{redteam/README.md}, infrastructure).} The Python red-team
  surface still emitted the historical \emph{three-residual} ``A reduced, not closed'' form, lagging the
  reader-facing note. It now encodes the sharper narrowing already in the paper: the residual collapses to
  the \emph{single} statement ``the seam--Calder\'on boundary net is holomorphic with $c=8$'' ($\Leftrightarrow$
  the index-4 simple-current extension), with the index-4 $(D5)_1\times(A3)_1\to(E8)_1$ glue realised at Lie
  level (\vref{v143}) and its odd sectors twisted/Ramond ($E_8=120_{\mathrm{NS}}+128_{\mathrm{R}}$, \vref{v148}),
  while the $q(A_3)$ normalisation collapses into the one declared anchor (\vref{v152}). Two exact adversarial
  checks added ($120{+}128=248$; glue index $=|\mu_4|=\Nfam{+}1=4$); status stays \mC/\mO\ (reduced, not closed).
\item \textbf{Shadow export now mirrors \texttt{figures/} but not \texttt{website/}
  (\texttt{scripts/export-shadow.sh}, \texttt{verification/make\_script\_index.py}, infrastructure).}
  \texttt{export-shadow.sh} ships \texttt{figures/*.pdf} (so \texttt{make\_manifest.py -{}-check} passes
  literally on the exported tree) while still excluding \texttt{website/} and the compiled paper PDFs; the
  \texttt{SHADOW\_MIRROR.md} table is corrected accordingly. \texttt{make\_script\_index.py} now detects a
  missing \texttt{website/} and skips its \texttt{ScriptIndex.tsx} mirror, so \texttt{build.sh notes} runs on
  the subset without crashing.
\end{itemize}

\subsection*{2026-06-17 (CP phases as $\mu_6$ powers --- a reduction of red-team Target D)}
\begin{itemize}
\item \textbf{Both CP phases are $\mu_6$ powers of one hexagonal CM unit, split by the sheet
  (\texttt{v231\_cp\_mu6\_phases}, \texttt{tfpt\_5\_redteam}, \mE/\mC).} Sharper than \vref{v220}/\vref{v225}
  (which only \emph{located} the CP residual). With $\rho=e^{i\pi/3}$ the primitive $6$th root (the $j{=}0$
  Eisenstein CM unit): $\delta_{\mathrm{CKM}}$ leading $=\arg(\rho^1)=\pi/3$ (quark) and
  $\delta_{\mathrm{PMNS}}=\arg(\rho^4)=4\pi/3$ (lepton, the phase lattice), with $\rho^4=-\rho$, so
  $\delta_{\mathrm{PMNS}}=\delta_{\mathrm{CKM,lead}}+\pi=(\text{CM unit})\times(\Z_2\text{ sheet}, \rho^3{=}{-}1)$.
  The two CP phases are \emph{one} hexagonal unit on the two sheets, not two independent inputs; the
  dual-frame Jarlskog orientations are sheet-flipped ($\pm21\sin(\pi/3)$). A structural reduction of Target~D
  (removes one of its two phase inputs); the quark seam correction $3\lambda_C^2$ stays the \vref{v88}
  misalignment, the deck stays $\Z/4$, and the physical CP derivation stays \mC\ (\texttt{CP.MU6.01}).
\item \textbf{The seam as the $E_8$ Kleinian singularity (\texttt{v232\_e8\_kleinian\_seam},
  \texttt{origin\_theory}, \mE/\mC).} The du~Val side of the McKay correspondence (\vref{v219}) gives the
  open seam-realisation premise \texttt{QGEO.REALIZE.01} a canonical algebraic-geometric model: dropping the
  trivial-rep node of the affine-$E_8$ McKay graph of $2I$ leaves the finite $E_8$ Dynkin $=$ the dual
  intersection graph of the eight exceptional $\PP^1$'s of the minimal resolution of $\mathbb C^2/2I$; the
  eight curves $=\operatorname{rank}E_8=g_{\mathrm{car}}{+}\Nfam$ (a fourth reading of the $8$), their negated
  intersection form is the $E_8$ Cartan ($\det1$, even, $(-2)$-curves), and the link is the Poincar\'e
  homology $3$-sphere $S^3/2I$ ($2I$ perfect $\Rightarrow H_1{=}0$, $\pi_1{=}2I$ order $120$). The raw seam
  ($\PP^1$ with marks)   is canonically a du~Val exceptional curve --- a model for the bedrock, not a P2 proof
  (it presupposes $E_8$; \texttt{TOPO.E8.01}, bedrock stays \mO).
\item \textbf{CP is the universal family/triality phase, only sheet-split
  (\texttt{v233\_cp\_triality\_phase}, \texttt{tfpt\_5\_redteam}, \mE/\mC).} One step past \vref{v231} in the
  $\mu_6=\mu_3$(family/triality)$\times\mu_2$(sheet) factorisation: $\rho=\omega^2(-1)$ with $\omega=e^{2\pi i/3}$
  the $\Z_3$ triality centre (the $2/3$ cusp weight). Since $\rho^4=\rho^1\rho^3$ with $\rho^3\in\mu_2$, the
  quark ($\rho^1$) and lepton ($\rho^4$) CP phases share the \emph{same} family/triality class and differ only
  by the sheet --- so CP \emph{is} the universal triality phase, sheet-split, not a free power choice
  (\texttt{CP.TRIALITY.01}).
\item \textbf{The Seam-Holomorphy selection certificate: the structural residual is one gate
  (\texttt{v234\_seam\_holomorphy\_selection}, \texttt{tfpt\_research\_contracts}, \mE/\mO).} The whole
  structural residual is \emph{one} condition --- ``the seam carries no nontrivial abelian sector'' --- with
  three provably-equivalent faces, all forcing $E_8$: (i) holomorphy ($\mu$-index $1$; Target A), (ii) the
  seam link is a homology $3$-sphere ($\Gamma$ perfect $\Leftrightarrow2I$; \vref{v232}), (iii) exactly one
  $1$-dim irrep (\vref{v219}). All equal $\#(\text{mark-}1)=|\Gamma^{\mathrm{ab}}|=|H_1|$, which is $1$ only
  for $E_8$; and holomorphic $c{=}8{=}\gcar{+}\Nfam$ gives the unique even unimodular rank-$8$ lattice $E_8$.
  So P2, $G_{\mathrm{net}}$, Target~A and the Kleinian seam are one gate. The stated closing theorem
  (\mO): RP$+$gap$+$chirality $\Rightarrow$ quasi-free bulk (\vref{v160}) $\Rightarrow$ holomorphic boundary
  $\Rightarrow E_8$; the single residual analytic step is ``free bulk $\Rightarrow$ holomorphic boundary''
  (\texttt{GATE.HOLO.01}).
\item \textbf{The closing step in Chern--Simons language: holomorphic $\Leftrightarrow\det K{=}1$
  (\texttt{v235\_seam\_chern\_simons}, \texttt{tfpt\_research\_contracts}, \mE/\mO).} A genuine reduction
  (not a closure) of \texttt{GATE.HOLO.01} into standard anyon-condensation physics: a free gapped bosonic
  $2{+}1$d bulk is an even integer $K$-matrix with $\#$anyons $=|\det K|$, edge $c={\rm signature}(K)$, and
  the edge net holomorphic $\Leftrightarrow|\det K|{=}1$. The TFPT extension tower (\vref{v92}) \emph{is} the
  condensation tower read by determinant: carrier $D_5{\oplus}A_3$ ($\det16$, $16$ anyons) $\to SO(16)_1{=}D_8$
  ($\det4$) $\to(E_8)_1$ ($\det1$, holomorphic) --- all rank $8$, $c{=}8{=}\gcar{+}\Nfam$ --- so holomorphic
  $=E_8=$ the Kitaev $E_8$ quantum-Hall state. Holomorphy $\Leftrightarrow$ condensing the order-$|\mu_4|$
  Lagrangian glue ($\det16{\to}1$, vs.\ a partial order-$2$ isotropic $\to4{=}D_8$). The residual narrows to
  one integer condition ``the free RP seam condenses the Lagrangian glue ($\det{=}1$)'' $=$ the sheet/QGEO
  selection, now with holomorphy$\Leftrightarrow\det1$ a theorem (\texttt{GATE.HOLO.02}).
\item \textbf{The $(2,3,5)$ Brieskorn singularity is the one generator of the skeleton
  (\texttt{v236\_brieskorn\_capstone}, \texttt{origin\_theory}, \mE).} Capstone of the icosahedral round:
  the singularity $x^2{+}y^3{+}z^5$, whose exponents are the atoms $(|\Z_2|,\Nfam,\gcar){=}(2,3,5)$, has
  Milnor number $\mu{=}(2{-}1)(3{-}1)(5{-}1){=}8{=}\operatorname{rank}E_8$ (a \emph{fifth} origin of the
  ``$8$''), Milnor monodromy $=$ the order-$30$ $E_8$ Coxeter element (eigenvalues the primitive $30$th
  roots $=$ the $E_8$ exponents, charpoly $\Phi_{30}$), Milnor lattice $E_8$, link the Poincar\'e sphere; the
  two clocks are facets of this one monodromy --- the $\mu_3$ triality (CP, \vref{v233}) is $h^{10}$ in
  $\langle h\rangle{=}\Z/30$, the $\mu_4$ clock (\vref{v223}) is the order-$4$ Galois automorphism of
  $\mathbb Q(\zeta_{30})$ (\texttt{TOPO.BRIESKORN.01}).
\item \textbf{The closing step as a physical condition: no topological degeneracy $\Leftrightarrow\det K{=}1
  \Leftrightarrow$ the seam is SRE (\texttt{v237\_seam\_sre\_closure}, \texttt{tfpt\_research\_contracts},
  \mE/\mO).} Sharpens \texttt{GATE.HOLO.02}'s residual from definitional to falsifiable: the $K$-matrix
  ground-state degeneracy on a genus-$g$ surface is $|\det K|^g$ (torus: carrier $16$, $D_8$ $4$, $E_8$ $1$),
  so ``no topological degeneracy on any closed surface'' $\Leftrightarrow\det K{=}1$; among rank-$8$ even
  positive-definite $K$ ($c{=}8{=}\gcar{+}\Nfam$) only $E_8$ is short-range-entangled (the Kitaev $E_8$
  phase). A unique vacuum on the plane (RP$+$gap$+$cluster) is necessary but not sufficient (the plane
  cannot see $\det K$); so the one open step is the physical statement ``the free RP seam is SRE (no
  topological order)'' (\texttt{GATE.HOLO.03}).
\end{itemize}

\subsection*{2026-06-16 (the icosahedral bedrock, CM-norm duality, and a structural-finds round)}
\begin{itemize}
\item \textbf{McKay bedrock: why the atoms are $\{2,3,5\}$ (\texttt{v219\_icosahedral\_mckay},
  \texttt{origin\_theory}, \mE).} $E_8$ is the exceptional \emph{top} of the McKay tower of finite
  $SU(2)$ subgroups ($2T{\to}\hat E_6$, $2O{\to}\hat E_7$, $2I{\to}\hat E_8$). Built \emph{from the
  group}: the $120$ unit-quaternion icosians close to the binary icosahedral group $2I$ (element orders
  $\{1,2,3,4,5,6,10\}$ --- it contains the $2,3,5$ rotation-axis orders), $9$ conjugacy classes; the
  $9$ irreducible character degrees (Dixon, from the class algebra) are $\{1,2,2,3,3,4,4,5,6\}$, sum
  $30{=}h(E_8)$, sum of squares $120{=}|R^+(E_8)|$; the McKay adjacency from the natural $2$-dim rep
  \emph{is} the affine $E_8$ graph with Kac marks $=$ the degrees. A backward certificate of the closed
  $E_8$, not a P2 proof (\texttt{MCKAY.E8.01}).
\item \textbf{CM-norm duality: $41$ (square) and $7$ (hex) (\texttt{v222\_cm\_norm\_duality},
  \texttt{origin\_theory}, \mE).} The square seam (Gaussian $\Z[i]$, $j{=}1728$) gives
  $N(\gcar{+}i|\mu_4|){=}5^2{+}4^2{=}41{=}10b_1$ (the EM index \emph{is} the Gaussian norm of the
  carrier-glue vector) and $N(3{+}2i){=}13{=}\Delta_Q$; the hexagonal partner (Eisenstein $\Z[\omega]$,
  $j{=}0$) gives $N(3{+}2\omega){=}7{=}$ scalaron. The $(3,2)$ split generates $(5,6,7,13)$ by
  sum/product/Eisenstein/Gauss norm; rings rigid (\texttt{CMNORM.DUAL.01}).
\item \textbf{The $\mu_4$ clock is the order-$4$ character of the $E_8$ Coxeter cycle
  (\texttt{v223\_\allowbreak coxeter\_\allowbreak totative\_\allowbreak clock}, \texttt{origin\_theory}, \mE).} $(\Z/30)^\times$ are the
  $E_8$ exponents; the order-$4$ generator $7$ ($\langle7\rangle{=}\{1,7,13,19\}$) is a literal $\mu_4$
  clock permuting the four conjugate planes; only $E_8$ has $\varphi(h){=}\mathrm{rank}$ and
  $h{=}2{\cdot}3{\cdot}5$ (\texttt{COX.CLOCK.01}).
\item \textbf{$248{=}120{+}128$ as a magnitude/phase channel typing
  (\texttt{v227\_\allowbreak degree\_\allowbreak exponent\_\allowbreak channel\_\allowbreak split},
  \texttt{tfpt\_5\_redteam}, \mE).} Exponents sum $120{=}|R^+(E_8)|$ (magnitude channel), degrees sum
  $128{=}\mathrm{rank}\cdot\dim S^+$ (phase/glue channel); the red-team Target~D magnitude bijection
  lives in $120$, the un-covered CP phases in $128$; the dark-sector reading of $128$ stays Frontier
  (replaces the over-strong $S^-$ reading; \texttt{E8.CHAN.01}).
\item \textbf{P2 as the mode space of a degree-$4$ seam divisor (\texttt{v228\_rr\_index\_gate},
  \texttt{origin\_theory}, \mE/\mC/\mO).} A Riemann--Roch index gate: $\deg D{=}4{=}|\mu_4|$ on $\PP^1$
  forces $h^0{=}5{=}\gcar$, $\mathrm{rank}\,H_1{=}3{=}\Nfam$, $h^0{+}H_1{=}8{=}\mathrm{rank}\,E_8$,
  $\Lambda^{\mathrm{even}}(\mathbb C^5){=}16{=}\dim S^+$ --- bedrock language for P2, conditional on the
  seam producing the degree-$4$ divisor (\texttt{QGEO.RR.01}).
\item \textbf{The seam as a finite recoverability code (\texttt{v221\_seam\_qecc},
  \texttt{origin\_theory}, \mE/\mC).} Code dimension $\dim S^+{=}16$; the gapped transport is a CPTP
  doubly-stochastic contraction with spectrum $\{1,(2/3)^6,(1/3)^6\}$, recovery bound
  $\|T^n\delta\|{\le}(2/3)^{6n}\|\delta\|$ (Knill--Laflamme type); free ratio breaks it. Holographic/Petz
  reading \mC, gated on the Seam--Horizon theorem (\texttt{QEC.SEAM.01}).
\item \textbf{CP lives in the hexagonal phase fiber (\texttt{v220\_cp\_hexagonal\_modulus},
  \texttt{tfpt\_5\_redteam}, \mE/\mC).} The seam deck is the square modulus $j{=}1728$ ($\Z/4$); its
  partner is the hexagonal $j{=}0$ ($\Z/6$, $\arg\rho{=}\pi/3$). The frozen $\delta{=}\pi/3{+}3\lambda_C^2
  {=}68.654^\circ$ has leading term $\pi/3{=}\arg\rho$; the deck stays $\Z/4$, CP is the $\Z/6$ fiber
  (\texttt{CP.MOD.01}).
\item \textbf{The dual normal frame $(d,n)$ with CP as orientation (\texttt{v225\_dual\_normal\_frame},
  \texttt{tfpt\_5\_redteam}, \mE/\mC).} $d{=}a^\top R^{-1}{=}({-}\tfrac12,{-}\tfrac12,1){=}{-}\tfrac12$
  Nariai; $n{=}(5,{-}9,6)$ reads $\det$ on the first-generation column; $\det(\mathbf1,d,n){=}21{=}3{\cdot}7$;
  $\mathrm{Im}\det(\mathbf1,d,\rho n){=}21\sin(\pi/3)$ --- CP as orientation (\texttt{DUAL.FRAME.01}).
\item \textbf{$F_{\mathrm{transfer}}$ as one path on the Sheet Diamond (\texttt{v224\_diamond\_ftransfer\_path},
  \texttt{tfpt\_2\_standard\_model}, \mE/\mC).} $M(s,t){=}R{+}Q\,\mathrm{diag}(s,t,t)$: $K,C,F$ on the
  sheet axis (curved, 2nd diff $8$), the winding axis flat (slope $6$), Pl\"ucker steps $(1,8,10),(1,8,16)$;
  the Koide source$\to$pole is the $1$-D projection (\texttt{FTR.PATH.01}).
\item \textbf{The charged leptons as an \'etale Frobenius algebra (\texttt{v229\_lepton\_frobenius\_algebra},
  \texttt{tfpt\_2\_standard\_model}, \mE/\mC).} $(c_e,c_\mu,c_\tau){=}(\tfrac{16}7,\tfrac43,\tfrac76)$,
  ring closure $c_e c_\tau{=}\tfrac83{=}|\Z_2|c_\mu$, product $\tfrac{32}9$; $A{=}\mathbb Q[t]/(m)$ is \'etale
  (trace-form Gram nondegenerate), a commutative Frobenius algebra over the $\mu_6$ resolvent
  (\texttt{LEP.FROB.01}).
\item \textbf{The center budget $(7,11,13)$ as three local norms (\texttt{v230\_center\_budget\_norms},
  \texttt{tfpt\_2\_standard\_model}, \mE).} $C{=}R{+}Q\,\mathrm{diag}(1,0,0)$ row sums $(7,11,13)$:
  $7{=}N_{\Z[\omega]}(3{+}2\omega)$ (hex), $13{=}N_{\Z[i]}(3{+}2i)$ (square), $11{=}\binom40{+}\binom41{+}\binom42$
  (QBL Fock count); the two CM rings and the boundary count meet in one operator center
  (\texttt{CENTER.NORM.01}).
\end{itemize}

\subsection*{2026-06-15 (the diamond axis geometry --- two axes + the transfer corner)}
\begin{itemize}
\item \textbf{The Sheet Diamond is a discrete geometry with two axes
  (\texttt{v218\_diamond\_axis\_geometry}, \texttt{tfpt\_2\_standard\_model}, \mE).} Sharpens
  \texttt{v94}/\texttt{v95} with three exact \mE\ lemmas (no new numbers). \textbf{(1) Axis curvature:}
  along the centered cross the determinant is linear on the winding axis $\det(C{+}xU)=14{+}6x$ (slope
  $6{=}|R^+(A_3)|$) and quadratic on the sheet axis $\det(C{+}yV)=14{+}14y{+}4y^2$ (2nd difference
  $8{=}\mathrm{rank}\,E_8$); the anchor block has $\det B(C{+}xU)=2\det(C{+}xU)$ and sheet curvature
  $6{=}|R^+(A_3)|$ --- two curvatures $(8,6)=(\mathrm{rank}\,E_8,|R^+(A_3)|)$. \textbf{(2) Pl\"ucker
  transfer ladder:} $\mathrm{Pl}(K)\to\mathrm{Pl}(C)\to\mathrm{Pl}(F)$ lifts in steps
  $(1,8,10)=(N_\Phi,\mathrm{rank}\,E_8,A_\Lambda)$ then $(1,8,16)=(N_\Phi,\mathrm{rank}\,E_8,\dim S^+)$ ---
  the decuple then the full generation (identity \mE, source$\to$pole reading \mC). \textbf{(3) Spectral
  ramification:} for $Q,K,C,F$ the cubic discriminant factors as $q(r)^2\,\mathrm{Disc}(q)$ with squares
  $(1,3,4,6)$ and kernels $(13,48,65,105)$, $F$ carrying $105=3{\cdot}5{\cdot}7$. The anchor-defect
  spectrum and pair-sum/staircase blocks are honest \emph{audit} fingerprints ($28{=}2\dim G_2$,
  $52{=}\dim F_4$ stay audit-only, not spine, as in \texttt{v94}/\texttt{v95}); $F$ as the
  transfer-completion corner is a \emph{heuristic}, not a hard filter. Ledger \texttt{DIAMOND.AXIS.01},
  \texttt{DIAMOND.PLUCKER.01}, \texttt{DIAMOND.SPECTRAL.01}; Wolfram-mirrored ($249/249$).
\end{itemize}

\subsection*{2026-06-15 (QGEO: the four marks emerge from Gauss--Bonnet --- K1 executed)}
\begin{itemize}
\item \textbf{The four marks emerge from Gauss--Bonnet --- count derived, not assumed
  (\texttt{v216\_marks\_gauss\_bonnet}, \texttt{tfpt\_research\_contracts}, \mE; ledger \texttt{QGEO.MARKS.03}).}
  The K1 lever of the \texttt{v215} kill-test (``exactly four marks'') is
  \emph{executed}: if the marks are $\Z_2$ branch points (deficit $\pi$) on the flat seam sphere ($\chi=2$,
  the same $\chi$ as the $8$ in $c_3$), Gauss--Bonnet forces $n\pi=2\pi\chi=4\pi$, so
  $n=2\chi=4=|\mu_4|=\Nfam+1$. The closed Euclidean sphere $2$-orbifolds are exactly
  $(2,3,6)$, $(2,4,4)$, $(3,3,3)$, $(2,2,2,2)$, and three independent criteria --- all cone orders $=2$ (the $|\Z_2|$
  sheet branch), $\mathrm{rank}\,H^1=\#\text{marks}-1=3=\Nfam$ (the three generations pick the $4$-mark square
  over the $3$-mark hexagonal), and a free order-$4$ deck --- converge on the pillowcase $(2,2,2,2)$. The
  numerical sibling \texttt{v217\_marks\_emergence\_scan} (\mC, ledger \texttt{QGEO.EMERGE.01}) confirms it on
  the actual DtN/state (number $n$ and positions free, the $4$-square config is the unique joint minimiser of
  clock-invariance $+$ $3$-family cohomology $+$ gap $(2/3)^6$). The mark \emph{count} and \emph{equality}
  move from input to derived; only the square
  \emph{modulus} (cross-ratio $2$, the order-$4$ clock) stays the one carrier input, and the from-zero
  raw-seam emergence \texttt{QGEO.REALIZE.01} stays \mO. \texttt{v216} exact (Wolfram extension
  $\to248/248$); \texttt{v217} numerical (Python-only). Suite $\to$ 217 modules.
\end{itemize}

\subsection*{2026-06-15 (QGEO: the bedrock recast as a falsifiable kill-test)}
\begin{itemize}
\item \textbf{\texttt{QGEO.SYM.01} as a kill-test, not a proof-promise (\texttt{v215\_seam\_deck\_killtest},
  \texttt{tfpt\_research\_contracts}, \mE/\mO; ledger \texttt{QGEO.KILL.01}).} A foundational symmetry cannot
  be derived from nothing (Bisognano--Wichmann would presuppose the covariance it should produce), so the
  bedrock $\omega\circ\rho=\omega$ is recast as four independently-falsifiable predictions about the raw seam
  DtN. The non-circular reduction (\texttt{v198}/\texttt{v199}/\texttt{v201}) gives
  $\omega\circ\rho=\omega\Leftrightarrow[\rho,C]=0$ with $|k|$ commuting exactly, so the residual is the
  bounded sub-principal $M_f$ (equivalently the raw Gaussian bulk form $A$ is $\mu_4$-deck-invariant). Levers:
  \textbf{K1} exactly four marks ($b_1=\#\text{marks}-1=3=\Nfam\Rightarrow\#\text{marks}=4=|\mu_4|$);
  \textbf{K2} the square config (cross-ratio $2\Rightarrow j=1728$, $\mathrm{Aut}=\Z/4$; order $4$ selects
  $\Z/4$ not the $j=0$ $\Z/6$; generic $\Rightarrow\Z/2$); \textbf{K3} mod-$4$ sub-principal support
  ($[\rho,M_f]=0\Leftrightarrow f$ $\Z_4$-invariant); \textbf{K4} transfer gap $(2/3)^6=64/729$. Freeze-bound
  via \texttt{freeze\_file.csv} (\texttt{seam\_deck\_symmetry}), carrier-side \mE\ (regression guards), with
  the \emph{decisive} kill deferred to \texttt{QGEO.REALIZE.01} \mO\ (the raw collar DtN must \emph{produce}
  four square marks without inputting them --- an emergence test). A kill-test, not a closure. Python-only
  (falsification layer; the exact sub-parts $j=1728$ and $(2/3)^6$ are Wolfram-mirrored via
  \texttt{v214}/\texttt{v54}/\texttt{v56}). Suite $\to$ 215 modules.
\end{itemize}

\subsection*{2026-06-15 (QGEO: the pillowcase reduction --- two residuals become one canonical metric)}
\begin{itemize}
\item \textbf{Pillowcase reduction of \texttt{QGEO.SYM.01} (\texttt{v214\_seam\_pillowcase},
  \texttt{tfpt\_research\_contracts}, \mE/\mO; ledger \texttt{QGEO.PILLOW.01}).} The two separately-tracked
  open QGEO residuals --- \texttt{QGEO.ISO.01} (\texttt{v180}: the carrier clock is an order-$4$
  \emph{isometry} of the seam metric) and \texttt{QGEO.SUBPRIN.01} (\texttt{v201}: the DtN sub-principal
  symbol is \emph{mark-local}, the seam flat away from the $\mu_4$ marks) --- are shown to be \emph{one}
  statement: the seam carries the uniformising flat orbifold (\emph{pillowcase}) metric. \textbf{(1)} The
  four marks make the Euclidean orbifold $S^2(2,2,2,2)$ ($\chi_{\mathrm{orb}}=2-4(1-\tfrac12)=0$), so by
  Troyanov uniformisation the metric is flat (unique up to scale) with curvature only at the cone points
  (Gauss--Bonnet $4\pi=2\pi\chi$) --- this \emph{is} the \texttt{v201} ``flat away from the marks''.
  \textbf{(2)} New link: cross-ratio$(\mu_4)=2$ (\texttt{v168}) $\Rightarrow j=1728$
  ($j(\lambda)=256(\lambda^2-\lambda+1)^3/(\lambda^2(\lambda-1)^2)$; all six harmonic cross-ratios give
  $1728$) $\Rightarrow$ the \emph{square} modulus $\tau=i$, whose CM by $\Z[i]$ \emph{derives} the order-$4$
  clock $z\mapsto iz$ (explicit $(x,y)\mapsto(-x,iy)$ on $y^2=x^3-x$); generic cross-ratio gives
  $j\notin\{0,1728\}$ and only $\Z/2$. \textbf{(3)} Unification: ``seam $=$ uniformising flat pillowcase
  metric'' implies \emph{both} \texttt{v201} and \texttt{v180}, so two residuals collapse to one
  canonical-metric premise. \mO\ It does \emph{not} close \texttt{QGEO.SYM.01}: the choice ``RP seam metric
  $=$ the constant-curvature representative'' stays open, milder and more canonical than the bare isometry
  premise. Wolfram-mirrored (the exact orbifold/$j$-invariant/CM arithmetic); Klein-$J$ values
  mpmath-numerical. Suite $\to$ 214 modules.
\end{itemize}

\subsection*{2026-06-15 (the F\_transfer functor contract CONTRACT.F.01)}
\begin{itemize}
\item \textbf{$F_{\mathrm{transfer}}$ formalised as a typed functor with four axioms
  (\texttt{v213\_ftransfer\_functor}, \texttt{tfpt\_research\_contracts}, \mC).} The four frontier transfers
  are consolidated into ONE functor $F_{\mathrm{transfer}}=F_{\mathrm{observable}}\circ F_{\mathrm{threshold}}
  \circ F_{\mathrm{RG}}$, each instance a discrete compiler kernel \mE\ composed with an external continuous
  solver \mC: \textbf{(1)} $\mu_4$-deck equivariance (the Koide multiplier $\lambda_2{=}(2/3)^6{=}64/729$ is
  the deck transfer eigenvalue); \textbf{(2)} Pl\"ucker preservation ($53{=}a^T(R{+}Q)\mathbf1$,
  $\mathrm{Pl}(F){=}(1,22,30)$, $\|\mathrm{Pl}(K)\|_1{=}11$); \textbf{(3)} positivity/stochasticity
  ($\operatorname{spec}T$ positive, $\kappa_f\in(0,1)$); \textbf{(4)} external modules explicit
  ($b_3{=}{-}7$ a carrier output). The four instances are $F_{\mathrm{pole}}$ (\texttt{v183}),
  $F_{\mathrm{Boltzmann}}$ (\texttt{v212}), $F_{\mathrm{relic}}$ (\texttt{v211}), $F_{\mathrm{QCD}}$
  (\texttt{v164}). \texttt{CONTRACT.F.01} is the third research contract alongside $(U_{\mathrm{wall}})$ and
  $(G_{\mathrm{metric}})$, the structural complement of the \texttt{v187} typing guard --- an architectural
  consolidation, \emph{not} a closure of any frontier number. Ledger \texttt{CONTRACT.F.01}.
\end{itemize}

\subsection*{2026-06-15 (frontier: two sharper [C] scenario branches --- axion angle + leptogenesis)}
\begin{itemize}
\item \textbf{Axion DM spine-angle branch $\theta_i=\pi\Nfam/\gcar=3\pi/5$ (\texttt{v211\_axion\_spine\_angle},
  \texttt{tfpt\_4\_frontier}, \mC).} A more \emph{robust} misalignment angle than the determinant-line hilltop
  $\theta_i\approx170^\circ$ (\texttt{v185}, which over-produces $\Omega_a h^2\approx0.66$): the central spine
  quotient gives $\theta_i=3\pi/5=108^\circ$ exactly (no fit), the finite-$T$ solver reaches
  $\Omega_{\mathrm{DM}}$ at ${\approx}106^\circ$, and $108^\circ$ sits in the \emph{mild}-anharmonic regime
  ($62^\circ$ below the hill-top) --- not exponentially sensitive. An alternative ansatz to
  $\theta_i=\pi(1-\varphi_\Sigma)$ (mutually exclusive, the full solver decides, \texttt{DM.AXION.SPINE.01});
  \mX\ $\Omega_a h^2$ outside ${\sim}[0.08,0.16]$ demotes it. A sharper scenario, not a derivation.
\item \textbf{Leptogenesis scalaron-decuple branch (\texttt{v212\_leptogenesis\_decuple},
  \texttt{tfpt\_4\_frontier}, \mC).} Both Boltzmann inputs share the decuple $A_\Lambda=10=|E(K_5)|$:
  $M_1=M_{\mathrm{scal}}(\phiz)^2/A_\Lambda\approx8.65\times10^9$ GeV and $\tilde m_1=m_3/A_\Lambda\approx5$ meV.
  $M_1$ uses \emph{only} $\{M_{\mathrm{scal}},\phiz,A_\Lambda\}$ --- no hidden seesaw scale, cleaner than
  \texttt{v184}'s $M_R\varphi_0^4$ --- and lands in the thermal window where $\eta_B\approx1.2\times10^{-9}$
  brackets the observed $6.1\times10^{-10}$. The coupling mechanism is posited not derived, so $\eta_B$ stays
  \mC; \mX\ a precise Boltzmann/RGE solve outside the band falls the route, not the theory
  (\texttt{FR.ETAB.04}; Route~A independent).
\end{itemize}

\subsection*{2026-06-15 (Lean: QGEO.COHOM.01 character grading + MODULE parity machine-proved)}
\begin{itemize}
\item \textbf{The cohomology character grading is now Lean-formalised}
  (\texttt{CohomologyGrading.lean}, ledger \texttt{FORM.QGEO.03}, \mO). A new module machine-proves the
  \textsc{Cohom} node of the QGEO proof tree (\texttt{v177}; \textsc{audit: pass}, no
  \texttt{sorry}/\texttt{admit}, axioms \texttt{propext, Classical.choice, Quot.sound} only): the three
  $H^1(\PP\setminus\mu_4)$ eigenforms $\omega_k=z^{k-1}/(z^4-1)$ ($k{=}1,2,3$) have pullback character
  $\rho^*\omega_k=i^k\omega_k$ under the clock $\rho:z\mapsto iz$ (each an exact rational-function identity,
  the denominator clock-invariant since $i^4{=}1$), so the grading is $(i,-1,-i)$ with weights $(1,2,3)$ =
  the $A_3$ exponents $=\operatorname{Spec}(Q_+)$, rank $3=\Nfam$. The \textsc{Module} \emph{parity} is also
  proved: the reflection $\sigma:z\mapsto1/z$ satisfies $\sigma^*\omega_1=\omega_3$,
  $\sigma^*\omega_2=\omega_2$, $\sigma^*\omega_3=\omega_1$ (swap $\omega_1\!\leftrightarrow\!\omega_3$,
  $\omega_2$ fixed). Signature-locked in \texttt{AuditContract.lean}. The geometric \textsc{Cohom}/\textsc{Module}-parity
  nodes are now \mE; the \textsc{Marks}/\textsc{Kernel} obligations and the \textsc{Module} \emph{uniqueness}
  stay \mO.
\end{itemize}

\subsection*{2026-06-15 (Lean: QGEO.UNIFORM.01 geometric normal form machine-proved)}
\begin{itemize}
\item \textbf{The M\"obius uniformisation normal form is now Lean-formalised}
  (\texttt{Mobius\allowbreak Uniformisation.lean}, ledger \texttt{FORM.QGEO.02}, \mO). A new module machine-proves the
  constructive \textsc{Uniform} node of the QGEO proof tree (\texttt{v177}; \textsc{audit: pass}, no
  \texttt{sorry}/\texttt{admit}, axioms \texttt{propext, Classical.choice, Quot.sound} only): the clock
  $\rho:z\mapsto iz$ has $\rho^4{=}\mathrm{id}$ and $\rho^2{\neq}\mathrm{id}$ (order exactly $4$); the
  reflection $\sigma:z\mapsto1/z$ is an involution with $\sigma\rho\sigma=\rho^{-1}$ (so $\langle\rho,\sigma
  \rangle$ is the dihedral $D_4$ of order $8$); a non-fixed orbit $\{a,ia,-a,-ia\}$ scales to
  $\mu_4=\{1,i,-1,-i\}$; $\sigma$ permutes $\mu_4$ (fixes $1,-1$, swaps $i,-i$); and the multiplier
  classification ``$z\mapsto\zeta z$ has order exactly $4\Leftrightarrow\zeta=\pm i$''. Signature-locked in
  \texttt{AuditContract.lean}. This formalises the geometric half of the seam realisation \emph{given} the
  four marks and the clock; the raw-seam marking obligation \texttt{QGEO.MARKS.01} stays \mO, \emph{not}
  closed.
\end{itemize}

\subsection*{2026-06-15 (Lean: the QGEO.SYM.01 conditional theorem machine-proved)}
\begin{itemize}
\item \textbf{The mark-local $\Rightarrow\omega\circ\rho=\omega$ implication is now Lean-formalised}
  (\texttt{SeamDeckClosure.lean}, ledger \texttt{FORM.QGEO.01}, \mO). A new module in the
  carrier-rigidity Lean project machine-proves the algebraic core of \texttt{v201}/\texttt{v210}
  (\textsc{audit: pass}, no \texttt{sorry}/\texttt{admit}, no domain axioms --- \texttt{\#print axioms} $=$
  \texttt{propext, Classical.choice, Quot.sound} only): (i) the $4$th-root character orthogonality
  $\sum_{j<4}\zeta^j=(\text{if }\zeta{=}1\text{ then }4\text{ else }0)$ for $\zeta^4{=}1$ (so a $\mu_4$-mark
  sum is supported only on modes $\equiv0\bmod4$); (ii) the clock generator $-i$ has order $4$;
  (iii) \texttt{markLocal\_blockDiagonal}: a mark-local Toeplitz symbol connects only equal clock-characters,
  $[\rho,M_f]=0$; (iv) the premise is a typed \texttt{structure} \texttt{SeamDeckPremise} (the physical seam
  DtN \emph{is} mark-local) --- consumed, \emph{not} proved, exactly as \texttt{CalderonProjector} encodes the
  Paper-1 analytic input; (v) \texttt{SeamDeckPremise.clock\_invariant}: \emph{given} the premise, the clock
  commutes with the DtN, whence $\omega\circ\rho=\omega$. So the \emph{implication} is now \mE\ (formally
  proved); the \emph{premise} (the physical seam being mark-local) stays \mO\ --- the one fundamental
  seam-identification postulate, \emph{not} closed.
\end{itemize}

\subsection*{2026-06-15 (QGEO sharpening: mark-local DtN certified on realistic profiles)}
\begin{itemize}
\item \textbf{Mark-local DtN $\Rightarrow\omega\circ\rho=\omega$, certified on realistic Steklov profiles and
  at the state level (\texttt{v210\_mark\_local\_dtn}, \texttt{tfpt\_research\_contracts}, \mO).} A numerical
  sharpening of \texttt{QGEO.SUBPRIN.01}/\texttt{v201}: a real von-Mises curvature bump summed over the four
  $\mu_4$ marks, $f(\theta)=\sum_{j=0}^3 g(\theta-j\pi/2)$, builds the Steklov DtN $\Lambda=|D_\theta|+M_f$
  whose off-$(\mathrm{mod}\,4)$ Fourier support vanishes to $<10^{-16}$, $\|[\rho,\Lambda]\|<10^{-15}$, and ---
  the genuinely new step --- the quasi-free covariance $C=\tfrac12(1+\operatorname{sgn}H_1)$ is clock-invariant
  ($\rho C\rho^\dagger=C$ to $<10^{-13}$), i.e.\ the actual $\omega\circ\rho=\omega$. Negative controls (single
  off-centre bump, $\Z_3$ source, four generic marks) break both by $O(1)$; convergence stable for
  $N\in\{16,32,64\}$. This certifies the \emph{implication}; the premise that the physical seam \emph{is}
  mark-local stays \mO\ (it does \emph{not} close \texttt{QGEO.SYM.01}; net existence and full-cone RP remain
  the \mE\ of \texttt{v175}). Ledger \texttt{QGEO.MARKLOCAL.01}. Python-only (the exact mark-sum identity is
  Wolfram-mirrored via \texttt{v201}).
\end{itemize}

\subsection*{2026-06-15 (archive integration \#5: six dormant results revived from the old papers)}
\begin{itemize}
\item \textbf{Muon $g-2$ as a seam vertex (\texttt{v204\_muon\_seam\_g2}, \texttt{tfpt\_4\_frontier}, \mC).}
  The carrier's second-order topological defect $\delta_2=\tfrac54\delta_{\mathrm{top}}^2$ projected through the
  seam-loop phase gives $a_\mu^{\mathrm{seam}}=\delta_2/(2\pi)=45/(524288\,\pi^9)\approx2.879\times10^{-9}$
  ($0.81\sigma$ vs the dispersive $\Delta a_\mu$; ${\sim}1.5\sigma$ vs lattice/CMD-3). The value is exact \mE;
  the vertex identification is the \mC\ bridge. Ledger \texttt{FR.MUONG2.01}; Wolfram-mirrored.
\item \textbf{An independent gravitational $3/4$ (\texttt{v205\_xi\_threequarter}, \texttt{tfpt\_4\_frontier}, \mE/\mC).}
  $\xi=\cthree/\varphi_{\mathrm{tree}}=3/4$ exactly (Einstein limit of $\kappa^2=\xi\phiz/\cthree^2$) --- the
  same $3/4=q(A_3)=\ln(m/\mu)$ as the seam-determinant replica (\texttt{v152}), an over-determination. Ledger
  \texttt{GRAV.XI.01}; Wolfram-mirrored.
\item \textbf{Quantitative $H_0$ from the $\Lambda$ branch (\texttt{v206\_h0\_lambda\_branch}, \texttt{tfpt\_4\_frontier}, \mC).}
  $\delta_\Sigma=48\,e^{-2\pi\ainv/3}\approx1.085\times10^{-123}$, the $(8\pi)^2$ Planck-convention split, and
  $H_0=66.5$--$67.1$ km/s/Mpc (below Planck, far below SH0ES --- the Hubble tension is \emph{not} relieved).
  Ledger \texttt{GRAV.H0.01}.
\item \textbf{Asymptotic Safety as a second QG route (\texttt{v207\_asymptotic\_safety}, \texttt{tfpt\_4\_frontier}, \mO).}
  A complementary continuum-FRG argument (a non-Gaussian UV fixed point from the same axioms;
  $y^2=16\cthree^2=1/(4\pi^2)$) --- a plausibility cross-check, \emph{not} load-bearing, does \emph{not} close
  $G_{\mathrm{metric}}$. Ledger \texttt{GRAV.ASYMP.01}.
\item \textbf{Black-hole thermodynamics from the seam} (\texttt{v208\_bh\_\allowbreak thermodynamics},
  \texttt{tfpt\_horizon\_\allowbreak readouts}, \mE/\mC).
  Modular $T_H=\kappa/(2\pi)$ (the $2\pi=1/(4\cthree)$ seam unit, ties to \texttt{v198}/\texttt{v199}) and the
  scalaron-corrected Wald entropy $S_W=(A/4G)(1+R_h/3M_s^2)$ (exact from \texttt{v28}). Ledger
  \texttt{HOR.BHTHERMO.01}; Wolfram-mirrored.
\item \textbf{The black hole as a seam fixed point} (\texttt{v209\_bh\_\allowbreak regular\_core},
  \texttt{tfpt\_horizon\_\allowbreak readouts}, \mC).
  No singularity ($\varphi\to\varphi_\star$ at the gapped attractor $(2/3)^6$); the maximal BH $=$ the anchor
  (Nariai roots $(1,1,-2)$); information via Page recovery; a Planck-scale holographic floor. The superseded
  RN/torsion metric is \emph{not} resurrected. Ledger \texttt{HOR.BHCORE.01}.
\end{itemize}

\subsection*{2026-06-15 (archive integration \#4: M\"obius $\cong$ Lorentz foundation citation)}
\begin{itemize}
\item \textbf{The M\"obius seam is the boundary Lorentz structure (\texttt{tfpt\_3}, \mO).} Added a paragraph
  to the ``M\"obius origin of $\pi$'' section: $\mathrm{M\ddot{o}b}(\hat{\mathbb C})\cong\mathrm{PSL}(2,\mathbb C)
  \cong\mathrm{SO}^+(3,1)$ (Penrose \& Rindler, \emph{Spinors and Space-time}, Vol.~1, \S1.2--1.4), the
  celestial sphere of null directions via stereographic projection. This gives the self-consistency loop a
  spacetime meaning --- the carrier clock $z\mapsto iz$ is an elliptic $\mathrm{PSL}(2,\mathbb C)$ rotation
  (\vref{v180}) and the RP$\to$OS causal cone is the same Lorentz structure --- so ``M\"obius origin of $\pi$''
  and ``one Lorentzian cone'' are two faces of one boundary $\mathrm{PSL}(2,\mathbb C)$. A foundation citation,
  not a new claim ($\pi$ stays primitive).
\end{itemize}

\subsection*{2026-06-15 (archive integration \#3: axion coupling $g_{a\gamma\gamma}=-4c_3$ + retired small-angle reading)}
\begin{itemize}
\item \textbf{Haloscope coupling tied to $c_3$ (\texttt{tfpt\_4\_frontier}, \mC).} Made explicit: in the
  determinant-line normalization the axion--photon anomaly coefficient is $g_{a\gamma\gamma}=-4c_3=-1/(2\pi)$
  ($y^2=16c_3^2=1/(4\pi^2)\approx0.0253$), so the haloscope $F\tilde F$ coupling is set by the \emph{same}
  $c_3$ that fixes $\alpha$ and $\beta_{\mathrm{rad}}=\varphi_0/4\pi$ --- a \mC\ structural relation (the
  coefficient, not a parameter-free physical $g_{a\gamma\gamma}$). The earlier small-angle
  $\theta_i=\varphi_0$ reading (old determinant-line note, a much higher axion mass) is \emph{superseded} by
  the closed near-hilltop $\theta_i=\pi(1-\varphi_{\mathrm{seam}})=170.4^\circ$, recorded as a retired reading
  and guarded by \vref{v188} (a new sentinel forbids that stale axion mass from re-entering the active docs).
\end{itemize}

\subsection*{2026-06-15 (archive integration \#2: the EHT achromatic polarization intercept --- v203)}
\begin{itemize}
\item \textbf{\texttt{HOR.EHT.01} (\vref{v203}, \mE/\mC/\mX).} The surviving core of the old UFE/black-hole
  notes (\emph{not} the RN-type metric --- superseded by the Nariai/seam$=$horizon readouts
  \vref{v101}--\vref{v104}/\vref{v190}; only the polarization signature survives): a local achromatic
  polarization-rotation intercept around a horizon-scale black hole,
  $\beta_{\mathrm{BH}}(r)=16c_3^4\,Q_e^{\mathrm{eff}}Q_m^{\mathrm{eff}}/r^2$. The coupling
  $16c_3^4=1/(256\pi^4)=\delta_{\mathrm{top}}/3$ is \emph{exact} (\mE, Wolfram-mirrored) --- the \emph{same}
  top-form coefficient $\delta_{\mathrm{top}}=48c_3^4$ that fixes the $\alpha$-kernel precision-zone
  correction, one row from the cosmic-birefringence seed $\beta_{\mathrm{rad}}=\varphi_0/4\pi$. TFPT fixes the
  $1/r^2$ shape, achromaticity and sign-flip (\mC); the amplitude $Q_eQ_m$ is an MHD/GR weight, never a
  pixel prediction. \textbf{Dated kill test \mX}: the residual intercept must pass three nulls (frequency,
  spatial $1/r^2$, sign-flip) after honest GRMHD subtraction. Integrated into \texttt{tfpt\_horizon\_readouts}
  (new EHT section), the ledger, registry, Wolfram ($243/243$), and the website (\texttt{predictions.ts}).
  Suite $202$ modules.
\end{itemize}

\subsection*{2026-06-15 (archive integration \#1: the rare kaon sector $K\to\pi\nu\bar\nu$ --- v202)}
\begin{itemize}
\item \textbf{\texttt{FR.RAREKAON.01} (\vref{v202}, \mC).} The closed TFPT CKM point ($s_{12}{=}\lambda_C$,
  $s_{23}{=}\varphi_0/(1{+}\lambda_C){=}|V_{cb}|$, $s_{13}{=}\lambda_C^3/3$, $\delta{=}\pi/3{+}3\lambda_C^2{=}1.19823$
  rad; \vref{v18}/\vref{v88}, no flavor fit) feeds the cleanest FCNC probe. With standard external
  short-distance input (Brod--Gorbahn--Stamou $X_t,P_c,\kappa_\pm$) it gives
  $\mathrm{BR}(K^+\!\to\pi^+\nu\bar\nu)=9.45\times10^{-11}$ and $\mathrm{BR}(K_L\to\pi^0\nu\bar\nu)=3.33\times10^{-11}$
  --- a \mC\ downstream flavor readout, \emph{not} a compiler power (the SD functions are external). Recomputed
  from the \emph{current} CKM point (an earlier archive scaffold quoted $\mathrm{BR}(K_L)=3.47\times10^{-11}$
  from an $\Im(\lambda_t)/\lambda^5$ slip, corrected here). Grossman--Nir ratio $0.352\ll4.3$; NA62
  $(13.0^{+3.3}_{-3.0})\times10^{-11}$ is $\sim1.2\sigma$ above. \textbf{Dated kill test \mX}: a stable NA62
  $\mathrm{BR}(K^+)$ outside $[7,12]\times10^{-11}$, or a KOTO-II $\mathrm{BR}(K_L)$ off the GN point, breaks the
  flavor bridge (core untouched). Integrated into \texttt{tfpt\_2\_standard\_model} (\S rare kaon), the ledger,
  \vref{v187} guard (new \texttt{FR.RAREKAON.} family), registry, and the website (\texttt{predictions.ts}).
  Python-only. Suite $201$ modules.
\end{itemize}

\subsection*{2026-06-15 (bedrock: the $\omega\circ\rho=\omega$ residual reduced once more --- v201)}
\begin{itemize}
\item \textbf{\texttt{QGEO.SUBPRIN.01} (\vref{v201}, \mE/\mO).} The \vref{v199} bedrock residual --- ``the
  bounded sub-principal symbol of the raw seam DtN has no off-character (mod 4) matrix elements'' --- is
  reduced one genuine step further: block-diagonality is \emph{not} an independent postulate. Writing the
  DtN as $\Lambda=|k|+M_f$ with $M_f$ the bounded sub-principal piece $=$ multiplication by a curvature
  $f(\theta)$ (standard Steklov structure), $M_f$ is $\mu_4$-character-block-diagonal iff $f$ is
  $\Z_4$-invariant (\mE; principal $|k|$ already commutes, \vref{v198}); and a $\mu_4$-mark sum
  $f=\sum_{j=0}^3 g(\theta-2\pi j/4)$ has $f_m=4g_m[m\equiv0\bmod4]$ for any profile $g$, hence is
  automatically $\Z_4$-invariant (\mE). So the $\mu_4$-mark orbit (forced by \vref{v195}) \emph{forces} the
  sub-principal symbol block-diagonal; $3$ marks ($\Z_3$) and $4$ generic marks break it (negative
  controls). The residual collapses to ``the DtN sub-principal symbol is mark-local (seam flat away from the
  $\mu_4$ marks $=$ conformal deck, \vref{v177})'', structurally definitional --- the narrowest form yet of
  \texttt{QGEO.SYM.01}, \mO. Registered in \texttt{run\_all.py}, the ledger, \texttt{tfpt\_research\_contracts},
  \texttt{origin\_theory}; Wolfram-mirrored (the mark-sum Fourier identity is exact; extension now
  $242/242$). Suite $200$ modules.
\end{itemize}

\subsection*{2026-06-15 (F\_transfer workshop: the axion relic solver --- an honest over-production tension)}
\begin{itemize}
\item \textbf{Axion relic solver (\texttt{experiments/ftransfer/axion\_relic/relic\_solver.py}, \mC).} The
  first real $F_{\mathrm{transfer}}$ pipeline computation (work package C / review \S6.2): a standard
  misalignment relic with a numerically-computed anharmonic factor $F(\theta_i)\approx4$ at the hilltop.
  Honest finding: at the \emph{predicted} $\theta_i\approx170^\circ$ the estimate \emph{over}-produces dark
  matter, $\Omega_a h^2\sim0.6$--$2.3$ (robustly $>0.12$), because the large $\theta_i^2\approx8.8$ times $F$
  overshoots. So the determinant-line axion as the \emph{dominant} DM is in \emph{mild tension} (it would
  prefer $\theta_i\sim120$--$130^\circ$ or extra dilution) --- this \emph{refines} \vref{v185}'s optimistic
  ``can be all-DM'' toward an over-production tension. The near-hilltop regime is O(1)-uncertain, so a full
  finite-$T$ solve decides; over-production kills only the axion-as-dominant-DM \emph{branch}, not the
  compiler. Reflected in \texttt{tfpt\_4\_frontier} (dark-matter section) and the \vref{v185} docstring;
  experiments-only, not a suite/ledger claim. No refitted exponents; $\theta_i=\pi(1-\varphi_{\mathrm{seam}})$
  only.
\item \textbf{Full finite-$T$ solve confirms it (\texttt{axion\_relic/full\_finiteT\_solve.py}).} A converged
  nonlinear misalignment solve ($\theta''+(3+\mathrm{d}\ln H/\mathrm{d}N)\theta'+(m_a(T)/H)^2\sin\theta=0$,
  lattice $\chi(T)\propto T^{-8.16}$, realistic $g_*(T)$; normalised so $\theta_i{=}1\to\Omega_a h^2\approx0.03$,
  the standard value) gives $\Omega_a h^2\approx0.66$ at the predicted $\theta_i\approx170^\circ$ ---
  $\sim$5.5$\times$ above $\Omega_{\mathrm{DM}}=0.12$, reached only at $\theta_i\approx106^\circ$. The
  over-production is thus \emph{confirmed} (not the optimistic ``all-DM''); \texttt{tfpt\_4\_frontier},
  \vref{v185} docstring and the website updated accordingly. Stays \mC; kills only the
  axion-as-dominant-DM branch.
\end{itemize}

\subsection*{2026-06-14 (work packages A+B: attacking $\omega\circ\rho=\omega$ + the variational scan --- v199, v200)}
\begin{itemize}
\item \textbf{\texttt{v199\_seam\_state\_invariance.py} \mE/\mO\ (claim \texttt{QGEO.STATE.01}, work package A).}
  Attacking $\omega\circ\rho=\omega$ directly on the \emph{raw} seam. (1) \mE\ the setup is non-circular:
  $\rho$ is the Coxeter element of $W(A_3)=S_4$ ($\rho^4=1$, \vref{v117}), an automorphism of the raw CAR
  algebra (16 Majoranas) --- both carrier-side, no seam geometry. (2) \mE\ for a quasi-free RP state
  $C_\Sigma=\tfrac12(1{+}\operatorname{sgn}H_1)$, so $\omega\circ\rho=\omega\Leftrightarrow[\rho,H_1]=0$.
  (3) \mE\ $[\rho,H_1]=0\Leftrightarrow H_1$ is block-diagonal in the four $\mu_4$-character classes
  $\{n{=}r\bmod4\}$ (verified). (4) \mO\ the residual is sharpened to ``the bounded sub-principal symbol has
  no off-character matrix elements'' --- a bounded, finite-character condition, not a diffuse geometry; not
  a closure. Cited in \texttt{tfpt\_research\_contracts}; Wolfram-mirrored.
\item \textbf{\texttt{v200\_seam\_variational\_scan.py} \mC/\mO\ (claim \texttt{QGEO.VARI.02}, work package B).}
  The discretised variational test: with the clock angle free, $E_{\mathrm{fail}}(\theta)$ has its unique
  minimum at $\theta=\pi/2$ (the $\mu_4$ clock $z\mapsto iz$) --- order-4 \emph{and} the three distinct
  characters $i,-1,-i$ = the $(1,2,3)$ grading; decoys ($0,\pi,\pi/3,2\pi/3$) all lose. A numerical sign
  that the variational principle selects $\mu_4$; the full operator-valued minimisation stays the
  \vref{v199} residual \mO. Cited in \texttt{tfpt\_research\_contracts}.
\item \emph{Also (this pass, \texttt{experiments/} only, not the ledger): the $F_{\mathrm{transfer}}$
  four-pipeline scaffold (\texttt{experiments/ftransfer/}) with one CONTRACT per interface, and confirmation
  that the FRB preregistration (\texttt{frb\_tfpt\_v1.yaml}) and its status semantics already exist.}
  Suite now 199 modules, highest ID \texttt{v200}; Wolfram extension $241/241$.
\end{itemize}

\subsection*{2026-06-14 (cracking the bedrock to a state-invariance: principal symbol $+$ Tomita--Takesaki --- v198)}
\begin{itemize}
\item \textbf{\texttt{v198\_modular\_commutator\_reduction.py} \mO\ (claim \texttt{QGEO.MODULAR.01}).} The
  decisive crack on the last residual. (1)~\mE\ the DtN principal symbol
  $|k|=\sqrt{-\partial_\theta^2}=\mathrm{diag}(|n|)$ and the clock $\rho{:}z\mapsto iz=\mathrm{diag}(i^n)$ are
  both diagonal in the Fourier basis, so $[\rho,|k|]=0$ \emph{exactly} on all of $L^2$ (verified on 33
  modes) --- the leading-order commutation is free on the whole boundary, never the open part. (2)~\mE\ by
  Tomita--Takesaki the modular operator is intrinsic to $(M,\Omega)$, so a state-preserving symmetry
  ($\rho\Omega=\Omega$) commutes with $\log\Delta\sim\Lambda_\Sigma$: hence $[\rho,\Lambda_\Sigma]=0$
  \emph{follows from} $\omega\circ\rho=\omega$, using only the state $+$ reflection (RP) and \emph{no}
  conformal covariance --- which \textbf{removes the v194 Bisognano--Wichmann circularity worry}. (3)~\mE\
  the finite $H^1$ block is already $\mu_4$-invariant (\vref{v177}). So the entire residual collapses to the
  single \emph{state-invariance} ``the raw quasi-free seam state is $\mu_4$-invariant''
  ($\omega\circ\rho=\omega$ $\Leftarrow$ the Gaussian bulk measure is deck-invariant) --- the
  maximally-operational, non-circular form of \texttt{QGEO.SYM.01}, \mO. \emph{Not} a full closure (a
  foundational symmetry cannot be derived from nothing, like $c=\text{const}$), but the sharpest falsifiable
  form, with the circularity gone. Cited in \texttt{tfpt\_research\_contracts}; \texttt{OpenGates} updated.
  Suite now 197 modules, highest ID \texttt{v198}; Wolfram extension $240/240$.
\end{itemize}

\subsection*{2026-06-14 (three review levers: Marks-via-Lefschetz, E\_fail functional, RR$\to$D5 --- v195--v197)}
\begin{itemize}
\item \textbf{\texttt{v195\_marks\_lefschetz\_character.py} \mE/\mO\ (claim \texttt{QGEO.MARKS.02}).} The four
  seam marks are \emph{forced} (not posited): $\rho{:}z\mapsto iz$ fixes only $\{0,\infty\}$, $H^1=
  \chi_1{\oplus}\chi_2{\oplus}\chi_3$ (the $A_3$ exponents, $\operatorname{Tr}(\rho|H^1)=i{+}i^2{+}i^3={-}1$)
  has no trivial component $\Rightarrow$ no puncture at a fixed point, and $\operatorname{rank}H^1=n{-}1=3
  \Rightarrow n=4 \Rightarrow$ a single free $\mu_4$ orbit (cross-ratio $2$). So \textsc{Marks} reduces from
  the geometric posit ``$D_4$ marks'' to the milder premise ``$H^1$ carries the $A_3$-exponent rep'' ---
  less circular, still \mO. Cited in \texttt{tfpt\_research\_contracts}.
\item \textbf{\texttt{v196\_seam\_energy\_functional.py} \mE/\mO\ (claim \texttt{QGEO.VARI.01}).} The
  failure functional $E_{\mathrm{fail}}=\|[\rho,\Lambda_\Sigma]\|^2_{HS}+\|\rho^4{-}1\|^2+\|\Theta\rho\Theta-\rho^{-1}\|^2$,
  zero locus $=$ the \texttt{QGEO.SYM.01} conditions; on the finite $H^1$ block it vanishes at the $\mu_4$
  config \mE\ and is $>0$ for any $\mu_4$-breaking perturbation, so $\mu_4$ is a true minimiser. The
  full-operator minimisation is the \vref{v194} Bisognano--Wichmann residual --- a concrete discretisable
  \emph{target} on the open bedrock, \mO. Cited in \texttt{tfpt\_research\_contracts}.
\item \textbf{\texttt{v197\_rr\_carrier\_clifford\_d5.py} \mE/\mC\ (claim \texttt{ARCH.RRCAR.02}).} Hardens
  the Riemann--Roch carrier from $g_{\mathrm{car}}$ to $D_5$ itself: $\Lambda^{\mathrm{even}}(C_{\mathrm{car}})
  =\binom50{+}\binom52{+}\binom54=16=2^{g_{\mathrm{car}}-1}=\dim S^+$, the $\mathfrak{so}(10)=D_5$
  half-spinor --- so $D_5$ is the Clifford spinor of the $5$-dim mode space, closing $\mu_4{\to}g_{\mathrm{car}}{\to}D_5$.
  \mE\ arithmetic, \mC\ identification (as \vref{v189}). Cited in \texttt{origin\_theory}.
\item All three are validated external-review levers (the axion-hilltop ``$\pi-3\phi_0$'' proposal was
  \emph{rejected} as a $\pi\approx3$ coincidence, not built). Suite now 196 modules, highest ID
  \texttt{v197}; Wolfram extension $239/239$.
\end{itemize}

\subsection*{2026-06-14 (subclaim 2 of ENERGY.02 tackled: raw-seam-DtN RP-definability --- v194)}
\begin{itemize}
\item \textbf{\texttt{v194\_raw\_seam\_dtn\_rp.py} \mO\ (claim \texttt{QGEO.DTN.01}).} The next hard lever ---
  ``is the raw RP-seam DtN definable from RP data alone?'' (sub-claim 2 of \texttt{QGEO.ENERGY.02}) --- was
  tackled, and the honest result is a \emph{reduction}, not a closure. (1)~\mE\ the commutator
  $[\rho,\Lambda_\Sigma]=0$ closes on the finite cohomology $H^1$ ($\rho^*w_k=i^k w_k$, distinct $\mu_4$
  characters; \vref{v177}). (2)~\mE\ the \emph{hinge} is met: the DtN/transfer operator is RP-canonical
  (Osterwalder--Schrader, \vref{v54}) on a quasi-free seam state (\vref{v155}), so $\Lambda_\Sigma$ is
  RP-definable without naming $\PP^1\!\setminus\!\mu_4$. (3)~\mO\ the residual relocates: the full-$L^2$
  commutation $\Leftrightarrow$ Bisognano--Wichmann geometric modular flow of the quasi-free seam state
  (which must be intrinsic, else it re-circulates). So \texttt{QGEO.SYM.01} reduces from a definitional
  postulate to ``intrinsic BW geometric modular covariance'' --- one notch sharper, still \mO; the last
  structural fog point sharpens, it does \emph{not} close to \mE. Cited in
  \texttt{tfpt\_research\_contracts}; \texttt{OpenGates} updated. Suite now 193 modules, highest ID
  \texttt{v194}.
\end{itemize}

\subsection*{2026-06-14 (QGEO.ENERGY.02 energy-commutator + QFT-wording hardening --- v193)}
\begin{itemize}
\item \textbf{\texttt{v193\_qgeo\_energy\_commutator.py} \mO\ (claim \texttt{QGEO.ENERGY.02}).} The
  non-circular sharpening of \texttt{QGEO.ENERGY.01}: the energy commutator
  $[\rho,\Lambda_\Sigma]=0$ on the rank-$8$ Calder\'on polarisation, with three sub-claims --- (1) \mE\
  $\rho$ is carrier-defined (Coxeter of $W(A_3){=}S_4$, \vref{v117}), not imported from the seam; (2) \mO\
  the non-circularity hinge: $\Lambda_\Sigma$ must be the \emph{raw} RP-seam DtN, not the $\mu_4$ normal
  form; (3) \mE\ the commutator forces the $(1,2,3)$ grading on $H^1$ (\texttt{QGEO.COHOM.01}). Exact \mE\
  rider (Wolfram-mirrored): the induced EH coefficient $k=(\ln m)/(12\pi)$ (\vref{v150}) reproduces
  $c_3/2$ iff $\ln m=q(A_3)=\tfrac34$ (\emph{family}), not $q(D_5)=\tfrac54$ (carrier, off by $5/3$) ---
  gravity is family-geometry-induced. A \emph{proof target}; if sub-claim (2) holds, \texttt{QGEO.SYM.01}
  becomes an energy-rigidity theorem. Cited in \texttt{tfpt\_research\_contracts}. Suite now 192 modules,
  highest ID \texttt{v193}; Wolfram extension $236/236$.
\item \textbf{QFT-wording hardening (review point 7).} \texttt{tfpt\_2\_standard\_model} \S(4) was
  retitled to ``Constructive QFT closure of the admissible physical sector'', and its standalone
  opening over-claim replaced by an explicitly scoped sentence (the unprojected ambient metric measure is
  not constructed; $G_{\mathrm{metric}}$ frontier). The two superseded standalone phrasings were added to
  the \texttt{v188} prose guard so a frozen release cannot re-introduce them.
\end{itemize}

\subsection*{2026-06-14 (geometry round: Riemann-Roch carrier, Nariai bound, branch line, energy clock --- v189--v192)}
\begin{itemize}
\item \textbf{\texttt{v189\_riemann\_roch\_carrier.py} \mE/\mC\ (claim \texttt{ARCH.RRCAR.01}).} The pair
  $(\gcar,\Nfam)=(5,3)$ are the two canonical invariants of \emph{one} object, the four-point seam divisor
  $D=\mu_4$ on $\PP^1$: the cycle side $\operatorname{rank}H_1(\PP^1\!\setminus\!\mu_4)=\deg{-}1=3=\Nfam$
  (already \texttt{QGEO.COHOM.01}) and the function side $h^0(\PP^1,\mathcal O(\mu_4))=\deg{+}1=5=\gcar$,
  matched by $\operatorname{rank}(D_5)=5$. The carrier-as-mode-space reading is \mC\ (geometric, does not
  displace the over-determined $\gcar=5$). Cited in \texttt{origin\_theory}; Wolfram-mirrored.
\item \textbf{\texttt{v190\_nariai\_entropy\_bound.py} \mE\ (claim \texttt{HOR.NARIAI.02}).} A
  variation-free one-line proof of the SdS entropy floor: $3(x^2{+}1)-2\Phi_3(x)=(x{-}1)^2\ge0$, so
  $S_{\mathrm{tot}}\ge\tfrac23 S_{dS}$ with equality iff $x=1$ (the Nariai merge). Cited in
  \texttt{tfpt\_horizon\_readouts}; Wolfram-mirrored.
\item \textbf{\texttt{v191\_universal\_branch\_line.py} \mC\ (claim \texttt{HOR.BRANCHLINE.01}).} The affine
  map $q=\tfrac72+\tfrac{\Nfam^2}{2}m$ carries the SdS branch points ${\pm}1/\Nfam$ onto the flavor labels
  $\{2,5\}$. \emph{Honestly typed \mC} --- an exact \emph{relabeling}, not a theorem (a decoy pair $\{3,4\}$
  admits an equally exact map; the shared content is the known $2/3$ ramification). Cited in
  \texttt{tfpt\_horizon\_readouts}; Wolfram-mirrored.
\item \textbf{\texttt{v192\_qgeo\_energy\_clock.py} \mO\ (claim \texttt{QGEO.ENERGY.01}).} An
  operator-checkable restatement of the bedrock: $\rho^*\Lambda_\Sigma\rho=\Lambda_\Sigma$ (the clock
  preserves the DtN energy form). \emph{Honestly typed:} it \emph{relocates} \texttt{QGEO.SYM.01} to a more
  falsifiable surface but does \emph{not} eliminate it (plausibly equivalent unless $\rho$ is independently
  defined and the invariance proven). Cited in \texttt{tfpt\_research\_contracts}. Suite now 191 modules,
  highest ID \texttt{v192} (v186 skipped).
\item \emph{All four are validated external-review proposals (\texttt{problem\_b}); each is built with the
  honest typing determined on review --- the branch line is recorded as an alignment, not a theorem, and
  the energy clock as a relocation, not a closure.}
\end{itemize}

\subsection*{2026-06-14 (Zenodo release 5.1 (rev 120) --- F\_transfer firewall, v184--v188)}
\begin{itemize}
\item \textbf{Published to Zenodo.} Version \texttt{5.1 (rev 120)} of the ten-PDF document set was
  published as a new version of the TFPT deposit --- record \texttt{20687564},
  DOI \texttt{10.5281/zenodo.20687564}. This version carries the F\_transfer-firewall round
  (\vref{v184}--\vref{v188}): the honest $\eta_B$ anchored-Boltzmann test (sharper scenario, not a
  closure), the axion hilltop-relic typing, the ledger \texttt{v187} and prose \texttt{v188} guards, and
  the Route~B/Koide/dark-matter wording fixes plus the P1/P2-vs-\texttt{QGEO.SYM.01} two-layer
  clarification. The uploader's \texttt{DEFAULT\_RECORD\_ID} was advanced to the new record for the next
  release. Suite 187 modules (highest ID \texttt{v188}; v186 skipped). \texttt{run\_all.py} green, audit
  clean, website built.
\end{itemize}

\subsection*{2026-06-14 (F\_transfer round: eta\_B honest test v184, axion relic v185, discipline guard v187)}
\begin{itemize}
\item \textbf{\texttt{v184\_etaB\_anchored\_boltzmann.py} \mC\ (claim \texttt{FR.ETAB.03}).} An honest
  test of the external-review $\eta_B$ proposal ($M_1=M_R\varphi_0^4$, $\tilde m_1=m_3/A_\Lambda$).
  Firewall verdict: \emph{sharper scenario, not a closure}. The washout anchors plausibly
  ($\tilde m_1=m_3/10\approx5$ meV, $A_\Lambda=10$ atom, in the strong-washout window) \mC; but $M_1$
  does \emph{not} --- $M_R$ is the seesaw scale $\sim v^2/m_3$ and the nearest clean TFPT powers of
  $\bar M_{\mathrm{Pl}}$ both miss it ($c_3$-/$\varphi_0$-powers off ${\sim}75\%$/${\sim}40\%$), so
  $M_1=M_R\varphi_0^4$ merely relocates the free input. $\eta_B$ stays \mC, the route viable but with one
  (not zero) free input. Cited in \texttt{tfpt\_4\_frontier}.
\item \textbf{\texttt{v185\_axion\_relic\_solver.py} \mC\ (claim \texttt{FR.DM.03}).} Honest misalignment
  estimate: the determinant-line axion $f_a=M_{\mathrm{scal}}/128\approx2.39{\times}10^{11}$ GeV
  ($m_a\approx23.8\,\mu$eV) CAN be all dark matter, but the harmonic misalignment under-produces
  (${\sim}21\%$ at $\theta\sim O(1)$), so the $\theta_i\approx170^\circ$ hilltop anharmonic enhancement is
  \emph{required} --- where the relic is exponentially sensitive. Hence a \mC\ scenario, not a sharp
  prediction; the relic contract is a kill test for the BRANCH, not the theory. Cited in
  \texttt{tfpt\_4\_frontier}.
\item \textbf{\texttt{v187\_ftransfer\_laws.py} \mE\ (claim \texttt{FR.TRANSFER.01}).} A CI-style
  firewall guard: the four continuous-transfer frontier observables (Koide, $\eta_B$, axion,
  $m_p/m_e$) are read from the ledger and required to carry a \mC/\mO\ marker --- never a primitive
  \mE\ compiler prediction (exact sub-parts like the Koide $53/54$ factor or $b_3=-7$ may be \mE, the
  physical prediction never is). Records the four interfaces $F_{\mathrm{pole}}/F_{\mathrm{Boltzmann}}/
  F_{\mathrm{relic}}/F_{\mathrm{QCD}}$; prevents any future edit from quietly promoting a frontier
  number to a closed output. Cited in \texttt{tfpt\_4\_frontier}.
\item \textbf{\texttt{v188\_frontier\_wording\_guard.py} \mE\ (claim \texttt{AUDIT.WORDING.01}).} A prose
  sentinel (no new physics): \texttt{v187} protects the ledger \emph{typing}, this guard protects the
  \emph{prose}. It scans the 10 active documents and forbids five stale phrasings whose semantics earlier
  rounds superseded (the old \mE-typed Route~B leptogenesis claim and its heavy-scale wording $\to$ v184
  \mC; the old ``open relic scale'' dark-matter line $\to$ v185; the old ``near, not exact'' Koide line
  $\to$ v183; and the module-count/ID conflation), so a frozen Zenodo release can never re-introduce
  wording that was true yesterday and is half-true today. The same pass updated the
  \texttt{tfpt\_4\_frontier} Route~B (to \mC), the Koide and dark-matter summary lines, and added the
  P1/P2-vs-\texttt{QGEO.SYM.01} two-layer clarification to the introduction. Suite now has \textbf{187
  modules}, highest verification ID \texttt{v188} (v186 was intentionally skipped as redundant ---
  $m_p/m_e$ is already typed \mO\ as a QCD matching contract, \texttt{QCD.LAMBDA.01}).
\item \emph{Review framing points (P1/P2 as projections of the seam-deck postulate, $v_{\mathrm{geo}}$
  as unit gauge, $G_{\mathrm{net}}$ a corollary of \texttt{QGEO.SYM.01}, grammar tuning $=$ data) were
  validated as already implemented in the prior rounds; $m_p/m_e$ is already typed \mO\ as a QCD
  matching contract (\texttt{QCD.LAMBDA.01}), so no redundant module was added.}
\end{itemize}

\subsection*{2026-06-14 (operator origin of the Koide 53/54 factor: the missing Sheet-Diamond corner, v183)}
\begin{itemize}
\item \textbf{\texttt{v183\_koide\_f\_corner\_transfer.py} \mE/\mC\ (claim \texttt{FR.KOIDE.07}).} An
  external-review proposal, validated exactly: the Koide source$\to$pole factor $\tfrac{53}{54}$ is not
  a bare arithmetic guess but an \emph{operator} identity on the carrier,
  $u_{\mathrm{pole}}/u_{\mathrm{source}} = a^T(R+Q)\mathbf1 / (2\,\mathbf1^T R a) = 53/(2{\cdot}27) =
  \tfrac{53}{54}$. Here $\mathbf1^T R a = 27$ is the $E_6{\times}A_2$ cubic family block
  ($248 = \dim E_6 + \det R + 2(\mathbf1^T R a)\Nfam = 78+8+2{\cdot}27{\cdot}3$) and
  $a^T(R+Q)\mathbf1 = 53 = 52+1$, where $F = R+Q$ is the \emph{missing} Sheet-Diamond corner with
  $\det B_F = 52 = \dim F_4$ (\vref{v80}). Hard negative control: $a^T M\mathbf1$ for $M\in\{R,Q,K,L\}$
  is $\{32,21,35,56\}$ --- only the absent corner $F$ gives $53$. This upgrades \texttt{FR.KOIDE.03}
  from ``near miss $+$ conjecture'' to ``operator-sourced source$\to$pole transfer'': the \emph{factor}
  is \mE\ (exact, mirrored in Wolfram, $232/232$); the \emph{mechanism} (the leptonic source$\to$pole
  transfer reads the $F$ corner) stays \mC, an $F_{\mathrm{transfer}}$ special case. The prediction
  itself stays \mC. Cited in \texttt{tfpt\_4\_frontier} (Koide section). Suite now 183 modules.
\item \textbf{Review point 2 noted as already-present:} the claim that flavor and Nariai share one
  double-cover ClockFunctor (flavor rate $(2/3)^{2\Nfam}$ vs gravity curvature $(2/3)^{\Nfam}$, exponent
  ratio $|\Z_2|$, ``one clock, two geometries'') is exactly \texttt{HOR.TRISECT.01}/\vref{v103} --- a
  rediscovery of an existing result, no new module.
\end{itemize}

\subsection*{2026-06-14 (review recommendations 1/3/4 + the four concerns A--D mapped to the named residuals)}
\begin{itemize}
\item \textbf{\texttt{v182\_reviewer\_residual\_map.py} \mE/\mC\ (claim \texttt{REVIEW.MAP.01}).} A
  careful external review raised four concerns (A mapping $2D\!\to\!4D$, B UV-gravity abstractness,
  C grammar-tuning/meta-look-elsewhere, D Koide M\"obius flow). This module shows three of them
  \emph{reduce}, by the same discipline as \vref{v175}--\vref{v181}, onto the \emph{two already-named}
  residuals $\{\texttt{QGEO.SYM.01},F_{\mathrm{transfer}}\}$: A (Pl\"ucker-$11$ $=$ QBL boundary count
  \vref{v174} $+$ holographic reduction), B ($\equiv$ \texttt{QGEO.SYM.01}), D (M\"obius forced by
  $\mathrm{Aut}(\PP)=\mathrm{PSL}(2,\mathbb C)$ on the deck; the missing generator $=F_{\mathrm{transfer}}$).
  Only C is genuinely \emph{experiment-only} (frozen $+$ minimal $+$ over-determined grammar; residual
  falls to JUNO/CMB-S4). A unification of the concern \emph{structure}, not a closure. Cited in
  \texttt{tfpt\_5\_redteam}. Suite now 182 modules.
\item \textbf{Review recommendation \#3 --- a ``Rosetta'' translation lexicon} (website
  \texttt{RosettaLexicon}): TFPT's compiler-speak (seam, deck, readout, microcode, audit hull, gap,
  anchor, $F_{\mathrm{transfer}}$, $v_{\mathrm{geo}}$, \texttt{QGEO.SYM.01}) mapped onto standard QFT /
  mathematical-physics language (Wilsonian boundary CFT, orbifold deck, index/intersection number, RG
  irrelevance rate, renormalization condition, fundamental postulate) --- a reading aid for
  mainstream physicists, not a new claim.
\item \textbf{Review recommendation \#1 --- kill-tests up front} (website \texttt{TrustContract}): the
  frozen pre-data predictions (sin$^2\theta_{12}=0.3067$, JUNO; $r\approx0.004$, CMB-S4) and the null
  model ($P\le10^{-30.7}$) are now a prominent strip directly under the hero.
\item \textbf{Review recommendation \#4 --- the bedrock as a postulate.} \texttt{QGEO.SYM.01} is now
  framed confidently as TFPT's \emph{one fundamental postulate} (the role ``$c=$ const'' plays in
  relativity), not a gap --- in the \texttt{tfpt\_research\_contracts} box and the website ``what is
  open'' card; the achievement is that the whole theory is compressed onto exactly one sharply-located,
  falsifiable premise.
\end{itemize}

\subsection*{2026-06-14 (external-review response: CSV fix, G\_net 3-level, QGEO.SYM.01 page, claim detox)}
\begin{itemize}
\item \textbf{Ledger CSV bug fixed + guarded.} Three rows (\texttt{AX.P1.01}, \texttt{AX.P2.01},
  \texttt{QGEO.ISO.01}) had \emph{unquoted commas} in a status/external field (e.g.\ ``a=(1,1,2)'',
  ``PSL(2,C)''), so a strict CSV parser read 11--12 columns instead of 10 --- a real
  machine-readability defect in the single source of truth. All offending fields are now quoted (every
  row parses to exactly 10 columns), and \texttt{audit\_sync.py} gained a \texttt{check\_csv\_wellformed}
  guard (ledger, registry, clusters, freeze must all parse to constant width) so it cannot regress.
\item \textbf{$G_{\mathrm{net}}$ typed in three explicit levels} (website ``What is open'' card): (1)
  \emph{algebra} \mE\ $(D_5)_1{\otimes}(A_3)_1{\rtimes}\langle(1,1)\rangle\cong(E_8)_1$; (2) \emph{AQFT
  machinery} \mE\ (net existence $+$ full-cone RP, CAR functor, \vref{v175}); (3) \emph{seam
  instantiation} \mO\ (\texttt{QGEO.SYM.01}). The target object's mathematics is closed; only the
  physical coupling of the raw seam is open.
\item \textbf{\texttt{QGEO.SYM.01} now has its own one-page box} in \texttt{tfpt\_research\_contracts}:
  what is identified, why it is weaker than \texttt{CONF}/\texttt{ISO}, what follows automatically (the
  conditional theorem), and \emph{what would falsify it} (genus $>0$ double; non-deck transport;
  $\Nfam\neq3$); with the explicit conditional framing ``\emph{given} \texttt{QGEO.SYM.01}, the closure
  follows'' rather than ``the theory derives the seam geometry''.
\item \textbf{Claim-language detox.} ``no free fundamental number'' softened to ``no free
  \emph{dimensionless compiler dial} beyond the anchor and $\pi$ (dimensionful scale $+$ transfer
  physics stay typed)'' (\texttt{origin\_theory}, \texttt{introduction}, website); the site title
  softened from ``the Standard Model Derived'' to ``the Standard-Model \emph{Skeleton} Derived''.
\item \textbf{External-reviewer map} added to the website verification page: four boxes (exact kernel
  \mE, conditional physics \mC, open premises \mO, kill tests \mX) so a reviewer sees the attack
  surface without reading 181 scripts. Suite unchanged at 181.
\end{itemize}

\subsection*{2026-06-14 (Zenodo release 5.1 (rev 114) --- v175--v181 bedrock + figures + P1/P2)}
\begin{itemize}
\item \textbf{Published to Zenodo.} Version \texttt{5.1 (rev 114)} of the ten-PDF document set was
  published as a new version of the TFPT deposit --- record \texttt{20686284},
  DOI \texttt{10.5281/zenodo.20686284}. This version carries the AQFT-closure-to-bedrock chain
  (\vref{v175}--\vref{v181}, the structural residual reduced to the single definitional premise
  \texttt{QGEO.SYM.01}), the two overview figures (\texttt{residual\_chain}, \texttt{script\_timeline}),
  and the P1/P2 anchor-reduction provenance on the axiom surfaces. The \texttt{README} and the Zenodo
  description were refreshed (181 modules), and the uploader's \texttt{DEFAULT\_RECORD\_ID} was advanced
  to the new record for the next release.
\end{itemize}

\subsection*{2026-06-14 (overview figures + P1/P2 reduction reflected on the axiom surfaces)}
\begin{itemize}
\item \textbf{Two overview figures} (\texttt{make\_figures.py}; PDF $+$ website PNG). (i)
  \texttt{residual\_chain} --- the structural-residual reduction chain \vref{v175}--\vref{v181} as a
  descending staircase from ``build a quantum-gravity measure'' to the single definitional bedrock
  \texttt{QGEO.SYM.01}; embedded in \texttt{tfpt\_research\_contracts}. (ii) \texttt{script\_timeline}
  --- the eight-phase journey of the $\sim$181 scripts (foundations $\to$ SM readouts $\to$ seam$=$
  horizon $\to$ horizon/flavor geometry $\to$ R1--R5/premise-(A) $\to$ PyR@TE cross-checks $\to$ AQFT
  bridges $\to$ AQFT closure), what each did mathematically and physically; embedded in
  \texttt{introduction} ahead of the master script index, and both shown on the website verification page.
\item \textbf{P1/P2 reduction now reflected on the axiom surfaces.} The reduction of the two axioms to
  the single parabolic anchor $a=(1,1,2)$ plus $\pi$ (with $g_{\mathrm{car}}=5$ an over-determined
  bootstrap fixed point --- forced three ways, \vref{v6}, Pascal-unique and Lean-formalised,
  \texttt{FORM.LADDER.01}) was already established (\texttt{ANCHOR.GEN.01}/\vref{v23},
  \texttt{ARCH.CORE.01}/\vref{v53}) and stated in the papers/glossary, but the \emph{axiom surfaces}
  still read as bare ``declared inputs''. Fixed: the ledger rows \texttt{AX.P1.01}/\texttt{AX.P2.01} now
  carry the anchor/bootstrap reduction and point to it, and the website dependency-graph nodes P1/P2 now
  show the anchor input ($c_3=1/(2e_1(a)\pi)$; $g_{\mathrm{car}}=e_2(a)$, bootstrap-forced) rather than
  ``declared axiom''. No marker change (still declared inputs), only honest provenance.
\item Manifests refreshed (two new figures added to the \texttt{FIG} list). Suite unchanged at 181.
\end{itemize}

\subsection*{2026-06-14 (the final reduction to bedrock v181 + full non-changelog status sweep)}
\begin{itemize}
\item \textbf{\texttt{v181\_clock\_is\_conformal\_symmetry.py} \mE/\mO\ (claim \texttt{QGEO.SYM.01}).}
  The isometry premise \texttt{QGEO.ISO.01} (\vref{v180}) is weakened one more genuine step --- to a
  conformal-\emph{symmetry} premise --- via \emph{equivariant uniformisation} (Nielsen realisation; for
  cyclic groups Ker\'ekj\'art\'o $+$ uniformisation): a \emph{conformal} automorphism (strictly weaker
  than an isometry --- every isometry is conformal, conformal allows any positive scale) already suffices
  to put the order-$4$ clock in the form $z\mapsto iz$. Since the clock is the Coxeter element of
  $W(A_3)=S_4$ (\vref{v117}), the $\mu_4$ deck, and a deck transformation preserves the pulled-back
  conformal structure by definition, the residual collapses to the \emph{definitional} identification
  \texttt{QGEO.SYM.01}: ``the seam's conformal structure \emph{is} the $\mu_4$-deck structure of the
  carrier clock''. This is bedrock --- a physical/definitional statement tying P2 to the seam's conformal
  geometry, \emph{not} a finite computation and not reducible further without relabeling. The chain
  \texttt{REALIZE}(\vref{v175})$\to\dots\to$\texttt{SYM.01}(\vref{v181}) ends here; we stop honestly.
  Python-only. Suite now 181 modules.
\item \textbf{Full non-changelog status sweep.} The current bedrock framing was propagated to every
  live status surface (not just the changelog): the \texttt{introduction} ``latest reductions'' prose,
  \texttt{tfpt\_5\_redteam} Target~A, the \texttt{tfpt\_research\_contracts} central-theorem keybox,
  \texttt{origin\_theory}; and on the website \texttt{OpenGates}, \texttt{VerificationDag},
  \texttt{papers.ts} (Target~A $\times2$, $G_{\mathrm{net}}$), the \texttt{glossary} $G_{\mathrm{net}}$
  entry and the \texttt{faq} live-residual answer --- all now end at \texttt{QGEO.SYM.01}.
\end{itemize}

\subsection*{2026-06-14 (the conformal premise reduces to a milder isometry premise v180)}
\begin{itemize}
\item \textbf{\texttt{v180\_clock\_is\_mobius.py} \mE/\mO\ (claim \texttt{QGEO.ISO.01}).} Cracks
  \texttt{QGEO.CONF.01} one level further: the conformal-realisation premise is \emph{replaced}, via
  three classical theorems, by a strictly \emph{milder, non-circular} premise. (1)~\emph{Uniformisation}
  (Poincar\'e--Koebe): a genus-$0$ Riemann surface is conformally $\PP$, so the genus-$0$ seam double
  (P1, \vref{v179}) with its RP-metric conformal structure \emph{is} $\PP$ --- the target is
  \emph{produced}, not assumed; (2)~\emph{Ker\'ekj\'art\'o} (1919; Constantin--Kolev 2003): a
  finite-order orientation-preserving homeomorphism of $S^2$ is conjugate to a rotation, so the
  order-$4$ clock ($h(A_3){=}4$) is topologically $z\mapsto iz$; (3)~\emph{isometry$\Rightarrow$
  conformal$\Rightarrow$M\"obius}: an orientation-preserving isometry of a Riemannian surface is
  holomorphic, $\mathrm{Aut}(\PP)=\mathrm{PSL}(2,\mathbb C)$; (4)~an order-$4$ M\"obius map is
  $z\mapsto iz$ (verified: projective order $4$, fixed $\{0,\infty\}$, multiplier $i$, free orbit
  $\mu_4$). Hence \texttt{QGEO.CONF.01} is \emph{implied} by the milder premise \texttt{QGEO.ISO.01}:
  ``the carrier clock is an order-$4$ orientation-preserving \emph{isometry} of the RP seam metric'' ---
  which does not name $\PP/\mu_4$ (uniformisation produces them) and is the natural statement that the
  seam transport is metric-compatible (a holonomy preserving the RP inner product). That milder premise
  is the single, now milder, structural residual of the whole theory; its surface realisation from the
  raw seam stays honestly \mO. Cited in \texttt{tfpt\_research\_contracts}; Python-only. Suite now 180
  modules.
\end{itemize}

\subsection*{2026-06-14 (the two obligations collapse to ONE geometric premise v179)}
\begin{itemize}
\item \textbf{\texttt{v179\_conformal\_realisation.py} \mE/\mO\ (claim \texttt{QGEO.CONF.01}).}
  Investigating the two residual premises left by \vref{v178} shows they are \emph{not} independent ---
  they collapse onto a single geometric premise (honest unification; the premise itself stays \mO).
  \textsc{Marks}'s residual is not three independent assumptions: (1)~genus-$0$ \emph{is} P1 --- the
  one-sided Gauss--Bonnet $c_3=1/(|\Z_2|\,2\pi\,\chi(S^2))=1/(8\pi)$ uses $\chi(S^2)=2$ and
  $\chi=2-2g\Rightarrow g=0$, so ``genus-$0$'' is the same $\chi=2$ that gives the ``$8$'' in $c_3$
  (\vref{v58}/\vref{v73}); (2)~the order-$4$ clock \emph{is} the carrier --- the Coxeter element of
  $W(A_3)=S_4$ (\vref{v117}), order $h(A_3)=4=|\mu_4|$; (3)~marks $=$ one orbit is \emph{forced} (the
  parabolic marks are not the two elliptic fixed points, a free order-$4$ orbit has exactly $4=e_1(a)$
  points). \textsc{Kernel} then \emph{follows} from the same geometry (DtN symbol $|k|$, Lee--Uhlmann
  \vref{v156}; $c=8$ rigidity \vref{v158}; the cusped-surface residual $=H^1=\mathbb C^3=\Nfam$). So
  the \emph{entire} structural residual of the theory is the \emph{single} geometric premise
  \texttt{QGEO.CONF.01}: ``the raw RP seam normal double is conformally $(\PP,\mu_4)$ with the carrier
  clock as the order-$4$ M\"obius automorphism''. The two doors of \vref{v177}/\vref{v178} are one
  geometric realisation, left honestly \mO. Cited in \texttt{tfpt\_research\_contracts}; Python-only.
  Suite now 179 modules.
\end{itemize}

\subsection*{2026-06-14 (an honest attempt at the two obligations v178 --- deeper reduction, not closure)}
\begin{itemize}
\item \textbf{\texttt{v178\_marks\_kernel\_attempt.py} \mE/\mO\ (claim \texttt{QGEO.REDUCE.01}).} An
  honest attempt at \texttt{QGEO.MARKS.01} and \texttt{QGEO.KERNEL.01}. These are genuine
  constructive-geometry/AQFT statements, \emph{not} finite computations --- neither is closed. What
  the module does is push each as far as computation allows: it closes the finite \mE\ core of each
  and reduces each to \emph{one sharper} premise. \emph{Marks core} \mE: given a genus-$0$ double with
  an order-$4$ clock $\rho$ (fixed points $\{0,\infty\}$) and reflection $\tau$, the marks are forced
  to be a generic $\rho$-orbit $\{1,i,-1,-i\}=\mu_4$ (\emph{not} the fixed points), distinct iff
  $b_1=4-1=3=\Nfam$ (any collision drops $b_1$), with $\tau\rho\tau=\rho^{-1}$ giving a faithful $D_4$
  of order $8$ --- so \textsc{Marks} reduces to the single topological/clock premise. \emph{Kernel
  core} \mE: on the $3$-dim multiplicity-free $H^1$ the $\mu_4$ characters $(1,2,3)$ are distinct, so
  by Schur a $\mu_4$-equivariant operator is forced \emph{diagonal} and completely determined by its
  eigenvalue per character; two such with the forced transfer spectrum $\{1,(2/3)^6,(1/3)^6\}$
  (\vref{v162}) and the unique residue-normalised basis (\vref{v177}) are \emph{equal as operators},
  not merely isospectral --- the spectrum-vs-operator worry \emph{vanishes} on the finite block. So
  \textsc{Kernel} reduces to the single full-operator-reduction premise (principal symbol $|k|$,
  Lee--Uhlmann/\vref{v156}; no drift \vref{v158}). Net: neither obligation closed; both sharpened to
  milder premises with their finite cores \mE. Cited in \texttt{tfpt\_research\_contracts}; Python-only
  (M\"obius/Schur symbolic $+$ numeric). Suite now 178 modules.
\end{itemize}

\subsection*{2026-06-14 (QGEO proof tree v177 --- the residual sharpened into two named obligations)}
\begin{itemize}
\item \textbf{\texttt{v177\_seam\_marking\_kernel.py} \mE/\mO\ (claims \texttt{QGEO.TREE.01},
  \texttt{QGEO.MARKS.01}, \texttt{QGEO.KERNEL.01}).} A second external residual-class audit pointed
  out that the \vref{v176} statement takes the marks/$D_4$ as a \emph{hypothesis} --- a near-circular
  trap. This module factors the central theorem honestly as
  $\textsc{Realize}=\textsc{Marks}\cdot\textsc{Uniform}\cdot\textsc{Cohom}\cdot\textsc{Module}\cdot
  \textsc{Kernel}\cdot\textsc{Net}$ and closes \emph{four} nodes \emph{constructively} (all validated
  symbolically before adoption): \textsc{Uniform} \mE\ --- an order-$4$ M\"obius map conjugates to
  $z\mapsto iz$, a non-fixed orbit scales to $\mu_4$, and $\sigma\rho\sigma=\rho^{-1}$ for
  $\sigma:z\mapsto1/z$ gives a faithful $D_4$ (order $8$), so a genus-$0$ four-marked faithful-$D_4$
  boundary \emph{is} $(\PP,\mu_4)$ (strengthening \vref{v168}'s cross-ratio to the full
  uniformisation); \textsc{Cohom} \mE\ --- $\rho^*\omega_k=i^k\omega_k$, grading $(1,2,3)=A_3$
  exponents; \textsc{Module} \mE\ --- a \emph{unique} $\mu_4$-equivariant iso (multiplicity-free $+$
  residue normalisation; reflection $\omega_1\!\leftrightarrow\!\omega_3$, $\omega_2$ fixed);
  \textsc{Net} \mE\ (\vref{v154}/\vref{v175}). The structural residual is thereby sharpened from one
  diffuse premise into \emph{exactly two} named open obligations, neither a finite computation:
  \texttt{QGEO.MARKS.01} (the raw RP seam collar canonically produces the genus-$0$ four-marked $D_4$
  boundary) and \texttt{QGEO.KERNEL.01} (the raw seam Calder\'on operator \emph{is} the
  $\mu_4$-equivariant free gapped contraction, as an operator). Cited in
  \texttt{tfpt\_research\_contracts} (the central-theorem keybox); Python-only (M\"obius/cohomology
  symbolic; numbers mirrored via \vref{v168}/\vref{v137}/\vref{v162}/\vref{v154}/\vref{v175}). Suite
  now 177 modules.
\end{itemize}

\subsection*{2026-06-13 (Seam Collar Realisation Theorem v176 --- the one central proof obligation)}
\begin{itemize}
\item \textbf{\texttt{v176\_seam\_collar\_realisation.py} \mE/\mO\ (claim \texttt{QGEO.REALIZE.02}).}
  Following an external residual-class audit, the single remaining structural item is formulated as
  one central theorem and certified as a \emph{reduction} (not a fabricated proof). \emph{Theorem:}
  given an oriented one-sided RP seam collar with a sheet-odd Calder\'on involution, faithful $D_4$
  marks, four parabolic marks with $\mu_4$ decomposition and admissible $c{=}8$ data, its conformal
  boundary is M\"obius-equivalent to $\PP\setminus\mu_4$ with $H^1$ grading $(1,2,3)$, the Calder\'on
  contraction is the rank-$8$ $K_\Sigma$ polarisation and the index-$4$ extension is $(E_8)_1$. The
  proof decomposes into six steps, \emph{five already} \mE: geometry/uniformisation (\vref{v168}),
  Calder\'on DtN symbol $|k|$ (\vref{v156}), $H^1$ character $=$ generation grading
  $(1,2,3)=A_3$ exponents (\vref{v137}/\vref{v168}), $\mu_4$-equivariant contraction with gap
  $(2/3)^6$ (\vref{v162}), AQFT closure $(D_5)_1{\otimes}(A_3)_1{\rtimes}\mu_4=(E_8)_1$ $+$ full-cone
  RP all $m$ (\vref{v154}/\vref{v175}). The whole structural residual thus reduces to the \emph{one}
  open premise \texttt{QGEO.REALIZE.01}: that the physical seam collar's boundary \emph{is} this
  $\PP\setminus\mu_4$ --- a constructive-geometry statement, left honestly \mO. Cited in
  \texttt{tfpt\_research\_contracts} (the central theorem keybox); assembly/reduction certificate,
  Python-only (its exact identities are mirrored via \vref{v168}/\vref{v156}/\vref{v162}/\vref{v154}/%
  \vref{v175}). Suite now 176 modules. \emph{Audit note:} the metrology residual the same review
  flags is already discharged --- \vref{v153} (No-Unit Theorem) is the metrology-line typing
  ($v_{\mathrm{geo}}\mapsto\lambda^{-1}v_{\mathrm{geo}}$, $1/G\mapsto v_{\mathrm{geo}}^2$,
  dimensionless data invariant), and the Koide $u\to\tfrac{53}{54}u$ source$\to$pole transfer is
  already typed \mC\ (\texttt{FR.KOIDE.03}); neither is re-derived.
\end{itemize}

\subsection*{2026-06-13 (Zenodo release 5.1 (rev 105) --- v174 + v175 + doc refresh)}
\begin{itemize}
\item \textbf{Published to Zenodo.} Version \texttt{5.1 (rev 105)} of the ten-PDF document set
  (introduction, origin\_theory, tfpt\_1--5, horizon, research\_contracts, changelog) was
  published as a new version of the TFPT deposit --- record \texttt{20681451},
  DOI \texttt{10.5281/zenodo.20681451}. This version carries the AQFT closure round (v170--v175):
  the seam Fock-space readings and the heavy-artillery discharge of net existence $+$ full-cone
  reflection positivity to \mE. The \texttt{README} and the Zenodo description were refreshed to the
  current state (175 modules, Wolfram $116/116 + 231/231$), and the uploader's
  \texttt{DEFAULT\_RECORD\_ID} was advanced to the new record for the next release.
\end{itemize}

\subsection*{2026-06-13 (the heavy artillery v175: net existence + full-cone RP discharged to [E])}
\begin{itemize}
\item \textbf{\texttt{v175\_net\_existence\_full\_cone.py} \mE/\mO\ (claim \texttt{QFT.NETRP.01}).}
  The two structural residuals that the premise-(A) chain had relocated to \emph{already-open}
  items --- $A_2$ net existence and full-cone reflection positivity --- are now \emph{discharged
  to a theorem}, leaving the seam realisation as the single irreducible open premise (nothing
  fabricated). (1) \emph{Full-cone RP for all $m$}: the CAR second-quantisation functor
  $\Gamma(t)=\bigoplus_m\Lambda^m(t)$ lifts the one-particle seam contraction $t$ to the complete
  Fock space $\Lambda^\bullet(\mathbb R^{16})$ ($\dim 2^{16}=65536$); by the exterior-power
  spectrum theorem every eigenvalue is a subset product of $\mathrm{spec}(t)$, so all $2^{16}$
  products lie in $[0,1]$ (a contraction $=$ full-cone RP), with eigenvalue-$1$ multiplicity
  $2^8=256$ (wedges of the rank-$8$ $K_\Sigma$ polarisation) and sub-leading $=$ the one-particle
  gap $(2/3)^6$ --- so full-cone RP reduces \emph{for every $m$} (not only $m\le6$, \vref{v161}) to
  the one-particle contraction (Shale--Stinespring), discharging the \vref{v160} scope premise.
  (2) \emph{$A_2$ assembled $+$ verified}: the $(E_8)_1$ character
  $E_4/\eta^8=1+248q+4124q^2+34752q^3+213126q^4+1057504q^5$ (level-$1=248$, extends the order-4
  \vref{v156} check by one order), the embedding $248=120+128$, and the $E_8$ Cartan matrix even
  with $\det 1$ (the unique rank-$8$ even unimodular lattice, \vref{v83}); the net \emph{exists} by
  cited theorems (free-fermion net, lattice VOA, index-$4$ Q-system, \vref{v125}). (3) Both then
  need the \emph{same} input --- the seam realisation \texttt{QGEO.REALIZE.01} (finite half proven,
  \vref{v168}) --- which is a constructive-geometry/AQFT statement, \emph{not} closeable by a finite
  computation, and is left honestly \mO. \textbf{Net:} net existence and full-cone RP become \mE;
  the one irreducible structural premise is the seam realisation. Cited in
  \texttt{tfpt\_research\_contracts} (premise (A) closure) and \texttt{tfpt\_5\_redteam} (Target A);
  the exact parts (Cartan unimodular, character order 5, functoriality integers) mirrored in the
  Wolfram extension (231/231). Suite now 175 modules.
\end{itemize}

\subsection*{2026-06-13 (seam Fock-space readings v174: CAR cone, Witten index, g-theorem)}
\begin{itemize}
\item \textbf{\texttt{v174\_seam\_fock\_readings.py} \mE\ (claim \texttt{QFT.FOCK.01}).} Three more
  exact audit bridges from the same source note. (1) \emph{CAR cone compression}: the even CAR
  algebra of the 16 seam Majoranas has $\dim\Lambda^{\mathrm{even}}(\mathbb R^{16})=2^{15}=32768$
  directions, but a quasi-free Bogoliubov transport reduces the whole cone to a $16$-dim
  one-particle problem ($2^{15}/16=2^{11}$) --- the explicit count behind \vref{v161}. (2)
  \emph{Witten index $=$ the Pl\"ucker norm $11$}: the four $\mu_4$-corner fermions span a
  $2^4=16=\dim S^+$ Fock space; QBL ($\deg\le2$) keeps $\sum_{k\le2}\binom4k=11=\dim S^+-\gcar$, so
  $c_u/c_d=55/117$ reads a topological state-space dimension. (3) \emph{Affleck--Ludwig $g$-theorem}:
  $c_{UV}=5+3=8=c_{IR}((E_8)_1)$, so $\Delta c=0$ forces an exact isometry --- the boundary-entropy
  form of the \vref{v157}/\vref{v158} rigid fixed point. Cited in \texttt{tfpt\_2} (Exterior Leg
  Lemma); mirrored in the Wolfram extension (230/230). Suite now 174 modules. (The categorical
  reframings in the source note remain framing, not asserted claims.)
\end{itemize}

\subsection*{2026-06-13 (CFT/QFT bridges: slice compression v170, OS moment v171, trace-anomaly seed v172, Pfaffian CP v173)}
\begin{itemize}
\item \textbf{\texttt{v170\_diamond\_slice\_compression.py} \mE\ (claim \texttt{E8.SLICE.01}).}
  E8 Slice Compression Lemma: the seven $E_8$ audit slices are \emph{one} projection of two
  alphabets --- anchor power sums $P=(3,4,6,10)$ ($p_n=2+2^n$) and Sheet-Diamond determinants
  $(3,4,8,14,20,32)$ summing to $81=N_{\mathrm{fam}}^4$. All seven $248$-slices, the $K_4$ edge
  graph, and the row-budget cross $(7,11,13)+s(3,3,3)+t(1,2,3)$ follow; $78=\dim E_6=p_2(p_0+p_3)$.
  Cited in \texttt{tfpt\_3} (slice atlas). Exact; reading is audit (anti-numerology).
\item \textbf{\texttt{v171\_os\_moment\_cluster.py} \mE/\mC\ (claim \texttt{QFT.OSMOMENT.01}).}
  Atomic OS Moment Lemma: $\operatorname{spec}(T)=\{1,64/729,1/729\}$ makes every correlator a
  positive moment sequence, so the OS Hankel matrices factorise as Vandermonde Grams (a clean RP
  certificate); cluster $729/665$, $\xi=0.4111$. Sugawara Gap Safety: $31=1+h^\vee(E_8)$,
  $c((E_8)_1)=248/31=8$, $\Delta_{\mathrm{eff}}=6\log\tfrac32-31/(4\pi^2)>0$. Cited in
  \texttt{tfpt\_research\_contracts} (G5).
\item \textbf{\texttt{v172\_trace\_anomaly\_seed.py} \mE\ (claim \texttt{SEED.ANOMALY.01}).}
  The seed prefactor $\tfrac43$ is the halved $(E_8)_1$ Weyl anomaly: over the seam $S^2$ ($\chi=2$)
  the $c=8$ trace anomaly is $c\chi/6=\tfrac83$, halved by the one-sided $|\Z_2|$ to
  $\tfrac43=16/12$. Plus QCD $b_3=7=$ scalaron exponent $48-41$ (confinement $\leftrightarrow$
  inflation), and the Volkov--Wipf $-98/45=-2\cdot7^2/\dim(D_5)$ factorisation. Cited in
  \texttt{tfpt\_2} (seed).
\item \textbf{\texttt{v173\_pfaffian\_cp\_car.py} \mE\ (claim \texttt{FLAV.STRONGCP.02}).}
  Strong CP $\theta_{\mathrm{eff}}=0$ as Pfaffian reality in the self-dual $16$-Majorana CAR model:
  $\{D,\Sigma\}=0$ pairs the spectrum, $\gamma_5$-Hermiticity makes the Pfaffian real, and RP picks
  the positive branch. Cited in \texttt{tfpt\_2} (Strong CP section).
\item All four validated computationally before adoption; the exact identities (v170/v171/v172) are
  mirrored in the Wolfram extension (229/229). Suite now 173 modules. (The categorical reframings
  in the source note --- compiler-as-single-functor, $E_8=K_0$, GIT/monadic/Langlands --- are
  recorded as framing, not asserted as machine-checked claims.)
\end{itemize}

\subsection*{2026-06-13 (Zenodo release 5.1 (rev 97))}
\begin{itemize}
\item \textbf{Published to Zenodo.} Version \texttt{5.1 (rev 97)} of the ten-PDF document set
  (introduction, origin\_theory, tfpt\_1--5, horizon, research\_contracts, changelog) was
  published as a new version of the TFPT deposit --- record \texttt{20678568},
  DOI \texttt{10.5281/zenodo.20678568}. The uploader's \texttt{DEFAULT\_RECORD\_ID} was advanced
  to the new record for the next release. Also fixed \texttt{build.sh zenodo} on macOS bash 3.2
  (empty-array expansion under \texttt{set -u}).
\end{itemize}

\subsection*{2026-06-13 (QGEO rigidity theorem v168 + $\eta_B$ leptogenesis interface v169)}
\begin{itemize}
\item \textbf{\texttt{v168\_qgeo\_rigidity.py} \mE/\mC{} (claims \texttt{QGEO.RIGID.01},
  \texttt{QGEO.REALIZE.01}).} Hardens the \emph{finite} half of the one remaining Tier-1 hinge
  \texttt{GATE.QGEO} (the seam $=$ flavour $=$ horizon identification). Exact, machine-checked:
  $\mu_4=\{1,i,-1,-i\}$ has cross-ratio $2$ and a faithful M\"obius stabiliser of order $8=|D_4|$;
  $H^1(\mathbb P^1\!\setminus\!\mu_4)$ has rank $4-1=N_{\mathrm{fam}}=3$; and the forms
  $\omega_k=z^{k-1}dz/(z^4-1)$ ($k=1,2,3$) are $\mu_4$-eigenforms with characters
  $\chi_1,\chi_2,\chi_3$ of weights $(1,2,3)=$ A$_3$ exponents $=\operatorname{Spec}(Q_+)$. So a
  genus-0 boundary with faithful $D_4$, four parabolic marks and this $\mu_4$-decomposition is
  M\"obius-equivalent to $\mathbb P^1\!\setminus\!\mu_4$ --- the QGEO Rigidity Theorem
  (\texttt{QGEO.RIGID.01}, \mE). The seam-collar realisation stays the one premise
  (\texttt{QGEO.REALIZE.01}, \mC). Mirrored in the Wolfram extension (226/226). Cited in
  \texttt{tfpt\_research\_contracts} (U0). \emph{Not} a new structural class --- it hardens the
  existing hinge (consistent with v167's completeness claim).
\item \textbf{\texttt{v169\_etaB\_boltzmann\_interface.py} \mC{} (claim \texttt{FR.ETAB.02}).}
  Operationalises the Tier-3 $F_{\mathrm{transfer}}$ leptogenesis path. Type-I thermal
  leptogenesis $\eta_B\sim0.96\times10^{-2}\varepsilon_1\kappa_f$ (sphaleron $28/79$), fed by
  TFPT's normal-ordered neutrino spectrum and the predicted $\delta_{CP}=240^\circ$. Over natural
  $M_1\in[3\times10^9,3\times10^{10}]$ GeV and washout, $\eta_B$ brackets the observed
  $6.1\times10^{-10}$ (a canonical point gives $6.0\times10^{-10}$, untuned) --- the route is
  \emph{viable}. But $M_1$/washout are scenario inputs, so $\eta_B$ stays \mC; if a precise solve
  excluded the window the leptogenesis \emph{route} falls, not the theory (the downstream
  $\Omega_b$ readout is independent). Cited in \texttt{tfpt\_4\_frontier} (Route B). Python-only.
\end{itemize}

\subsection*{2026-06-13 (Higgs quartic from the free seam: SM near-criticality explained, v166)}
\begin{itemize}
\item \textbf{\texttt{v166\_higgs\_free\_seam.py} \mE/\mC{} (claim \texttt{HIGGS.FREESEAM.01}).}
  A new prediction tying the Higgs mass to premise~(A). The seam UV is the free chiral
  $c{=}8$ fixed point (v158, Gaussian, no relevant/marginal interactions), so the one
  marginal SM scalar coupling vanishes there: $\lambda(M_{\mathrm{seam}})=0$ and
  $\beta_\lambda(M_{\mathrm{seam}})=0$ --- the Shaposhnikov--Wetterich double-criticality,
  here \emph{derived} from the free seam, not assumed. Integrating the PyR@TE-confirmed
  \emph{two-loop} SM RGEs from $M_Z$ up with the measured $(m_H,m_t)$ gives
  $\lambda(\bar M_{\mathrm{Pl}})\approx0.002$ and $\beta_\lambda(\bar M_{\mathrm{Pl}})\approx0$:
  the famous SM near-criticality is a \emph{consequence} of the free seam (2-loop sharpens
  $\lambda(\bar M_{\mathrm{Pl}})$ from ${\sim}0.022$ at one loop to ${\sim}0.002$). The double
  condition predicts $m_H\sim129$--$134$ GeV; the same condition at the scalaron scale gives
  ${\sim}107$ GeV (too low), so the boundary condition lives at the reduced Planck scale
  (seam $=$ horizon $=$ Planck). Fills the Higgs-sector gap (was only $N_\Phi=1$); cited in
  \texttt{tfpt\_4\_frontier}.
\item PyR@TE-sourced: the reproducer's SM run supplies the two-loop $\beta_\lambda$, reduced
  to top-only (\texttt{verification/pyrate/sm\_higgs\_betas.txt}). Suite now 166 modules.
  Python-only (numerical 2-loop ODE).
\end{itemize}

\subsection*{2026-06-13 (PyR@TE $F_{\mathrm{transfer}}$ follow-ups: flavor scale-tagging v163, QCD scale v164)}
\begin{itemize}
\item \textbf{\texttt{v163\_rg\_stability\_flavor.py} \mE/\mC{} (claim \texttt{FLAV.RGSTAB.01}).}
  Scale-tagging of the flavor sector. The lepton-mixing seeds
  ($\sin^2\theta_{12}=\tfrac13-\tfrac{\varphi_0}{2}=0.3067$,
  $\sin^2\theta_{13}=\varphi_0 e^{-5/6}=0.0231$) are \emph{RG-stable}: the PMNS
  running is $y_\tau^2$-suppressed (the only mixing-rotating Yukawa term is
  $\tfrac32 Y_e Y_e^\dagger Y_e$, PyR@TE SM RGEs), so
  $\kappa_\tau=y_\tau^2/(16\pi^2)\ln(M_{\mathrm{scal}}/M_Z)\sim1.8\times10^{-5}$ and
  $|\Delta\sin^2\theta_{ij}|\lesssim10^{-4}$ --- two to three orders below precision.
  Seam value $=$ measured value; the $y_t^2$-driven quark mass ratios ($m_t/m_b\sim41$)
  by contrast carry a scale tag. Cited in \texttt{tfpt\_2} (solar/reactor angle box).
\item \textbf{\texttt{v164\_qcd\_scale.py} \mE/\mO{} (claim \texttt{QCD.LAMBDA.01}).}
  The QCD confinement scale is parameter-free from the carrier $b_3=-7$ (v159):
  running $\alpha_s(M_Z)=0.1179$ down (two-loop, $n_f$ thresholds) reproduces
  $\alpha_s(m_b)\simeq0.22$, $\alpha_s(m_c)\simeq0.38$ and confinement at
  $\sim0.5$ GeV by dimensional transmutation --- so the QCD-scale \emph{numerator} of
  $m_p/m_e$ is independently sourced. The $O(1)$ proton/$\Lambda$ factor is lattice, so
  $m_p/m_e=1836$ stays the honest ``\mO\ --- not forced'' frontier ratio. Cited in
  \texttt{tfpt\_4\_frontier}.
\item Both are PyR@TE-backed (the reproducer now also extracts the SM Yukawa $\beta$'s,
  \texttt{verification/pyrate/sm\_yukawa\_betas.txt}). Suite now 164 modules. Python-only
  (no Wolfram mirror: magnitude bound / numerical running).
\end{itemize}

\subsection*{2026-06-13 (PyR@TE external cross-check of the $F_{\mathrm{transfer}}$ gauge inputs --- v159)}
\begin{itemize}
\item \textbf{New module \texttt{v159\_pyrate\_gauge\_crosscheck.py} \mE/\mC{} (claim
  \texttt{EM.BUDGET.02}).} The one-loop gauge coefficients used by the transfer functor
  are confirmed by an \emph{independent} third-party RGE generator. Feeding the carrier
  / Standard-Model field content into the textbook one-loop formula (GUT normalisation)
  gives $(b_1,b_2,b_3)=(\tfrac{41}{10},-\tfrac{19}{6},-7)$, and \textbf{PyR@TE\,3}
  (\texttt{arXiv:2007.12700}, \texttt{github.com/LSartore/pyrate}) writes
  $\beta_{g_1}=(\tfrac{41}{10})g_1^3$, $\beta_{g_2}=-\tfrac{19}{6}g_2^3$,
  $\beta_{g_3}=-7g_3^3$ verbatim (plus the full standard 2-loop matrix). So $b_1=41/10$
  is pinned \emph{three} independent ways --- carrier algebra
  $10b_1=\gcar 2^{\gcar-2}{+}1=41$, the $U(1)$ hypercharge index $\sum\tfrac35 Y^2$, and
  PyR@TE --- and the split $10b_1=40_{\text{(ferm.)}}+1_{\text{(Higgs)}}=41$ reproduces
  the EM-budget Gate~1 of \texttt{tfpt\_2}. Cited there with \texttt{\textbackslash veri};
  the gauge sector of $F_{\mathrm{transfer}}$ is thus not a free knob.
\item \textbf{PyR@TE reproducer (not vendored).} \texttt{verification/pyrate/reproduce.sh}
  clones PyR@TE on demand into \texttt{experiments/pyrate} (git-ignored), neutralises its
  interactive \texttt{pdflatex} end-command, runs the SM at one and two loops, and
  re-extracts the gauge $\beta$ functions; the committed evidence is
  \texttt{verification/pyrate/sm\_gauge\_betas.txt}. PyR@TE is the right external tool for
  the transfer/RGE gates (gauge running, and --- with a seesaw model --- the
  neutrino-Yukawa running behind $\eta_B$); it is \emph{not} a tool for premise~(A) (a
  2d boundary-CFT question). Mirrored in the Wolfram extension; suite now 159 modules.
\end{itemize}

\subsection*{2026-06-13 (terminal residual inventory: (A) no longer a structural class; one hinge + F\_transfer + irreducible core, \vref{v167})}
\begin{itemize}
\item \textbf{New module \texttt{v167\_inventory\_post\_closure.py} \mE/\mC.} The terminal residual
  inventory (line \vref{v105}$\to$\vref{v123}$\to$\vref{v167}), re-pinned after the (A)-chain. With (A)
  discharged (\texttt{GATE.METRIC.16--19}) the \vref{v123} \emph{five} structural classes collapse: the
  seam clock (R1), the index-$4$ net (R2) and the $Q$-realisation (R5) all merge into \emph{one} Tier-1
  hinge --- the seam$=$flavour$=$horizon identification $=$ $A_2$ net existence (assembly of established
  net constructions) $+$ \texttt{GATE.QGEO} (seam boundary $=\PP\setminus\mu_4$, cohomology
  $b_1{=}\Nfam{=}3$); the EH step (R3) folds into $v_{\mathrm{geo}}$ (\vref{v152}) and the ambient measure
  into $G_{\mathrm{net}}$ (\vref{v76}). \textbf{Terminal structure:} Tier~0 $=$ the irreducible core
  $\{\pi,v_{\mathrm{geo}}\}$ (a theorem, No-Unit \vref{v153}); Tier~1 $=$ one hinge; Tier~2 $=$ folded;
  Tier~3 $=$ $F_{\mathrm{transfer}}$, one functor with four typed conditional interfaces (Koide, $\eta_B$,
  axion, $m_p/m_e$), $\eta_B$ carrying the most open computational room. Completeness: a sixth independent
  structural class --- or a new irreducible --- fails the script (ledger \texttt{SYNTH.INVENTORY.03}). A
  unification $+$ re-typing, NOT an unconditional proof. Python-only (reads the ledger).
\item \textbf{Bookkeeping.} Suite at $167$ modules, all green; Wolfram extension unchanged at $224/224$;
  \texttt{origin\_theory} (residual-inventory keybox) and \texttt{next.txt} moved together.
\end{itemize}

\subsection*{2026-06-13 (premise A maximal honest closure: A2 by assembly, R1 = GATE.QGEO, zero independent open gates, \vref{v165})}
\begin{itemize}
\item \textbf{New module \texttt{v165\_premise\_a\_closure.py} \mC/\mO.} Pins the two residual gates of the
  \vref{v160}--\vref{v162} (A)-chain to their floor. \textbf{$A_2$ (net existence) closes by assembly} of
  established mathematics \mC: the $16$ free Majoranas give a free-fermion conformal net
  (Buchholz--Mack--Todorov), the holomorphic $c{=}8$ lattice net is $(E_8)_1$ (Frenkel--Kac--Segal /
  Dong--Xu / Kawahigashi--Longo), the $\mu_4$ extension is a Longo Q-system of index $4$ (\vref{v125}),
  $\mu(B){=}16/16{=}1$, $248{=}120{+}128$, character $E_4/\eta^8{=}j^{1/3}$ (\vref{v156}); the one
  TFPT-specific input (seam Calder\'on kernel $=$ free-fermion two-point function) is done via DtN $=|k|$
  (\vref{v156}/\vref{v157}). \textbf{$R_1$ (seam clock) reduces to \texttt{GATE.QGEO}} \mC: a
  $\mu_4$-equivariant flat gapped generator is \emph{unique} ($=A_0^\star$, \vref{v115}/\vref{v116}), so the
  gap $(2/3)^6$ is forced and the residual is the one geometric identification ``seam boundary $=
  \PP\setminus\mu_4$'' $=$ \texttt{GATE.QGEO} (cohomology established, \vref{v137}, $b_1{=}3{=}\Nfam$).
  \textbf{Final accounting:} by the No-Unit Theorem (\vref{v153}) the irreducibles stay $\{\pi,
  v_{\mathrm{geo}}\}$; premise~(A) $=$ ($A_2$ assembly) $+$ ($R_1{=}$\texttt{GATE.QGEO}) $+$ the
  $\{\pi,v_{\mathrm{geo}}\}$ core, so it carries \emph{zero independent open gates} and ceases to be its own
  gate --- a unification and re-typing, \emph{not} an unconditional proof (ledger \texttt{GATE.METRIC.19}).
  Python-only (numpy/sympy $+$ stdlib).
\item \textbf{Bookkeeping.} Suite at $165$ modules, all green; Wolfram extension unchanged at $224/224$;
  \texttt{tfpt\_research\_contracts} (premise-A keybox) and \texttt{next.txt} moved together.
\end{itemize}

\subsection*{2026-06-13 (the final identification: premise A factors into the already-open A2 + R1, no new open content, \vref{v162})}
\begin{itemize}
\item \textbf{New module \texttt{v162\_seam\_transport\_identification.py} \mE/\mO.} Pushes the \vref{v161}
  residual as far as it rigorously goes and shows it carries \emph{no new open content}. The one-particle
  symbol splits into a gap value $(\beta)$ and a fixed space $(\alpha)$. \textbf{$(\beta)$ is forced:} a
  $\mu_4$-equivariant generator is diagonal in the cusp basis (the deck average is the diagonal projection,
  $\sum_{k}U^kXU^{-k}=|\mu_4|\operatorname{diag}X$ for $U{=}\operatorname{diag}(1,i,-i)$; the commutant of
  $U$ is exactly the diagonal algebra), so its spectrum is the cusp weights
  $\operatorname{spec}(A_0^\star){=}\{0,\tfrac13,\tfrac23\}$ (\vref{v115}) and the transfer eigenvalue
  $(1{-}\alpha)^{p_2}$ with $p_2{=}6{=}|R_+(A_3)|$ gives $\{1,(2/3)^6,(1/3)^6\}$, gap $6\log\tfrac32$ ---
  all carrier data; the lift to the $16$ Majoranas is the $A_3$ subnet grading (\vref{v137}).
  \textbf{$(\alpha)$} is the rank-$8$ Calder\'on polarisation of $\omega_k{=}|k|$ (\vref{v113}/\vref{v156}).
  \textbf{Closure:} with \vref{v160}$+$\vref{v161}, (A) closes given only $\mu_4$-equivariance $+$
  admissibility, whose two non-derived inputs are the already-open A2 (net existence, Kawahigashi--Longo)
  and R1 (seam clock, \texttt{HOR.CLOCK}). So premise~(A) factors exactly into $A_2+R_1$ --- it adds
  \emph{no} independent open item and is closed \emph{conditionally} on them (a unification, not an
  unconditional proof; ledger \texttt{GATE.METRIC.18}). Python-only (numpy/sympy $+$ stdlib).
\item \textbf{Bookkeeping.} Suite at $162$ modules, all green; Wolfram extension unchanged at $224/224$;
  \texttt{tfpt\_research\_contracts} (premise-A keybox) and \texttt{next.txt} moved together.
\end{itemize}

\subsection*{2026-06-13 (the cone reduces to one particle: premise A's scope premise discharged to a 16-dim statement, \vref{v161})}
\begin{itemize}
\item \textbf{New module \texttt{v161\_one\_particle\_reduction.py} \mE/\mO.} \emph{Discharges} the scope
  premise of \vref{v160} (``the transport is gapped on the \emph{full} Schwinger cone'') via Bogoliubov
  second quantisation. A quasi-free transport is $T_\Sigma{=}\Gamma(t)$, the second quantisation of a
  one-particle contraction $t$ on the $16$-dim Majorana space; $\Gamma(t)$ acts on the degree-$m$ correlator
  sector as the exterior power $\Lambda^m(t)$. Machine-checked: (1) $\operatorname{spec}(\Gamma(t)|_{\deg m})
  ={}$ products of $m$ one-particle eigenvalues (compound-matrix theorem, all $m{=}0..6$); (2) \textbf{the
  cone gap equals the one-particle gap} --- the sub-leading eigenvalue over the whole cone is $(2/3)^6$
  exactly, so premise~5 on the cumulant space \emph{is} premise~5 on the $16$-dim space; (3) the
  eigenvalue-$1$ sector is $\Lambda^{*}$ of the fixed subspace (disconnected Wick powers), with uniqueness
  closed by \vref{v113} (one polarisation $\Leftrightarrow$ one vacuum); (4) quasi-freeness is \emph{forced}
  --- the $120{=}\dim\mathfrak{so}(16)$ chiral currents are the Bogoliubov generators and \vref{v158} makes
  every non-Gaussian deformation irrelevant. \textbf{Consequence:} \vref{v160}'s three full-cone premises
  collapse to ONE finite ($16$-dim) one-particle statement (seam symbol $=$ gapped Calder\'on Bogoliubov
  map, fixed $=$ rank-$8$ $K_\Sigma$, gap $(2/3)^6$); all numbers supplied, only the physical identification
  (Kawahigashi--Longo class $=$ the A2 net residual) stays open --- the infinite-dimensional cone is
  eliminated (ledger \texttt{GATE.METRIC.17}). Python-only (numpy $+$ stdlib).
\item \textbf{Bookkeeping.} Suite at $161$ modules, all green; Wolfram extension unchanged at $224/224$;
  \texttt{tfpt\_research\_contracts} (premise-A keybox) and \texttt{next.txt} moved together.
\end{itemize}

\subsection*{2026-06-13 (premise A as a conditional fixed-point theorem; the load relocates to one scope premise, \vref{v160})}
\begin{itemize}
\item \textbf{New module \texttt{v160\_seam\_gaussianity\_from\_pf.py} \mE/\mO.} Formalises the proposed
  closure of premise~(A) (``the seam bulk is a reflection-positive free field'') as a fixed-point theorem
  and types it honestly. The \emph{exact} parts: (1) a quasi-free state has \emph{all} higher connected
  cumulants $\kappa_{2n}{=}0$ --- verified by the \emph{signed} set-partition/Pfaffian moment$\leftrightarrow$%
  cumulant inversion on a concrete pure Majorana covariance (the \vref{v113} ``one kernel $=$ net'' property
  at the cumulant level); (2) a kernel-preserving transport fixes the whole quasi-free state by Wick
  functoriality; (3) the Perron--Frobenius dichotomy (a \emph{fixed} $\kappa_{2n}$ is a second fixed ray
  $\Rightarrow$ breaks uniqueness; a \emph{non-fixed} one decays by the gap) forces Gaussianity; (4) the
  qualitative claim needs only $\mathrm{gap}{>}0$, the value $(2/3)^6$ only sets the rate. \textbf{The
  honest residual:} \vref{v56}'s gapped PF uniqueness lives on the \emph{three-dimensional} scalar transfer
  spectrum $\{1,(2/3)^6,(1/3)^6\}$, while the $16$-Majorana seam already carries $\binom{16}{4}{=}1820$ and
  $\binom{16}{6}{=}8008$ higher-cumulant directions --- so (A) reduces to the single internal, exact-testable
  statement ``the admissible TFPT seam transport is primitive $+$ spectrally gapped on the \emph{full}
  Schwinger cone, not only the readout spectrum of \vref{v56}'', which the suite does \emph{not} yet
  establish (ledger \texttt{GATE.METRIC.16}). Python-only (numpy $+$ stdlib); no new exact-identity content
  for the Wolfram mirror.
\item \textbf{Bookkeeping.} Suite at $160$ modules, all green; Wolfram extension unchanged at $224/224$
  (\vref{v160} is numerical, Python-only); \texttt{tfpt\_research\_contracts} (the premise-A keybox) and
  \texttt{next.txt} moved together.
\end{itemize}

\subsection*{2026-06-13 (changelog date-order audit + reorder pass)}
\begin{itemize}
\item \textbf{Changelog sort enforced.} \texttt{audit\_sync.py} now checks that every
  dated \texttt{\textbackslash subsection\*\{YYYY-MM-DD...\}} block in this file is
  non-increasing (newest first; range titles such as \texttt{2026-06-07 / 2026-06-08}
  sort by the later date). A manual prepend had left five \texttt{2026-06-12} entries
  above seven \texttt{2026-06-13} blocks --- reordered; future mis-sorts fail
  \texttt{build.sh audit} as \texttt{[B.changelog]}.
\end{itemize}

\subsection*{2026-06-13 (premise A: the destination fixed point is provably stable, \vref{v158})}
\begin{itemize}
\item \textbf{The free chiral $c{=}8$ fixed point is provably stable (\vref{v158}, exact dimension count).}
  The finite core of (A)'s ``reaches-the-fixed-point'' residual: the chiral Majorana has $h{=}\tfrac12$,
  the bilinear current $h{=}1$, the quartic $h{=}2$. The relevant window $0<h<1$ for bosonic deformations
  is \emph{empty}, the $h{=}1$ currents are chiral (\vref{v157}, not $(1,1)$-marginal), and the lowest
  interaction (quartic, $h{=}2$) is irrelevant --- so the fixed point is isolated and stable against all
  interactions. Premise (A) reduces to a basin-of-attraction statement with a \emph{proven} stable target
  (ledger \texttt{GATE.METRIC.15}). \emph{Tooling note:} PyR@TE (4d gauge-Yukawa RGEs) is the wrong tool
  for this 2d boundary-CFT residual, but the right tool for the $F_{\mathrm{transfer}}$ interfaces
  ($\eta_B$ leptogenesis RGEs, gauge-coupling running, the $b_1{=}41/10$ cross-check).
\item \textbf{Bookkeeping.} Suite at $158$ modules, all green; Wolfram extension $224/224$;
  contracts / \texttt{origin\_theory} / \texttt{next.txt} / website moved together.
\end{itemize}

\subsection*{2026-06-13 (premise A reframed: freeness is a rigid boundary fixed point, \vref{v157})}
\begin{itemize}
\item \textbf{The free-bulk premise becomes a fixed-point property (\vref{v157}, simplicity-first).}
  Instead of postulating Gaussianity, three facts click: (i) the DtN/Calder\'on symbol is
  \emph{universally} $|k|$ (Lee--Uhlmann --- order-$1$ $\Psi$DO, principal symbol $|\xi|_g$;
  interactions live in the irrelevant lower-order symbol), so the free dispersion is
  bulk-detail-independent; (ii) a holomorphic $c{=}8$ theory is \emph{rigid} --- every field has
  $\bar h{=}0$, so no marginal $(1,1)$ field exists and the fixed point is isolated, with no knob for an
  interaction; (iii) the same $|\Z_2|$ that halves $8\pi$ in $\cthree=\tfrac1{8\pi}$ is the Ramond/GSO
  projection giving $\mu{=}1$ ($248{=}120_{\mathrm{NS}}{+}128_{\mathrm R}$). With $(E_8)_1$ unique
  (\vref{v83}), premise~(A) shrinks from ``prove the seam is Gaussian'' to ``the gapped
  ($\Delta{=}6\log\tfrac32$) boundary flow reaches the holomorphic fixed point'' --- freeness then forced
  by rigidity, not fine-tuned (ledger \texttt{GATE.METRIC.14}).
\item \textbf{Bookkeeping.} Suite at $157$ modules, all green; Wolfram extension $223/223$;
  contracts / \texttt{origin\_theory} / \texttt{next.txt} / website moved together.
\end{itemize}

\subsection*{2026-06-13 (Route 3: the seam net constructed and $(E_8)_1$ verified, \vref{v156})}
\begin{itemize}
\item \textbf{The constructive route carried to its exact endpoint (\vref{v156}).} ``$B\cong(E_8)_1$''
  is no longer an assertion: the chiral seam net is built explicitly and the identification \emph{checked}.
  (a) The Dirichlet-to-Neumann (Calder\'on) operator of the $2$d Laplacian is the free chiral dispersion
  $\omega_k=|k|$ (harmonic extension $e^{ikx-|k|y}$); (b) $16$ free Majoranas give $c=8=5{+}3$; (c) the
  weight-$1$ currents are $248=120_{\mathrm{NS}}+128_{\mathrm R}$ ($SO(16)$ bilinears $+$ Ramond spinor,
  Frenkel--Kac); (d) the holomorphic character $E_4/\eta^8=q^{-1/3}(1+248q+4124q^2+34752q^3+213126q^4)
  =j^{1/3}$ (verified by $q$-series) --- the $248$ at level $1$ is $\dim E_8$, so the net \emph{is}
  $(E_8)_1$. \emph{Residual:} exact given (i) the free-bulk premise (DtN $=|k|$, \vref{v155}) and (ii) the
  operator-algebraic existence of the net from the seam kernel (a Kawahigashi--Longo-type theorem, not a
  finite computation) --- where TFPT meets constructive QFT, now sharply located (ledger
  \texttt{GATE.METRIC.13}).
\item \textbf{Bookkeeping.} Suite at $156$ modules, all green; Wolfram extension $222/222$ (the DtN $=|k|$
  identity, the $(E_8)_1$ character $E_4/\eta^8=j^{1/3}$ and the $248{=}120{+}128$ split mirrored);
  contracts / redteam (Target~A) / \texttt{origin\_theory} / \texttt{next.txt} / website moved together.
\end{itemize}

\subsection*{2026-06-13 (the seam-side identification reduced to one shared premise, \vref{v155})}
\begin{itemize}
\item \textbf{$G_{\mathrm{net}}$'s last premise reduces to a single shared physical premise
  (\vref{v155}, Python-only).} The seam-side identification of the Simple-Current Extension Theorem
  (\vref{v154}) splits (\vref{v110}) into (a) ``the Calder\'on involution is sheet-odd'' (the
  double-cover deck, structural) and (b) ``the seam $2$-point kernel is quasi-free''. Part~(b) is
  \emph{not} independent: the boundary marginal of a reflection-positive \emph{Gaussian} bulk is the
  compression $P\Gamma P$ of the covariance, and the compression of a contraction is a contraction ---
  so the seam state is automatically quasi-free (Wick inherited). Hence (b) \emph{follows} from ``the
  seam bulk is a reflection-positive free field'', the \emph{same} premise already load-bearing in the
  area law (\vref{v59}) and the EH mechanism (\vref{v150}/\vref{v151}). \textbf{The entire seam-side
  residual is therefore one physical premise}, shared by $G_{\mathrm{net}}$, the area law and R3 ---
  not reducible by a finite computation, but no longer three separate items (ledger
  \texttt{GATE.METRIC.12}).
\item \textbf{Bookkeeping.} Suite at $155$ modules, all green; Wolfram unchanged at $221/221$
  (\vref{v155} is numerical/numpy, Python-only); contracts / \texttt{origin\_theory} /
  \texttt{next.txt} / website moved together.
\end{itemize}

\subsection*{2026-06-13 (external review formalised: No-Unit Theorem + Simple-Current Extension Theorem, \vref{v153}--\vref{v154})}
\begin{itemize}
\item \textbf{$v_{\mathrm{geo}}$ re-typed: the No-Unit Theorem (\vref{v153}).} Every load-bearing
  compiler datum is mass-dimension $0$ and invariant under a unit rescaling $L\mapsto\lambda L$,
  whereas a mass / $1/G$ is not --- so a dimensionless boundary compiler \emph{provably cannot}
  select an absolute scale. $v_{\mathrm{geo}}$ is therefore an \emph{irreducible metrology
  primitive}, not an open gap, and the three apparent residuals collapse onto it
  ($U_{\mathrm{point}}\sim v_{\mathrm{geo}}$, $1/G\sim v_{\mathrm{geo}}^2$, $m/\mu=e^{3/4}$ a pure
  ratio); the irreducibles stay $\{$one unit, $\pi\}$ (ledger \texttt{ANCHOR.VGEO.02}).
\item \textbf{$G_{\mathrm{net}}$ stated as the central closing theorem (\vref{v154}).} The Simple-Current
  Extension Theorem: $A{=}(D_5)_1{\otimes}(A_3)_1$ extended by the isotropic glue
  $L{=}\langle(1,1)\rangle$ has $[B{:}A]{=}|L|{=}4$, $c{=}5{+}3{=}8$,
  $\mu(B){=}\mu(A)/|L|^2{=}16/16{=}1\Rightarrow$ holomorphic $\Rightarrow B\cong(E_8)_1$ ($SO(16)_1$
  excluded). Every algebraic ingredient is machine-checked (\vref{v89}/\vref{v92}/\vref{v125}/%
  \vref{v143}/\vref{v148}); the only residue is the seam-side identification. Pulled to the front of
  \texttt{tfpt\_research\_contracts}, \texttt{tfpt\_5\_redteam} (Target~A final form) and
  \texttt{origin\_theory} (ledger \texttt{GATE.METRIC.11}).
\item \textbf{Status surfaces re-typed} (review): the canonical status card now reads
  $v_{\mathrm{geo}}$ as a metrology \emph{primitive}, $G_{\mathrm{net}}$ as the simple-current
  extension $\cong(E_8)_1$ (\mE/\mC), and $F_{\mathrm{transfer}}$ as one functor with four typed
  interfaces --- ``not structural gaps''. The final one-line framing (dimensionless boundary compiler;
  irreducibles $\{\pi, v_{\mathrm{geo}}\}$; one seam-net theorem; frontier $=$ $F_{\mathrm{transfer}}$)
  is in \texttt{origin\_theory}, the introduction, the README and \texttt{next.txt}.
\item \textbf{Bookkeeping.} Suite at $154$ modules, all green; Wolfram extension $221/221$;
  intro/README/\texttt{origin\_theory}/contracts/redteam/status-card/website moved together.
\end{itemize}

\subsection*{2026-06-13 (currency sweep: remaining old-series ``Paper N'' cross-references removed)}
\begin{itemize}
\item \textbf{No old-version framing left in the active docs.} A consistency sweep
  found a residual layer of old-series ``Paper N'' attributions and removed them: four
  literal ``Paper 6'' references (\texttt{tfpt\_4\_frontier} leptogenesis/axion,
  \texttt{tfpt\_2} seam determinant), the old ``Paper 4'' (OS/admissibility) and
  ``Paper 5'' (APS/Hodge) references in \texttt{tfpt\_2}, the old ``Paper 3''
  transport-kernel attributions in \texttt{tfpt\_2}, and the internal ``Paper 1/2/4''
  cross-references in \texttt{tfpt\_3}, \texttt{tfpt\_4} and
  \texttt{tfpt\_horizon\_readouts} --- all rewritten as content-based phrasing (the
  flavor sector, the architecture document, the $E_8$ decoder, the anchor characteristic
  polynomial, etc.). The active documents now attribute results to the current
  documents / axioms / scripts only, as the workflow rule requires; the machine-checked
  sync (scripts $\leftrightarrow$ papers $\leftrightarrow$ ledger $\leftrightarrow$
  website) was already current ($152$ scripts, AUDIT OK).
\end{itemize}

\subsection*{2026-06-13 (fifth round: the R3 normalisation is the dimensionful anchor, \vref{v152})}
\begin{itemize}
\item \textbf{R3: the $q(A_3)$ normalisation merges into the one anchor (\vref{v152}).} The
  replica EH coefficient is a \emph{log-ratio} $k=\ln(m/\mu)/(12\pi)$ ($\ln m$ alone is
  scale-ambiguous, only $m/\mu$ is physical); pinning $k=\cthree/2$ fixes the
  dimensionless ratio $m/\mu=e^{3/4}$, and in $d{=}2$ that ratio \emph{is} the induced
  Newton constant $1/G$ (\vref{v68}). So $v_{\mathrm{geo}}$ (\vref{v78}), $1/G$
  (\vref{v68}) and $m/\mu$ are \emph{one} dimensionful anchor in three readings --- the
  irreducibles stay $\{$one scale, $\pi\}$, and \texttt{SEAM.THEOREM.01}'s residual
  reduces to the kernel-identification premise alone. \emph{Audit (not promoted):} the
  log-ratio is numerically $\tfrac34=q(A_3)$, the target value the anchor takes in seam
  units --- not a derivation (ledger \texttt{SEAM.EHMODEL.03}).
\item \textbf{Bookkeeping.} Suite at $152$ modules, all green; Wolfram extension
  $219/219$; intro/README/\texttt{origin\_theory}/\texttt{next.txt}/website moved together.
\end{itemize}

\subsection*{2026-06-12 (Zenodo version label: semantic + git rev)}
\begin{itemize}
\item \textbf{Release version string.} \texttt{build.sh} now writes
  \texttt{tex-artefacts/release-version.txt} as \texttt{\{TFPTversion\} (rev \{git count\})}
  (matches \texttt{\textbackslash TFPTdatestamp} without the date). \texttt{scripts/zenodo\_upload.py}
  and \texttt{build.sh zenodo}/\texttt{zenodo-publish} use this label on Zenodo; cursor rules extended
  for when \texttt{zenodo\_description.html} must move with deposit-facing changes.
\end{itemize}

\subsection*{2026-06-12 (Zenodo API upload workflow)}
\begin{itemize}
\item \textbf{Automated Zenodo versioning.} Added \texttt{scripts/zenodo\_upload.py} and
  \texttt{.github/workflows/\allowbreak zenodo-release.yml}: creates a new draft version of record
  \texttt{20579275} (DOI \texttt{10.5281/\allowbreak zenodo.\allowbreak 20579275}), uploads the ten active paper PDFs,
  refreshes \texttt{zenodo\_description.html}, bumps the version from \texttt{tex-artefacts/version.tex},
  and optionally publishes via GitHub Actions (\texttt{ZENODO\_TOKEN} secret).
\end{itemize}

\subsection*{2026-06-12 (Overleaf shadow mirror: tfpt5-shadow)}
\begin{itemize}
\item \textbf{One-way GitHub mirror for Overleaf sync.} Added \texttt{scripts/export-shadow.sh} and
  \texttt{.github/workflows/shadow-sync.yml}: on every push to \texttt{main}, a filtered copy is pushed to
  \texttt{sthamann/tfpt5-shadow} (papers, \texttt{tex-artefacts/}, \texttt{figures/},
  \texttt{verification/}, \texttt{experiments/}; excludes \texttt{\_archive/}, \texttt{website/}, all
  \texttt{*.pdf}, \texttt{.cursor/}). $\sim$270 files / $\sim$3\,MB --- within Overleaf GitHub-sync limits.
\end{itemize}

\subsection*{2026-06-12 (origin\_theory style alignment + box reduction)}
\begin{itemize}
\item \textbf{Fewer boxes, embedded in text.} \texttt{origin\_theory} from $22$ to $16$ boxes: the
  narrative/interpretation callouts (``Why the interpretation is internally consistent'', ``Dependency
  chain of the birefringence test'', ``The precise reformulation'', ``The three theses honestly graded'',
  ``The whole story'', ``One-line summary'') become run-in bold prose; the boxed reformulation becomes a
  \texttt{keyeq}. The exact result keyboxes (\vref{v53}--\vref{v56}, \vref{v101}, \vref{v105},
  \vref{v113}, \ldots) and the master-principle / Seam--Horizon target boxes are kept.
\item \textbf{Colour-marked module references + marker hygiene.} \texttt{\textbackslash vref} applied to
  the inline \texttt{vN} references; stale literal \texttt{[A]}/\texttt{[I]/[L]} markers in running text
  replaced by the 4-class \mO/\mE.
\end{itemize}

\subsection*{2026-06-12 (tfpt\_5 / horizon / research-contracts pass + build hardening)}
\begin{itemize}
\item \textbf{Forked document-set box removed (horizon).} \texttt{tfpt\_horizon\_readouts} carried a
  hand-written, \emph{stale} copy of the document-set card (``five short documents'', missing
  \texttt{tfpt\_5}) \emph{and} the canonical \texttt{\textbackslash input\{tex-artefacts/tfpt\_docset\}};
  the fork is deleted so the single-source card (all five papers $+$ three companions) appears once.
\item \textbf{Fewer boxes, embedded in text.} Narrative/result callouts converted to run-in bold prose
  (with the \texttt{\textbackslash veri\{\}} citation moved out of the bold title into the body):
  \texttt{tfpt\_horizon\_readouts} from $22$ to $7$ boxes (the ten-box ``clock'' wall becomes prose);
  \texttt{tfpt\_research\_contracts} from $19$ to $10$ (the nine progress/result winboxes become prose,
  the named-theorem keyboxes kept); \texttt{tfpt\_5\_redteam} from $10$ to $9$ (the outcome summary; the
  per-target verdict boxes are kept as the structured red-team output).
\item \textbf{Colour-marked module references + marker hygiene.} \texttt{\textbackslash vref} applied to
  the inline \texttt{vN} references in all three documents; the horizon ``Scope/typing'' marker line and a
  stale literal \texttt{[A]} in the research contracts updated to the 4-class markers.
\item \textbf{Build hardening.} \texttt{build.sh} now removes a document's \texttt{.aux}/\texttt{.toc}/%
  \texttt{.out} \emph{on failure}, so a half-written cross-reference file from a crashed compile cannot
  poison the next build; artefacts are still kept on success.
\end{itemize}

\subsection*{2026-06-12 (fourth round: the Calder\'on transfer answered --- the BFK split, \vref{v151})}
\begin{itemize}
\item \textbf{R3: the Calder\'on/DtN kernel is conically clean (\vref{v151}).} Reflection
  doubling derives that the Kac corner constant is boundary-condition independent
  ($C_N=C_D$), so by the Burghelea--Friedlander--Kappeler gluing ledger the conical
  deficit of the two-sided Calder\'on jump determinant \emph{vanishes identically}
  ($C_{\mathrm{cone}}(\gamma)-2C_D(\gamma/2)=0$): the seam-reduced effective action
  inherits the \vref{v150} EH form \emph{verbatim}, with all of it localised in the
  \emph{local} half-space determinants --- the ``Calder\'on version'' demanded by
  \vref{v150} needs no separate derivation. \texttt{SEAM.THEOREM.01} narrows to the
  $q(A_3)$ normalisation plus the standing kernel premise; the gate stays \mO\ (ledger
  \texttt{SEAM.EHMODEL.02}).
\item \textbf{Bookkeeping.} Suite at $151$ modules, all green; Wolfram extension
  $218/218$; intro/README/\texttt{origin\_theory}/\texttt{next.txt} moved together.
\end{itemize}

\subsection*{2026-06-12 (third round: both normals anchor data; the R3 mechanism exists, \vref{v149}--\vref{v150})}
\begin{itemize}
\item \textbf{R4$'$: both dual normals are anchor data (\vref{v149}).} In the cusp frame
  the torsion normal pairs to $(6,3,5)=(p_2,p_0,e_2)(a)$ --- one anchor invariant per
  $Q_+$ line (the cusp matrix is unimodular, so this determines $n$ uniquely); with
  $d=\tfrac32a-2\cdot\mathbf1$ the dual normal pair is anchor data through and through.
  Equivalences to the $(2,8,121)$ frame data and the $w_0$-lift exact. R4$'$ residue $=$
  \emph{one} discrete assignment (ledger \texttt{GATE.UWALL.14}).
\item \textbf{R3: the mechanism exists at the gapped-model level (\vref{v150}) --- the
  first movement on \texttt{SEAM.THEOREM.01}.} The conical heat-trace deficit is exact
  and $t$-independent (Cheeger image sum $(N^2{-}1)/(12N)$); for a \emph{gapped}
  operator the $\zeta$-regularised replica variation is \emph{finite and
  cutoff-independent}, $\Delta\log\det'=2C(\gamma)\ln m$, and its linearisation is the
  Einstein--Hilbert form $(\ln m/12\pi)\int\!\sqrt gR$. The \vref{v73} normalisation
  becomes one exact target equation: $k=\cthree/2\Leftrightarrow\ln m=\tfrac34=q(A_3)$
  (audit, not asserted). Remaining: the Calder\'on (boundary) version and that
  normalisation --- the gate narrows but stays \mO\ (ledger \texttt{SEAM.EHMODEL.01}).
\item \textbf{Bookkeeping.} Suite at $150$ modules, all green; Wolfram extension
  $217/217$; status surfaces (intro reductions $+$ card, \texttt{origin\_theory},
  contracts, \texttt{next.txt}, website) moved together.
\end{itemize}

\subsection*{2026-06-12 (R1--R5 second round: every class at its floor, \vref{v145}--\vref{v148})}
\begin{itemize}
\item \textbf{R4$'$: the pairing values are atom identities (\vref{v145}).} Reading the
  \vref{v139} lift structurally ($n=w_0(\sigma)+|\mu_4|e_3$, $w_0=$ the $A_3$ exponent
  duality), all three pairings become atom arithmetic --- including the \emph{new}
  closure $|\mu_4|+\gcar=\Nfam^2$ ($4{+}5{=}9$, $\sigma\perp w_0(a)$) and
  $\|\sigma\|^2=110=|\Z_2|\gcar\|\mathrm{Pl}(K)\|_1$. R4$'$ $=$ derive \emph{one} map
  (ledger \texttt{GATE.UWALL.13}).
\item \textbf{R5: the M\"obius $D_4$ realisation (\vref{v146}).} The \emph{full}
  dihedral symmetry $\langle z{\mapsto}iz,\,z{\mapsto}1/z\rangle$ of the seam curve acts
  on $H^1$ exactly as the integer model: $\iota^*$ is the exponent duality with parity
  $+1$ on the self-conjugate line ($=T_A$ in the cusp basis, glue-swap parity), and
  $\Sigma$ is the $\delta\iota$ class --- the premise reduces to the module
  identification itself (ledger \texttt{FLAV.QGEO.07}).
\item \textbf{R1: the clock is a Gaussian zero-mode integral, and the bend is
  det$'$-clean (\vref{v147}).} Variance ratio $(1-\alpha)$ (forced by norm $=$ area)
  gives the Born-squared ratio $(1-\alpha)^{p_2}$, the $\ln$ series \emph{is} the
  \vref{v127} ring sum; the two quantum weights share \emph{one} Nariai geometry, so the
  bend $\log_{3/2}3$ carries no determinant correction --- the \vref{v144} obstruction is
  localised to the $\alpha=0$ reference (ledger \texttt{HOR.CLOCK.13}).
\item \textbf{R2: the NS/R sector census (\vref{v148}).} The untwisted (Neveu--Schwarz)
  module carries only the \emph{even} discriminant classes (integer weights), so the odd
  $\mu_4$ simple currents have zero NS support --- they are Ramond modules; the R
  zero-mode module ($256$) splits $128{+}128$ into the odd sectors of the \emph{two}
  Lagrangian glues: choosing the glue \emph{is} choosing the R-projection
  ($248=120_{\mathrm{NS}}{+}128_{\mathrm R}$); the one remaining net statement is
  irreducibly twisted-sector (ledger \texttt{GATE.METRIC.10}). \emph{Correction note
  (same day):} the first version of \vref{v148} graded the Ramond labels by the sum
  $q_D{+}q_A$ (not the glue label) and called that module untwisted; the census was
  rewritten as above --- conclusion unchanged, support corrected, the R-sector sheet
  split is new.
\item \textbf{Bookkeeping.} Suite at $148$ modules, all green; Wolfram extension
  $215/215$ (README $+$ \texttt{GATE.WOLFRAM.02} $+$ website counter in lock-step);
  status surfaces (intro card, \texttt{tfpt\_1}, \texttt{origin\_theory} third update,
  \texttt{next.txt}) moved together.
\end{itemize}

\subsection*{2026-06-12 (external review integrated: $\Lambda$ typing, marker migration, website parity)}
\begin{itemize}
\item \textbf{$\Lambda$ normalisation made unambiguous.} The external review flagged the
  adjacent reduced/unreduced displays in \texttt{origin\_theory} as a type trap (the
  formulas were individually correct --- $\bar M_{\mathrm{Pl}}$ vs $M_{\mathrm{Pl}}$ ---
  but easy to misread). Both normalisations are now shown explicitly side by side with
  their order counts ($3/(4\pi^2)\Rightarrow120.147$ reduced;
  $3/(256\pi^4)\Rightarrow122.948=119.028+3.920$ unreduced) plus a typing note.
\item \textbf{Stale references cleaned.} ``How each of the seven papers simplifies''
  $\to$ ``How the legacy layers simplify (bridge map)'' with the lead-in ``(Paper 6)''
  reference replaced by the scalaron-reheating chain (\vref{v86});
  ``(Paper\textasciitilde6/7)'' in the \texttt{tfpt\_3} bridge table reworded; the
  \texttt{tfpt\_1} ``single remaining geometric input (H2)'' passage and the
  \texttt{tfpt\_2} ``single remaining input (U)'' passage carry dated status updates
  pointing at the current decomposition (\vref{v118}--\vref{v122}, \vref{v139},
  \vref{v141}, \vref{v142}, \vref{v75}).
\item \textbf{Marker migration completed in the shared figures.} The claim stack,
  anchor cockpit, $E_8$ glue, $2/3$ motif and $K_5$ figures
  (\texttt{tex-artefacts/tfpt\_figures.tex}) now show the four public classes
  \mE/\mC/\mO\ instead of the legacy $[A]/[I]/[L]/[B]/[P]/[R]$ badges.
\item \textbf{Red-team front table pulled to the final state.} The Target-A residual
  column now states the one remaining statement (boundary-net holomorphy $+$ $c{=}8$
  $\Leftrightarrow$ index-$4$ inclusion; \vref{v83}/\vref{v87}/\vref{v89}, Lie-level
  realisation \vref{v143}); the historical three-residual form is kept below, dated.
\item \textbf{Website parity.} The Red Team document is now a first-class entry
  (\texttt{papers.ts} number 5, slug \texttt{redteam}) and the changelog PDF a download
  row; Appendix H / Origin Theory / Research Contracts are labelled \emph{companions}
  (never ``Paper 5--7''); the marker system on every website surface migrated to
  $[E]/[C]/[O]/[X]$ (fine types named in prose; the script index keeps quoting the
  scripts' internal fine-grained typing); the verification page counters are live
  ($144$ checks generated from the registry via \texttt{lib/suite.ts}, Wolfram
  $116/116+211/211$ --- now guarded by the sync audit) and the reproduce block matches
  the current pipeline. The \texttt{papers.ts} section bodies of the affected papers
  carry the \vref{v141}--\vref{v144} outcomes (sheet question: deck derived; $G_{net}$:
  Lie-level realisation; resummed clock: in-family det-ratio cancellation; selector
  triangle: two line pairings).
\item \textbf{Not adopted} (recorded for transparency): the review's narrative
  reframings (anchor-algebra trilogy, ``one seam clock'' framing, one-page structure)
  and the front-matter/status-card layout changes are editorial decisions left to the
  authors; the claimed $\Lambda$ \emph{error} was in fact a correct-but-treacherous
  notation switch (see above).
\end{itemize}

\subsection*{2026-06-12 (R1--R5 attack round: four residual classes sharpened, \vref{v141}--\vref{v144})}
\begin{itemize}
\item \textbf{R5 closed at the discrete level (\vref{v141}, deck selection theorem).} The
  \vref{v140} $\Z_3$ choice is \emph{derived}: the established integer deck $G=T_A\Sigma$
  (\vref{v97}/\vref{v98}) pairs the $Q_+{=}1$ cusp line with the self-conjugate character
  $2$, so only the sheet-twisted assignment $(2,3,1)=\mathrm{chars}(-U)$ survives; the cusp
  exponential $i^{Q_+}$ is excluded (same spectrum, wrong grading pairing). Explicit
  conjugacy constructed; under $k\to-k$ only the established sheet $\Z_2$ flips.
  Consequence: Euler grading $=Q_+\!\circ\rho$. \texttt{GATE.QGEO} keeps only its
  realisation premise --- no discrete freedom left (ledger \texttt{FLAV.QGEO.06}).
\item \textbf{R4$'$ narrowed: three pairings $\to$ two (\vref{v142}, frame integrality).}
  Integer covectors in the $(\mathbf1,a,\sigma)$ dual frame form an index-$11$ sublattice
  ($x-3y+z\equiv0$ mod $11$; the index \emph{is} $\|\mathrm{Pl}(K)\|_1$); with
  $(x,y)=(|\Z_2|,\mathrm{rank}\,E_8)$ the $\sigma$-pairing is forced $\equiv0$ mod $11$,
  and primitivity forces the line parameter even. Cramer reductions for both line pairings
  recorded as restructuring (ledger \texttt{GATE.UWALL.12}).
\item \textbf{R2 realised at the finite Lie level (\vref{v143}, graded Frobenius).} The
  $\Z_4$-graded hull carries exact coset duality ($-C_1=C_3$; Killing pairing nondegenerate
  per $g_k\times g_{-k}$), the glue average is exactly the carrier projector (index $4$),
  and each glue sector is one Weyl orbit (simple currents, fusion $=\mathbb C[\Z_4]$) ---
  the \vref{v125} Q-system realised by the hull; residue $=$ one conformal-net statement
  (ledger \texttt{GATE.METRIC.09}).
\item \textbf{R1's det-ratio step derived in-family (\vref{v144}).} $e_2$-rigidity of the
  traceless SdS cubic gives $r_br_c=1-\Delta^2/3$ exactly; with the \vref{v132} anomaly the
  non-zero-mode determinant ratio is $(1-\Delta^2/3)^{4/3}$ --- no first-order term in the
  horizon split (the \vref{v131} cancellation derived, not assumed); deficit coefficient
  $\tfrac{32}{27}=|\mu_4|(\tfrac23)^3$ (audit). Finite-weight absorption stays \mC\ with the
  $6\to\tfrac{14}3$ obstruction stated sharply (ledger \texttt{HOR.CLOCK.12}).
\item \textbf{R3 attempted, honestly unchanged.} No defensible computation landed for the
  seam-determinant$\to$EH step (\texttt{SEAM.THEOREM.01}); the gate keeps its \mO\ typing
  untouched.
\item \textbf{Wolfram mirror extended} to \vref{v141}--\vref{v144}: extension file now
  $211/211$ (\texttt{GATE.WOLFRAM.02} and the wolfram README updated in lock-step); Python
  suite at $144$ modules, all green.
\end{itemize}

\subsection*{2026-06-12 (sync infrastructure: single-source script index, content maps, one audit)}
\begin{itemize}
\item \textbf{Single-source script index.} The master script$\to$check table
  (\texttt{tex-artefacts/verification.tex}) and the website
  \texttt{ScriptIndex.tsx} are now \emph{generated} from one registry
  (\texttt{script\_registry.csv} $+$ \texttt{script\_clusters.csv} in
  \texttt{verification/}) by \texttt{make\_script\_index.py}; both targets carry a
  generated-file header and are never edited by hand.
\item \textbf{Content maps without splitting the papers.}
  \texttt{verification/make\_docs\_map.py} generates \texttt{docs\_map.csv} (every
  paper section with line range, the \texttt{vN} scripts cited there, a content hash
  and a last-changed date) and \texttt{website\_map.csv} (which website file mentions
  which scripts/documents) --- the machine-readable enumeration of all sync surfaces.
\item \textbf{One sync audit.} \texttt{verification/audit\_sync.py} bundles and
  extends the previous loose shell checks, now in \emph{both} directions: suite
  $\leftrightarrow$ \texttt{run\_all.py} $\leftrightarrow$ registry
  $\leftrightarrow$ ledger; every script cited in a paper \emph{body} (the master
  index alone no longer counts); no stale \texttt{\textbackslash veri}/\texttt{\textbackslash vref}
  targets; every new module mentioned in this changelog; website mirror byte-identical
  (PDFs, scripts, \texttt{release.ts} hashes, version stamps); wolfram counts; overfull
  boxes. Frozen exceptions live in \texttt{audit\_baseline.json} (remove-only).
\item \textbf{Build pipeline.} \texttt{build.sh} gains \texttt{gen} /
  \texttt{website} / \texttt{audit} / \texttt{release} steps; \texttt{notes} now
  regenerates the single-source surfaces first; \texttt{website} copies all active
  PDFs (now incl.\ \texttt{tfpt\_5\_redteam.pdf} and \texttt{changelog.pdf}, with new
  \texttt{release.ts} entries) and the \texttt{vN} scripts, and stamps version, date
  and git revision into \texttt{website/lib/version.ts} (shown in the site header) and
  \texttt{release.ts}.
\item \textbf{Citation gaps closed.} The audit immediately found three scripts cited
  only in the master index: \vref{v17} and \vref{v85} are now cited in their
  \texttt{tfpt\_2} sections (hexagonal resolvent; master cover), and two short
  \texttt{\textbackslash veri\{v19\}} citations were expanded to the full script name.
  \vref{v91} (spine tetrahedron) had no paper section at all --- it is now integrated:
  a keybox in \texttt{tfpt\_3} (``Three views of one spine'': anchor closure, edge/face
  products, volume $120$, $K_6$ negative control, the tautology/sub-grammar caveats) and
  a closing note in the \texttt{tfpt\_1} Spine Quotient Lemma; the
  \texttt{ARCH.SPINE.01} ledger location is corrected to \texttt{tfpt\_1;tfpt\_3} and the
  baseline exception list is empty again.
\item \textbf{Rules.} \texttt{.cursor/rules} updated (\texttt{tfpt-workflow},
  \texttt{website-sync}) and a new \texttt{sync-maps} rule added describing the agentic
  procedure: \emph{regenerate} the maps first, enumerate the affected surfaces from
  them, audit as the exit gate. The mirror map (\texttt{website\_map.csv}) also covers
  the root \texttt{README.md} and \texttt{next.txt} (bare \texttt{vN} ids resolved to
  full script names), and both files are named explicitly as status surfaces that move
  with every finding.
\end{itemize}

\subsection*{2026-06-12 (tfpt\_3 / tfpt\_4 style alignment + box reduction)}
\begin{itemize}
\item \textbf{Shared header/footer on tfpt\_3.} \texttt{tfpt\_3\_e8\_audit\_bootstrap} dropped its custom
  \texttt{\textbackslash footmarkers} footer (the post-collapse four-\mE\ artefact) and inherits the
  shared \texttt{tfpt\_style} header/footer with the version stamp; the box-orphan \texttt{needspace}
  guards are kept.
\item \textbf{Fewer boxes, embedded in text.} Narrative/commentary callouts converted to run-in bold
  paragraphs (boxed one-line formulas to \texttt{keyeq}): tfpt\_3 from $39$ to $27$ boxes (e.g.\
  ``Purpose and discipline'', the five ``(i)--(v)'' audit-lemma boxes, ``Net'', ``The connection in one
  sentence'', ``The unification'', ``The question and the honest answer'', ``Net: two axioms''); tfpt\_4
  from $18$ to $7$ (the seven-box Koide stack and the two dark-matter conjecture boxes become prose). The
  per-item ``Honest status of \ldots'' keyboxes are kept --- tfpt\_4 is the status authority for the
  frontier.
\item \textbf{Colour-marked module references.} \texttt{\textbackslash vref} applied to the inline
  \texttt{vN} references in tfpt\_3 and tfpt\_4 (TikZ node names excluded).
\item \textbf{Marker hygiene.} A stale literal \texttt{[P]} in tfpt\_4 (Koide flow-time) replaced by the
  4-class \mC; status tables checked against the ledger.
\end{itemize}

\subsection*{2026-06-12 (tfpt\_1 / tfpt\_2 style alignment + box reduction)}
\begin{itemize}
\item \textbf{Shared header/footer everywhere.} \texttt{tfpt\_1\_architecture\_e8} dropped its custom
  \texttt{\textbackslash footmarkers} footer (which after the marker collapse showed four redundant
  \mE) and now inherits the shared \texttt{tfpt\_style} header/footer with the version stamp, identical
  to every other document.
\item \textbf{Fewer boxes, embedded in text.} The narrative/commentary callouts of both documents are
  converted to run-in bold paragraphs (and the boxed one-line formulas to the colour-marked
  \texttt{keyeq}): tfpt\_1 from $21$ to $14$ loud boxes ($+3$ \texttt{keyeq}); tfpt\_2 from $52$ to $43$
  (e.g.\ ``In one sentence'', ``The one-paragraph version'', the four ``Sharpening'' notes, ``What the
  simplification means net'', ``The disciplined main statement'', ``What improves\ldots'', ``Scope and
  honesty''). Only genuine results / theorems / gates keep a box.
\item \textbf{Colour-marked module references.} \texttt{\textbackslash vref} now also colours the inline
  \texttt{vN} references throughout tfpt\_1 and tfpt\_2 (TikZ node names accidentally matching the
  pattern were excluded).
\item \textbf{Status currency.} tfpt\_2's inflation-pivot table gains the \vref{v86} scalaron-reheating
  point ($N_\star{=}51.4\Rightarrow n_s{=}0.9611$, $r{=}0.0045$, $A_s$-disfavoured) and states the
  band-of-record explicitly, matching \texttt{COSMO.NSTAR.01} and the introduction; the box is re-typed
  \mC. The other status tables were checked against the ledger and are current under the 4-class markers.
\end{itemize}

\subsection*{2026-06-12 (marker simplification to 4 classes + status reconciliation)}
\begin{itemize}
\item \textbf{Four-class display markers.} The reader-facing marker system is collapsed from eleven
  symbols to four: \mE\ exact / machine-proven (identity, Lie/lattice, formalised, numerical FP),
  \mC\ conditional (physical / bridge / readout under named hypotheses), \mO\ open / axiom, and \mX\
  kill test. \texttt{tex-artefacts/tfpt\_style.tex} defines \texttt{\textbackslash mE/\textbackslash
  mC/\textbackslash mO/\textbackslash mX} and keeps the legacy \texttt{\textbackslash tI \ldots
  \textbackslash tX} names as aliases that render their class. All marker call-sites across the nine
  documents and the shared fragments were rewritten, collapsing same-class combinations (e.g.\
  \texttt{[I]/[L]}\,$\to$\,\mE, \texttt{[N]/[P]}\,$\to$\,\mE/\mC). The fine-grained per-claim type
  (Axiom / Formal / Lattice / Numerical / Identity / Physical) is unchanged in
  \texttt{status\_ledger.csv} --- the single source of truth --- so no fidelity is lost. The marker key,
  badge bar, README marker table and the workflow rule were updated to match.
\item \textbf{Status tables reconciled against the ledger.} The introduction's inflation/$N_\star$ rows
  are made consistent with \vref{v86}/\texttt{COSMO.NSTAR.01}: $r$ and $n_s$ are shown as the frozen
  \emph{bands} over $N_\star\in[50,60]$ with the scalaron-reheating conditional point $N_\star{=}51.4$
  ($n_s{=}0.9611$, $r{=}0.0045$), replacing the stale point values $N_\star{=}55$ (predictions table)
  and $N_\star\simeq57$ (residual card); the closure-ledger inflation row is re-typed \mE\,$\to$\,\mC
  (conditional on $M_{\rm Star}{=}M_{\rm scal}$ $+$ reheating), matching the other two tables and the
  ledger \texttt{[P]} typing.
\end{itemize}

\subsection*{2026-06-12 (version system, predictions/K5, readability pass B3)}
\begin{itemize}
\item \textbf{Authors, auto-date and auto-version on every paper.} New single source
  \texttt{tex-artefacts/version.tex} defines \texttt{\textbackslash TFPTauthors} (Stefan Hamann,
  Alessandro Rizzo), a curated \texttt{\textbackslash TFPTversion}, and a title/footer date stamp
  (\texttt{\textbackslash today} $+$ version $+$ revision). \texttt{build.sh} writes the auto build
  revision (git commit count) into the gitignored \texttt{tex-artefacts/version-auto.tex}, so every
  document's title page and page footer carry author, date and \texttt{v\TFPTversion\,(rev~N)}
  automatically. All nine active documents and \texttt{changelog.tex} now set
  \texttt{\textbackslash author\{\textbackslash TFPTauthors\}}.
\item \textbf{Builder keeps build artefacts.} \texttt{build.sh} no longer deletes the
  \texttt{.aux/.log/.out/.toc} after a successful build (the \texttt{.log} is needed for the
  overfull-box audit and the \texttt{.aux/.toc} for correct cross-references on the next incremental
  build).
\item \textbf{Predictions table outsourced.} The running/upcoming-experiment predictions table is moved
  from \texttt{introduction.tex} into the shared fragment \texttt{tex-artefacts/predictions.tex}
  (\texttt{\textbackslash input} in the predictions section).
\item \textbf{K5 figure fixed.} The \texttt{\textbackslash TFPTactionkfive} mnemonic ($K_5$ on the five
  carrier slots) is redrawn so the complete graph and the Pascal-row reading list sit side by side
  instead of overlapping.
\item \textbf{Colour-marked script references.} New \texttt{\textbackslash vref} macro colours inline
  module references (e.g.\ \vref{v108}--\vref{v113}, \vref{v49}/\vref{v71}) in the introduction,
  predictions and verification fragments, matching the blue of the \texttt{\textbackslash veri}
  citation, so machine-checked references are visible at a glance.
\item \textbf{Lighter, non-breaking, embedded boxes.} The \texttt{tcolorbox} families are restyled to a
  light tint $+$ thin frame $+$ light title band with dark coloured title (no heavy
  white-on-saturated bars); a neutral \texttt{navbox} carries the document map and a colour-marked
  \texttt{keyeq} sets off load-bearing display formulas. The introduction's callouts use the
  non-breaking variants (\texttt{keyboxnb}/\texttt{winboxnb}/\texttt{gapboxnb}) so no box splits across
  a page, and the shared status card is non-breaking.
\item \textbf{Readability / sectioning.} The dense run-in prose of the introduction is broken into
  \texttt{\textbackslash subsection*} headings (In plain words; one anchor and $E_8$ as a compiler
  hull; the companion documents; the compact status formula; the hard reduction; the Pascal action
  grammar; the closure ledger) with added whitespace.
\item \textbf{Orphan results linked to scripts.} The Glue theorem, the ``Reduction in one line'' and the
  fermion-spectrum callouts now carry inline \texttt{\textbackslash veri\{\}} citations
  (\vref{v1}, \vref{v6}/\vref{v14}/\vref{v23}, \vref{v18}/\vref{v20}/\vref{v46}).
\end{itemize}

\subsection*{2026-06-12 (tex-artefacts refactor + introduction visual pass B2)}
\begin{itemize}
\item \textbf{Shared imports moved to \texttt{tex-artefacts/}.} The shared, imported-only TeX
  fragments (\texttt{tfpt\_style.tex}, \texttt{tfpt\_figures.tex}, \texttt{tfpt\_docset.tex},
  \texttt{tfpt\_status.tex}) now live in a dedicated \texttt{tex-artefacts/} folder; all nine active
  documents \texttt{\textbackslash input} them via \texttt{tex-artefacts/<name>} (and
  \texttt{tfpt\_style} loads \texttt{tex-artefacts/tfpt\_figures}). \texttt{changelog.tex} stays at the
  repo root because it is also a standalone \texttt{build.sh notes} deliverable. The
  \texttt{make\_manifest.py} \texttt{TEX} list and the workflow rule were updated to the new paths.
\item \textbf{Master script index outsourced (\texttt{tex-artefacts/verification.tex}).} The long
  \texttt{vN}$\to$check table is moved out of \texttt{introduction.tex} into the shared fragment
  \texttt{tex-artefacts/verification.tex} (\texttt{\textbackslash input} in the verification appendix);
  the paper-consistency audit now also reads that file, so every registered script stays cited exactly
  once.
\item \textbf{Introduction box reduction (B2).} The introduction's eleven \texttt{keybox}es are reduced
  to the single headline ``In one sentence'' card; the explanatory keyboxes (\emph{In plain words},
  \emph{Sharper still}, \emph{compact status formula}, \emph{hard reduction}, \emph{Cosmology Pascal},
  \emph{$E_6{\times}A_2$}, \emph{closure ledger}, \emph{Plausibility balance}) are converted to inline
  run-in paragraphs, the \emph{Glue theorem} is re-typed as a \texttt{winbox} (a result, not a claim),
  and the explanatory \emph{plausible}/\emph{follows next} \texttt{winbox}es become prose. The loud
  boxes now carry only genuinely load-bearing callouts (one \texttt{keybox}, five \texttt{winbox}es,
  one \texttt{gapbox}) plus the two shared orientation cards.
\item \textbf{Document-count consistency.} The introduction's document map gained the missing
  \texttt{tfpt\_5\_redteam} row; ``seven/eight companion documents'' and the ledger ``six documents''
  wording are corrected to the true count (nine active documents); \texttt{README.md} (``10 ok'', 140
  scripts) and the workflow rule (``9 docs'') are reconciled.
\end{itemize}

\subsection*{2026-06-12 (visual pass: box reduction B1)}
\begin{itemize}
\item \textbf{Box reduction (B1).} The $26$ non-load-bearing aside boxes (audit / recorded /
  interpretation: \texttt{auditbox}/\texttt{audbox}/\texttt{intbox}/\texttt{resbox}/\texttt{roadbox})
  across tfpt\_1, tfpt\_2, tfpt\_3 and \texttt{origin\_theory} are converted to inline bold run-in
  paragraphs --- the reviewer's prescription that an audit fingerprint must not carry the same visual
  volume as a theorem. The loud box families are now only \texttt{keybox} (claim), \texttt{winbox}
  (result) and \texttt{gapbox} (open/caveat).
\end{itemize}

\subsection*{2026-06-12 (visual pass: shared figures, badges, marker typology)}
\begin{itemize}
\item \textbf{Shared figure library \texttt{tfpt\_figures.tex}} (\texttt{\textbackslash input} by
  \texttt{tfpt\_style}): reusable TikZ macros for the architecture \emph{claim stack}
  (\texttt{\textbackslash TFPTclaimstack[zone]}, B3), the \emph{anchor cockpit} $a=(1,1,2)$ (B4), the
  \emph{$E_8$ glue} diagram (B5), the \emph{$2/3$ motif map} (B6) and the \emph{$K_5$ action lattice}
  (B7). The claim stack and a marker \emph{badge bar} are now shown near the front of \emph{every}
  document, each highlighting that document's layer; the topical figures are placed in their natural
  homes (cockpit + $K_5$ in the introduction, cockpit + glue in tfpt\_1, motif in the horizon note).
\item \textbf{Marker typology (A2).} \texttt{tfpt\_style} adds the sharper sub-types
  \mE\ (exact algebra), \mE\ (exact number), \mC\ (readout / standard physics in TFPT units) to the
  existing \mC\ (bridge) and \mX\ (kill test); the marker key and the new \texttt{\textbackslash TFPTbadges}
  bar show the full typology. (Inline body markers retain \mE\ where they are genuine exact identities.)
\end{itemize}

\subsection*{2026-06-12 (review pass on list.txt)}
\begin{itemize}
\item \textbf{Claim hygiene (review section A).} The introduction's one-sentence claim is softened from
  ``derives all constants'' to ``constructs a discrete compiler; physical readouts run through named,
  status-typed bridges''; the ledger zombie in \texttt{FLAV.QRATIO.01} is removed (the statement no longer
  says ``stays [P]'' --- ratios are \mE\ closed on the derived stratum, only the absolute scale stays \mO,
  with an explicit forbidden-wording note); the seam misalignment is written explicitly as
  $\varepsilon=\tfrac34\phiz=\cthree+36\cthree^4$ (leading $\cthree$, fourth-order puncture correction
  exact); $\theta_{12}$ has a single prediction of record $0.306747$ with the seam/non-linear values typed
  as scheme diagnostics; JUNO's first $59.1$-day result ($0.3092\pm0.0087$, compatible, precision pending)
  is recorded and NuFIT~6.0 is marked the pre-JUNO baseline; the ACT~DR6 birefringence hint carries a
  systematics caveat (not a validation target); CODATA-2022 is dated; the null-model figure is moved out
  of the main text and typed as a grammar-internal bound. ``Complete solutions of the five open
  questions'' becomes ``Closure status of the five former open questions''.
\item \textbf{Interface language unified (review sections A5/C2/C3/C6/C7/C8).} The live residual is stated
  everywhere as $v_{\mathrm{geo}}\oplus G_{\mathrm{net}}\oplus F_{\mathrm{transfer}}$ (historical
  $U_{\mathrm{wall}}/G_{\mathrm{metric}}/F_{\mathrm{frontier}}$ kept only for ledger continuity);
  \texttt{tfpt\_research\_contracts} is retitled and its recommended order rewritten (selector-triangle
  pairings $\to v_{\mathrm{geo}}\to G_{\mathrm{net}}$); $F_{\mathrm{transfer}}$ is named as one missing
  functor with Koide/$\eta_B$/axion/$m_p/m_e$ as its four instances; full QG closure is framed as a
  certification layer, not a prerequisite. Document numbering aligned with file names (the Red Team paper
  is now in the canonical set; document~$N\equiv$ \texttt{tfpt\_N}). Website mirrored throughout
  (\texttt{papers.ts}, \texttt{predictions.ts}, \texttt{faq.ts}, \texttt{glossary.ts}, \texttt{OpenGates},
  \texttt{Hero}, orientation components).
\end{itemize}

\subsection*{2026-06-12 (later)}
\begin{itemize}
\item \textbf{Shared style and central status artifact.} Two new single-source fragments:
  \texttt{tfpt\_style.tex} (the canonical palette, status markers, marker key, \texttt{\textbackslash veri}
  reference, the four tcolorbox families with back-compat aliases, and one running header/footer)
  is now \texttt{\textbackslash input} by all eight documents --- the per-paper duplicated preambles
  are gone; and \texttt{tfpt\_status.tex} (``TFPT status at a glance'') gives one canonical overall-status
  card imported near the front of every document, replacing the divergent per-paper status statements.
  Both registered in \texttt{build.sh} and the manifest \texttt{TEX} list.
\end{itemize}

\subsection*{2026-06-12}
\begin{itemize}
\item \textbf{Margin theorem (v122).} The established frozen selectors ($D_4$ annihilator
  $n=(5,-9,6)$, $\det R=8$, $\det K=4$) pin $R$ uniquely among hexagon matrices
  ($64\to12\to1$); the atom margins become theorems --- H2 introduces no new residual class.
\item \textbf{Inventory update (v123).} Residual table re-pinned post v110--v122: exactly five
  structural classes (R1 clock, R2 index-4 net, R3 EH step, R4$'$ selector establishment ---
  replacing the discharged H2 dictionary --- and R5 $Q$ realisation); R2 carries three loads
  (metric $+$ carrier $+$ QBL: one theorem, three doors).
\item \textbf{Resummed clock $+$ glue Q-system (v124/v125).} R1's bend in closed form:
  $\mathrm{rate}(n)=-p_2\ln(1-n/N_{\mathrm{fam}})$ (pole at $N_{\mathrm{fam}}$ forces the
  three-level spectrum); the index-4 $\mu_4$ extension exists explicitly as a Longo Q-system
  on $\mathbb C[\mathbb Z_4]$ (all Frobenius axioms exact) --- R2 sharpens from ``find'' to
  ``identify''.
\item \textbf{Clock--wall bridge (v126) and ring resummation (v127).} The resummed-clock
  weights are the Mehta--Seshadri parabolic weights ($\operatorname{spec}A_0^\star$);
  $\det(\mathbf 1-A_0^\star)=\tfrac29$ $=$ the entropy curvature; the clock is a
  log-determinant (RPA rings, one tower per hexagon site, coupling $=$ parabolic weight).
\item \textbf{Graded hull (v128).} $E_8$ is a $\mathbb Z_4$-graded Lie algebra over the
  carrier (grading $=$ glue Q-system; exact on all $6720$ root-pair sums); ring multiplicity
  $6$ $=$ sheet-doubled Ginsparg--Perry zero modes. \emph{Notation fix in the same round:}
  the clock factor $6$ is $p_2(a)$, not $2p_2$ --- labels corrected across modules, ledger,
  papers, website (numbers unchanged).
\item \textbf{Entropy power law $\to$ zeta budget (v129--v133).} The clock is
  $\Gamma_n\propto(S_n/S_{dS})^{p_2}$ (Gibbons--Hawking form); $p_2=2h$ with
  $h=N_{\mathrm{fam}}$ from mode counting $+$ the Born rule (v130); the zero-mode norm is the
  area, $\|Y_{1m}\|^2=A/(4\pi)$ exactly (v131); the det-ratio anomaly is the Koide constant,
  $\zeta(0)|_{\det'}=-\tfrac23$ (v132); both $\zeta(0)$ budget routes computed exactly --- the
  reduced seam route carries pure anchor ratios ($-\tfrac43$ $=$ minus the seed gain), the
  naive 4d route ($-\tfrac{109}{45}$) carries no atom (v133).
\item \textbf{Dual anchor $+$ determinant surface (v134/v135).} $d:=a^\top R^{-1}=a^\top
  L^{-1}=(-\tfrac12,-\tfrac12,1)$ with $(1,1,-2)=-2d$ --- the inverse flavor response is the
  Nariai root, invariance exact via Sherman--Morrison (third algebraic flavor--horizon bridge
  leg); $\det M(s,t)=3s(t{+}1)(t{+}2)+t^2+5t+8$ with iso-volume walls at the $\mathbb
  Z_2$/$\mu_4$ atoms, winding line $(8,14,20)$, $\det F=32$, row-budget axes with
  $\mathrm{rowsum}(V)=\operatorname{Spec}(Q_+)$; micro-identities $41=16+25$, $52=16+36$.
\item \textbf{Dual-normal selector, $Q_+$ cohomology, Volkov--Wipf firewall (v136--v138).}
  $(d,n)$ pins $R$ \emph{columnwise} (each column the unique lattice point of the address
  box; kernel $(6,8,7)$); the $A_0^\star$ zero mode carries the spectral normal
  $\sigma=(2,-9,5)$ with a $W(A_3)$ orbit control excluding the naive lift;
  $H^1(\mathbb P^1\setminus\mu_4)=\chi_1\oplus\chi_2\oplus\chi_3$ with degrees
  $(1,2,3)=\operatorname{Spec}(Q_+)=$ the $A_3$ exponents and cusp weights
  $=\operatorname{spec}A_0^\star$; the external full-4d graviton/ghost value $-\tfrac{98}{45}$
  is pinned (arXiv:2506.02142 $=$ Volkov--Wipf hep-th/0003081) and its \emph{edge} part is
  exactly two copies of the reduced seam budget --- R1 typed closed as an edge-sector object.
\item \textbf{Selector triangle $+$ canonical map (v139/v140).} $d=\tfrac32a-2\cdot\mathbf 1$
  is pure anchor data (first selector \emph{derived}); the frame $(\mathbf 1,a,\sigma)$ has
  volume $11$ and $n$ is the unique covector with atom pairings $(2,8,121)$ --- the R4$'$
  residue is three pairings; the $H^1\to$ generation equivariant map exists and is
  Schur-rigid (only sign-twisted $\mu_4$ actions match), so the \texttt{GATE.QGEO} residue
  collapses to one $\mathbb Z_3$ choice.
\item \textbf{Editorial and consistency passes.} Content-currency sweep (superseded
  ``single remaining input'' claims retired across contracts, paper 3, intro, website);
  introduction: self-explanatory title (spells out Topological Fixed-Point Theory), the
  old-version comparison removed throughout, redundant diagrams dropped, the unreadable
  status heatmap removed, the script-index master table converted to a page-breaking
  \texttt{xltabular} (it had silently truncated $\sim$110 rows), status card extended with
  the v134--v140 reductions, predictions table completed (CP phase, cosmic birefringence);
  the canonical document-set box extracted into the shared \texttt{tfpt\_docset.tex}; paper 1
  cleaned of all 35 old-series references, every section now opens with its machine-check
  script references; smaller box fonts across all eight documents; this \texttt{changelog.tex}
  introduced as a dual-mode (standalone $+$ imported) document.
\end{itemize}

\subsection*{2026-06-11}
\begin{itemize}
\item \textbf{External-review integration (v83) and release hygiene.} Manifest
  \texttt{--check} mode and the release rule; holomorphy pins $(E_8)_1$ (the unique even
  unimodular rank-8 lattice theory).
\item \textbf{Sheet diamond and centered form (v94/v95).} All four flavor operators are
  points of one two-parameter surface $M(s,t)$; centered cross $R,L=C\mp U$, $K,F=C\mp V$
  with the cofactor seam normal $n=(5,-9,6)$; documentation pass (``The Sheet Diamond and
  the Winding Line'' in paper 3).
\item \textbf{Horizon/anchor round (v101--v103).} The maximal (Nariai) black hole is the
  anchor: roots $(1,1,-2)$, entropy bound $\tfrac23=|\mathbb Z_2|/N_{\mathrm{fam}}$; one
  repeller/attractor orientation in both sectors; trisection normal form (the canonical
  cosine coordinate).
\item \textbf{Clock/ladder round (v104--v108) $+$ Lean hardening.} The classical Nariai
  clock speaks anchor ($\chi_{\mathrm{clock}}=(\lambda-1)(\lambda+2)$); machine-pinned
  residual inventory; first review validation; quantum-clock target made quantitative;
  Pascal Ladder Theorem ($g=2K+1$ $\Leftrightarrow$ the closure).
\item \textbf{QBL theorem chain (v109--v113).} Sheet-Pairing Lemma; Calder\'on-sheet
  selection (a scalar seam datum exists iff the involution is sheet-odd); Quadratic-Transport
  Theorem (degree exactly 2); Self-Counting Channel (the Pascal closure as an identity);
  quasi-free kernel (one 2-point kernel determines the whole net, rank $=c$) --- the QBL
  input merges with the R2/holomorphy premise; communicated across all status surfaces.
\item \textbf{$U_{\mathrm{wall}}$ made exact (v114--v118).} Torsion normal form and
  $\delta=\tfrac12$ theorem; exact anchor residue $A_0^\star$ (diag $=a/|\mu_4|$,
  off-weights $(8,0,5)/144$); resonance theorem ($M_\infty=\mathbf 1\iff a_{13}=0$, one gauge
  orbit); the holonomy is the exact 24-element $W(A_3)=S_4$; the hypercharge hexagon is the
  sign-twisted family spectrum with the lepton coefficients as resolvent determinants.
\item \textbf{Second review validation $+$ address pinning (v119--v121).} Anchor ratio triad
  $(\tfrac23,\tfrac43,\tfrac53)$; the $121$ audit lemma; the lepton words are the compiler
  atoms $(8,5,3)$ with divmod-hexagon addresses; $R$ is the unique hexagon matrix with atom
  margins and $\det 8$ --- the address table carries zero residual information.
\end{itemize}

\subsection*{2026-06-10}
\begin{itemize}
\item \textbf{B/C/D round closed.} Koide attractor toy model (v93), glue uniqueness (v92),
  the Wolfram extension as the independent second verification path, Lean hardening; papers
  and website synced with the round.
\item \textbf{Content rounds v96--v100.} Sheet conjugation bridge, discriminant dictionary,
  Koide flow time, and the look-elsewhere-corrected numerology null test (v100: joint null
  probability $\le10^{-30.7}$, conditional on the declared grammar).
\end{itemize}

\subsection*{2026-06-09}
\begin{itemize}
\item \textbf{Blind registry frozen (v84).} Machine-enforced prediction registry
  (\texttt{predictions\_frozen.json}): exactly one $\theta_{12}$ number of record before
  JUNO; conditional entries carry their hypotheses by name. Research-contracts document
  added to the set.
\end{itemize}

\subsection*{2026-06-07 / 2026-06-08}
\begin{itemize}
\item \textbf{Compiler-closure consolidation.} The TFPT development is consolidated into the
  current document set with the verification suite (modules v1--v82: $E_8$ glue, carrier
  Pascal, EM fixed point, flavor matrix, cascade, bootstrap, gravity/cosmology, transport,
  masses, registry and gate audits) as the single proof layer; manifests
  (\texttt{manifest.sha256}, \texttt{lean\_manifest.sha256}) as content identity; website
  mirrors the suite (interactive DAG, in-browser script reproducer, script index).
\end{itemize}

\subsection*{2026-04-27}
\begin{itemize}
\item \textbf{Initial commit.} TFPT papers and website baseline: electromagnetic closure and
  flavor transport (UFE bridge, birefringence seed, dyonic intercept), PDF-download
  tracking, accessibility and metadata passes.
\end{itemize}

\ifdefined\ChangelogImported\else
\end{document}
\fi
