% ---------------------------------------------------------------------
%  tfpt_docset.tex -- THE canonical TFPT document-set box.
%  Single source of truth for the document list; \input by the
%  introduction and every paper. Uses only universally available
%  macros (keybox + plain LaTeX math) so it compiles in every doc.
%  Each document adds its own "You are reading ..." line directly
%  after the \input.  Numbering is aligned with the file names:
%  document N == tfpt_N_*, the introduction is the entry point, and
%  R/H/O are the appendix-style companions.
% ---------------------------------------------------------------------
\begin{navbox}[The TFPT document set --- what is treated where]
\textbf{Plain language:} TFPT (Topological Fixed-Point Theory) is a small discrete compiler. Two
inputs --- the seam constant $c_3=\tfrac1{8\pi}$ and the carrier rank $g_{\mathrm{car}}=5$ --- build
$D_5\oplus A_3+\mu_4\Rightarrow E_8$ and read off the Standard-Model skeleton, the constants and the
scale grammar. The series is \textbf{the introduction plus five numbered papers and three companions},
best read in order:
\begin{enumerate}[leftmargin=2.0em,itemsep=1pt,label=\textbf{\arabic*.}]
\setcounter{enumi}{-1}
\item \texttt{introduction} --- reading guide, compiler closure, predictions, the dependency DAG and the
      single proof ledger (\texttt{verification/status\_ledger.csv}). \emph{(entry point)}
\item \texttt{tfpt\_1\_architecture\_e8} --- the two axioms, the derivation map, the EM fixed point
      $\alpha^{-1}$, the $D_5\oplus A_3+\mu_4\Rightarrow E_8$ construction, the QBL theorem chain.
\item \texttt{tfpt\_2\_standard\_model} --- the SM in one $\varphi_0$-ladder formula, flavor from
      parabolic transport (sheet diamond, dual anchor, $Q_+$ cohomology), the worked closures.
\item \texttt{tfpt\_3\_e8\_audit\_bootstrap} --- the seven $E_8$ slices as an audit raster, the cascade
      bridge, the M\"obius bootstrap.
\item \texttt{tfpt\_4\_frontier} --- honest status of $\eta_B$, $m_p/m_e$, Koide, dark matter, full QG.
\item \texttt{tfpt\_5\_redteam} --- the adversarial audit: declared attacks, what survives, what each
      reduces to, and the kill tests.
\end{enumerate}
\noindent\textbf{Companions:} \textbf{R.} \texttt{tfpt\_research\_contracts} --- the open interfaces
$(v_{\mathrm{geo}}, G_{\mathrm{net}}, F_{\mathrm{transfer}})$ as numbered contracts;
\textbf{H.} \texttt{tfpt\_horizon\_readouts} --- Appendix~H (unit-system reframe): one seam constant as
the universal horizon thermal code, the Nariai/anchor surface, the resummed seam clock;
\textbf{O.} \texttt{origin\_theory} --- why no free fundamental number remains (exact core $+$ one
honestly-typed cyclic interpretation).
\end{navbox}
