% ---------------------------------------------------------------------
%  tfpt_status.tex -- THE canonical "status at a glance" card.
%  Single source for the overall theory status; \input near the front
%  of every document so there is ONE status statement, not one per
%  paper.  Requires tfpt_style.tex (keybox, markers).  Detailed,
%  paper-specific status expansions live only where they belong
%  (introduction: five-questions + closure ledger; tfpt_4: frontier
%  table; tfpt_research_contracts: the contracts).
% ---------------------------------------------------------------------
\begin{keyboxnb}[TFPT status at a glance --- read this card the same way in every document]
\textbf{Two inputs, one compiler.} From the boundary constant $c_3=\tfrac1{8\pi}$ (axiom~P1) and the
five-slot carrier $g_{\mathrm{car}}=5$ (axiom~P2) --- jointly the elementary symmetric data of one anchor
$a=(1,1,2)$ --- the discrete compiler $D_5\oplus A_3+\mu_4\Rightarrow E_8$ is \emph{built}, and the
Standard-Model skeleton (gauge group, three families, hypercharges, the flavor matrix), the dimensionless
constants ($\alpha^{-1}=137.0359992$) and the scale grammar are read off as fixed points. The algebraic
core is machine-checked; physical readouts run through \emph{named bridges} whose status is typed below.
\smallskip\\
\noindent\textbf{What is closed, and what genuinely remains.} The discrete/algebraic layer is closed
(\mE); the everything-open residual reduces to \emph{three named interface problems}:
\begin{center}\small
\renewcommand{\arraystretch}{1.18}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Interface} & \textbf{Question} & \textbf{Status} \\
\midrule
$v_{\mathrm{geo}}$ & the one metrology unit ($=1/\sqrt G=m/\mu$); No-Unit Thm: no compiler scale & primitive \mO \\
$G_{\mathrm{net}}$ & simple-current extension $(D_5)_1{\otimes}(A_3)_1{\rtimes}\langle(1,1)\rangle\cong(E_8)_1$ & \mC \\
$F_{\mathrm{transfer}}$ & one functor, four typed interfaces (Koide, $\eta_B$, axion, $m_p/m_e$) & \mC \\
\bottomrule
\end{tabular}
\end{center}
\noindent\textbf{Gravity is parameter-free.} The classical metric-sector field equation is no longer only an
$R{+}R^2$ readout: the fixed-volume entanglement equilibrium (Jacobson; Faulkner et al.), run with TFPT's atoms,
gives the \emph{full} covariant Einstein equation $G_{ab}+\Lambda g_{ab}=\cthree^{-1}T_{ab}$ with \emph{both}
coefficients fixed --- $\cthree^{-1}=8\pi$ (no free dimensionless Newton dial; the thermodynamic origin $2\pi/\eta$
\emph{coincides} with the geometric one $|\Z_2|2\pi\chi$ via $|\mu_4|=|\Z_2|\chi(S^2)=4$, so $\cthree$ is triply
over-determined --- anchor, geometry, thermodynamics, \texttt{v358}) and $\Lambda$ from $\alpha$ ($\rho_\Lambda
=(3/4\pi^2)e^{-2\alpha^{-1}}$, \texttt{v60}); the Einstein tensor (not Ricci) is forced by Lovelock, so matter
conservation is an output (\texttt{v359}). The residual here is only the equation-of-state status and the one unit
$v_{\mathrm{geo}}$; the global measure (C7 $=$ \texttt{QG.AMB.01}) is now a \mC\ redundancy (\texttt{v369}), a
certification object rather than missing dynamics, conditional on \texttt{SEAM.EQUIV.01} and Bisognano--Wichmann.
\smallskip\\
\noindent The seam-net structural theorem $G_{\mathrm{net}}$ ($=$ \texttt{SEAM.EQUIV.01}: the raw seam \emph{is} the
holomorphic $(E_8)_1$ net) is now \emph{closed modulo a cited theorem}. The explicit lattice model (\texttt{v367}/%
\texttt{v368}) and the $S_3$ closure stack pin the target at every computable level --- central charge $c=8$
(\texttt{v376}), the $(E_8)_1$ character with $248$ currents and one primary (\texttt{v377}), genus-one torus
$\mathrm{GSD}=1$ (\texttt{v378}) and reflection positivity (\texttt{v379}) --- and it is Lean-formalised as
\texttt{FORM.SEAM.MMST.01}: the collar's MMST hypotheses are kernel-proved, the MMST scaling-limit and
Adamo--Moriwaki--Tanimoto OS-reconstruction theorems enter as named cited axioms, and the \texttt{\#print axioms}
check is clean. The \emph{only} residual that stays \mO\ is the abstract continuum existence of the scaling limit, i.e.\
exactly those two cited published theorems (\texttt{v336}); so this is \emph{closed modulo a cited theorem}, not
solved. \texttt{QGEO.SYM.01} (the $\mu_4$ deck acting geometrically) is its \emph{corollary}: a conformal net's vacuum
is rotation-invariant by axiom, so the deck follows with no extra premise (\texttt{v335}, Lean
\texttt{FORM.QGEO.BW.01}). The nonperturbative quantum-gravity measure \texttt{QG.AMB.01} is no longer carried as an
open item: it is a \mC\ \emph{redundancy} (\texttt{v369}), a certification object rather than missing dynamics,
conditional on \texttt{SEAM.EQUIV.01} and Bisognano--Wichmann (and TFPT is moreover rigorously gap-decoupled from the
general Euclidean-QG conformal-factor problem, margin $1.648>0$, \texttt{v76}/\texttt{v330}). So the honest residual is
the one unit $v_{\mathrm{geo}}$ plus the typed $F_{\mathrm{transfer}}$ interfaces, above the cited-theorem ceiling on
the seam and with \texttt{QG.AMB.01} a \mC\ redundancy.
\noindent Everything carries a claim ID resolving to a row of \texttt{verification/status\_ledger.csv}
(the single source of truth); \textbf{if the text and the ledger ever disagree, the ledger wins.} The
historical labels $(U_{\mathrm{wall}},G_{\mathrm{metric}},F_{\mathrm{frontier}})$ are retained only for
ledger continuity --- the live residual is $v_{\mathrm{geo}}\oplus F_{\mathrm{transfer}}$, with the seam
$G_{\mathrm{net}}$ closed modulo a cited theorem and \texttt{QG.AMB.01} a \mC\ redundancy.
\markerkey
\end{keyboxnb}
