% ---------------------------------------------------------------------
%  tfpt_references.tex -- shared "external works built upon" appendix.
%  Single source (tex-artefacts/), \input near the end of the math-heavy
%  documents.  Plain LaTeX only (no document-specific macros), so it
%  compiles unchanged in every paper that imports it.
%  Every entry below was web-verified (journal, volume, year / arXiv id).
%  TFPT's discrete core is self-contained and machine-checked; the entries
%  here are the established mathematics its continuum/AQFT and gravity
%  BRIDGES build on, collected for the reader (the active papers refer to
%  these results by author name in the text).
% ---------------------------------------------------------------------
\section*{External works built upon}
\small
\noindent
The TFPT discrete core (the two axioms, the $E_8$ glue, the integer skeleton) is
self-contained and machine-checked. Its \emph{bridges} to continuum/AQFT physics, to
gravity and to the lattice/singularity picture build on established mathematics, listed
here by topic; the body refers to these by author name.

\paragraph{Modular theory and algebraic quantum field theory.}
\begin{itemize}\setlength\itemsep{1.5pt}
\item M.~Takesaki, \textit{Tomita's Theory of Modular Hilbert Algebras and its
  Applications}, Lecture Notes in Math.\ \textbf{128}, Springer (1970).
\item J.~J.~Bisognano, E.~H.~Wichmann, \textit{On the duality condition for a Hermitian
  scalar field} / \textit{for quantum fields}, J.~Math.\ Phys.\ \textbf{16} (1975)
  985--1007; \textbf{17} (1976) 303--321.
\item K.~Osterwalder, R.~Schrader, \textit{Axioms for Euclidean Green's functions} I, II,
  Comm.\ Math.\ Phys.\ \textbf{31} (1973) 83--112; \textbf{42} (1975) 281--305.
\item S.~Doplicher, R.~Haag, J.~E.~Roberts, \textit{Local observables and particle
  statistics} I, II, Comm.\ Math.\ Phys.\ \textbf{23} (1971) 199--230; \textbf{35} (1974)
  49--85.
\item R.~Haag, \textit{Quantum field theories with composite particles and asymptotic
  conditions}, Phys.\ Rev.\ \textbf{112} (1958) 669--673; D.~Ruelle, \textit{On the
  asymptotic condition in quantum field theory}, Helv.\ Phys.\ Acta \textbf{35} (1962)
  147--163.
\item R.~Longo, \textit{Index of subfactors and statistics of quantum fields} I, II, Comm.\
  Math.\ Phys.\ \textbf{126} (1989) 217--247; \textbf{130} (1990) 285--309.
\item Y.~Kawahigashi, R.~Longo, M.~M\"uger, \textit{Multi-interval subfactors and modularity
  of representations in conformal field theory}, Comm.\ Math.\ Phys.\ \textbf{219} (2001)
  631--669.
\end{itemize}

\paragraph{Conformal nets, vertex operator algebras and lattice constructions.}
\begin{itemize}\setlength\itemsep{1.5pt}
\item I.~B.~Frenkel, V.~G.~Kac, \textit{Basic representations of affine Lie algebras and
  dual resonance models}, Invent.\ Math.\ \textbf{62} (1980) 23--66; G.~Segal,
  \textit{Unitary representations of some infinite-dimensional groups}, Comm.\ Math.\ Phys.\
  \textbf{80} (1981) 301--342.
\item T.~J.~Osborne, A.~Stottmeister, \textit{Conformal field theory from lattice
  fermions}, Comm.\ Math.\ Phys.\ \textbf{398} (2023) 219--289,
  \texttt{arXiv:2107.13834}, \texttt{doi:10.1007/s00220-022-04521-8}.  (This is the
  seam scaling-limit theorem the TFPT continuum leg cites --- the Koo--Saleur $\to$
  Virasoro convergence, $c=\tfrac12$, and the smeared WZW-current Theorem~5.1.  The
  internal TFPT code-token ``MMST'' and the legacy claim-ids \texttt{SEAM.MMST.*} /
  filenames \texttt{v*\_mmst\_*} denote \emph{this} Osborne--Stottmeister theorem.)
\item V.~Morinelli, G.~Morsella, A.~Stottmeister, Y.~Tanimoto, \textit{Scaling limits
  of lattice quantum fields by wavelets}, Comm.\ Math.\ Phys.\ \textbf{387} (2021)
  299--360, \texttt{arXiv:2010.11121}, \texttt{doi:10.1007/s00220-021-04152-5}; and
  \textit{Operator-algebraic renormalization and wavelets}, Phys.\ Rev.\ Lett.\
  \textbf{127} (2021) 230601.  (The operator-algebraic (wavelet/Wilson--Kadanoff)
  renormalization \emph{framework} the Osborne--Stottmeister theorem above builds on.)
\item M.~S.~Adamo, Y.~Moriwaki, Y.~Tanimoto, \textit{Osterwalder--Schrader axioms for
  unitary full vertex operator algebras}, \texttt{arXiv:2407.18222} (2024).
\item M.~S.~Adamo, L.~Giorgetti, Y.~Tanimoto, \textit{Rational and non-rational
  two-dimensional conformal field theories arising from lattices}, \texttt{arXiv:2506.01008}
  (2025); \textit{Representations of conformal nets associated with infinite-dimensional
  groups}, \texttt{arXiv:2508.07109} (2025).
\item P.~Naaijkens, D.~Penneys, B.~Wallick, \textit{(commuting-projector reflection
  positivity / LTO-RP)}, \texttt{arXiv:2605.10693}.
\end{itemize}

\paragraph{Lattices and quadratic forms.}
\begin{itemize}\setlength\itemsep{1.5pt}
\item J.~H.~Conway, N.~J.~A.~Sloane, \textit{Sphere Packings, Lattices and Groups}, 3rd ed.,
  Grundlehren der math.\ Wiss.\ \textbf{290}, Springer (1999).
\item C.~L.~Siegel, \textit{\"Uber die analytische Theorie der quadratischen Formen}
  (the Minkowski--Siegel mass formula), Ann.\ of Math.\ \textbf{36} (1935) 527--606.
\end{itemize}

\paragraph{Singularities and geometry.}
\begin{itemize}\setlength\itemsep{1.5pt}
\item E.~Brieskorn, \textit{Beispiele zur Differentialtopologie von Singularit\"aten},
  Invent.\ Math.\ \textbf{2} (1966) 1--14.
\item J.~Milnor, \textit{Singular Points of Complex Hypersurfaces}, Ann.\ of Math.\ Studies
  \textbf{61}, Princeton Univ.\ Press (1968).
\end{itemize}

\paragraph{Spectral geometry, gravity and thermal time.}
\begin{itemize}\setlength\itemsep{1.5pt}
\item A.~H.~Chamseddine, A.~Connes, \textit{The spectral action principle}, Comm.\ Math.\
  Phys.\ \textbf{186} (1997) 731--750.
\item A.~Connes, C.~Rovelli, \textit{Von Neumann algebra automorphisms and
  time--thermodynamics relation in general covariant quantum theories}, Class.\ Quantum
  Grav.\ \textbf{11} (1994) 2899--2918.
\item R.~M.~Wald, \textit{Black hole entropy is the Noether charge}, Phys.\ Rev.\ D
  \textbf{48} (1993) R3427--R3431.
\item H.~Casini, M.~Huerta, R.~C.~Myers, \textit{Towards a derivation of holographic
  entanglement entropy}, JHEP \textbf{05} (2011) 036, \texttt{arXiv:1102.0440}.
\end{itemize}
\normalsize
